### 2018-04-26 Main.Rmd
First commit

List of libraries
```{r}
  library(purrr)
  library(readr)
  library(ggplot2)
  library(langcog)
  library(boot)
  library(dplyr)
  library(tidyr)
  library(wordbankr)
  library(directlabels)
  library(stringr)
  library(lmtest)
  library(rwebppl)
  library(jsonlite)
  library(nlme)
  library(feather)
  library(broom)
  library(HDInterval)
  library(BBmisc)
  library(igraph)
```

Import helper functions

```{r}
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
```

Create pairs

```{r}
#Import data form wordbank in a format that will be useful for us (especially when we will do development in time).

#The format: for each age (in months, it starts with 16, 17,..) list all words that have NOT yet been acquired  (acquisition is defined by the criterion that 50% of the children can produce the word). The "defintion" is the word, the "unilemma"" is the translation in English (but since we are using only English at this point, both are the same). "learned" is 1 when the word is acquired at that month, and 0 when the word is not aquired at that month. Thus, words with learned=1 at month n, will disapear from month n+1

wb_data <- make_aoa_dataframe(lang="English (American)", lang_form = "WS", lex_class = "nouns")

#extract the first age (it is 16 month in English)
first_age<- wb_data$age[1]

#Extract the list of all uni_lemmas (like Hills, we will start with the analysis of all words first)
lemma_list<- wb_data %>%
  trim_all_unilemma() %>% #We do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication
  filter(age==first_age) %>% #Since the fisrt month in our format is the month when all words are stil present 
  select(item, uni_lemma)

    # list of definitions (we don't need them at this point)
    def_list<- wb_data %>%
      trim_all_definition() %>% 
      filter(age==first_age) %>%
      select(item, definition)

#Make list of pairs for associative data
#The output: all pairs of words (first is named "item"" and seoncd is named "pair"), link =0 (no link), =1 (there is a link)
assoc_pairs<- make_assoc_pairs(lemma_list = lemma_list)

#Make list of pairs for MacRae features
#The output: same as above, but here instead of link, we have "shared" which specify the number of shared links 
feature_pairs <- make_feature_pairs(lemma_list = lemma_list)
```

```
```

Some useful functions

```{r}

#Extract the words
get_lang_item_data <- function(lang, lang_form = "WS", lex_class = "nouns") {

  item_data <- get_item_data(language = lang, form = lang_form) %>%
    select(num_item_id, definition, type, lexical_class, uni_lemma) %>%
    filter(type == "word", lexical_class == lex_class) %>%
    rename(item = num_item_id)

  #Initialize every item as NA (NOT yet learnt)
  lang_item <- item_data %>%
    select(item, definition, uni_lemma) %>%
    mutate(age = NA)

  return(lang_item)
}

##Extract the children' id (named data_id)  and their age
get_lang_admin_data <- function(lang, lang_form = "WS") {
  #get the kids' data_id from every age
  admin_data <- get_administration_data() %>%
    filter(form == lang_form, !is.na(production), language == lang) %>%
    select(data_id, age) %>%
    arrange(age)

  return(admin_data)
}

##get the children's id and the along with word's id (here called item) and whether the child produces that word (value)
##note that here we only select children who do produce the words
get_lang_instr_data <- function(lang, lang_form = "WS") {
  instr_data <- get_instrument_data(instrument_language = lang,
                                    instrument_form = lang_form) %>%
    filter(value == "produces") %>%
    arrange(num_item_id) %>%
    rename(item = num_item_id)

  return(instr_data)
}

# Number of kids in every age
get_kids_by_age <- function(admin_data) {
  #get number of kids by age
  nkids_by_age <- admin_data %>%
    group_by(age) %>%
    summarise(n = n())
  return(nkids_by_age)
}

## This fucntion takes output from all previous function and ??,
get_lang_aoa <- function(item_data, admin_data, instr_data) {
  nkids_by_age <- get_kids_by_age(admin_data)
  ages<- nkids_by_age$age

  #Calculate the age of acqusition for each word (defined as the month when at least 50% of the kids produce it)
  for (cur_age in ages) {
    rem_item <- item_data %>% filter(is.na(age))
    current_age_id <- admin_data %>% filter(age == cur_age)
    current_instr <- instr_data %>% 
      filter(data_id %in% current_age_id$data_id)
    for (w in rem_item$item) {
      proportion <- sum(current_instr$item == w) / nkids_by_age$n[which(ages==cur_age)]
      if (proportion >= 0.5) {
        item_data$age[which(item_data$item == w)] = cur_age
      }
    }
  }
  word_aoa<- item_data %>% filter(!is.na(age))
  return(word_aoa)
}

#check how many words are learnt each age
get_nwords_by_age <- function(word_aoa) {
  nwords_by_age <- word_aoa %>%
    arrange(age) %>%
    group_by(age) %>%
    summarise(n = n())

  return(nwords_by_age)
}

######################################################################################################################
#make a final dataframe
make_aoa_dataframe_helper <- function(word_aoa) {
  ages<- get_nwords_by_age(word_aoa)$age
  df <- data.frame()
  for (i in ages) {
    rem_words <- word_aoa %>% filter(age >= i)
    rem_lemma <- c(rem_words$uni_lemma)
    rem_def <- c(rem_words$definition)
    rem_item<- c(rem_words$item)
    corr_age <- rep(i, times = length(rem_lemma))
    curr_df <- data.frame(corr_age, rem_item, rem_lemma, rem_def)
    df <- rbind(df, curr_df)
  }  
  df <- df %>% rename(uni_lemma = rem_lemma, definition=rem_def, item=rem_item)%>%
    left_join(word_aoa %>% select(item, age)) %>%
    mutate(learned = as.numeric(age == corr_age)) %>%
    select(corr_age, item, definition, uni_lemma,learned) %>%
    rename(age = corr_age) %>%
    arrange(age, item)
  return(df)
}

item_data <- get_lang_item_data(lang = 'English (American)')

admin_data <- get_lang_admin_data(lang = 'English (American)')

instr_data <- get_lang_instr_data(lang = 'English (American)')

nkids_by_age <- get_kids_by_age(admin_data)

word_aoa <- get_lang_aoa(item_data = item_data,
                 admin_data = admin_data,
                 instr_data = instr_data)

#We might not need this right now since we start with all words (but we might need this if we decide to do lexical growth)
final <- make_aoa_dataframe_helper(word_aoa)

```
```{r}
trim_all_unilemma<-function(unilemma_list){
  unilemma_list<- unilemma_list %>%
    mutate(uni_lemma=gsub(" \\s*\\([^\\)]+\\)","", uni_lemma)) %>%
    mutate(uni_lemma=gsub("[*].*$","", uni_lemma)) %>%
    filter(!is.na(uni_lemma))
  return(unilemma_list)
}

######################################################################################################################
trim_all_definition<-function(def_list){
  def_list<- def_list %>%
    mutate(definition= gsub(" \\s*\\([^\\)]+\\)","", definition)) %>%
    mutate(definition= gsub("[*].*$","", definition)) %>%
    mutate(definition= gsub("\\/.*", "", definition)) %>%
    filter(definition!= "babysitter's name", 
           definition!= "child's own name", 
           definition!= "pet's name") %>%
    mutate(definition= gsub("[[:punct:]]", "", definition))

  return(def_list)
}
```

```{r}
#list of lemmas of learnt words
first_age<- final$age[1]

    lemma_list<- final %>%
      trim_all_unilemma() %>%
      filter(age==first_age) %>%
      select(item, uni_lemma)

    # list of definitions of learnt words
    def_list<- final %>%
      trim_all_definition() %>% 
      filter(age==first_age) %>%
      select(item, definition)
```

Associative parirs

```{r}
make_assoc_pairs <- function(lemma_list) {

  cue_target<- read.csv("data/association_cue_target.csv", as.is = T)
  # filter until words in lemma_list remain
  lemma_list<- lemma_list %>% filter((uni_lemma %in% cue_target$cue) | (uni_lemma %in% cue_target$target))
  lemma<- lemma_list$uni_lemma
  cue_target<- cue_target %>% 
    filter(cue %in% lemma, 
           target %in% lemma, 
           normed=="YES") %>% 
    select(cue, target) %>% 
    mutate(link=1)

  assoc_table<- expand.grid(cue= lemma, target= lemma) %>% 
    left_join(cue_target) %>% 
    mutate(link=if_else(is.na(link),0,link))

  #make a association network dataframe with item number
  #rename stuffs so it could conform to the format  needs
  #item corresponds to target ;  pair corresponds to cue
  assoc_link <- assoc_table %>%
    rename(pair.definition = cue) %>%
    left_join(lemma_list, c("pair.definition" = "uni_lemma")) %>%
    rename(pair = item, item.definition = target) %>%
    left_join(lemma_list, c("item.definition" = "uni_lemma")) %>%
    select(item, item.definition, pair, pair.definition, link) %>%
    arrange(item, pair) %>%
    filter(item!=pair)

  return(assoc_link)
}

```

MacRae features

```{r}

make_McRae_pairs <- function(lemma_list) {
  #Get the McRae features
  features <-
    hi <- read_delim("data/MacRae.csv", delim = ",") %>%
    select(Concept, Feature, WB_Label, BR_Label) %>%
    rename(uni_lemma=Concept)
  #Intersection of Wordbank with McRae concepts
  #(Note that we work with unilemmas and not with definitions becuase we would like to use cross-linguistic data)

  #List of word types in WordBank
  wb <- lemma_list
  # List of wordbank with feature

  #Here I still should deal with words in parenthesis (homophony/polysemy), e.g., chiken (animal) vs. chiken (food), etc...

  item_feat <- wb %>%
    left_join(features) %>%
    rename(item.definition = uni_lemma,
           item_feat = Feature) %>%
    filter(!is.na(item_feat)) %>%
    select(item, item.definition, item_feat)

  item_feat_list <- (wb %>%
                       filter(item %in% item_feat$item) %>%
                       select(item))$item

  # List these words pair-wise and compate the number of shared feature for each pair
  item_pair <- expand.grid(item = item_feat_list,
                           pair = item_feat_list)

  pair_feat <- item_feat %>%
    rename(pair = item,
           pair_feat = item_feat,
           pair.definition = item.definition)

  item_feat_pair <- left_join(item_feat, item_pair)

  item_pair_feat <- item_feat_pair %>%
    left_join(pair_feat)

  item_pair_shared <- item_pair_feat %>%
    group_by(item, item.definition, pair, pair.definition) %>%
    summarise(shared = sum(pair_feat == item_feat)) %>%
    filter(item!=pair)

  return(item_pair_shared)
}
```

```{r}
assoc_pairs<- make_assoc_pairs(lemma_list = lemma_list)
feature_pairs <- make_McRae_pairs(lemma_list = lemma_list)
```

### 2018-04-26 helpers/all_helper.r

@@ -1,0 +1,3 @@
+source("wb_helper.r")
+source("make_assoc_pairs.r")
+source("make_feature_pairs.r")

### 2018-04-26 helpers/make_assoc_pairs.r

@@ -1,0 +1,31 @@
+make_assoc_pairs <- function(lemma_list) {
+  
+  cue_target<- read.csv("data/association_cue_target.csv", as.is = T)
+  # filter until words in lemma_list remain
+  lemma_list<- lemma_list %>% filter((uni_lemma %in% cue_target$cue) | (uni_lemma %in% cue_target$target))
+  lemma<- lemma_list$uni_lemma
+  cue_target<- cue_target %>% 
+    filter(cue %in% lemma, 
+           target %in% lemma, 
+           normed=="YES") %>% 
+    select(cue, target) %>% 
+    mutate(link=1)
+  
+  assoc_table<- expand.grid(cue= lemma, target= lemma) %>% 
+    left_join(cue_target) %>% 
+    mutate(link=if_else(is.na(link),0,link))
+  
+  #make a association network dataframe with item number
+  #rename stuffs so it could conform to the format  needs
+  #item corresponds to target ;  pair corresponds to cue
+  assoc_link <- assoc_table %>%
+    rename(pair.definition = cue) %>%
+    left_join(lemma_list, c("pair.definition" = "uni_lemma")) %>%
+    rename(pair = item, item.definition = target) %>%
+    left_join(lemma_list, c("item.definition" = "uni_lemma")) %>%
+    select(item, item.definition, pair, pair.definition, link) %>%
+    arrange(item, pair) %>%
+    filter(item!=pair)
+  
+  return(assoc_link)
+}

### 2018-04-26 helpers/make_feature_pairs.r

@@ -1,0 +1,49 @@
+make_feature_pairs <- function(lemma_list) {
+  #Get the McRae features
+  features <-
+    hi <- read_delim("data/MacRae.csv", delim = ",") %>%
+    select(Concept, Feature, WB_Label, BR_Label) %>%
+    filter(BR_Label=="visual-form_and_surface") %>% #Here it depends what kind of features we would like to keep (perceptual? conceptual? both?)
+    rename(uni_lemma=Concept)
+  #Intersection of Wordbank with McRae concepts
+  #(Note that we work with unilemmas and not with definitions becuase we would like to use cross-linguistic data)
+  
+  #List of word types in WordBank
+  wb <- lemma_list
+  # List of wordbank with feature
+  
+  #Here I still should deal with words in parenthesis (homophony/polysemy), e.g., chiken (animal) vs. chiken (food), etc...
+  
+  item_feat <- wb %>%
+    left_join(features) %>%
+    rename(item.definition = uni_lemma,
+           item_feat = Feature) %>%
+    filter(!is.na(item_feat)) %>%
+    select(item, item.definition, item_feat)
+  
+  
+  item_feat_list <- (wb %>%
+                       filter(item %in% item_feat$item) %>%
+                       select(item))$item
+  
+  # List these words pair-wise and compate the number of shared feature for each pair
+  item_pair <- expand.grid(item = item_feat_list,
+                           pair = item_feat_list)
+  
+  pair_feat <- item_feat %>%
+    rename(pair = item,
+           pair_feat = item_feat,
+           pair.definition = item.definition)
+  
+  item_feat_pair <- left_join(item_feat, item_pair)
+  
+  item_pair_feat <- item_feat_pair %>%
+    left_join(pair_feat)
+  
+  item_pair_shared <- item_pair_feat %>%
+    group_by(item, item.definition, pair, pair.definition) %>%
+    summarise(shared = sum(pair_feat == item_feat)) %>%
+    filter(item!=pair)
+  
+  return(item_pair_shared)
+}

### 2018-04-26 helpers/wb_helper.r

@@ -1,0 +1,189 @@
+# This file contains functions used to get item data, admin data, etc. , and generate dataframes for analysis
+import_all_library<- function(){
+  library(tidyr)
+  library(purrr)
+  library(readr)
+  library(ggplot2)
+  library(langcog)
+  library(boot)
+  library(lazyeval)
+  library(dplyr)
+  library(wordbankr)
+  library(directlabels)
+  library(scales)
+  library(stringr)
+  library(lmtest)
+}
+######################################################################################################################
+get_lang_item_data <- function(lang, lang_form = "WS", lex_class = "nouns") {
+
+  item_data <- get_item_data(language = lang, form = lang_form) %>%
+    select(num_item_id, definition, type, lexical_class, uni_lemma) %>%
+    filter(type == "word", lexical_class == lex_class) %>%
+    rename(item = num_item_id)
+  
+  #Initialize every item as NA (NOT yet learnt)
+  lang_item <- item_data %>%
+    select(item, definition, uni_lemma) %>%
+    mutate(age = NA)
+  
+  return(lang_item)
+}
+
+######################################################################################################################
+# get only "useful" admin data (where production is not NA)
+get_lang_admin_data <- function(lang, lang_form = "WS") {
+  #get the kids' data_id from every age
+  admin_data <- get_administration_data() %>%
+    filter(form == lang_form, !is.na(production), language == lang) %>%
+    select(data_id, age) %>%
+    arrange(age)
+  
+  return(admin_data)
+}
+
+######################################################################################################################
+# See how many kids we have in every age
+get_kids_by_age <- function(admin_data) {
+  #get number of kids by age
+  nkids_by_age <- admin_data %>%
+    group_by(age) %>%
+    summarise(n = n())
+  return(nkids_by_age)
+}
+
+######################################################################################################################
+#get "produces" instrument data 
+get_lang_instr_data <- function(lang, lang_form = "WS") {
+  instr_data <- get_instrument_data(instrument_language = lang,
+                                    instrument_form = lang_form) %>%
+    filter(value == "produces") %>%
+    arrange(num_item_id) %>%
+    rename(item = num_item_id)
+  
+  return(instr_data)
+}
+
[…]

### 2018-04-26 Main.Rmd
minor

@@
 ```
-
-```
-```
-
-Some useful functions
-
-```{r}
-
-#Extract the words
-get_lang_item_data <- function(lang, lang_form = "WS", lex_class = "nouns") {
-
-  item_data <- get_item_data(language = lang, form = lang_form) %>%
-    select(num_item_id, definition, type, lexical_class, uni_lemma) %>%
-    filter(type == "word", lexical_class == lex_class) %>%
-    rename(item = num_item_id)
-
-  #Initialize every item as NA (NOT yet learnt)
-  lang_item <- item_data %>%
-    select(item, definition, uni_lemma) %>%
-    mutate(age = NA)
-
-  return(lang_item)
-}
-
-##Extract the children' id (named data_id)  and their age
-get_lang_admin_data <- function(lang, lang_form = "WS") {
-  #get the kids' data_id from every age
-  admin_data <- get_administration_data() %>%
-    filter(form == lang_form, !is.na(production), language == lang) %>%
-    select(data_id, age) %>%
-    arrange(age)
-
-  return(admin_data)
-}
-
-##get the children's id and the along with word's id (here called item) and whether the child produces that word (value)
-##note that here we only select children who do produce the words
-get_lang_instr_data <- function(lang, lang_form = "WS") {
-  instr_data <- get_instrument_data(instrument_language = lang,
-                                    instrument_form = lang_form) %>%
-    filter(value == "produces") %>%
-    arrange(num_item_id) %>%
-    rename(item = num_item_id)
-
-  return(instr_data)
-}
-
-# Number of kids in every age
-get_kids_by_age <- function(admin_data) {
-  #get number of kids by age
-  nkids_by_age <- admin_data %>%
-    group_by(age) %>%
-    summarise(n = n())
-  return(nkids_by_age)
-}
-
-## This fucntion takes output from all previous function and ??,
-get_lang_aoa <- function(item_data, admin_data, instr_data) {
-  nkids_by_age <- get_kids_by_age(admin_data)
-  ages<- nkids_by_age$age
-
-  #Calculate the age of acqusition for each word (defined as the month when at least 50% of the kids produce it)
-  for (cur_age in ages) {
-    rem_item <- item_data %>% filter(is.na(age))
-    current_age_id <- admin_data %>% filter(age == cur_age)
-    current_instr <- instr_data %>% 
-      filter(data_id %in% current_age_id$data_id)
-    for (w in rem_item$item) {
-      proportion <- sum(current_instr$item == w) / nkids_by_age$n[which(ages==cur_age)]
-      if (proportion >= 0.5) {
-        item_data$age[which(item_data$item == w)] = cur_age
-      }
-    }
-  }
-  word_aoa<- item_data %>% filter(!is.na(age))
-  return(word_aoa)
-}
-
-#check how many words are learnt each age
-get_nwords_by_age <- function(word_aoa) {
-  nwords_by_age <- word_aoa %>%
-    arrange(age) %>%
-    group_by(age) %>%
-    summarise(n = n())
-
-  return(nwords_by_age)
-}
-
-######################################################################################################################
-#make a final dataframe
-make_aoa_dataframe_helper <- function(word_aoa) {
-  ages<- get_nwords_by_age(word_aoa)$age
-  df <- data.frame()
-  for (i in ages) {
-    rem_words <- word_aoa %>% filter(age >= i)
-    rem_lemma <- c(rem_words$uni_lemma)
-    rem_def <- c(rem_words$definition)
-    rem_item<- c(rem_words$item)
-    corr_age <- rep(i, times = length(rem_lemma))
-    curr_df <- data.frame(corr_age, rem_item, rem_lemma, rem_def)
-    df <- rbind(df, curr_df)
-  }  
-  df <- df %>% rename(uni_lemma = rem_lemma, definition=rem_def, item=rem_item)%>%
-    left_join(word_aoa %>% select(item, age)) %>%
-    mutate(learned = as.numeric(age == corr_age)) %>%
-    select(corr_age, item, definition, uni_lemma,learned) %>%
-    rename(age = corr_age) %>%
-    arrange(age, item)
-  return(df)
-}
-
-item_data <- get_lang_item_data(lang = 'English (American)')
-
-admin_data <- get_lang_admin_data(lang = 'English (American)')
-
-instr_data <- get_lang_instr_data(lang = 'English (American)')
-
-nkids_by_age <- get_kids_by_age(admin_data)
-
-word_aoa <- get_lang_aoa(item_data = item_data,
-                 admin_data = admin_data,
-                 instr_data = instr_data)
-
-#We might not need this right now since we start with all words (but we might need this if we decide to do lexical growth)
-final <- make_aoa_dataframe_helper(word_aoa)
-
-```
-```{r}
-trim_all_unilemma<-function(unilemma_list){
-  unilemma_list<- unilemma_list %>%
-    mutate(uni_lemma=gsub(" \\s*\\([^\\)]+\\)","", uni_lemma)) %>%
-    mutate(uni_lemma=gsub("[*].*$","", uni_lemma)) %>%
-    filter(!is.na(uni_lemma))
-  return(unilemma_list)
-}
-
-######################################################################################################################
-trim_all_definition<-function(def_list){
-  def_list<- def_list %>%
-    mutate(definition= gsub(" \\s*\\([^\\)]+\\)","", definition)) %>%
-    mutate(definition= gsub("[*].*$","", definition)) %>%
-    mutate(definition= gsub("\\/.*", "", definition)) %>%
-    filter(definition!= "babysitter's name", 
-           definition!= "child's own name", 
-           definition!= "pet's name") %>%
-    mutate(definition= gsub("[[:punct:]]", "", definition))
-
-  return(def_list)
-}
-```
-
-```{r}
-#list of lemmas of learnt words
-first_age<- final$age[1]
-
-    lemma_list<- final %>%
-      trim_all_unilemma() %>%
-      filter(age==first_age) %>%
-      select(item, uni_lemma)
-
-    # list of definitions of learnt words
-    def_list<- final %>%
-      trim_all_definition() %>% 
-      filter(age==first_age) %>%
-      select(item, definition)
-```
-
-Associative parirs
-
-```{r}
-make_assoc_pairs <- function(lemma_list) {
-
-  cue_target<- read.csv("data/association_cue_target.csv", as.is = T)
-  # filter until words in lemma_list remain
-  lemma_list<- lemma_list %>% filter((uni_lemma %in% cue_target$cue) | (uni_lemma %in% cue_target$target))
-  lemma<- lemma_list$uni_lemma
-  cue_target<- cue_target %>% 
-    filter(cue %in% lemma, 
-           target %in% lemma, 
-           normed=="YES") %>% 
-    select(cue, target) %>% 
-    mutate(link=1)
-
-  assoc_table<- expand.grid(cue= lemma, target= lemma) %>% 
-    left_join(cue_target) %>% 
-    mutate(link=if_else(is.na(link),0,link))
-
-  #make a association network dataframe with item number
-  #rename stuffs so it could conform to the format  needs
-  #item corresponds to target ;  pair corresponds to cue
-  assoc_link <- assoc_table %>%
-    rename(pair.definition = cue) %>%
-    left_join(lemma_list, c("pair.definition" = "uni_lemma")) %>%
-    rename(pair = item, item.definition = target) %>%
-    left_join(lemma_list, c("item.definition" = "uni_lemma")) %>%
-    select(item, item.definition, pair, pair.definition, link) %>%
-    arrange(item, pair) %>%
-    filter(item!=pair)
-
-  return(assoc_link)
-}
-
-```
-
-MacRae features
-
-```{r}
-
-make_McRae_pairs <- function(lemma_list) {
-  #Get the McRae features
-  features <-
-    hi <- read_delim("data/MacRae.csv", delim = ",") %>%
-    select(Concept, Feature, WB_Label, BR_Label) %>%
-    rename(uni_lemma=Concept)
-  #Intersection of Wordbank with McRae concepts
-  #(Note that we work with unilemmas and not with definitions becuase we would like to use cross-linguistic data)
-
-  #List of word types in WordBank
-  wb <- lemma_list
-  # List of wordbank with feature
-
-  #Here I still should deal with words in parenthesis (homophony/polysemy), e.g., chiken (animal) vs. chiken (food), etc...
-
-  item_feat <- wb %>%
-    left_join(features) %>%
-    rename(item.definition = uni_lemma,
-           item_feat = Feature) %>%
-    filter(!is.na(item_feat)) %>%
-    select(item, item.definition, item_feat)
-
-  item_feat_list <- (wb %>%
-                       filter(item %in% item_feat$item) %>%
-                       select(item))$item
-
-  # List these words pair-wise and compate the number of shared feature for each pair
-  item_pair <- expand.grid(item = item_feat_list,
-                           pair = item_feat_list)
-
-  pair_feat <- item_feat %>%
-    rename(pair = item,
-           pair_feat = item_feat,
-           pair.definition = item.definition)
-
-  item_feat_pair <- left_join(item_feat, item_pair)
-
-  item_pair_feat <- item_feat_pair %>%
-    left_join(pair_feat)
-
-  item_pair_shared <- item_pair_feat %>%
-    group_by(item, item.definition, pair, pair.definition) %>%
-    summarise(shared = sum(pair_feat == item_feat)) %>%
-    filter(item!=pair)
-
-  return(item_pair_shared)
-}
-```
-
-```{r}
-assoc_pairs<- make_assoc_pairs(lemma_list = lemma_list)
-feature_pairs <- make_McRae_pairs(lemma_list = lemma_list)
-```

### 2018-05-07 Main.Rmd
Fixed bug in argument name to helper function.

@@
 ```{r}
-#Import data form wordbank in a format that will be useful for us (especially when we will do development in time).
+#Import data from wordbank in a format that will be useful for us (especially when we will do development in time).
 
@@
 but we will have to be careful in our choices if we are preparing later for publication
-  filter(age==first_age) %>% #Since the fisrt month in our format is the month when all words are stil present 
+  filter(age==first_age) %>% #Since the first month in our format is the month when all words are stil present 
   select(item, uni_lemma)

### 2018-05-07 helpers/wb_helper.r

@@ -55,8 +55,8 @@ get_kids_by_age <- function(admin_data) {
 ######################################################################################################################
 #get "produces" instrument data 
 get_lang_instr_data <- function(lang, lang_form = "WS") {
-  instr_data <- get_instrument_data(instrument_language = lang,
-                                    instrument_form = lang_form) %>%
+  instr_data <- get_instrument_data(language = lang,
+                                    form = lang_form) %>%
     filter(value == "produces") %>%
     arrange(num_item_id) %>%
     rename(item = num_item_id)

### 2018-05-10 Main.Rmd
Created basic igraph from assoc_pairs.

@@
 #Make list of pairs for associative data
-#The output: all pairs of words (first is named "item"" and seoncd is named "pair"), link =0 (no link), =1 (there is a link)
-assoc_pairs<- make_assoc_pairs(lemma_list = lemma_list)
+#The output: all pairs of words (first is named "item"" and second is named "pair"), link =0 (no link), =1 (there is a link)
+assoc_pairs <- make_assoc_pairs(lemma_list = lemma_list)
 
@@
 ```
+
+```{r}
+lemma_vertices <- lemma_list %>%
+  rename("name"="item")
+
+assoc_links <- assoc_pairs %>%
+  filter(link==1) %>%
+  select(item, pair, item.definition, pair.definition) %>%
+  rename("from"="item", "to"="pair")
+
+g <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>% simplify()
+print(g, e=TRUE, v=TRUE)
+```

### 2018-05-10 Main.Rmd
Generate basic assoc and feature graphs.

@@
 
+Build graphs
+
 ```{r}
-lemma_vertices <- lemma_list %>%
-  rename("name"="item")
-
 assoc_links <- assoc_pairs %>%
   filter(link==1) %>%
-  select(item, pair, item.definition, pair.definition) %>%
-  rename("from"="item", "to"="pair")
+  select(item, pair, item.definition, pair.definition)
 
-g <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>% simplify()
-print(g, e=TRUE, v=TRUE)
+feature_links <- feature_pairs %>%
+  filter(shared > 0) %>% # arbitrary, what does the # of shared links represent?
+  select(item, pair, item.definition, pair.definition)
+
+assoc_graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>%
+  simplify()
+
+feature_graph <- graph_from_data_frame(feature_links, directed=FALSE, vertices=lemma_list) %>%
+  simplify()
+
+print(assoc_graph, e=TRUE, v=TRUE)
+print(feature_graph, e=TRUE, v=TRUE)
 ```

### 2018-05-24 Main.Rmd

@@
+---
+output:
+  html_document: default
+  pdf_document: default
+---
+# Basic Network Analysis of Wordbank Data
+
+## Build Networks
+
 List of libraries
-```{r}
+```{r echo=TRUE, warning=FALSE, message=FALSE}
 library(purrr)
@@
 library(igraph)
+library(knitr)
+library(lemon)
+library(tibble)
 ```
 
-Import helper functions
+Import helper functions and configure RMarkdown
+```{r echo=TRUE, warning=FALSE, message=FALSE}
+source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
 
-```{r}
-source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
+knit_print.data.frame <- lemon_print # use kable when displaying tibbles in knit
 ```
@@
 Create pairs 
-
-```{r}
+```{r echo=TRUE, warning=FALSE, message=FALSE}
 #Import data from wordbank in a format that will be useful for us (especially when we will do development in time).
@@
 
-Build graphs
-
+Build networks
 ```{r}
@@
 
-assoc_graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>%
-  simplify()
+assoc_network <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>%
+  simplify() %>%
+  set.graph.attribute("name", "Assoc") # maybe rewrite as g$name <- "Name"
 
-feature_graph <- graph_from_data_frame(feature_links, directed=FALSE, vertices=lemma_list) %>%
-  simplify()
+feature_network <- graph_from_data_frame(feature_links, directed=FALSE, vertices=lemma_list) %>%
+  simplify() %>%
+  set.graph.attribute("name", "Feature")
 
-print(assoc_graph, e=TRUE, v=TRUE)
-print(feature_graph, e=TRUE, v=TRUE)
+networks <- list(assoc_network, feature_network)
 ```
+
+## Network Analysis
+
+### Large-Scale Structure of Networks
+
+a la Steyvers 2005
+
+```{r, results='asis'}
+network_properties <- tibble(
+  names = map_chr(networks, ~ .x$name),
+  vertices = map_int(networks, vcount),
+  edges = map_dbl(networks, ecount) %>%
+    as.integer(), # for some reason igraph ecount returns double
+  avg_degree = map(networks, degree) %>%
+    map_dbl(mean),
+  avg_shortest_path = map_dbl(networks, mean_distance),
+  diameter = map_dbl(networks, diameter) %>%
+    as.integer(),
+  clustering_coefficient = map_dbl(networks, transitivity),
+  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
+  diameter_random = 0,
+  clustering_coefficient_random = 0
+)
+
+network_properties # improve formatting
+```
+
+Degree Distribution
+```{r}
+assoc_degree <- tibble(k = 1:length(degree_distribution(assoc_network)),
+                       p = degree_distribution(assoc_network))
+feature_degree <- tibble(k = 1:length(degree_distribution(feature_network)),
+                       p = degree_distribution(feature_network))
+
+ggplot(data = assoc_degree, aes(x = k, y = p)) + geom_line()
+ggplot(data = feature_degree, aes(x = k, y = p)) + geom_line()
+```

### 2018-07-05 Main.Rmd

@@
 ```{r echo=TRUE, warning=FALSE, message=FALSE}
-library(purrr)
-library(readr)
+library(purrr) # fp library
+library(readr) # read text data files (csv, etc.)
 library(ggplot2)
-library(langcog)
-library(boot)
-library(dplyr)
-library(tidyr)
-library(wordbankr)
-library(directlabels)
-library(stringr)
-library(lmtest)
-library(rwebppl)
-library(jsonlite)
-library(nlme)
-library(feather)
-library(broom)
-library(HDInterval)
-library(BBmisc)
-library(igraph)
-library(knitr)
-library(lemon)
-library(tibble)
+library(langcog) # useful things used by Language and Cognition Lab
+library(boot) # functions for bootstrapping
+library(dplyr) # for working with datafram-like objects
+library(tidyr) # for data tidying
+library(wordbankr) # access to wordbank data
+library(directlabels) # direct labeling of data in plots
+library(stringr) # common string operations
+library(lmtest) #  diagnostic checking in linear regression models
+library(rwebppl) # interface to probabilistic programming language WebPPL
+library(jsonlite) # JSON parser
+library(nlme) # gaussian linear and nonlinear mixed-effects models
+library(feather) # read and write fast lightweight binary columnar data
+library(broom) # converts R function outputs to tidy data frames
+library(HDInterval) # calculate highest density intervals of objects w/ pdf
+library(BBmisc) # misc helper functions
+library(igraph) # network analysis and visualization
+library(knitr) # general-purpose tool for dynamic report generation
+library(lemon) # functions for working w/ ggplot2 and knitr extensions
+library(tibble) # modern dataframes
 ```

### 2018-07-06 Main.Rmd
Expanded network analysis, tested clique percolation.

--- 2018-05-10 Main.Rmd
@@
+---
+output:
+  html_document: default
+  pdf_document: default
+---
+# Basic Network Analysis of Wordbank Data
+
+## Build Networks
+
 List of libraries
-```{r}
-  library(purrr)
-  library(readr)
-  library(ggplot2)
-  library(langcog)
-  library(boot)
-  library(dplyr)
-  library(tidyr)
-  library(wordbankr)
-  library(directlabels)
-  library(stringr)
-  library(lmtest)
-  library(rwebppl)
-  library(jsonlite)
-  library(nlme)
-  library(feather)
-  library(broom)
-  library(HDInterval)
-  library(BBmisc)
-  library(igraph)
+```{r echo=TRUE, warning=FALSE, message=FALSE}
+library(purrr) # fp library
+library(readr) # read text data files (csv, etc.)
+library(ggplot2) # plotting
+library(langcog) # useful things used by Language and Cognition Lab
+library(boot) # functions for bootstrapping
+library(dplyr) # for working with datafram-like objects
+library(tidyr) # for data tidying
+library(wordbankr) # access to wordbank data
+library(directlabels) # direct labeling of data in plots
+library(stringr) # common string operations
+library(lmtest) #  diagnostic checking in linear regression models
+library(rwebppl) # interface to probabilistic programming language WebPPL
+library(jsonlite) # JSON parser
+library(nlme) # gaussian linear and nonlinear mixed-effects models
+library(feather) # read and write fast lightweight binary columnar data
+library(broom) # converts R function outputs to tidy data frames
+library(HDInterval) # calculate highest density intervals of objects w/ pdf
+library(BBmisc) # misc helper functions
+library(igraph) # network analysis and visualization
+library(knitr) # general-purpose tool for dynamic report generation
+library(lemon) # functions for working w/ ggplot2 and knitr extensions
+library(tibble) # modern dataframes
+library(doParallel)
 ```
 
-Import helper functions
+Import helper functions and configure RMarkdown
+```{r echo=TRUE, warning=FALSE, message=FALSE}
+source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
 
-```{r}
-source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
+knit_print.data.frame <- lemon_print # use kable when displaying tibbles in knit
 ```
 
-Create pairs
+Create vocab 
+```{r echo=TRUE, warning=FALSE, message=FALSE}
+# Import data from wordbank.
+Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word.
+The "defintion" is the word, the "unilemma"" is the translation in English.
 
-```{r}
-#Import data from wordbank in a format that will be useful for us (especially when we will do development in time).
+# We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,..
+but we will have to be careful in our choices if we are preparing later for publication
 
-#The format: for each age (in months, it starts with 16, 17,..) list all words that have NOT yet been acquired  (acquisition is defined by the criterion that 50% of the children can produce the word).
-The "defintion" is the word, the "unilemma"" is the translation in English (but since we are using only English at this point, both are the same).
-"learned" is 1 when the word is acquired at that month, and 0 when the word is not aquired at that month.
-Thus, words with learned=1 at month n, will disapear from month n+1
-
-wb_data <- make_aoa_dataframe(lang="English (American)", lang_form = "WS", lex_class = "nouns")
-
-#extract the first age (it is 16 month in English)
-first_age<- wb_data$age[1]
-
-#Extract the list of all uni_lemmas (like Hills, we will start with the analysis of all words first)
-lemma_list<- wb_data %>%
-  trim_all_unilemma() %>% #We do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,..
-but we will have to be careful in our choices if we are preparing later for publication
-  filter(age==first_age) %>% #Since the first month in our format is the month when all words are stil present 
-  select(item, uni_lemma)
-
-    # list of definitions (we don't need them at this point)
-    def_list<- wb_data %>%
-      trim_all_definition() %>% 
-      filter(age==first_age) %>%
-      select(item, definition)
-
-#Make list of pairs for associative data
-#The output: all pairs of words (first is named "item"" and second is named "pair"), link =0 (no link), =1 (there is a link)
-assoc_pairs <- make_assoc_pairs(lemma_list = lemma_list)
-
-#Make list of pairs for MacRae features
-#The output: same as above, but here instead of link, we have "shared" which specify the number of shared links 
-feature_pairs <- make_feature_pairs(lemma_list = lemma_list)
+vocab <- make_vocab_dataframe(lang="English (American)",
+                              lang_form = "WS",
+                              lex_class = "nouns") %>%
+  trim_all_unilemma() %>%
+  trim_all_definition() # %>%
+  # distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
 ```
 
-Build graphs
-
+Build networks
 ```{r}
-assoc_links <- assoc_pairs %>%
+assoc_network <- function(vocab, max_age) {
+  vocab_up_to_age = filter(vocab, age <= max_age)
+  assoc_links <- make_assoc_pairs(lemma_list = vocab_up_to_age) %>%
     filter(link==1) %>%
     select(item, pair, item.definition, pair.definition)
+  graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=vocab_up_to_age) %>%
+    simplify() %>%
+    set.graph.attribute("name", "Assoc") %>%
+    set.graph.attribute("age", max_age)
+  return(graph)
+}
 
-feature_links <- feature_pairs %>%
-  filter(shared > 0) %>% # arbitrary, what does the # of shared links represent?
+feature_network <- function(vocab, max_age, shared_threshold) {
+  vocab_up_to_age = filter(vocab, age <= max_age)
+  feature_links <- make_feature_pairs(lemma_list = vocab_up_to_age) %>%
+    filter(shared >= shared_threshold) %>%
     select(item, pair, item.definition, pair.definition)
+  graph <- graph_from_data_frame(feature_links, directed=FALSE, vertices=vocab_up_to_age) %>%
+    simplify() %>%
+    set.graph.attribute("name", "Feature") %>%
+    set.graph.attribute("age", max_age)
+  return(graph)
+}
 
-assoc_graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>%
-  simplify()
+ages <- vocab$age %>% unique() %>% sort()
+assoc_networks <- list()
+feature_networks <- list()
+for (age in ages) {
+  assoc_networks <- append(assoc_networks, list(assoc_network(vocab, age)))
+  feature_networks <- append(feature_networks, list(feature_network(vocab, age, 1)))
 
-feature_graph <- graph_from_data_frame(feature_links, directed=FALSE, vertices=lemma_list) %>%
-  simplify()
+}
+```
 
-print(assoc_graph, e=TRUE, v=TRUE)
-print(feature_graph, e=TRUE, v=TRUE)
+## Network Analysis
+
+### Large-Scale Structure of Networks
+
+a la Steyvers 2005
+
+```{r, results='asis'}
+network_properties <- function(networks) {
+  return( tibble(
+  names = map_chr(networks, ~ .x$name),
+  ages = map_dbl(networks, ~ .x$age) %>%
+    as.integer(),
+  vertices = map_int(networks, vcount),
+  edges = map_dbl(networks, ecount) %>%
+    as.integer(), # for some reason igraph ecount returns double
+  avg_degree = map(networks, degree) %>%
+    map_dbl(mean),
+  avg_shortest_path = map_dbl(networks, mean_distance),
+  diameter = map_dbl(networks, diameter) %>%
+    as.integer(),
+  clustering_coefficient = map_dbl(networks, transitivity),
+  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
+  diameter_random = 0,
+  clustering_coefficient_random = 0) )
+}
+
+network_properties(assoc_networks) # improve formatting
+network_properties(feature_networks)
 ```
+
+Visualize Networks
+```{r}
+plot_network <- function(g, remove_isolated=FALSE) {
+  if (remove_isolated) {
+    g <- delete.vertices(g, degree(g)==0)
+  }
+
+  plot(g, vertex.label=V(g)$uni_lemma, vertex.shape="none")
+}
+
+g <- assoc_networks[[6]]
+plot_network(g, remove_isolated = FALSE)
+
+plot(g,vertex.size=.01,vertex.label.cex=.8,
+     layout=layout.fruchterman.reingold(g, niter=10000, 
+                                        area=40*vcount(g)^2),
+     edge.width=E(g)$weight)
+```
+
+Test Clique Percolation
+```{r}
+### Register Parallelisation (used by clique.community.opt.par())
+cl <- makeCluster(4)
+registerDoParallel(cl)
+getDoParWorkers()
+
+### Loading Benchmarks
+#1 
+g <- graph(c(1,2,1,3,1,4,2,3,3,4,4,5,4,6,5,6,5,8,5,7,6,8,6,7,7,8,7,9), directed=F)
+#2
+g <- make_graph("Zachary") #the karate network
+
+#Execution of the different implementation of the algorithm
+ptm <- proc.time()
+res1<-clique.community(g,3)
+proc.time() - ptm
+ptm <- proc.time()
+res2<-clique.community.opt(g,3)
+proc.time() - ptm
+ptm <- proc.time()
+res3<-clique.community.opt.par(g,3)
+proc.time() - ptm
+
+identical(res1,res2)
+identical(res2,res3)
+
+### PLOT
+
+#which one? the outcome is always the same
+res <- res3
+
+## Paint them to different colors
+colbar <- rainbow( length(res)+1 )
+for (i in seq(along=res)) {
+  V(g)[ res[[i]] ]$color <- colbar[i+1]
+}
+
+## Paint the vertices in multiple communities to red
+V(g)[ unlist(res)[ duplicated(unlist(res)) ] ]$color <- "red"
+
+## Plot with the new colors
+plot(g, layout=layout_with_fr, vertex.label=V(g)$name)
+
+#REAL PERFORMANCE TEST
+require(microbenchmark)
+b1<-microbenchmark(t1<-clique.community(g,3),times = 100,unit = 'ms')
+b2<-microbenchmark(t2<-clique.community.opt(g,3),times = 100,unit = 'ms')
+b3<-microbenchmark(t2<-clique.community.opt.par(g,3),times = 100,unit = 'ms')
+rbind(b1,b2,b3)
+mean(b1$time)/mean(b2$time)
+mean(b2$time)/mean(b3$time)
+mean(b1$time)/mean(b3$time)
+```

### 2018-07-06 helpers/all_helper.r

@@ -1,3 +1,4 @@
 source("wb_helper.r")
 source("make_assoc_pairs.r")
 source("make_feature_pairs.r")
+source("clique_percolation.r")

### 2018-07-06 helpers/clique_percolation.r

@@ -1,0 +1,114 @@
+clique.community <- function(graph, k) {
+  require(igraph)
+  clq <- cliques(graph, min=k, max=k) %>% lapply(as.vector)
+  
+  
+  #find edges
+  edges <- c()
+  for (i in seq_along(clq)) {
+    for (j in seq_along(clq)) {
+      if ( length(unique(c(clq[[i]], clq[[j]]))) == k+1 ) {
+        edges[[length(edges)+1]] <- c(i,j)
+      }
+    }
+  }
+  
+  #Create an empty graph and then adding edges
+  clq.graph <- make_empty_graph(n = length(clq)) %>% add_edges(unlist(edges))
+  clq.graph <- simplify(clq.graph)
+  V(clq.graph)$name <- seq_len(vcount(clq.graph))
+  
+  
+  comps <- decompose.graph(clq.graph)
+  
+  lapply(comps, function(x) {
+    unique(unlist(clq[ V(x)$name ]))
+  })
+}
+
+######################################################################################################################
+
+clique.community.opt <- function(graph, k){
+  require(igraph)
+  
+  ###################################
+  ### STEP #1: Clique discovery
+  ###################################
+  
+  clq <- cliques(graph, min=k, max=k) %>% lapply(as.vector)
+  
+  
+  ###################################
+  ### STEP #2: Clique-graph creation
+  ###################################
+  
+  #find edges between cliques
+  edges <- c()
+  for (i in 1:(length(clq)-1)) {
+    for (j in (i+1):length(clq)) {
+      if ( length(unique(c(clq[[i]], clq[[j]]))) == k+1 ) {
+        edges[[length(edges)+1]] <- c(i,j)
+      }
+    }
+  }
+  
+  #Create an empty graph and then adding edges
+  clq.graph <- make_empty_graph(n = length(clq)) %>% add_edges(unlist(edges))
+  clq.graph <- simplify(clq.graph)
+  V(clq.graph)$name <- seq_len(vcount(clq.graph))
+  
+  
+  comps <- decompose.graph(clq.graph)
+  
+  lapply(comps, function(x) {
+    unique(unlist(clq[ V(x)$name ]))
+  })
+}
+
+######################################################################################################################
+
+clique.community.opt.par <- function(graph, k){
+  require(igraph)
+  if(!require(foreach)){
+    install.packages("foreach")
[…]

### 2018-07-06 helpers/wb_helper.r

@@ -140,6 +140,49 @@ make_aoa_dataframe <- function(lang, lang_form = "WS", lex_class = "nouns") {
 }
 
 ######################################################################################################################
+#make a final dataframe
+make_vocab_dataframe_helper <- function(word_aoa) {
+  ages <- word_aoa$age %>% unique() %>% sort()
+  tb <- tibble()
+  for (i in ages) {
+    new_vocab <- word_aoa %>% filter(age = i)
+    tb <- bind_rows
+    rem_words <- word_aoa %>% filter(age >= i)
+    rem_lemma <- c(rem_words$uni_lemma)
+    rem_def <- c(rem_words$definition)
+    rem_item<- c(rem_words$item)
+    corr_age <- rep(i, times = length(rem_lemma))
+    curr_df <- data.frame(corr_age, rem_item, rem_lemma, rem_def)
+    df <- rbind(df, curr_df)
+  }  
+  df <- df %>% rename(uni_lemma = rem_lemma, definition=rem_def, item=rem_item)%>%
+    left_join(word_aoa %>% select(item, age)) %>%
+    mutate(learned = as.numeric(age == corr_age)) %>%
+    select(corr_age, item, definition, uni_lemma,learned) %>%
+    rename(age = corr_age) %>%
+    arrange(age, item)
+  return(df)
+}
+
+
+######################################################################################################################
+make_vocab_dataframe <- function(lang, lang_form = "WS", lex_class = "nouns") {
+  item_data <- get_lang_item_data(lang = lang,
+                                  lang_form = lang_form,
+                                  lex_class = lex_class)
+  admin_data <-
+    get_lang_admin_data(lang = lang, lang_form = lang_form)
+  instr_data <-
+    get_lang_instr_data(lang = lang, lang_form = lang_form)
+  word_aoa <-
+    get_lang_aoa(item_data = item_data,
+                 admin_data = admin_data,
+                 instr_data = instr_data)
+  
+  return(arrange(word_aoa, age))
+}
+
+######################################################################################################################
 trim_all_unilemma<-function(unilemma_list){
   unilemma_list<- unilemma_list %>%
     mutate(uni_lemma=gsub(" \\s*\\([^\\)]+\\)","", uni_lemma)) %>%

### 2018-07-06 helpers/clique_percolation.r
Added clique implementation source

@@ -1,3 +1,5 @@
+# https://github.com/angelosalatino/CliquePercolationMethod-R
+
 clique.community <- function(graph, k) {
   require(igraph)
   clq <- cliques(graph, min=k, max=k) %>% lapply(as.vector)

### 2018-07-06 Main.Rmd
Testing visualization approaches
Show uni-lemmas in visualizaiton

@@
 library(doParallel)
+library(networkD3)
 ```
@@
 ```
+
+Initial Clique Analysis
+```{r}
+age <- 20
+g <- assoc_networks[[age - 15]]
+g <- delete.vertices(g, degree(g)==0)
+res <- clique.community.opt(g,3)
+
+## Paint them to different colors
+colbar <- rainbow( length(res)+1 )
+for (i in seq(along=res)) {
+  V(g)[ res[[i]] ]$color <- colbar[i+1]
+}
+
+## Paint the vertices in multiple communities to red
+V(g)[ unlist(res)[ duplicated(unlist(res)) ] ]$color <- "red"
+
+## Plot with the new colors
+plot(g, layout=layout_with_fr, vertex.label=V(g)$uni_lemma)
+```
+
+Dynamic Visualization
+```{r}
+karate <- make_graph("Zachary")
+wc <- cluster_walktrap(karate)
+members <- membership(wc)
+
+# Convert to object suitable for networkD3
+karate_d3 <- igraph_to_networkD3(karate, group = members)
+
+# Create force directed network plot
+forceNetwork(Links = karate_d3$links, Nodes = karate_d3$nodes,
+             Source = 'source', Target = 'target', NodeID = 'name',
+             Group = 'group')
+```

### 2018-07-12 Testing.Rmd
Created testing notebook, started unifying igraph clustering framework with clique percolation

--- 2018-07-06 Main.Rmd
@@
 ---
-# Basic Network Analysis of Wordbank Data
-
-## Build Networks
+# Testing of Functions and Techniques for Graph Analysis and Display
 
@@
 library(directlabels) # direct labeling of data in plots
-library(stringr) # common string operations
+library(stringr) #common string operations
 library(lmtest) #  diagnostic checking in linear regression models
@@
   trim_all_unilemma() %>%
-  trim_all_definition() # %>%
-  # distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
+  trim_all_definition() %>%
+  distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
 ```
@@
 Build networks
-```{r}
+```{r, warning = FALSE }
 assoc_network <- function(vocab, max_age) {
@@
   clustering_coefficient = map_dbl(networks, transitivity),
+  p_random = edges / (vertices * (vertices - 1) / 2),
   avg_shortest_path_random = 0, # either estimate or calculate values for random nets
   diameter_random = 0,
-  clustering_coefficient_random = 0) )
+  clustering_coefficient_random = p_random ) )
 }
@@
 
-plot(g,vertex.size=.01,vertex.label.cex=.8,
+plot(g, vertex.label=V(g)$uni_lemma, vertex.size=.01,vertex.label.cex=.8,
      layout=layout.fruchterman.reingold(g, niter=10000, 
@@
 ```{r}
-### Register Parallelisation (used by clique.community.opt.par())
+## Register Parallelisation (used by clique.community.opt.par())
 cl <- makeCluster(4)
@@
 #which one? the outcome is always the same
-res <- res3
+res <- res2
 
@@
 age <- 20
-g <- assoc_networks[[age - 15]]
+g <- feature_networks[[age - 15]]
 g <- delete.vertices(g, degree(g)==0)

### 2018-07-18 Hills2009Replication.Rmd
Progress on Hills replication

---
title: "Replication of Hills 2009"
author: "Isaac Scheinfeld"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: default
    df_print: paged
---
# Networks

## Setup

First we import helper functions and configure RMarkdown.
```{r message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(broom) # converts R function outputs to tidy data frames
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(kableExtra) # table formatting
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(tidygraph)
library(doParallel)
library(networkD3)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

# knit_print.data.frame <- lemon_print # use kable when displaying tibbles in knit
```

We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.
```{r warning=FALSE}
# The "defintion" is the word, the "unilemma"" is the translation in English.

vocab <- make_vocab_dataframe(lang="English (American)",
                              lang_form = "WS",
                              lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition() %>%
  #distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
```

## Build Networks

Next, we construct networks following the example of Hills. Using vocabulary obtained by 30 months and the same MacRae features as Hills, we construct networks from perceptual and conceptual features. We consider only words for which some feature data is available (though not necessarily perceptual or conceptual), and track the number of features that generate each edge.

```{r message=FALSE}
perceptual_features = c("sound", "taste", "smell", "tactile", 
                           "visual-form_and_surface", "visual-motion", "visual-color")
conceptual_features = c("function")

full_network <- feature_network(vocab, max_age = 30, shared_threshold = 1,
                                feature_types = c(perceptual_features,
                                                  conceptual_features)) %>%
                  set.graph.attribute("type", "both")

perceptual_network <- feature_network(vocab, max_age = 30, shared_threshold = 1,
                                      feature_types = perceptual_features) %>%
                        set.graph.attribute("type", "perceptual")
conceptual_network <- feature_network(vocab, max_age = 30, shared_threshold = 1,
                                      feature_types = conceptual_features) %>%
                        set.graph.attribute("type", "conceptual")
```

## Basic Vocab and Feature Properties

Compared to Hills' 130 nouns that overlapped the MacRae data and vocabulary data, we have `r vcount(perceptual_network)` nouns.

*TODO extend*

## Basic Network Properties

Some basic properties of networks built from perceptual and conceptual features.
```{r, results='asis'}
max_w <- 4

network_properties <- function(networks) {
  return( tibble(
  name = map_chr(networks, ~ .x$name),
  type = map_chr(networks, ~ .x$type),
  age = map_dbl(networks, ~ .x$age) %>%
    as.integer(),
  w = map_dbl(networks, ~ .x$w) %>%
    as.integer(),
  vertices = map_int(networks, vcount),
  edges = map_dbl(networks, ecount) %>%
    as.integer(), # for some reason igraph ecount returns double
  avg_degree = map(networks, degree) %>%
    map_dbl(mean),
  avg_shortest_path = map_dbl(networks, mean_distance),
  diameter = map_dbl(networks, diameter) %>%
    as.integer(),
  clustering_coefficient = map_dbl(networks, transitivity),
  density = edges / (vertices * (vertices - 1) / 2),
  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
  diameter_random = 0,
  clustering_coefficient_random = density,
  isolates = map_dbl(networks, function (g) sum(degree(g) == 0)),
  components = map_dbl(networks, count_components) %>%
    as.integer() - isolates))
}

full_networks <- list()
perceptual_networks <- list()
conceptual_networks <- list()
for (w in 1:max_w) {
  full_networks[[w]] <- full_network %>%
    activate(what = edges) %>%
    filter(shared >= w) %>%
    set.graph.attribute("w", w)

  perceptual_networks[[w]] <- perceptual_network %>%
    activate(what = edges) %>%
    filter(shared >= w) %>%
    set.graph.attribute("w", w)

  conceptual_networks[[w]] <- conceptual_network %>%
    activate(what = edges) %>%
    filter(shared >= w) %>%
    set.graph.attribute("w", w)
}

networks <- full_networks %>%
  append(perceptual_networks) %>%
  append(conceptual_networks)

our_network_properties <- network_properties(networks)

our_network_properties %>%
  select(type, w, vertices, edges, avg_degree, diameter, avg_shortest_path, clustering_coefficient) %>%
  kable(format="html",
        escape = FALSE,
        col.names = c("Type", "w", "V", "E", "Average degree", "Diameter", "Average length", "Clustering coefficient"),
        digits = 2,
        align = rep("l", 8)) %>%
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1:3, valign = "top")
```

We can compare these networks to those from Hills, noting that we have a different set of words/nodes but that the induced subgraph of those words shared between our analysis and that of Hills should be the same.
```{r}
hills_network_properties <- tibble( # table from Hills 2009
  type = c(rep("all", times=4), rep("perceptual", times=4), rep("conceptual", 4)),
  w = c(1:max_w, 1:max_w, 1:max_w),
  clustering_coefficient = c(0.55, 0.54, 0.58, 0.60, 0.54, 0.54, 0.62, 0.62, 0.88, 0.59, 0.38, 1.00),
  avg_shortest_path = c(1.72, 2.57, 4.96, 3.22, 1.76, 2.69, 5.02, 2.55, 3.08, 1.59, 5.02, 1.00),
  density = c(0.29, 0.10, 0.04, 0.02, 0.27, 0.08, 0.03, 0.01, 0.05, 0.01, 0.0, 0.0),
  components = c(1, 1, 4, 10, 1, 2, 8, 11, 7, 14, 7, 2),
  isolates = c(0, 6, 20, 47, 0, 10, 31, 69, 33, 81, 113, 126)
)

# convert contents to text
display_our_properties <- our_network_properties %>% mutate_all(funs(format(., digits=2, trim=TRUE)))
display_hills_properties <- hills_network_properties %>% mutate_all(funs(paste("(", ., ")", sep='')))

# combine text tables for display
display_properties <- bind_rows(display_our_properties %>% mutate(row = 1:n()), 
                                display_hills_properties %>% mutate(row = 1:n())) %>%
  group_by(row) %>%
  summarise_if(is.character, funs(paste(., collapse=" "))) %>%
  arrange(row)

# display combined properties
select(hills_network_properties, type, w) %>%
  bind_cols(select(display_properties, clustering_coefficient, avg_shortest_path,
                   density, components, isolates)) %>%
  kable(format="html",
        escape = FALSE,
        col.names = c("Type", "w", "Clustering Coefficient", "Average length", "Density", "Components", "Isolates"),
        align = rep("l", 7)) %>%
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1:2, valign = "top")
```

## Visualize Networks
```{r out.width = '100%'}
par(mfcol=c(3, 3), mar=c(0.5,0.5,0.5,0.5))
for (n in networks[c(TRUE, TRUE, TRUE, FALSE, # display networks for w=1,2,3
                     TRUE, TRUE, TRUE, FALSE,
                     TRUE, TRUE, TRUE, FALSE)]) {
  plot_network(n, remove_isolated = TRUE, frame=FALSE)
}
```

# Clusters

## Visualize Networks
```{r out.width = '100%'}
networks <- perceptual_networks[2]
```

## Clique Percolation

Initial Clique Analysis
```{r out.width = '100%'}
trimmed_networks <- map(networks, function (g) delete.vertices(g, degree(g)==0))

# cl <- makeCluster(3)
# registerDoParallel(cl)
# getDoParWorkers()
## Plot with the new colors
for (net in networks) {
  for (k in 3:4) {
    clusters <- clique.community.opt(net,k)
    plot_network(net, clusters = clusters, labels=FALSE)
  }
}
# stopCluster(cl)
```

Dynamic Visualization
```{r}
conceptual_clusters <- membership(cluster_walktrap(conceptual_network))

# Convert to object suitable for networkD3
conceptual_d3 <- igraph_to_networkD3(conceptual_network, group = conceptual_clusters)

# Create force directed network plot
forceNetwork(Links = conceptual_d3$links, Nodes = conceptual_d3$nodes,
             Source = 'source', Target = 'target', NodeID = 'name',
             Group = 'group')
```

### 2018-07-18 Main.Rmd
Progress on Hills replication

@@
 library(langcog) # useful things used by Language and Cognition Lab
-library(boot) # functions for bootstrapping
+#library(boot) # functions for bootstrapping
 library(dplyr) # for working with datafram-like objects
@@
 library(wordbankr) # access to wordbank data
-library(directlabels) # direct labeling of data in plots
+#library(directlabels) # direct labeling of data in plots
 library(stringr) # common string operations
-library(lmtest) #  diagnostic checking in linear regression models
-library(rwebppl) # interface to probabilistic programming language WebPPL
-library(jsonlite) # JSON parser
-library(nlme) # gaussian linear and nonlinear mixed-effects models
-library(feather) # read and write fast lightweight binary columnar data
+#library(lmtest) #  diagnostic checking in linear regression models
+#library(rwebppl) # interface to probabilistic programming language WebPPL
+#library(jsonlite) # JSON parser
+#library(nlme) # gaussian linear and nonlinear mixed-effects models
+#library(feather) # read and write fast lightweight binary columnar data
 library(broom) # converts R function outputs to tidy data frames
-library(HDInterval) # calculate highest density intervals of objects w/ pdf
-library(BBmisc) # misc helper functions
+#library(HDInterval) # calculate highest density intervals of objects w/ pdf
+#library(BBmisc) # misc helper functions
 library(igraph) # network analysis and visualization

### 2018-07-18 Testing.Rmd
Progress on Hills replication

@@
 library(networkD3)
+```
+
+```{r, setup, include=FALSE}
+#knitr::opts_chunk$set(collapse = TRUE)
 ```
@@
 ## Network Analysis
-
-### Large-Scale Structure of Networks
 
@@
 
-Initial Clique Analysis
+# Initial Cluster Analysis
+
+## Clique Percolation
 ```{r}
@@
 g <- delete.vertices(g, degree(g)==0)
-res <- clique.community.opt(g,3)
+res <- clique.community.opt(g,4)
 
@@
 plot(g, layout=layout_with_fr, vertex.label=V(g)$uni_lemma)
+```
+
+## Walktrap 
+```{r}
+age <- 20
+g <- feature_networks[[age - 15]]
+g <- delete.vertices(g, degree(g)==0)
+res_w <- communities(cluster_walktrap(g))
+
+## Paint them to different colors
+colbar <- rainbow( length(res_w)+1 )
+for (i in seq(along=res_w)) {
+  V(g)[ res[[i]] ]$color <- colbar[i+1]
+}
+
+## Paint the vertices in multiple communities to red
+V(g)[ unlist(res_w)[ duplicated(unlist(res_w)) ] ]$color <- "red"
+
+## Plot with the new colors
+plot(g, layout=layout_with_fr, vertex.label=V(g)$uni_lemma)
+plt(res_w, g)
 ```

### 2018-07-18 helpers/all_helper.r

@@ -1,4 +1,5 @@
 source("wb_helper.r")
-source("make_assoc_pairs.r")
-source("make_feature_pairs.r")
+source("assoc_helper.r")
+source("feature_helper.r")
+source("plot_helper.r")
 source("clique_percolation.r")

### 2018-07-18 helpers/assoc_helper.r

@@ -25,7 +25,18 @@ make_assoc_pairs <- function(lemma_list) {
     left_join(lemma_list, c("item.definition" = "uni_lemma")) %>%
     select(item, item.definition, pair, pair.definition, link) %>%
     arrange(item, pair) %>%
-    filter(item!=pair)
+    filter(item > pair) # filters item = pair and duplicates
   
   return(assoc_link)
+}
+
+assoc_network <- function(vocab, max_age) {
+  vocab_up_to_age = filter(vocab, age <= max_age)
+  assoc_links <- make_assoc_pairs(lemma_list = vocab_up_to_age) %>%
+    filter(link==1) %>%
+    select(item, pair)
+  graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=vocab_up_to_age) %>%
+    set.graph.attribute("name", "Assoc") %>%
+    set.graph.attribute("age", max_age)
+  return(graph)
 }

### 2018-07-18 helpers/feature_helper.r

@@ -1,0 +1,61 @@
+make_feature_pairs <- function(lemma_list, features) {
+  wb <- lemma_list
+  
+  # Here I still should deal with words in parenthesis (homophony/polysemy), e.g., chiken (animal) vs. chiken (food), etc...
+  
+  item_feat <- wb %>%
+    left_join(features) %>%
+    rename(item.definition = uni_lemma,
+           item_feat = Feature) %>%
+    filter(!is.na(item_feat)) %>%
+    select(item, item.definition, item_feat)
+  
+  
+  item_feat_list <- (wb %>%
+                       filter(item %in% item_feat$item) %>%
+                       select(item))$item
+  
+  # List these words pair-wise and compute the number of shared feature for each pair
+  item_pair <- expand.grid(item = item_feat_list,
+                           pair = item_feat_list)
+  
+  pair_feat <- item_feat %>%
+    rename(pair = item,
+           pair_feat = item_feat,
+           pair.definition = item.definition)
+  
+  item_feat_pair <- left_join(item_feat, item_pair)
+  
+  item_pair_feat <- item_feat_pair %>%
+    left_join(pair_feat)
+  
+  item_pair_shared <- item_pair_feat %>%
+    group_by(item, item.definition, pair, pair.definition) %>%
+    summarise(shared = sum(pair_feat == item_feat)) %>%
+    filter(item > pair) %>% # removes item = pair and duplicates
+    ungroup()
+  
+  return(item_pair_shared)
+}
+
+feature_network <- function(vocab, max_age, shared_threshold, feature_types, trim_to_macrae=TRUE) {
+  features <- read_delim("data/MacRae.csv", delim = ",") %>%
+    select(Concept, Feature, WB_Label, BR_Label) %>%
+    rename(uni_lemma=Concept)
+
+  vocab_up_to_age = vocab %>%
+    filter(age <= max_age)
+  feature_links <- make_feature_pairs(lemma_list = vocab_up_to_age,
+                                      features = filter(features, BR_Label %in% feature_types)) %>%
+    filter(shared >= shared_threshold) %>%
+    select(item, pair, shared)
+  if (trim_to_macrae) {
+    vocab_up_to_age <- filter(vocab_up_to_age,
+                              uni_lemma %in% features$uni_lemma)
+  }
+  graph <- graph_from_data_frame(feature_links, directed=FALSE,
+                                 vertices = vocab_up_to_age) %>%
[…]

### 2018-07-18 helpers/make_feature_pairs.r

@@ -1,49 +1,0 @@
-make_feature_pairs <- function(lemma_list) {
-  #Get the McRae features
-  features <-
-    hi <- read_delim("data/MacRae.csv", delim = ",") %>%
-    select(Concept, Feature, WB_Label, BR_Label) %>%
-    filter(BR_Label=="visual-form_and_surface") %>% #Here it depends what kind of features we would like to keep (perceptual? conceptual? both?)
-    rename(uni_lemma=Concept)
-  #Intersection of Wordbank with McRae concepts
-  #(Note that we work with unilemmas and not with definitions becuase we would like to use cross-linguistic data)
-  
-  #List of word types in WordBank
-  wb <- lemma_list
-  # List of wordbank with feature
-  
-  #Here I still should deal with words in parenthesis (homophony/polysemy), e.g., chiken (animal) vs. chiken (food), etc...
-  
-  item_feat <- wb %>%
-    left_join(features) %>%
-    rename(item.definition = uni_lemma,
-           item_feat = Feature) %>%
-    filter(!is.na(item_feat)) %>%
-    select(item, item.definition, item_feat)
-  
-  
-  item_feat_list <- (wb %>%
-                       filter(item %in% item_feat$item) %>%
-                       select(item))$item
-  
-  # List these words pair-wise and compate the number of shared feature for each pair
-  item_pair <- expand.grid(item = item_feat_list,
-                           pair = item_feat_list)
-  
-  pair_feat <- item_feat %>%
-    rename(pair = item,
-           pair_feat = item_feat,
-           pair.definition = item.definition)
-  
-  item_feat_pair <- left_join(item_feat, item_pair)
-  
-  item_pair_feat <- item_feat_pair %>%
-    left_join(pair_feat)
-  
-  item_pair_shared <- item_pair_feat %>%
-    group_by(item, item.definition, pair, pair.definition) %>%
-    summarise(shared = sum(pair_feat == item_feat)) %>%
-    filter(item!=pair)
-  
-  return(item_pair_shared)
-}

### 2018-07-18 helpers/plot_helper.r

@@ -1,0 +1,24 @@
+plot_network <- function(g, name=NA, remove_isolated=FALSE, frame=FALSE, labels=FALSE, clusters=NULL) {
+  if (remove_isolated) {
+    g <- delete.vertices(g, degree(g)==0)
+  }
+  l <- layout_with_fr(g) #layout.forceatlas2(g, iterations=2000, plotstep=5000) #layout_with_fr(g)
+  
+  if (!is.null(clusters)) {
+    ## Paint them to different colors
+    colbar <- rainbow(length(clusters) + 1)
+    for (i in seq(along=clusters)) {
+      V(g)[ clusters[[i]] ]$color <- colbar[i+1]
+    }
+    
+    ## Paint the vertices in multiple communities to red
+    V(g)[ unlist(clusters)[ duplicated(unlist(clusters)) ] ]$color <- "red"
+  }
+  
+  if (labels) {
+    plot(g, layout=l, vertex.label=V(g)$uni_lemma, edge.width=0.5, vertex.size=4, frame=frame)
+  } else {
+    plot(g, layout=l, vertex.label=NA, edge.width=0.5, vertex.size=4, frame=frame)
+  }
+}
+

### 2018-07-20 Clustering.Rmd
Added clustering notebook, refactored network generation.

--- 2018-07-18 Hills2009Replication.Rmd
@@
     theme: default
-    df_print: paged
 ---
@@
 source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
-
-# knit_print.data.frame <- lemon_print # use kable when displaying tibbles in knit
 ```
@@
   trim_all_unilemma() %>%
-  trim_all_definition() %>%
-  #distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
+  trim_all_definition()
 ```
@@
 
-## Basic Vocab and Feature Properties
-
-Compared to Hills' 130 nouns that overlapped the MacRae data and vocabulary data, we have `r vcount(perceptual_network)` nouns.
-
-*TODO extend*
-
-## Basic Network Properties
-
-Some basic properties of networks built from perceptual and conceptual features.
-```{r, results='asis'}
-max_w <- 4
-
-network_properties <- function(networks) {
-  return( tibble(
-  name = map_chr(networks, ~ .x$name),
-  type = map_chr(networks, ~ .x$type),
-  age = map_dbl(networks, ~ .x$age) %>%
-    as.integer(),
-  w = map_dbl(networks, ~ .x$w) %>%
-    as.integer(),
-  vertices = map_int(networks, vcount),
-  edges = map_dbl(networks, ecount) %>%
-    as.integer(), # for some reason igraph ecount returns double
-  avg_degree = map(networks, degree) %>%
-    map_dbl(mean),
-  avg_shortest_path = map_dbl(networks, mean_distance),
-  diameter = map_dbl(networks, diameter) %>%
-    as.integer(),
-  clustering_coefficient = map_dbl(networks, transitivity),
-  density = edges / (vertices * (vertices - 1) / 2),
-  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
-  diameter_random = 0,
-  clustering_coefficient_random = density,
-  isolates = map_dbl(networks, function (g) sum(degree(g) == 0)),
-  components = map_dbl(networks, count_components) %>%
-    as.integer() - isolates))
-}
-
-full_networks <- list()
-perceptual_networks <- list()
-conceptual_networks <- list()
-for (w in 1:max_w) {
-  full_networks[[w]] <- full_network %>%
-    activate(what = edges) %>%
-    filter(shared >= w) %>%
-    set.graph.attribute("w", w)
-
-  perceptual_networks[[w]] <- perceptual_network %>%
-    activate(what = edges) %>%
-    filter(shared >= w) %>%
-    set.graph.attribute("w", w)
-
-  conceptual_networks[[w]] <- conceptual_network %>%
-    activate(what = edges) %>%
-    filter(shared >= w) %>%
-    set.graph.attribute("w", w)
-}
-
-networks <- full_networks %>%
-  append(perceptual_networks) %>%
-  append(conceptual_networks)
-
-our_network_properties <- network_properties(networks)
-
-our_network_properties %>%
-  select(type, w, vertices, edges, avg_degree, diameter, avg_shortest_path, clustering_coefficient) %>%
-  kable(format="html",
-        escape = FALSE,
-        col.names = c("Type", "w", "V", "E", "Average degree", "Diameter", "Average length", "Clustering coefficient"),
-        digits = 2,
-        align = rep("l", 8)) %>%
-  kable_styling(full_width = F) %>%
-  collapse_rows(columns = 1:3, valign = "top")
-```
-
-We can compare these networks to those from Hills, noting that we have a different set of words/nodes but that the induced subgraph of those words shared between our analysis and that of Hills should be the same.
-```{r}
-hills_network_properties <- tibble( # table from Hills 2009
-  type = c(rep("all", times=4), rep("perceptual", times=4), rep("conceptual", 4)),
-  w = c(1:max_w, 1:max_w, 1:max_w),
-  clustering_coefficient = c(0.55, 0.54, 0.58, 0.60, 0.54, 0.54, 0.62, 0.62, 0.88, 0.59, 0.38, 1.00),
-  avg_shortest_path = c(1.72, 2.57, 4.96, 3.22, 1.76, 2.69, 5.02, 2.55, 3.08, 1.59, 5.02, 1.00),
-  density = c(0.29, 0.10, 0.04, 0.02, 0.27, 0.08, 0.03, 0.01, 0.05, 0.01, 0.0, 0.0),
-  components = c(1, 1, 4, 10, 1, 2, 8, 11, 7, 14, 7, 2),
-  isolates = c(0, 6, 20, 47, 0, 10, 31, 69, 33, 81, 113, 126)
-)
-
-# convert contents to text
-display_our_properties <- our_network_properties %>% mutate_all(funs(format(., digits=2, trim=TRUE)))
-display_hills_properties <- hills_network_properties %>% mutate_all(funs(paste("(", ., ")", sep='')))
-
-# combine text tables for display
-display_properties <- bind_rows(display_our_properties %>% mutate(row = 1:n()), 
-                                display_hills_properties %>% mutate(row = 1:n())) %>%
-  group_by(row) %>%
-  summarise_if(is.character, funs(paste(., collapse=" "))) %>%
-  arrange(row)
-
-# display combined properties
-select(hills_network_properties, type, w) %>%
-  bind_cols(select(display_properties, clustering_coefficient, avg_shortest_path,
-                   density, components, isolates)) %>%
-  kable(format="html",
-        escape = FALSE,
-        col.names = c("Type", "w", "Clustering Coefficient", "Average length", "Density", "Components", "Isolates"),
-        align = rep("l", 7)) %>%
-  kable_styling(full_width = F) %>%
-  collapse_rows(columns = 1:2, valign = "top")
-```
-
 ## Visualize Networks
 ```{r out.width = '100%'}
-par(mfcol=c(3, 3), mar=c(0.5,0.5,0.5,0.5))
-for (n in networks[c(TRUE, TRUE, TRUE, FALSE, # display networks for w=1,2,3
-                     TRUE, TRUE, TRUE, FALSE,
-                     TRUE, TRUE, TRUE, FALSE)]) {
-  plot_network(n, remove_isolated = TRUE, frame=FALSE)
-}
+dense_network <- perceptual_network
+sparse_network <- perceptual_network %E>%
+  filter(shared >= 2)
+
+plot_network(dense_network)
+plot_network(sparse_network)
 ```
@@
 
-## Visualize Networks
+Here I experiment with various clustering algorithms, which vary in whether they take weighting into account, whether they allow overlapping clusters, and various other properties.
+
+## Clique Percolation - Unweighted, Overlapping
+
+Clique percolation requires the choice of a parameter k, which is the size of the clique by which vertices must be connected to be considered contained in the same cluster.
+For this reason, vertices which are themselves not part of a k-clique are not included in a cluster.
 ```{r out.width = '100%'}
-networks <- perceptual_networks[2]
+par(mfrow=c(1,2), mar=rep(1,4))
+dense_clusters <- clique.community.opt(dense_network, 2)
+sparse_clusters <- clique.community.opt(sparse_network, 3)
+
+plot_network(dense_network, clusters = dense_clusters)
+plot_network(sparse_network, clusters = sparse_clusters)
 ```
 
-## Clique Percolation
+## Maximum Modularity - Unweighted
+```{r}
+dense_clusters <- cluster_fast_greedy(dense_network, weights = NULL)
 
-Initial Clique Analysis
-```{r out.width = '100%'}
-trimmed_networks <- map(networks, function (g) delete.vertices(g, degree(g)==0))
+# Plot
+par(mfrow=c(1,2), mar=rep(1,4))
+layout <-layout_with_fr(dense_network)
+plot(dense_clusters, dense_network, layout=layout, vertex.label=NA, vertex.size=5,  edge.arrow.size=.2)
 
-# cl <- makeCluster(3)
-# registerDoParallel(cl)
-# getDoParWorkers()
-## Plot with the new colors
-for (net in networks) {
-  for (k in 3:4) {
-    clusters <- clique.community.opt(net,k)
-    plot_network(net, clusters = clusters, labels=FALSE)
-  }
-}
-# stopCluster(cl)
+# # Change colors of nodes, polygons, and polygon borders
+# new_cols <- c("white", "red", "black")[membership(sparse_clusters)]
+# plot(sparse_clusters, sparse_network, col=new_cols, mark.border="black", mark.col=c("tan", "pink", "lightgray"), 
+#     layout=layout, vertex.label=NA, vertex.size=5, edge.arrow.size=.2)
 ```
-
-Dynamic Visualization
-```{r}
-conceptual_clusters <- membership(cluster_walktrap(conceptual_network))
-
-# Convert to object suitable for networkD3
-conceptual_d3 <- igraph_to_networkD3(conceptual_network, group = conceptual_clusters)
-
-# Create force directed network plot
-forceNetwork(Links = conceptual_d3$links, Nodes = conceptual_d3$nodes,
-             Source = 'source', Target = 'target', NodeID = 'name',
-             Group = 'group')
-```

### 2018-07-20 Hills2009Replication.Rmd
Added clustering notebook, refactored network generation.

@@
     theme: default
-    df_print: paged
 ---
+# Background
+
+Questions
+
+1. Are shared features sufficient to form meaningful categories?
+2. Are some kinds of features more important than others?
+3. Are perceptual or conceptual features more important for forming superordinate categories?
+4. Are perceptual features a developmentally earlier source of categorical information?
+5. Are conceptual features  privileged in superordinate category formation?
+
+Hills intends to "take the feature correlation approach to build network representations, and then use the formalisms of graph theory to examine the noun–feature relationships in terms of the structure they provide." "By examining the small-world structure of early noun networks – as well as other graph- theoretic properties – we take a quantitative approach to evaluating the structural contributions of perceptual and conceptual features in the development of early categories." "What is needed [] is a better understanding of [perceptual and conceptual features'] inter-related roles in a larger system of developing categories."
+
+Hills intends to address these specific questions:
+
+1. Do features provide sufficient structure to infer common adult taxonomic categorizations among the nouns children know at 30 months of age?
+2. If so, what are the available categories?
+3. How robust are these categories to more or less stringent criteria for feature correlations?
+4. Do perceptual and conceptual features differ in the structure they provide – are some feature types more robust, more discriminating, or more redundant?
+
 # Networks
 
-## Setup
-
-First we import helper functions and configure RMarkdown.
-```{r message=FALSE, warning=FALSE} 
+```{r echo=FALSE, message=FALSE, warning=FALSE} 
 library(purrr) # fp library
@@
 
-We begin by importing data from wordbank.
+## Nouns
+
+Hills selected nouns from the Todler version of the MacArthur-Bates Communicative Developmental Inventory. This includes nouns which were aquired by 50% of children by 30 months.
+
+*This needs to be fixed to match Hills exactly*.
+```{r warning=FALSE}
+# We begin by importing data from wordbank.
 Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word.
@@
 but we will have to be careful in our choices if we are preparing later for publication.
-```{r warning=FALSE}
-# The "defintion" is the word, the "unilemma"" is the translation in English.
 
@@
   trim_all_unilemma() %>%
-  trim_all_definition() %>%
-  #distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
+  trim_all_definition()
+
+features <- load_features()
+
+vocab <- vocab %>%
+  filter(age <= 30) %>%
+  filter(uni_lemma %in% features$uni_lemma)
 ```
@@
 
-full_network <- feature_network(vocab, max_age = 30, shared_threshold = 1,
+full_network <- feature_network(vocab, features, shared_threshold = 1,
                                 feature_types = c(perceptual_features,
                                                   conceptual_features)) %>%
-                  set.graph.attribute("type", "both")
+                  set.graph.attribute("type", "both") %>%
+                  set.graph.attribute("age", 30)
 
-perceptual_network <- feature_network(vocab, max_age = 30, shared_threshold = 1,
+perceptual_network <- feature_network(vocab, features, shared_threshold = 1,
                                       feature_types = perceptual_features) %>%
-                        set.graph.attribute("type", "perceptual")
-conceptual_network <- feature_network(vocab, max_age = 30, shared_threshold = 1,
+                        set.graph.attribute("type", "perceptual") %>%
+                        set.graph.attribute("age", 30)
+
+conceptual_network <- feature_network(vocab, features, shared_threshold = 1,
                                       feature_types = conceptual_features) %>%
-                        set.graph.attribute("type", "conceptual")
+                        set.graph.attribute("type", "conceptual") %>%
+                        set.graph.attribute("age", 30)
 ```

### 2018-07-20 helpers/feature_helper.r

@@ -38,24 +38,23 @@ make_feature_pairs <- function(lemma_list, features) {
   return(item_pair_shared)
 }
 
-feature_network <- function(vocab, max_age, shared_threshold, feature_types, trim_to_macrae=TRUE) {
+load_features <- function() {
   features <- read_delim("data/MacRae.csv", delim = ",") %>%
     select(Concept, Feature, WB_Label, BR_Label) %>%
     rename(uni_lemma=Concept)
+  
+  return(features)
+}
 
-  vocab_up_to_age = vocab %>%
-    filter(age <= max_age)
-  feature_links <- make_feature_pairs(lemma_list = vocab_up_to_age,
+feature_network <- function(vocab, features, feature_types, shared_threshold) {
+  feature_links <- make_feature_pairs(lemma_list = vocab,
                                       features = filter(features, BR_Label %in% feature_types)) %>%
     filter(shared >= shared_threshold) %>%
     select(item, pair, shared)
-  if (trim_to_macrae) {
-    vocab_up_to_age <- filter(vocab_up_to_age,
-                              uni_lemma %in% features$uni_lemma)
-  }
+  
   graph <- graph_from_data_frame(feature_links, directed=FALSE,
-                                 vertices = vocab_up_to_age) %>%
-    set.graph.attribute("name", "Feature") %>%
-    set.graph.attribute("age", max_age)
+                                 vertices = vocab) %>%
+    set.graph.attribute("name", "Feature")
+  
   return(as_tbl_graph(graph))
 }

### 2018-07-26 Hills2009Replication.Rmd
Changed network generation method, breaking changes for Hills2009Replication.

@@
 
-# Networks
+# Methods
 
@@
 library(networkD3)
+library(ForceAtlas2)
 
 source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
-
-# knit_print.data.frame <- lemon_print # use kable when displaying tibbles in knit
 ```
@@
 
-Hills selected nouns from the Todler version of the MacArthur-Bates Communicative Developmental Inventory. This includes nouns which were aquired by 50% of children by 30 months.
+Hills selected nouns from the Todler version of the MacArthur-Bates Communicative Developmental Inventory.
+This includes nouns which were aquired by 50% of children by 30 months.
+*This needs to be fixed to match Hills exactly*.
 
-*This needs to be fixed to match Hills exactly*.
 ```{r warning=FALSE}
@@
 
-vocab <- make_vocab_dataframe(lang="English (American)",
+full_vocab <- make_vocab_dataframe(lang="English (American)",
                               lang_form = "WS",
@@
   trim_all_definition()
+```
 
+The initial vocabulary contains `r nrow(full_vocab)` (compared to Hills' 312).
+
+## Features
+
+Features taken from McRae et al. (2005), in which features were collected for 541 nouns from 725 adults, with 30 adults providing  14 features for each noun.
+
+```{r warning=FALSE}
 features <- load_features()
 
-vocab <- vocab %>%
+vocab <- full_vocab %>%
   filter(age <= 30) %>%
-  filter(uni_lemma %in% features$uni_lemma)
+  filter(uni_lemma %in% features$uni_lemma) %>%
+  distinct(uni_lemma, .keep_all = TRUE)
 ```
+
+Only the words for which feature data are available are considered, an overlap of `r nrow(vocab)` in our data compared to Hills' 130.
 
@@
 
-Next, we construct networks following the example of Hills.
-Using vocabulary obtained by 30 months and the same MacRae features as Hills, we construct networks from perceptual and conceptual features.
-We consider only words for which some feature data is available (though not necessarily perceptual or conceptual), and track the number of features that generate each edge.
+Using vocabulary obtained by 30 months and the same MacRae features as Hills, we construct networks from perceptual and conceptual features. We track the number of features that generate each edge.
 
@@
 
+# Results
+
+## The Full Network
+
+### Network statistics and small-world analyses
+
+```{r}
+# testing dense layout
+source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
+
+plot_network(full_network %E>% filter(shared >= 2), remove_isolated = TRUE, labels=TRUE, frame=TRUE)
+```
+
+The full network is shown in the following figure, for w = 1, 2, 3, and 4.
+
+```{r out.width = '100%'}
+full_networks = list()
+for (w in 1:4) {
+  full_networks[[w]] = full_network %E>%
+    filter(shared >= w)
+}
+
+#par(mfcol=c(2, 2), mar=c(0.5,0.5,0.5,0.5))
+for (network in full_networks) {
+  plot_network(network, remove_isolated = FALSE, labels=TRUE, frame=TRUE)
+}
+```
+
 ## Basic Vocab and Feature Properties
-
-Compared to Hills' 130 nouns that overlapped the MacRae data and vocabulary data, we have `r vcount(perceptual_network)` nouns.
-
-*TODO extend*
 
@@
 
-## Visualize Networks
-```{r out.width = '100%'}
-par(mfcol=c(3, 3), mar=c(0.5,0.5,0.5,0.5))
-for (n in networks[c(TRUE, TRUE, TRUE, FALSE, # display networks for w=1,2,3
-                     TRUE, TRUE, TRUE, FALSE,
-                     TRUE, TRUE, TRUE, FALSE)]) {
-  plot_network(n, remove_isolated = TRUE, frame=FALSE)
-}
-```
-
 # Clusters

### 2018-07-26 Main.Rmd
Changed network generation method, breaking changes for Hills2009Replication.

--- 2018-07-06 Main.Rmd
@@
 ---
+title: "Replication of Hills 2009"
+author: "Isaac Scheinfeld"
+date: "`r Sys.Date()`"
 output:
-  html_document: default
-  pdf_document: default
+  html_document:
+    theme: default
 ---
-# Basic Network Analysis of Wordbank Data
+# Background
 
-## Build Networks
+...
 
-List of libraries
-```{r echo=TRUE, warning=FALSE, message=FALSE}
+# Networks
+
+```{r echo=FALSE, message=FALSE, warning=FALSE} 
 library(purrr) # fp library
@@
 library(langcog) # useful things used by Language and Cognition Lab
-library(boot) # functions for bootstrapping
 library(dplyr) # for working with datafram-like objects
@@
 library(wordbankr) # access to wordbank data
-library(directlabels) # direct labeling of data in plots
 library(stringr) # common string operations
-library(lmtest) #  diagnostic checking in linear regression models
-library(rwebppl) # interface to probabilistic programming language WebPPL
-library(jsonlite) # JSON parser
-library(nlme) # gaussian linear and nonlinear mixed-effects models
-library(feather) # read and write fast lightweight binary columnar data
 library(broom) # converts R function outputs to tidy data frames
-library(HDInterval) # calculate highest density intervals of objects w/ pdf
-library(BBmisc) # misc helper functions
 library(igraph) # network analysis and visualization
 library(knitr) # general-purpose tool for dynamic report generation
+library(kableExtra) # table formatting
 library(lemon) # functions for working w/ ggplot2 and knitr extensions
 library(tibble) # modern dataframes
+library(tidygraph)
 library(doParallel)
 library(networkD3)
+library(ForceAtlas2)
+
+source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
 ```
 
-Import helper functions and configure RMarkdown
-```{r echo=TRUE, warning=FALSE, message=FALSE}
-source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
+## Nouns
 
-knit_print.data.frame <- lemon_print # use kable when displaying tibbles in knit
-```
+We begin with roughly the same data used by Hills. *(TODO fix, get same data)*
 
-Create vocab 
-```{r echo=TRUE, warning=FALSE, message=FALSE}
-# Import data from wordbank.
+```{r warning=FALSE}
+# We begin by importing data from wordbank.
 Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word.
-The "defintion" is the word, the "unilemma"" is the translation in English.
+We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,..
+but we will have to be careful in our choices if we are preparing later for publication.
 
-# We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,..
-but we will have to be careful in our choices if we are preparing later for publication
-
-vocab <- make_vocab_dataframe(lang="English (American)",
+full_vocab <- make_vocab_dataframe(lang="English (American)",
                               lang_form = "WS",
@@
   trim_all_unilemma() %>%
-  trim_all_definition() # %>%
-  # distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
+  trim_all_definition() %>%
+  arrange(age) %>%            # keep first age for duplicates
+  distinct(uni_lemma, .keep_all = TRUE) %>%
+  select(uni_lemma, definition, age)
 ```
 
-Build networks
+The initial vocabulary contains `r nrow(full_vocab)` (compared to Hills' 312).
+
+## Perceptual & Conceptual Features
+
+Features taken from McRae et al. (2005), in which features were collected for 541 nouns from 725 adults, with 30 adults providing  14 features for each noun.
+
+```{r warning=FALSE}
+features <- load_features()
+
+hills_vocab <- full_vocab %>%
+  filter(age <= 30) %>%
+  filter(uni_lemma %in% features$Concept) # filter to words with features
+```
+
+To begin our analysis, we only consider the words for which feature data are available, an overlap of `r nrow(vocab)` in our data compared to Hills' 130.
+
+## Word2Vec
+
+## Build Networks
+
+Using vocabulary obtained by 30 months and the same McRae features as Hills, we construct networks from perceptual and conceptual features. We track the number of features that generate each edge.
+
+```{r message=FALSE}
+# perceptual and conceptual McRae features
+perceptual_features = c("sound", "taste", "smell", "tactile",
+                        "visual-form_and_surface", "visual-motion", "visual-color")
+conceptual_features = c("function")
+
+# count shared features between words in vocabulary
+perceptual_links <- make_feature_links(vocab = hills_vocab,
+                                       feature_types = perceptual_features) %>%
+  rename(perceptual = shared)
+
+conceptual_links <- make_feature_links(vocab = hills_vocab,
+                                       feature_types = conceptual_features) %>%
+  rename(conceptual = shared)
+
+# get word2vec distance between words in vocabulary
+w2v_links <- make_w2v_links(vocab = hills_vocab) #TODO still problem w/ vocab matching w2v data
+
+links <- perceptual_links %>%
+  full_join(conceptual_links, by=c("from", "to")) %>%
+  full_join(w2v_links, by=c("from", "to"))
+
+full_network <- graph_from_data_frame(links, vertices = hills_vocab, directed = FALSE) %>%
+  as_tbl_graph()
+```
+
+# Results
+
+## The Full Network
+
+### Network statistics and small-world analyses
+
 ```{r}
-assoc_network <- function(vocab, max_age) {
-  vocab_up_to_age = filter(vocab, age <= max_age)
-  assoc_links <- make_assoc_pairs(lemma_list = vocab_up_to_age) %>%
-    filter(link==1) %>%
-    select(item, pair, item.definition, pair.definition)
-  graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=vocab_up_to_age) %>%
-    simplify() %>%
-    set.graph.attribute("name", "Assoc") %>%
-    set.graph.attribute("age", max_age)
-  return(graph)
+# testing dense layout
+source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
+
+plot_network(full_network %E>% filter(w2v_similarity >= 0.5), remove_isolated = TRUE, labels=TRUE, frame=TRUE)
+```
+
+The full network is shown in the following figure, for w = 1, 2, 3, and 4.
+
+```{r out.width = '100%'}
+full_networks = list()
+for (w in 1:4) {
+  full_networks[[w]] = full_network %E>%
+    filter(shared >= w)
 }
 
-feature_network <- function(vocab, max_age, shared_threshold) {
-  vocab_up_to_age = filter(vocab, age <= max_age)
-  feature_links <- make_feature_pairs(lemma_list = vocab_up_to_age) %>%
-    filter(shared >= shared_threshold) %>%
-    select(item, pair, item.definition, pair.definition)
-  graph <- graph_from_data_frame(feature_links, directed=FALSE, vertices=vocab_up_to_age) %>%
-    simplify() %>%
-    set.graph.attribute("name", "Feature") %>%
-    set.graph.attribute("age", max_age)
-  return(graph)
-}
-
-ages <- vocab$age %>% unique() %>% sort()
-assoc_networks <- list()
-feature_networks <- list()
-for (age in ages) {
-  assoc_networks <- append(assoc_networks, list(assoc_network(vocab, age)))
-  feature_networks <- append(feature_networks, list(feature_network(vocab, age, 1)))
-
+#par(mfcol=c(2, 2), mar=c(0.5,0.5,0.5,0.5))
+for (network in full_networks) {
+  plot_network(network, remove_isolated = FALSE, labels=TRUE, frame=TRUE)
 }
@@
 
-## Network Analysis
+## Basic Vocab and Feature Properties
 
-### Large-Scale Structure of Networks
+<!-- ## Basic Network Properties -->
 
-a la Steyvers 2005
+<!-- Some basic properties of networks built from perceptual and conceptual features. -->
+<!-- ```{r, results='asis'} -->
+<!-- max_w <- 4 -->
 
-```{r, results='asis'}
-network_properties <- function(networks) {
-  return( tibble(
-  names = map_chr(networks, ~ .x$name),
-  ages = map_dbl(networks, ~ .x$age) %>%
-    as.integer(),
-  vertices = map_int(networks, vcount),
-  edges = map_dbl(networks, ecount) %>%
-    as.integer(), # for some reason igraph ecount returns double
-  avg_degree = map(networks, degree) %>%
-    map_dbl(mean),
-  avg_shortest_path = map_dbl(networks, mean_distance),
-  diameter = map_dbl(networks, diameter) %>%
-    as.integer(),
-  clustering_coefficient = map_dbl(networks, transitivity),
-  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
-  diameter_random = 0,
-  clustering_coefficient_random = 0) )
-}
+<!-- network_properties <- function(networks) { -->
+<!--   return( tibble( -->
+<!--   name = map_chr(networks, ~ .x$name), -->
+<!--   type = map_chr(networks, ~ .x$type), -->
+<!--   age = map_dbl(networks, ~ .x$age) %>% -->
+<!--     as.integer(), -->
+<!--   w = map_dbl(networks, ~ .x$w) %>% -->
+<!--     as.integer(), -->
+<!--   vertices = map_int(networks, vcount), -->
+<!--   edges = map_dbl(networks, ecount) %>% -->
+<!--     as.integer(), # for some reason igraph ecount returns double -->
+<!--   avg_degree = map(networks, degree) %>% -->
+<!--     map_dbl(mean), -->
+<!--   avg_shortest_path = map_dbl(networks, mean_distance), -->
+<!--   diameter = map_dbl(networks, diameter) %>% -->
+<!--     as.integer(), -->
+<!--   clustering_coefficient = map_dbl(networks, transitivity), -->
+<!--   density = edges / (vertices * (vertices - 1) / 2), -->
+<!--   avg_shortest_path_random = 0, # either estimate or calculate values for random nets -->
+<!--   diameter_random = 0, -->
+<!--   clustering_coefficient_random = density, -->
+<!--   isolates = map_dbl(networks, function (g) sum(degree(g) == 0)), -->
+<!--   components = map_dbl(networks, count_components) %>% -->
+<!--     as.integer() - isolates)) -->
+<!-- } -->
 
-network_properties(assoc_networks) # improve formatting
-network_properties(feature_networks)
-```
+<!-- full_networks <- list() -->
+<!-- perceptual_networks <- list() -->
+<!-- conceptual_networks <- list() -->
+<!-- for (w in 1:max_w) { -->
+<!--   full_networks[[w]] <- full_network %>% -->
+<!--     activate(what = edges) %>% -->
+<!--     filter(shared >= w) %>% -->
+<!--     set.graph.attribute("w", w) -->
 
-Visualize Networks
-```{r}
-plot_network <- function(g, remove_isolated=FALSE) {
-  if (remove_isolated) {
-    g <- delete.vertices(g, degree(g)==0)
-  }
+<!--   perceptual_networks[[w]] <- perceptual_network %>% -->
+<!--     activate(what = edges) %>% -->
+<!--     filter(shared >= w) %>% -->
+<!--     set.graph.attribute("w", w) -->
 
-  plot(g, vertex.label=V(g)$uni_lemma, vertex.shape="none")
-}
+<!--   conceptual_networks[[w]] <- conceptual_network %>% -->
+<!--     activate(what = edges) %>% -->
+<!--     filter(shared >= w) %>% -->
+<!--     set.graph.attribute("w", w) -->
+<!-- } -->
 
-g <- assoc_networks[[6]]
-plot_network(g, remove_isolated = FALSE)
+<!-- networks <- full_networks %>% -->
+<!--   append(perceptual_networks) %>% -->
+<!--   append(conceptual_networks) -->
 
-plot(g,vertex.size=.01,vertex.label.cex=.8,
-     layout=layout.fruchterman.reingold(g, niter=10000, 
-                                        area=40*vcount(g)^2),
-     edge.width=E(g)$weight)
-```
+<!-- our_network_properties <- network_properties(networks) -->
 
-Test Clique Percolation
-```{r}
-### Register Parallelisation (used by clique.community.opt.par())
-cl <- makeCluster(4)
-registerDoParallel(cl)
-getDoParWorkers()
+<!-- our_network_properties %>% -->
+<!--   select(type, w, vertices, edges, avg_degree, diameter, avg_shortest_path, clustering_coefficient) %>% -->
+<!--   kable(format="html", -->
+<!--         escape = FALSE, -->
+<!--         col.names = c("Type", "w", "V", "E", "Average degree", "Diameter", "Average length", "Clustering coefficient"), -->
+<!--         digits = 2, -->
+<!--         align = rep("l", 8)) %>% -->
+<!--   kable_styling(full_width = F) %>% -->
+<!--   collapse_rows(columns = 1:3, valign = "top") -->
+<!-- ``` -->
 
-### Loading Benchmarks
-#1 
-g <- graph(c(1,2,1,3,1,4,2,3,3,4,4,5,4,6,5,6,5,8,5,7,6,8,6,7,7,8,7,9), directed=F)
-#2
-g <- make_graph("Zachary") #the karate network
+<!-- We can compare these networks to those from Hills, noting that we have a different set of words/nodes but that the induced subgraph of those words shared between our analysis and that of Hills should be the same.
+-->
+<!-- ```{r} -->
+<!-- hills_network_properties <- tibble( # table from Hills 2009 -->
+<!--   type = c(rep("all", times=4), rep("perceptual", times=4), rep("conceptual", 4)), -->
+<!--   w = c(1:max_w, 1:max_w, 1:max_w), -->
+<!--   clustering_coefficient = c(0.55, 0.54, 0.58, 0.60, 0.54, 0.54, 0.62, 0.62, 0.88, 0.59, 0.38, 1.00), -->
+<!--   avg_shortest_path = c(1.72, 2.57, 4.96, 3.22, 1.76, 2.69, 5.02, 2.55, 3.08, 1.59, 5.02, 1.00), -->
+<!--   density = c(0.29, 0.10, 0.04, 0.02, 0.27, 0.08, 0.03, 0.01, 0.05, 0.01, 0.0, 0.0), -->
+<!--   components = c(1, 1, 4, 10, 1, 2, 8, 11, 7, 14, 7, 2), -->
+<!--   isolates = c(0, 6, 20, 47, 0, 10, 31, 69, 33, 81, 113, 126) -->
+<!-- ) -->
 
-#Execution of the different implementation of the algorithm
-ptm <- proc.time()
-res1<-clique.community(g,3)
-proc.time() - ptm
-ptm <- proc.time()
-res2<-clique.community.opt(g,3)
-proc.time() - ptm
-ptm <- proc.time()
-res3<-clique.community.opt.par(g,3)
-proc.time() - ptm
+<!-- # convert contents to text -->
+<!-- display_our_properties <- our_network_properties %>% mutate_all(funs(format(., digits=2, trim=TRUE))) -->
+<!-- display_hills_properties <- hills_network_properties %>% mutate_all(funs(paste("(", ., ")", sep=''))) -->
 
-identical(res1,res2)
-identical(res2,res3)
+<!-- # combine text tables for display -->
+<!-- display_properties <- bind_rows(display_our_properties %>% mutate(row = 1:n()), -->
+<!--                                 display_hills_properties %>% mutate(row = 1:n())) %>% -->
+<!--   group_by(row) %>% -->
+<!--   summarise_if(is.character, funs(paste(., collapse=" "))) %>% -->
+<!--   arrange(row) -->
 
-### PLOT
+<!-- # display combined properties -->
+<!-- select(hills_network_properties, type, w) %>% -->
+<!--   bind_cols(select(display_properties, clustering_coefficient, avg_shortest_path, -->
+<!--                    density, components, isolates)) %>% -->
+<!--   kable(format="html", -->
+<!--         escape = FALSE, -->
+<!--         col.names = c("Type", "w", "Clustering Coefficient", "Average length", "Density", "Components", "Isolates"), -->
+<!--         align = rep("l", 7)) %>% -->
+<!--   kable_styling(full_width = F) %>% -->
+<!--   collapse_rows(columns = 1:2, valign = "top") -->
+<!-- ``` -->
 
-#which one? the outcome is always the same
-res <- res3
+<!-- # Clusters -->
 
-## Paint them to different colors
-colbar <- rainbow( length(res)+1 )
-for (i in seq(along=res)) {
-  V(g)[ res[[i]] ]$color <- colbar[i+1]
-}
+<!-- ## Visualize Networks -->
+<!-- ```{r out.width = '100%'} -->
+<!-- networks <- perceptual_networks[2] -->
+<!-- ``` -->
 
-## Paint the vertices in multiple communities to red
-V(g)[ unlist(res)[ duplicated(unlist(res)) ] ]$color <- "red"
+<!-- ## Clique Percolation -->
 
-## Plot with the new colors
-plot(g, layout=layout_with_fr, vertex.label=V(g)$name)
+<!-- Initial Clique Analysis -->
+<!-- ```{r out.width = '100%'} -->
+<!-- trimmed_networks <- map(networks, function (g) delete.vertices(g, degree(g)==0)) -->
 
-#REAL PERFORMANCE TEST
-require(microbenchmark)
-b1<-microbenchmark(t1<-clique.community(g,3),times = 100,unit = 'ms')
-b2<-microbenchmark(t2<-clique.community.opt(g,3),times = 100,unit = 'ms')
-b3<-microbenchmark(t2<-clique.community.opt.par(g,3),times = 100,unit = 'ms')
-rbind(b1,b2,b3)
-mean(b1$time)/mean(b2$time)
-mean(b2$time)/mean(b3$time)
-mean(b1$time)/mean(b3$time)
-```
+<!-- # cl <- makeCluster(3) -->
+<!-- # registerDoParallel(cl) -->
+<!-- # getDoParWorkers() -->
+<!-- ## Plot with the new colors -->
+<!-- for (net in networks) { -->
+<!--   for (k in 3:4) { -->
+<!--     clusters <- clique.community.opt(net,k) -->
+<!--     plot_network(net, clusters = clusters, labels=FALSE) -->
+<!--   } -->
+<!-- } -->
+<!-- # stopCluster(cl) -->
+<!-- ``` -->
 
-Initial Clique Analysis
-```{r}
-age <- 20
-g <- assoc_networks[[age - 15]]
-g <- delete.vertices(g, degree(g)==0)
-res <- clique.community.opt(g,3)
+<!-- Dynamic Visualization -->
+<!-- ```{r} -->
+<!-- conceptual_clusters <- membership(cluster_walktrap(conceptual_network)) -->
 
-## Paint them to different colors
-colbar <- rainbow( length(res)+1 )
-for (i in seq(along=res)) {
-  V(g)[ res[[i]] ]$color <- colbar[i+1]
-}
+<!-- # Convert to object suitable for networkD3 -->
+<!-- conceptual_d3 <- igraph_to_networkD3(conceptual_network, group = conceptual_clusters) -->
 
-## Paint the vertices in multiple communities to red
-V(g)[ unlist(res)[ duplicated(unlist(res)) ] ]$color <- "red"
-
-## Plot with the new colors
-plot(g, layout=layout_with_fr, vertex.label=V(g)$uni_lemma)
-```
-
-Dynamic Visualization
-```{r}
-karate <- make_graph("Zachary")
-wc <- cluster_walktrap(karate)
-members <- membership(wc)
-
-# Convert to object suitable for networkD3
-karate_d3 <- igraph_to_networkD3(karate, group = members)
-
-# Create force directed network plot
-forceNetwork(Links = karate_d3$links, Nodes = karate_d3$nodes,
-             Source = 'source', Target = 'target', NodeID = 'name',
-             Group = 'group')
-```
+<!-- # Create force directed network plot -->
+<!-- forceNetwork(Links = conceptual_d3$links, Nodes = conceptual_d3$nodes, -->
+<!--              Source = 'source', Target = 'target', NodeID = 'name', -->
+<!--              Group = 'group') -->
+<!-- ``` -->

### 2018-07-26 helpers/all_helper.r

@@ -1,5 +1,6 @@
 source("wb_helper.r")
 source("assoc_helper.r")
 source("feature_helper.r")
+source("word2vec_helper.r")
 source("plot_helper.r")
 source("clique_percolation.r")

### 2018-07-26 helpers/feature_helper.r

@@ -1,60 +1,21 @@
-make_feature_pairs <- function(lemma_list, features) {
-  wb <- lemma_list
-  
-  # Here I still should deal with words in parenthesis (homophony/polysemy), e.g., chiken (animal) vs. chiken (food), etc...
-  
-  item_feat <- wb %>%
-    left_join(features) %>%
-    rename(item.definition = uni_lemma,
-           item_feat = Feature) %>%
-    filter(!is.na(item_feat)) %>%
-    select(item, item.definition, item_feat)
-  
-  
-  item_feat_list <- (wb %>%
-                       filter(item %in% item_feat$item) %>%
-                       select(item))$item
-  
-  # List these words pair-wise and compute the number of shared feature for each pair
-  item_pair <- expand.grid(item = item_feat_list,
-                           pair = item_feat_list)
-  
-  pair_feat <- item_feat %>%
-    rename(pair = item,
-           pair_feat = item_feat,
-           pair.definition = item.definition)
-  
-  item_feat_pair <- left_join(item_feat, item_pair)
-  
-  item_pair_feat <- item_feat_pair %>%
-    left_join(pair_feat)
-  
-  item_pair_shared <- item_pair_feat %>%
-    group_by(item, item.definition, pair, pair.definition) %>%
-    summarise(shared = sum(pair_feat == item_feat)) %>%
-    filter(item > pair) %>% # removes item = pair and duplicates
-    ungroup()
-  
-  return(item_pair_shared)
-}
-
 load_features <- function() {
   features <- read_delim("data/MacRae.csv", delim = ",") %>%
-    select(Concept, Feature, WB_Label, BR_Label) %>%
-    rename(uni_lemma=Concept)
+    select(Concept, Feature, WB_Label, BR_Label)# %>%
+  #rename(uni_lemma=Concept)
   
   return(features)
 }
 
-feature_network <- function(vocab, features, feature_types, shared_threshold) {
-  feature_links <- make_feature_pairs(lemma_list = vocab,
-                                      features = filter(features, BR_Label %in% feature_types)) %>%
-    filter(shared >= shared_threshold) %>%
-    select(item, pair, shared)
+make_feature_links <- function(vocab, feature_types) {
+  features <- load_features() %>%                  
+    filter(Concept %in% vocab$uni_lemma) %>% # remove unneccessary features
+    filter(BR_Label %in% feature_types) %>%  # filter to feature type
[…]

### 2018-07-26 helpers/plot_helper.r

@@ -2,7 +2,21 @@ plot_network <- function(g, name=NA, remove_isolated=FALSE, frame=FALSE, labels=
   if (remove_isolated) {
     g <- delete.vertices(g, degree(g)==0)
   }
-  l <- layout_with_fr(g) #layout.forceatlas2(g, iterations=2000, plotstep=5000) #layout_with_fr(g)
+  l <- layout_with_fr(g, niter = 500)
+  # l <- layout.forceatlas2(g,
+  #                         iterations=1500,
+  #                         plotstep=500,
+  #                         directed = FALSE,
+  #                         delta = 1,
+  #                         gravity = 100,
+  #                         k = 10000)
+  
+  # rescale
+  x_size <- max(l[,1]) - min(l[,1])
+  y_size <- max(l[,2]) - min(l[,2])
+  max_size <- max(x_size, y_size)
+  
+  l <- l / max_size
   
   if (!is.null(clusters)) {
     ## Paint them to different colors
@@ -16,7 +30,39 @@ plot_network <- function(g, name=NA, remove_isolated=FALSE, frame=FALSE, labels=
   }
   
   if (labels) {
-    plot(g, layout=l, vertex.label=V(g)$uni_lemma, edge.width=0.5, vertex.size=4, frame=frame)
+    plot(g,
+         layout=l,
+         frame=frame,
+         rescale=FALSE,
+         asp=0,
+         xlim=c(min(l[,1]), max(l[,1])),
+         ylim=c(min(l[,2]), max(l[,2])),
+         
+         # === vertex
+         vertex.color = rgb(0.0,0.0,0.7,0.5),                        # Node color
+         vertex.frame.color = NA,                 # Node border color
+         vertex.shape="circle",                        # One of “none”, “circle”, “square”, “csquare”, “rectangle” “crectangle”, “vrectangle”, “pie”, “raster”, or “sphere”
+         vertex.size=2,                               # Size of the node (default is 15)
+         vertex.size2=NA,                              # The second size of the node (e.g. for a rectangle)
+         
+         # === vertex label
+         vertex.label=V(g)$uni_lemma,                   # Character vector used to label the nodes
+         vertex.label.color="black",
+         vertex.label.family="Helvetica",                  # Font family of the label (e.g.“Times”, “Helvetica”)
+         vertex.label.font=1,                          # Font: 1 plain, 2 bold, 3, italic, 4 bold italic, 5 symbol
+         vertex.label.cex=0.5,                           # Font size (multiplication factor, device-dependent)
[…]

### 2018-07-26 helpers/wb_helper.r

@@ -140,29 +140,29 @@ make_aoa_dataframe <- function(lang, lang_form = "WS", lex_class = "nouns") {
 }
 
 ######################################################################################################################
-#make a final dataframe
-make_vocab_dataframe_helper <- function(word_aoa) {
-  ages <- word_aoa$age %>% unique() %>% sort()
-  tb <- tibble()
-  for (i in ages) {
-    new_vocab <- word_aoa %>% filter(age = i)
-    tb <- bind_rows
-    rem_words <- word_aoa %>% filter(age >= i)
-    rem_lemma <- c(rem_words$uni_lemma)
-    rem_def <- c(rem_words$definition)
-    rem_item<- c(rem_words$item)
-    corr_age <- rep(i, times = length(rem_lemma))
-    curr_df <- data.frame(corr_age, rem_item, rem_lemma, rem_def)
-    df <- rbind(df, curr_df)
-  }  
-  df <- df %>% rename(uni_lemma = rem_lemma, definition=rem_def, item=rem_item)%>%
-    left_join(word_aoa %>% select(item, age)) %>%
-    mutate(learned = as.numeric(age == corr_age)) %>%
-    select(corr_age, item, definition, uni_lemma,learned) %>%
-    rename(age = corr_age) %>%
-    arrange(age, item)
-  return(df)
-}
+# #make a final dataframe
+# make_vocab_dataframe_helper <- function(word_aoa) {
+#   ages <- word_aoa$age %>% unique() %>% sort()
+#   tb <- tibble()
+#   for (i in ages) {
+#     new_vocab <- word_aoa %>% filter(age = i)
+#     tb <- bind_rows
+#     rem_words <- word_aoa %>% filter(age >= i)
+#     rem_lemma <- c(rem_words$uni_lemma)
+#     rem_def <- c(rem_words$definition)
+#     rem_item<- c(rem_words$item)
+#     corr_age <- rep(i, times = length(rem_lemma))
+#     curr_df <- data.frame(corr_age, rem_item, rem_lemma, rem_def)
+#     df <- rbind(df, curr_df)
+#   }  
+#   df <- df %>% rename(uni_lemma = rem_lemma, definition=rem_def, item=rem_item)%>%
+#     left_join(word_aoa %>% select(item, age)) %>%
+#     mutate(learned = as.numeric(age == corr_age)) %>%
+#     select(corr_age, item, definition, uni_lemma,learned) %>%
[…]

### 2018-07-26 helpers/word2vec_helper.r

@@ -1,0 +1,16 @@
+load_w2v <- function() {
+  w2v <- read_delim("data/w2v_pair.csv", delim = ",") %>%
+    rename(from = item.definition, to = pair.definition, w2v_similarity = sim) %>%
+    #filter(w2v_similarity > 0.0) %>%
+    filter(from < to) # remove duplicates
+
+  return(w2v)
+}
+
+make_w2v_links <- function(vocab) {
+  w2v <- load_w2v() %>%
+    filter(from %in% vocab$uni_lemma &
+             to %in% vocab$uni_lemma)
+  
+  return(w2v)
+}

### 2018-08-03 Main.Rmd
Progress on clustering comparison.

@@
 ---
-title: "Replication of Hills 2009"
+title: "Word2Vec Analysis"
 author: "Isaac Scheinfeld"
@@
 ---
-# Background
-
-...
-
 # Networks
@@
   distinct(uni_lemma, .keep_all = TRUE) %>%
-  select(uni_lemma, definition, age)
+  select(uni_lemma, definition, age, category)
 ```
@@
 
-```{r warning=FALSE}
+```{r warning=FALSE, message=FALSE}
 features <- load_features()
+w2v <- load_w2v()
 
@@
   filter(uni_lemma %in% features$Concept) # filter to words with features
+
+vocab <- hills_vocab %>%
+  filter(uni_lemma %in% w2v$from | uni_lemma %in% w2v$to)
 ```
 
-To begin our analysis, we only consider the words for which feature data are available, an overlap of `r nrow(vocab)` in our data compared to Hills' 130.
+To begin our analysis, we only consider the words for which feature data are available, an overlap of `r nrow(hills_vocab)` in our data compared to Hills' 130.
+Then we filter the `r nrow(hills_vocab) - nrow(vocab)` words for which word2vec data is not available, for a final vocabulary of `r nrow(vocab)`.
 
-## Word2Vec
+## Build Network
 
-## Build Networks
-
-Using vocabulary obtained by 30 months and the same McRae features as Hills, we construct networks from perceptual and conceptual features. We track the number of features that generate each edge.
+Using vocabulary obtained by 30 months and the same McRae features as Hills, we construct a network with edge attributes for perceptual and conceptual features, and for word2vec similarity.
 
 ```{r message=FALSE}
-# perceptual and conceptual McRae features
+# perceptual and conceptual McRae feature types
 perceptual_features = c("sound", "taste", "smell", "tactile",
@@
 # count shared features between words in vocabulary
-perceptual_links <- make_feature_links(vocab = hills_vocab,
+perceptual_links <- make_feature_links(vocab = vocab,
                                        feature_types = perceptual_features) %>%
@@
 
-conceptual_links <- make_feature_links(vocab = hills_vocab,
+conceptual_links <- make_feature_links(vocab = vocab,
                                        feature_types = conceptual_features) %>%
@@
 # get word2vec distance between words in vocabulary
-w2v_links <- make_w2v_links(vocab = hills_vocab) #TODO still problem w/ vocab matching w2v data
+w2v_links <- make_w2v_links(vocab = vocab) #TODO still problem w/ vocab matching w2v data
 
@@
 
-full_network <- graph_from_data_frame(links, vertices = hills_vocab, directed = FALSE) %>%
+network <- graph_from_data_frame(links, vertices = vocab, directed = FALSE) %>%
   as_tbl_graph()
@@
 
-## The Full Network
+## The Network
 
-### Network statistics and small-world analyses
+First we generate a display layout for the network, based on the word2vec data.
 
 ```{r}
-# testing dense layout
 source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
 
-plot_network(full_network %E>% filter(w2v_similarity >= 0.5), remove_isolated = TRUE, labels=TRUE, frame=TRUE)
+layout <- layout_network(network %E>% mutate(weights = w2v_similarity))
 ```
 
-The full network is shown in the following figure, for w = 1, 2, 3, and 4.
+We can examine the networks generated by filtering edges with a word2vec similarity threshold.
 
-```{r out.width = '100%'}
-full_networks = list()
-for (w in 1:4) {
-  full_networks[[w]] = full_network %E>%
-    filter(shared >= w)
+```{r out.width = '100%', fig.height = 5, fig.width = 5}
+source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
+
+par(mfrow=c(2, 2), mar=c(2,0.4,0.8,0.4)) # row x col, column first
+
+for (s in seq(0.35, 0.5, 0.05)) {
+  plot_network(network %E>% filter(w2v_similarity > s),
+               layout = layout,
+               labels=TRUE,
+               title=str_glue("Threshold = {s}"))
 }
 
-#par(mfcol=c(2, 2), mar=c(0.5,0.5,0.5,0.5))
-for (network in full_networks) {
-  plot_network(network, remove_isolated = FALSE, labels=TRUE, frame=TRUE)
-}
 ```
 
-## Basic Vocab and Feature Properties
+Test igraph clustering algorithms
 
-<!-- ## Basic Network Properties -->
+```{r fig.height = 5, fig.width = 5}
+source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
 
-<!-- Some basic properties of networks built from perceptual and conceptual features. -->
-<!-- ```{r, results='asis'} -->
-<!-- max_w <- 4 -->
+# cluster_edge_betweenness - doesn't cluster reasonably, treats weights as distances?
 
-<!-- network_properties <- function(networks) { -->
-<!--   return( tibble( -->
-<!--   name = map_chr(networks, ~ .x$name), -->
-<!--   type = map_chr(networks, ~ .x$type), -->
-<!--   age = map_dbl(networks, ~ .x$age) %>% -->
-<!--     as.integer(), -->
-<!--   w = map_dbl(networks, ~ .x$w) %>% -->
-<!--     as.integer(), -->
-<!--   vertices = map_int(networks, vcount), -->
-<!--   edges = map_dbl(networks, ecount) %>% -->
-<!--     as.integer(), # for some reason igraph ecount returns double -->
-<!--   avg_degree = map(networks, degree) %>% -->
-<!--     map_dbl(mean), -->
-<!--   avg_shortest_path = map_dbl(networks, mean_distance), -->
-<!--   diameter = map_dbl(networks, diameter) %>% -->
-<!--     as.integer(), -->
-<!--   clustering_coefficient = map_dbl(networks, transitivity), -->
-<!--   density = edges / (vertices * (vertices - 1) / 2), -->
-<!--   avg_shortest_path_random = 0, # either estimate or calculate values for random nets -->
-<!--   diameter_random = 0, -->
-<!--   clustering_coefficient_random = density, -->
-<!--   isolates = map_dbl(networks, function (g) sum(degree(g) == 0)), -->
-<!--   components = map_dbl(networks, count_components) %>% -->
-<!--     as.integer() - isolates)) -->
-<!-- } -->
+# cluster_infomap - returns one cluster
 
-<!-- full_networks <- list() -->
-<!-- perceptual_networks <- list() -->
-<!-- conceptual_networks <- list() -->
-<!-- for (w in 1:max_w) { -->
-<!--   full_networks[[w]] <- full_network %>% -->
-<!--     activate(what = edges) %>% -->
-<!--     filter(shared >= w) %>% -->
-<!--     set.graph.attribute("w", w) -->
+# cluster_label_prop - returns one cluster
 
-<!--   perceptual_networks[[w]] <- perceptual_network %>% -->
-<!--     activate(what = edges) %>% -->
-<!--     filter(shared >= w) %>% -->
-<!--     set.graph.attribute("w", w) -->
+# cluster_optimal - too computationally intensive for laptop, may not be possible (NP)
 
-<!--   conceptual_networks[[w]] <- conceptual_network %>% -->
-<!--     activate(what = edges) %>% -->
-<!--     filter(shared >= w) %>% -->
-<!--     set.graph.attribute("w", w) -->
-<!-- } -->
+plot_network(network, layout = layout,
+             clusters = cluster_fast_greedy(network, weights = E(network)$w2v_similarity)$membership,
+             labels=TRUE, frame=TRUE)
 
-<!-- networks <- full_networks %>% -->
-<!--   append(perceptual_networks) %>% -->
-<!--   append(conceptual_networks) -->
+plot_network(network, layout = layout,
+             clusters = cluster_leading_eigen(network, weights = E(network)$w2v_similarity)$membership,
+             labels=TRUE, frame=TRUE)
 
-<!-- our_network_properties <- network_properties(networks) -->
+plot_network(network, layout = layout,
+             clusters = cluster_louvain(network, weights = E(network)$w2v_similarity)$membership,
+             labels=TRUE, frame=TRUE)
 
-<!-- our_network_properties %>% -->
-<!--   select(type, w, vertices, edges, avg_degree, diameter, avg_shortest_path, clustering_coefficient) %>% -->
-<!--   kable(format="html", -->
-<!--         escape = FALSE, -->
-<!--         col.names = c("Type", "w", "V", "E", "Average degree", "Diameter", "Average length", "Clustering coefficient"), -->
-<!--         digits = 2, -->
-<!--         align = rep("l", 8)) %>% -->
-<!--   kable_styling(full_width = F) %>% -->
-<!--   collapse_rows(columns = 1:3, valign = "top") -->
-<!-- ``` -->
+plot_network(network, layout = layout,
+             clusters = cluster_spinglass(network, weights = E(network)$w2v_similarity)$membership,
+             labels=TRUE, frame=TRUE)
 
-<!-- We can compare these networks to those from Hills, noting that we have a different set of words/nodes but that the induced subgraph of those words shared between our analysis and that of Hills should be the same.
--->
-<!-- ```{r} -->
-<!-- hills_network_properties <- tibble( # table from Hills 2009 -->
-<!--   type = c(rep("all", times=4), rep("perceptual", times=4), rep("conceptual", 4)), -->
-<!--   w = c(1:max_w, 1:max_w, 1:max_w), -->
-<!--   clustering_coefficient = c(0.55, 0.54, 0.58, 0.60, 0.54, 0.54, 0.62, 0.62, 0.88, 0.59, 0.38, 1.00), -->
-<!--   avg_shortest_path = c(1.72, 2.57, 4.96, 3.22, 1.76, 2.69, 5.02, 2.55, 3.08, 1.59, 5.02, 1.00), -->
-<!--   density = c(0.29, 0.10, 0.04, 0.02, 0.27, 0.08, 0.03, 0.01, 0.05, 0.01, 0.0, 0.0), -->
-<!--   components = c(1, 1, 4, 10, 1, 2, 8, 11, 7, 14, 7, 2), -->
-<!--   isolates = c(0, 6, 20, 47, 0, 10, 31, 69, 33, 81, 113, 126) -->
-<!-- ) -->
-
-<!-- # convert contents to text -->
-<!-- display_our_properties <- our_network_properties %>% mutate_all(funs(format(., digits=2, trim=TRUE))) -->
-<!-- display_hills_properties <- hills_network_properties %>% mutate_all(funs(paste("(", ., ")", sep=''))) -->
-
-<!-- # combine text tables for display -->
-<!-- display_properties <- bind_rows(display_our_properties %>% mutate(row = 1:n()), -->
-<!--                                 display_hills_properties %>% mutate(row = 1:n())) %>% -->
-<!--   group_by(row) %>% -->
-<!--   summarise_if(is.character, funs(paste(., collapse=" "))) %>% -->
-<!--   arrange(row) -->
-
-<!-- # display combined properties -->
-<!-- select(hills_network_properties, type, w) %>% -->
-<!--   bind_cols(select(display_properties, clustering_coefficient, avg_shortest_path, -->
-<!--                    density, components, isolates)) %>% -->
-<!--   kable(format="html", -->
-<!--         escape = FALSE, -->
-<!--         col.names = c("Type", "w", "Clustering Coefficient", "Average length", "Density", "Components", "Isolates"), -->
-<!--         align = rep("l", 7)) %>% -->
-<!--   kable_styling(full_width = F) %>% -->
-<!--   collapse_rows(columns = 1:2, valign = "top") -->
-<!-- ``` -->
-
-<!-- # Clusters -->
-
-<!-- ## Visualize Networks -->
-<!-- ```{r out.width = '100%'} -->
-<!-- networks <- perceptual_networks[2] -->
-<!-- ``` -->
-
-<!-- ## Clique Percolation -->
-
-<!-- Initial Clique Analysis -->
-<!-- ```{r out.width = '100%'} -->
-<!-- trimmed_networks <- map(networks, function (g) delete.vertices(g, degree(g)==0)) -->
-
-<!-- # cl <- makeCluster(3) -->
-<!-- # registerDoParallel(cl) -->
-<!-- # getDoParWorkers() -->
-<!-- ## Plot with the new colors -->
-<!-- for (net in networks) { -->
-<!--   for (k in 3:4) { -->
-<!--     clusters <- clique.community.opt(net,k) -->
-<!--     plot_network(net, clusters = clusters, labels=FALSE) -->
-<!--   } -->
-<!-- } -->
-<!-- # stopCluster(cl) -->
-<!-- ``` -->
-
-<!-- Dynamic Visualization -->
-<!-- ```{r} -->
-<!-- conceptual_clusters <- membership(cluster_walktrap(conceptual_network)) -->
-
-<!-- # Convert to object suitable for networkD3 -->
-<!-- conceptual_d3 <- igraph_to_networkD3(conceptual_network, group = conceptual_clusters) -->
-
-<!-- # Create force directed network plot -->
-<!-- forceNetwork(Links = conceptual_d3$links, Nodes = conceptual_d3$nodes, -->
-<!--              Source = 'source', Target = 'target', NodeID = 'name', -->
-<!--              Group = 'group') -->
-<!-- ``` -->
+plot_network(network, layout = layout,
+             clusters = cluster_walktrap(network, weights = E(network)$w2v_similarity)$membership,
+             labels=TRUE, frame=TRUE)
+```

### 2018-08-03 helpers/all_helper.r

@@ -4,3 +4,4 @@ source("feature_helper.r")
 source("word2vec_helper.r")
 source("plot_helper.r")
 source("clique_percolation.r")
+source("cluster_helper.r")

### 2018-08-03 helpers/plot_helper.r

@@ -1,46 +1,62 @@
-plot_network <- function(g, name=NA, remove_isolated=FALSE, frame=FALSE, labels=FALSE, clusters=NULL) {
-  if (remove_isolated) {
-    g <- delete.vertices(g, degree(g)==0)
-  }
-  l <- layout_with_fr(g, niter = 500)
-  # l <- layout.forceatlas2(g,
-  #                         iterations=1500,
-  #                         plotstep=500,
-  #                         directed = FALSE,
-  #                         delta = 1,
-  #                         gravity = 100,
-  #                         k = 10000)
+layout_network <- function(g) {
+  l <- layout.forceatlas2(g %E>% select(weights),
+                          iterations=40000,
+                          plotstep=100000,
+                          directed = FALSE,
+                          delta = 3,
+                          gravity = 1,
+                          k = 10000)
   
-  # rescale
-  x_size <- max(l[,1]) - min(l[,1])
+  # move disconnected vertices to 0, 0
+  l[degree(g) == 0,] <- 0
+
+  # move them to bottom
   y_size <- max(l[,2]) - min(l[,2])
+  l[degree(g) == 0,2] <- min(l[,2]) - (y_size / 6)
+
+  # spread them out
+  num_disconnected <- length(l[degree(g) == 0,1])
+  x_size <- max(l[,1]) - min(l[,1])
+  l[degree(g) == 0,1] <- (0:(num_disconnected - 1) / (num_disconnected - 1)) * x_size + min(l[,1])
+  
+  return(l)
+}
+
+plot_network <- function(g, layout = NULL, name=NA, frame=FALSE, labels=FALSE, clusters=NULL, title = NULL) {
+  
+  # layout if no layout provided
+  if (is.null(layout)) {
+    layout <- layout_with_fr(g, niter = 500)
+  }
+  
+  # rescale layout
+  x_size <- max(layout[,1]) - min(layout[,1])
+  y_size <- max(layout[,2]) - min(layout[,2])
   max_size <- max(x_size, y_size)
   
-  l <- l / max_size
+  layout <- layout / max_size
   
+  # color clusters
   if (!is.null(clusters)) {
-    ## Paint them to different colors
-    colbar <- rainbow(length(clusters) + 1)
-    for (i in seq(along=clusters)) {
-      V(g)[ clusters[[i]] ]$color <- colbar[i+1]
-    }
+    V(g)$color <- clusters+1
     
[…]

### 2018-08-03 helpers/wb_helper.r

@@ -18,13 +18,13 @@ import_all_library<- function(){
 get_lang_item_data <- function(lang, lang_form = "WS", lex_class = "nouns") {
 
   item_data <- get_item_data(language = lang, form = lang_form) %>%
-    select(num_item_id, definition, type, lexical_class, uni_lemma) %>%
+    select(num_item_id, definition, type, lexical_class, uni_lemma, category) %>%
     filter(type == "word", lexical_class == lex_class) %>%
     rename(item = num_item_id)
   
   #Initialize every item as NA (NOT yet learnt)
   lang_item <- item_data %>%
-    select(item, definition, uni_lemma) %>%
+    select(item, definition, uni_lemma, category) %>%
     mutate(age = NA)
   
   return(lang_item)
@@ -35,6 +35,7 @@ get_lang_item_data <- function(lang, lang_form = "WS", lex_class = "nouns") {
 get_lang_admin_data <- function(lang, lang_form = "WS") {
   #get the kids' data_id from every age
   admin_data <- get_administration_data() %>%
+    filter(source_name == "Marchman (Norming)") %>%
     filter(form == lang_form, !is.na(production), language == lang) %>%
     select(data_id, age) %>%
     arrange(age)

### 2018-08-03 helpers/word2vec_helper.r

@@ -1,9 +1,21 @@
 load_w2v <- function() {
   w2v <- read_delim("data/w2v_pair.csv", delim = ",") %>%
     rename(from = item.definition, to = pair.definition, w2v_similarity = sim) %>%
-    #filter(w2v_similarity > 0.0) %>%
-    filter(from < to) # remove duplicates
+    # filter(w2v_similarity > 0.000001) %>%
+    filter(from < to) %>% # remove duplicates
+    trim_w2v()
 
+  return(w2v)
+}
+
+trim_w2v <- function(w2v) {
+  w2v <- w2v %>%
+    mutate(from = gsub(" \\s*\\([^\\)]+\\)","", from)) %>% # remove parenthesized
+    mutate(to = gsub(" \\s*\\([^\\)]+\\)","", to)) %>%
+    group_by(from, to) %>%
+    summarise(w2v_similarity = max(w2v_similarity)) %>%
+    filter(from < to) # remove duplicates created during trimming
+  
   return(w2v)
 }
 

### 2018-08-28 Hills2009Replication.Rmd
Presentation prep

@@
 
-# Methods
+# Preparation
+
+This analysis requires a working copy of CFinder and the CFinder license in the same directory (necessary for running CFinder). The following must point to the command line executable:
+
+```{r}
+cfinder_program <- "./CFinder_commandline_mac"
+```
 
@@
 library(networkD3)
-library(ForceAtlas2)
+library(formattable)
+library(viridis)
 
@@
   trim_all_unilemma() %>%
-  trim_all_definition()
+  trim_all_definition() %>%
+  arrange(age) %>%            # keep first age for duplicates arising from trimming
+  distinct(uni_lemma, .keep_all = TRUE) %>%
+  select(uni_lemma, definition, age, category)
 ```
@@
 
-```{r warning=FALSE}
-features <- load_features()
-
+```{r warning=FALSE, message=FALSE}
 vocab <- full_vocab %>%
   filter(age <= 30) %>%
-  filter(uni_lemma %in% features$uni_lemma) %>%
-  distinct(uni_lemma, .keep_all = TRUE)
+  filter_to_features()
 ```
 
-Only the words for which feature data are available are considered, an overlap of `r nrow(vocab)` in our data compared to Hills' 130.
+Only the words aquired by 30 months for which feature data are available are considered, an overlap of `r nrow(vocab)` in our data compared to Hills' 130.
 
@@
 
-full_network <- feature_network(vocab, features, shared_threshold = 1,
-                                feature_types = c(perceptual_features,
-                                                  conceptual_features)) %>%
-                  set.graph.attribute("type", "both") %>%
+feature_links <-
+  make_feature_links(vocab = vocab, feature_types = union(perceptual_features, conceptual_features))
+perceptual_links <-
+  make_feature_links(vocab = vocab, feature_types = perceptual_features)
+conceptual_links <-
+  make_feature_links(vocab = vocab, feature_types = conceptual_features)
+
+feature_network <- graph_from_data_frame(feature_links, vertices = vocab, directed = FALSE) %>%
+  as_tbl_graph() %E>%
+  mutate(weight = shared) %>%
+  set.graph.attribute("type", "Features") %>%
   set.graph.attribute("age", 30)
 
-perceptual_network <- feature_network(vocab, features, shared_threshold = 1,
-                                      feature_types = perceptual_features) %>%
-                        set.graph.attribute("type", "perceptual") %>%
+perceptual_network <- graph_from_data_frame(perceptual_links, vertices = vocab, directed = FALSE) %>%
+  as_tbl_graph() %E>%
+  mutate(weight = shared) %>%
+  set.graph.attribute("type", "Perceptual") %>%
   set.graph.attribute("age", 30)
 
-conceptual_network <- feature_network(vocab, features, shared_threshold = 1,
-                                      feature_types = conceptual_features) %>%
-                        set.graph.attribute("type", "conceptual") %>%
+conceptual_network <- graph_from_data_frame(conceptual_links, vertices = vocab, directed = FALSE) %>%
+  as_tbl_graph() %E>%
+  mutate(weight = shared) %>%
+  set.graph.attribute("type", "Conceptual") %>%
   set.graph.attribute("age", 30)
@@
 
-## The Full Network
+## Network statistics and small-world analyses
 
-### Network statistics and small-world analyses
+The network are shown in the following figure, for w = 1, 2, 3, and 4.
 
-```{r}
-# testing dense layout
-source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
+```{r out.width = '25%', fig.asp=1}
+par(oma=c(0,0,0.2,0))
 
-plot_network(full_network %E>% filter(shared >= 2), remove_isolated = TRUE, labels=TRUE, frame=TRUE)
-```
-
-The full network is shown in the following figure, for w = 1, 2, 3, and 4.
-
-```{r out.width = '100%'}
-full_networks = list()
+for (network in list(feature_network, perceptual_network, conceptual_network)) {
   for (w in 1:4) {
-  full_networks[[w]] = full_network %E>%
-    filter(shared >= w)
+    net <- network %E>% filter(shared >= w)
+    layout <- layout_with_fr(net)
+    plot_vocab_network(net, plot_title = title(str_glue("{net$type} w={w}"), cex.main=2), frame=FALSE, layout = layout, labels="")
   }
-
-#par(mfcol=c(2, 2), mar=c(0.5,0.5,0.5,0.5))
-for (network in full_networks) {
-  plot_network(network, remove_isolated = FALSE, labels=TRUE, frame=TRUE)
 }
@@
 
-## Basic Vocab and Feature Properties
+Some basic properties of networks built from perceptual and conceptual features.
 
-## Basic Network Properties
+```{r, results='asis'}
+network_properties <- function(network) {
+  return( tibble(
+    type = network$type,
+    age = network$age,
+    w = network$w,
+    vertices = vcount(network),
+    edges = ecount(network),
+    avg_degree = mean(degree(network)),
+    avg_distance = mean_distance(network),
+    diameter = diameter(network),
+    clustering_coef = transitivity(network),
+    density = edges / (vertices * (vertices - 1) / 2),
+    clustering_coefficient_random = density,
+    isolates = sum(degree(network) == 0),
+    components = count_components(network) - isolates
+  ))
+}
 
-Some basic properties of networks built from perceptual and conceptual features.
-```{r, results='asis'}
 max_w <- 4
 
-network_properties <- function(networks) {
-  return( tibble(
-  name = map_chr(networks, ~ .x$name),
-  type = map_chr(networks, ~ .x$type),
-  age = map_dbl(networks, ~ .x$age) %>%
-    as.integer(),
-  w = map_dbl(networks, ~ .x$w) %>%
-    as.integer(),
-  vertices = map_int(networks, vcount),
-  edges = map_dbl(networks, ecount) %>%
-    as.integer(), # for some reason igraph ecount returns double
-  avg_degree = map(networks, degree) %>%
-    map_dbl(mean),
-  avg_shortest_path = map_dbl(networks, mean_distance),
-  diameter = map_dbl(networks, diameter) %>%
-    as.integer(),
-  clustering_coefficient = map_dbl(networks, transitivity),
-  density = edges / (vertices * (vertices - 1) / 2),
-  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
-  diameter_random = 0,
-  clustering_coefficient_random = density,
-  isolates = map_dbl(networks, function (g) sum(degree(g) == 0)),
-  components = map_dbl(networks, count_components) %>%
-    as.integer() - isolates))
-}
+feature_networks <- map(1:max_w, function(w) {
+  feature_network %>%
+    filter(shared >= w) %>%
+    set.graph.attribute("w",w)})
+perceptual_networks <- map(1:max_w, function(w) {
+  perceptual_network %>%
+    filter(shared >= w) %>%
+    set.graph.attribute("w",w)})
+conceptual_networks <- map(1:max_w, function(w) {
+  conceptual_network %>%
+    filter(shared >= w) %>%
+    set.graph.attribute("w",w)})
 
-full_networks <- list()
-perceptual_networks <- list()
-conceptual_networks <- list()
-for (w in 1:max_w) {
-  full_networks[[w]] <- full_network %>%
-    activate(what = edges) %>%
-    filter(shared >= w) %>%
-    set.graph.attribute("w", w)
-
-  perceptual_networks[[w]] <- perceptual_network %>%
-    activate(what = edges) %>%
-    filter(shared >= w) %>%
-    set.graph.attribute("w", w)
-
-  conceptual_networks[[w]] <- conceptual_network %>%
-    activate(what = edges) %>%
-    filter(shared >= w) %>%
-    set.graph.attribute("w", w)
-}
-
-networks <- full_networks %>%
+networks <- feature_networks %>%
   append(perceptual_networks) %>%
@@
 
-our_network_properties <- network_properties(networks)
-
-our_network_properties %>%
-  select(type, w, vertices, edges, avg_degree, diameter, avg_shortest_path, clustering_coefficient) %>%
-  kable(format="html",
-        escape = FALSE,
-        col.names = c("Type", "w", "V", "E", "Average degree", "Diameter", "Average length", "Clustering coefficient"),
-        digits = 2,
-        align = rep("l", 8)) %>%
-  kable_styling(full_width = F) %>%
-  collapse_rows(columns = 1:3, valign = "top")
+properties <- bind_rows(map(networks, network_properties))
 ```
@@
 We can compare these networks to those from Hills, noting that we have a different set of words/nodes but that the induced subgraph of those words shared between our analysis and that of Hills should be the same.
+
 ```{r}
-hills_network_properties <- tibble( # table from Hills 2009
-  type = c(rep("all", times=4), rep("perceptual", times=4), rep("conceptual", 4)),
-  w = c(1:max_w, 1:max_w, 1:max_w),
-  clustering_coefficient = c(0.55, 0.54, 0.58, 0.60, 0.54, 0.54, 0.62, 0.62, 0.88, 0.59, 0.38, 1.00),
-  avg_shortest_path = c(1.72, 2.57, 4.96, 3.22, 1.76, 2.69, 5.02, 2.55, 3.08, 1.59, 5.02, 1.00),
-  density = c(0.29, 0.10, 0.04, 0.02, 0.27, 0.08, 0.03, 0.01, 0.05, 0.01, 0.0, 0.0),
-  components = c(1, 1, 4, 10, 1, 2, 8, 11, 7, 14, 7, 2),
-  isolates = c(0, 6, 20, 47, 0, 10, 31, 69, 33, 81, 113, 126)
-)
-
-# convert contents to text
-display_our_properties <- our_network_properties %>% mutate_all(funs(format(., digits=2, trim=TRUE)))
-display_hills_properties <- hills_network_properties %>% mutate_all(funs(paste("(", ., ")", sep='')))
-
-# combine text tables for display
-display_properties <- bind_rows(display_our_properties %>% mutate(row = 1:n()),
-                                display_hills_properties %>% mutate(row = 1:n())) %>%
-  group_by(row) %>%
-  summarise_if(is.character, funs(paste(., collapse=" "))) %>%
-  arrange(row)
-
-# display combined properties
-select(hills_network_properties, type, w) %>%
-  bind_cols(select(display_properties, clustering_coefficient, avg_shortest_path,
-                   density, components, isolates)) %>%
+properties %>%
+  mutate(h_clustering_coef = c(0.55, 0.54, 0.58, 0.60, 0.54, 0.54, 0.62, 0.62, 0.88, 0.59, 0.38, 1.00),
+         h_avg_distance = c(1.72, 2.57, 4.96, 3.22, 1.76, 2.69, 5.02, 2.55, 3.08, 1.59, 5.02, 1.00),
+         h_density = c(0.29, 0.10, 0.04, 0.02, 0.27, 0.08, 0.03, 0.01, 0.05, 0.01, 0.0, 0.0),
+         h_components = c(1, 1, 4, 10, 1, 2, 8, 11, 7, 14, 7, 2),
+         h_isolates = c(0, 6, 20, 47, 0, 10, 31, 69, 33, 81, 113, 126)) %>%
+  select(type, age, w,
+         clustering_coef, h_clustering_coef,
+         avg_distance, h_avg_distance,
+         density, h_density,
+         components, h_components,
+         isolates, h_isolates) %>%
   kable(format="html",
         escape = FALSE,
-        col.names = c("Type", "w", "Clustering Coefficient", "Average length", "Density", "Components", "Isolates"),
-        align = rep("l", 7)) %>%
+        col.names = c("Type", "age", "w",
+                      "Clustering Coefficient", "",
+                      "Average length", "",
+                      "Density", "",
+                      "Components", "",
+                      "Isolates", ""),
+        align = c("l", "l", "l", rep(c("r", "l"), 5)),
+        digits = 2) %>%
   kable_styling(full_width = F) %>%
+  column_spec(seq(5,13,2), color = "grey") %>%
   collapse_rows(columns = 1:2, valign = "top")
@@
 
-# Clusters
+## Clique Percolation Clustering
 
-## Visualize Networks
-```{r out.width = '100%'}
-networks <- perceptual_networks[2]
+### Full Network
+
+Here we find parameter values for clique percolation according to the "principled approach" given in Hills, raising k for a given w until the the second largest cluster is greater than half the size of the largest, and then choosing the k for which this gives the most clusters.
+
+```{r}
+best_count <-  0
+for (w in 1:5) {
+  result <- cluster_cfinder(feature_network %E>% filter(shared >= w),
+                            cfinder_program = cfinder_program)
+  clusters <- result$clusters
+  k <- result$k
+  if (length(clusters) > best_count) {
+    best_w <- w
+    best_k <- k
+    best_count <- length(clusters)
+    best_clusters <- clusters
+  }
+}
 ```
 
-## Clique Percolation
+This gives values of w=`r best_w` and k=`r best_k`, as opposed to Hills' w=3 and k=3, and gives the following clusters:
 
-Initial Clique Analysis
-```{r out.width = '100%'}
-trimmed_networks <- map(networks, function (g) delete.vertices(g, degree(g)==0))
+```{r}
+title <- str_glue("Feature Network Clique Percolation Clusters, w = {best_w} and k = {best_k}")
+kable_clusters(best_clusters, title)
+```
 
-# cl <- makeCluster(3)
-# registerDoParallel(cl)
-# getDoParWorkers()
-## Plot with the new colors
-for (net in networks) {
-  for (k in 3:4) {
-    clusters <- clique.community.opt(net,k)
-    plot_network(net, clusters = clusters, labels=FALSE)
+Hills' values of w=3 and k=3 also give reasonable clusters:
+
+```{r}
+clusters <- cluster_cfinder(feature_network %E>% filter(shared >= 3),
+                            k = 3,
+                            cfinder_program = cfinder_program)$clusters
+kable_clusters(clusters, "Feature Network Clique Percolation Clusters, w = 3 and k = 3")
+```
+
+Note that this difference may be due to the minor differences between our networks.
+The largest cluster produced by w=3, k=3 is only one larger than twice the size of the second largest, and had it been smaller these parameters would have returned more clusters (and thus been selected) than w=`r best_w` and k=`r best_k`.
+However, these minor differences do lead to substantially different clusterings.
+
+### Perceptual Network
+
+Here we find parameter values for clique percolation on the perceptual network.
+
+```{r}
+best_count <-  0
+for (w in 1:5) {
+  result <- cluster_cfinder(perceptual_network %E>% filter(shared >= w),
+                            cfinder_program = cfinder_program)
+  clusters <- result$clusters
+  k <- result$k
+  if (length(clusters) > best_count) {
+    best_w <- w
+    best_k <- k
+    best_count <- length(clusters)
+    best_clusters <- clusters
   }
 }
-# stopCluster(cl)
 ```
 
-Dynamic Visualization
+This gives values of w=`r best_w` and k=`r best_k`, as opposed to Hills' w=2 and k=5, and gives the following clusters:
+
 ```{r}
-conceptual_clusters <- membership(cluster_walktrap(conceptual_network))
+title <- str_glue("Perceptual Network Clique Percolation Clusters, w = {best_w} and k = {best_k}")
+kable_clusters(best_clusters, title)
+```
 
-# Convert to object suitable for networkD3
-conceptual_d3 <- igraph_to_networkD3(conceptual_network, group = conceptual_clusters)
+Hills' values of w=2 and k=5 also give reasonable clusters:
 
-# Create force directed network plot
-forceNetwork(Links = conceptual_d3$links, Nodes = conceptual_d3$nodes,
-             Source = 'source', Target = 'target', NodeID = 'name',
-             Group = 'group')
+```{r}
+clusters <- cluster_cfinder(perceptual_network %E>% filter(shared >= 2),
+                            k = 5,
+                            cfinder_program = cfinder_program)$clusters
+kable_clusters(clusters, "Feature Network Clique Percolation Clusters, w = 2 and k = 5")
 ```
+
+### Conceptual Network
+
+Here we find parameter values for clique percolation on the conceptual network.
+
+```{r}
+best_count <-  0
+for (w in 1:5) {
+  result <- cluster_cfinder(conceptual_network %E>% filter(shared >= w),
+                            cfinder_program = cfinder_program)
+  clusters <- result$clusters
+  k <- result$k
+  if (length(clusters) > best_count) {
+    best_w <- w
+    best_k <- k
+    best_count <- length(clusters)
+    best_clusters <- clusters
+  }
+}
+```
+
+This gives values of w=`r best_w` and k=`r best_k`, matching Hills' w=1 and k=3, and gives the following clusters:
+
+```{r}
+title <- str_glue("Conceptual Network Clique Percolation Clusters, w = {best_w} and k = {best_k}")
+kable_clusters(best_clusters, title)
+```

### 2018-08-28 HillsComparison.Rmd
Presentation prep

---
title: "Comparison Word2Vec Analysis"
author: "Isaac Scheinfeld"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: default
---
# Preparation

This analysis requires a working copy of CFinder and the CFinder license in the same directory (necessary for running CFinder). The following must point to the command line executable:

```{r}
cfinder_program <- "./CFinder_commandline_mac"
```

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(broom) # converts R function outputs to tidy data frames
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(kableExtra) # table formatting
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(tidygraph)
library(doParallel)
library(networkD3)
library(viridis)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
```

## Nouns

We begin with roughly the same data used by Hills. *(TODO fix, get same data)*

```{r warning=FALSE}
# We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.

full_vocab <- make_vocab_dataframe(lang="English (American)",
                                   lang_form = "WS",
                                   lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition() %>%
  arrange(age) %>%            # keep first age for duplicates
  distinct(uni_lemma, .keep_all = TRUE) %>%
  select(uni_lemma, definition, age, category)
```

The initial vocabulary contains `r nrow(full_vocab)` (compared to Hills' 312).

## Features and Word2Vec

Features taken from McRae et al. (2005), in which features were collected for 541 nouns from 725 adults, with 30 adults providing 14 features for each noun. Word2Vec similarities are from child directed speach (source Abdellah).

```{r warning=FALSE, message=FALSE}
vocab <- full_vocab %>%
  filter(age <= 30) %>%
  filter_to_features() %>%
  filter_to_w2v()
```

Filtering to this data gives a vocab of `r nrow(vocab)`.

## Build Network

Using this vocabulary, we construct a network with edge attributes for features, and for word2vec similarity.

```{r message=FALSE}
# perceptual and conceptual McRae feature types
perceptual_features = c("sound", "taste", "smell", "tactile",
                        "visual-form_and_surface", "visual-motion", "visual-color")
conceptual_features = c("function")

# count shared features between words in vocabulary
feature_links <- make_feature_links(vocab = vocab,
                                    feature_types = union(perceptual_features,
                                                          conceptual_features))

# get word2vec distance between words in vocabulary
w2v_links <- make_w2v_links(vocab = vocab) #TODO still problem w/ vocab matching w2v data

links <- full_join(feature_links, w2v_links, by=c("from", "to"))

network <- graph_from_data_frame(links, vertices = vocab, directed = FALSE) %>%
  as_tbl_graph() %E>%
  mutate(shared = replace_na(shared, as.integer(0))) # is this replacement necessary?
```

# Results

## Word2Vec vs Feature Network

```{r out.width = '25%', fig.asp=1, fig.show = 'hold'}
par(oma=c(0,0,0.2,0))

ecounts <- list()
for (w in 1:4) {
  net <- network %E>% filter(shared >= w)
  ecounts[[length(ecounts) + 1]] <- ecount(net)
  layout <- layout_with_fr(net)
  plot_vocab_network(net,
                     plot_title = title(str_glue("Features w={w}"), cex.main = 2),
                     frame=FALSE, layout = layout, labels="")
}

# find thresholds that give matching edge counts
thresholds <- list()
for (i in seq_along(ecounts)) {
  e <- ecounts[[i]]
  curr_pow <- 1
  curr_e <- 0
  curr_t <- 1
  while (as.integer(curr_e) != as.integer(e)) {
    if (curr_e < e) {
      curr_t <- curr_t - (1/2) ^ curr_pow
    } else {
      curr_t <- curr_t + (1/2) ^ curr_pow
    }
    curr_e <- ecount(network %E>% filter(w2v_similarity >= curr_t))
    curr_pow <- curr_pow + 1
  }
  thresholds[[length(thresholds) + 1]] <- curr_t
}

for (w in thresholds) {
  net <- network %E>% filter(w2v_similarity >= w)
  layout <- layout_with_fr(net)
  plot_vocab_network(net, plot_title = title(str_glue("Word2Vec w={format(w,digits=3)}"), cex.main = 2),
                     frame=FALSE, layout = layout, labels="")
}

```

```{r}
network_properties <- function(network) {
  return( tibble(
    type = network$type,
    w = network$w,
    avg_distance = mean_distance(network),
    clustering_coef = transitivity(network),
    isolates = sum(degree(network) == 0),
    components = count_components(network) - isolates
  ))
}

feature_networks <- map(1:4, function(w) {
  network %>%
    filter(shared >= w) %>%
    set.graph.attribute("type", "Feature") %>%
    set.graph.attribute("w",w)})
w2v_networks <- map(thresholds, function(w) {
  network %>%
    filter(w2v_similarity >= w) %>%
    set.graph.attribute("type", "Word2Vec") %>%
    set.graph.attribute("w",w)}
)

feature_properties <- bind_rows(map(feature_networks, network_properties))
w2v_properties <- bind_rows(map(w2v_networks, network_properties))

bind_rows(feature_properties, w2v_properties) %>%
  kable(format="html",
        escape = FALSE,
        col.names = c("Type", "w",
                      "Clustering Coefficient",
                      "Average length",
                      "Components",
                      "Isolates"),
        align = rep("l",6),
        digits = 2) %>%
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1, valign = "top")
```

## Clique Percolation

We can now compare clique percolation on feature and word2vec networks.

```{r}
best_count <-  0
for (w in 1:5) {
  result <- cluster_cfinder(network %E>% filter(shared >= w),
                            cfinder_program = cfinder_program)
  clusters <- result$clusters
  k <- result$k
  if (length(clusters) > best_count) {
    best_w <- w
    best_k <- k
    best_count <- length(clusters)
    best_clusters <- clusters
  }
}

title <- str_glue("Feature Network Clique Percolation Clusters, w = {best_w} and k = {best_k}")
kable_clusters(best_clusters, title)
```

We can compare this to the corresponding clustering on the word2vec network with the same density, using the same parameters.

```{r}
clusters <- cluster_cfinder(network %E>%
                              filter(w2v_similarity >= thresholds[[best_w]]),
                            k = best_k,
                            cfinder_program = cfinder_program)$clusters

title <- str_glue("Word2Vec Network Clique Percolation Clusters, w = {format(thresholds[[best_w]], digits=2)} and k = {best_k}")
kable_clusters(clusters, title)
```

We can also search for parameters for the word2vec network using Hills' approach. Note that
w is given a lower bound of 0.25 as below this the network is too dense for cfinder to compute the clusters in a minute or less.

```{r}
best_count <-  0
for (w in seq(0.25,0.9,0.05)) {
  result <- cluster_cfinder(network %E>% filter(w2v_similarity >= w),
                            cfinder_program = cfinder_program)
  clusters <- result$clusters
  k <- result$k
  if (length(clusters) > best_count) {
    best_w <- w
    best_k <- k
    best_count <- length(clusters)
    best_clusters <- clusters
  }
}

title <- str_glue("Word2Vec Network Clique Percolation Clusters, w = {best_w} and k = {best_k}")
kable_clusters(best_clusters, title)
```

## Other Clustering Algorithms

We can cluster both the feature and word2vec networks using other clustering algorithms.

### Walktrap

```{r}
clusters <- cluster_walktrap(network, weights = E(network)$shared) # NA weights are treated as 0
kable_clusters(clusters, title = "Feature Network Walktrap Clusters")
```

```{r}
clusters <- cluster_walktrap(network, weights = E(network)$w2v_similarity)
kable_clusters(clusters, title = "Word2Vec Network Walktrap Clusters")
```

### Louvain

```{r}
clusters <- cluster_louvain(network, weights = E(network)$shared) # NA weights are treated as 0
kable_clusters(clusters, title = "Feature Network Louvain Clusters")
```

```{r}
clusters <- cluster_louvain(network, weights = E(network)$w2v_similarity)
kable_clusters(clusters, title = "Word2Vec Network Louvain Clusters")
```

### Spinglass

```{r}
clusters <- cluster_spinglass(network, weights = E(network)$shared) # NA weights are treated as 0
kable_clusters(clusters, title = "Feature Network Spinglass Clusters")
```

```{r}
clusters <- cluster_spinglass(network, weights = E(network)$w2v_similarity)
kable_clusters(clusters, title = "Word2Vec Network Spinglass Clusters")
```

### 2018-08-28 Main.Rmd
Presentation prep

@@
 ---
-title: "Word2Vec Analysis"
+title: "Comparison Word2Vec Analysis"
 author: "Isaac Scheinfeld"
@@
 ---
-# Networks
+# Preparation
 
@@
 layout <- layout_network(network %E>% mutate(weights = w2v_similarity))
+
+network <- network %N>%
+  mutate(x = layout[,1]) %>%
+  mutate(y = layout[,2])
 ```
@@
 
-```{r out.width = '100%', fig.height = 5, fig.width = 5}
+```{r out.width = '100%', dpi=300}
 source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
@@
                labels=TRUE,
+               frame=FALSE,
                title=str_glue("Threshold = {s}"))
@@
 
-Test igraph clustering algorithms
+## Clustering algorithms
 
-```{r fig.height = 5, fig.width = 5}
+```{r out.width='100%', fig.asp=1/2, dpi=300}
+# cluster_edge_betweenness - doesn't cluster reasonably, treats weights as distances?
+# 
+# cluster_infomap - returns one cluster
+# 
+# cluster_label_prop - returns one cluster
+# 
+# cluster_optimal - too computationally intensive for laptop, may not be possible (NP)
+
 source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
 
-# cluster_edge_betweenness - doesn't cluster reasonably, treats weights as distances?
+par(mfrow=c(1, 2), mar=c(2,0.4,0.8,0.4)) # row x col, column first
 
-# cluster_infomap - returns one cluster
+feature_network <- network %E>%
+  mutate_all(funs(replace(., is.na(.), 0))) %>%
+  mutate(features = perceptual + conceptual) %>%
+  filter(features > 0)
 
-# cluster_label_prop - returns one cluster
-
-# cluster_optimal - too computationally intensive for laptop, may not be possible (NP)
-
+# cluster_fast_greedy
 plot_network(network, layout = layout,
-             clusters = cluster_fast_greedy(network, weights = E(network)$w2v_similarity)$membership,
+             clusters = cluster_fast_greedy(network,
+                                            weights = E(network)$w2v_similarity)$membership,
              labels=TRUE, frame=TRUE)
 
-plot_network(network, layout = layout,
-             clusters = cluster_leading_eigen(network, weights = E(network)$w2v_similarity)$membership,
+plot_network(feature_network, layout = layout,
+             clusters = cluster_fast_greedy(feature_network,
+                                            weights = E(feature_network)$features)$membership,
              labels=TRUE, frame=TRUE)
 
+# cluster_leading_eigen
 plot_network(network, layout = layout,
-             clusters = cluster_louvain(network, weights = E(network)$w2v_similarity)$membership,
+             clusters = cluster_leading_eigen(network,
+                                              weights = E(network)$w2v_similarity)$membership,
              labels=TRUE, frame=TRUE)
 
-plot_network(network, layout = layout,
-             clusters = cluster_spinglass(network, weights = E(network)$w2v_similarity)$membership,
+plot_network(feature_network, layout = layout,
+             clusters = cluster_leading_eigen(feature_network,
+                                              weights = E(feature_network)$features)$membership,
              labels=TRUE, frame=TRUE)
 
+# cluster_louvain
 plot_network(network, layout = layout,
-             clusters = cluster_walktrap(network, weights = E(network)$w2v_similarity)$membership,
+             clusters = cluster_louvain(network,
+                                        weights = E(network)$w2v_similarity)$membership,
+             labels=TRUE, frame=TRUE)
+
+plot_network(feature_network, layout = layout,
+             clusters = cluster_louvain(feature_network,
+                                        weights = E(feature_network)$features)$membership,
+             labels=TRUE, frame=TRUE)
+
+# cluster_spinglass
+plot_network(network, layout = layout,
+             clusters = cluster_spinglass(network,
+                                          weights = E(network)$w2v_similarity)$membership,
+             labels=TRUE, frame=TRUE)
+
+plot_network(feature_network, layout = layout,
+             clusters = cluster_spinglass(feature_network,
+                                          weights = E(feature_network)$features)$membership,
+             labels=TRUE, frame=TRUE)
+
+# cluster_walktrap
+plot_network(network, layout = layout,
+             clusters = cluster_walktrap(network,
+                                         weights = E(network)$w2v_similarity)$membership,
+             labels=TRUE, frame=TRUE)
+
+plot_network(feature_network, layout = layout,
+             clusters = cluster_walktrap(feature_network,
+                                         weights = E(feature_network)$features)$membership,
              labels=TRUE, frame=TRUE)
 ```
+
+```{r out.width='100%', fig.asp=1/2, dpi=300}
+# cluster_walktrap
+for (age_limit in seq(16, 30, by=2)) {
+  net_at_age <- network %N>% filter(age <= age_limit) %E>% mutate(weights = w2v_similarity)
+
+  plot_network(net_at_age,
+               clusters = cluster_walktrap(net_at_age,
+                                           weights = E(net_at_age)$w2v_similarity)$membership,
+               labels = TRUE,
+               frame = TRUE)
+}
+```
+
+```{r}
+feature_net <- network %E>% mutate(weights = perceptual) %E>% filter(weights > 0) %N>% filter(!node_is_isolated())
+feature_layout <- layout_network(feature_net)
+
+feature_net <- feature_net %N>%
+  mutate(x = feature_layout[,1]) %>%
+  mutate(y = feature_layout[,2])
+
+```
+
+```{r out.width='100%', fig.asp=1/2, dpi=300}
+# cluster_walktrap
+for (age_limit in seq(16, 30, by=2)) {
+  net_at_age <- feature_net %N>% filter(age <= age_limit) %E>% mutate(weights = perceptual)
+
+  plot_network(net_at_age,
+               clusters = cluster_walktrap(net_at_age,
+                                           weights = E(net_at_age)$perceptual)$membership,
+               labels = TRUE,
+               frame = TRUE)
+}
+```

### 2018-08-28 RandomSubgraphModularity.Rmd
Presentation prep

---
title: "Word2Vec Analysis"
author: "Isaac Scheinfeld"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: default
---
# Networks

This report explores the clustering of nouns aquired by 16 - 30 month old children using word2vec similarity, and the dynamics of those clusters.

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(broom) # converts R function outputs to tidy data frames
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(kableExtra) # table formatting
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(tidygraph)
library(doParallel)
library(networkD3)
library(ForceAtlas2)
library(riverplot) # install from github at ischeinfeld/riverplot to hide debug messages in CRAN package
```

## Random Network

```{r}

```

### 2018-08-28 Word2Vec.Rmd
Presentation prep

---
title: "Word2Vec Analysis"
author: "Isaac Scheinfeld"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: default
---
# Networks

This report explores the clustering of nouns aquired by 16 - 30 month old children using word2vec similarity, and the dynamics of those clusters.

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(broom) # converts R function outputs to tidy data frames
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(kableExtra) # table formatting
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(tidygraph)
library(doParallel)
library(networkD3)
library(viridis)
library(riverplot) # install from github at ischeinfeld/riverplot to hide debug messages in CRAN package
library(ggm)
library(networkD3)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
```

## Nouns

We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.

```{r warning=FALSE}
full_vocab <- make_vocab_dataframe(lang="English (American)",
                                   lang_form = "WS",
                                   lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition() %>%
  arrange(age) %>%            # keep first age for duplicates
  distinct(uni_lemma, .keep_all = TRUE) %>%
  select(uni_lemma, definition, age, category)
```

The initial vocabulary contains `r nrow(full_vocab)` words.

## Word2Vec

Features taken from McRae et al. (2005), in which features were collected for 541 nouns from 725 adults, with 30 adults providing 14 features for each noun. Word2Vec similarities are from child directed speach (source Abdellah).

```{r warning=FALSE, message=FALSE}
vocab <- full_vocab %>%
  filter(age <= 30) %>%
  filter_to_w2v()
```

To begin our analysis, we only consider the words for which word2vec data are available, an overlap of `r nrow(vocab)` in our data. The missing words are `r setdiff(full_vocab$uni_lemma, vocab$uni_lemma)`.

## Build Network

We construct a network with an edge attribute for word2vec similarity.

```{r message=FALSE}
w2v_links <- make_w2v_links(vocab = vocab) #TODO still problem w/ vocab matching w2v data

network <- graph_from_data_frame(w2v_links, vertices = vocab, directed = FALSE) %>%
  as_tbl_graph() %E>%
  mutate(weight = w2v_similarity) # layout and clustering algorithms automatically use the weight attribute
```

# Analysis

## Layout the Network

First we generate a display layout for the network, based on the word2vec data.

```{r out.width = '100%', fig.asp = 1, dpi=300}
if (FALSE) {
  layout <- layout_network(network)
  saveRDS(layout, file = "layout.rds")
} else {
  layout <- readRDS(file = "layout.rds")
}

network <- network %N>%
  mutate(x = layout[,1]) %>%
  mutate(y = layout[,2])

plot_vocab_network(network,
                   frame=FALSE,
                   plot_title=title("Word2Vec Network",cex.main=1),
                   labels="",
                   edge_color = rgb(0,0,0,alpha = (E(network)$weight)^(5/2)))

```

## Clustering algorithms {.tabset}

### Walktrap

```{r out.width='33%', fig.asp=1, dpi=300, results='asis'}
par(oma=c(0,0,0.2,0))

for (age_limit in seq(16, 30, by=2)) {

  net <- network %N>% filter(age <= age_limit)
  clusters <- cluster_walktrap(net,
                               weights = E(net)$w2v_similarity)

  filename <- str_glue("images/walktrap_network_{age_limit}.png")
  png(filename=filename)
  plot_vocab_network(network %N>%
                       filter(age <= age_limit),
                     clusters = clusters$membership,
                     frame = FALSE,
                     labels = "",
                     edge_color = rgb(0,0,0,alpha = (E(network)$weight)^(5/2)))
  dev.off()

  cat("<table style='width:100%'><col width='30%'><col width='70%'><tr>")

  cat("<td valign='top'>")

  cat(str_glue('<img src="{filename}">'))

  cat("</td><td valign='top'>")

  print(kable_clusters(clusters,
                 title=str_glue("Age = {age_limit} Months")))
  cat("</tr></table>")

}
```

#### River Plot

```{r}
subgraphs_by_age <- get_subgraphs_by_age(network, cluster_walktrap)
```

```{r out.width='100%'}
#out.width='100%', fig.asp=1, dpi=300
river <- cluster_river(subgraphs_by_age = subgraphs_by_age)

plot(river, gravity = "center", plot_area = 0.8)
```

```{r}
suppressWarnings(precursors_graph(subgraphs_by_age, 0)) %>% plot_river_network()
```

### 2018-08-28 helpers/all_helper.r

@@ -5,3 +5,6 @@ source("word2vec_helper.r")
 source("plot_helper.r")
 source("clique_percolation.r")
 source("cluster_helper.r")
+source("cfinder_helper.r")
+source("river_helper.r")
+source("dynamics_helper.r")

### 2018-08-28 helpers/cfinder_helper.R

@@ -1,0 +1,41 @@
+cluster_cfinder <- function(g, debug = FALSE, k = NULL, cfinder_program) {
+  temp_dir <- paste(tempdir(), as.integer(Sys.time()), sep = "/")
+  while (dir.exists(temp_dir)) {temp_dir <- paste(temp_dir,"_",sep = "")}
+  dir.create(temp_dir)
+  if (debug) {print(str_glue("Working in directory: {temp_dir}"))}
+  write_graph(g, str_glue("{temp_dir}/graph"), format = "ncol")
+  system(str_glue("{cfinder_program} -i {temp_dir}/graph"),
+         ignore.stdout = !debug,
+         ignore.stderr = !debug)
+  if (is.null(k)) {
+    optimal <- FALSE
+    k <- 3
+    while (!optimal) {
+      file <- str_glue("{temp_dir}/graph_files/k={k}/communities")
+      if (file.exists(file)) {
+        clusters <- load_cfinder_communities(file)
+      } else {
+        k <- NULL
+        break
+      }
+      sizes <- sort(map_int(clusters, length), decreasing = T)
+      if (length(clusters) >= 2 && sizes[[2]] * 2 > sizes[[1]]) {
+        optimal <- TRUE
+      } else {
+        k <- k + 1
+      }
+    }
+  }
+  if (is.null(k)) {
+    clusters <- list()
+  } else {
+    clusters <- load_cfinder_communities(str_glue("{temp_dir}/graph_files/k={k}/communities"))
+  }
+  return(list(clusters = clusters, k = k))
+}
+
+load_cfinder_communities <- function(file) {
+  x <- system(str_glue("grep -v -E '(^#|^[[:space:]]*$)' {file} | sed 's/^[^:]*://g'"), intern = TRUE)
+  string_to_vec <- function(s) {unlist(str_split(str_trim(s), " "))}
+  return(map(x, string_to_vec))
+}

### 2018-08-28 helpers/cluster_helper.r

@@ -1,0 +1,43 @@
+apply_color_box <- function(s, color) {
+  return(str_glue("<span style=\"padding: 0 4px; border-radius: 4px; background-color: {color}\">{s}</span>"))
+} # display: block; 
+
+clusters_to_html_vec <- function(clusters, colors) {
+  word_freqs <- clusters %>%
+    unlist() %>%
+    table() %>% 
+    sort(decreasing = T)
+  color_word <- function(w) {
+    color <- colors[[word_freqs[[w]]]]
+    return(apply_color_box(w, color))
+  }
+  formatted_clusters <- clusters %>%
+    map(~ names(sort(word_freqs[.], decreasing = T))) %>% # sort
+    map(~ map_chr(.,color_word)) %>%                      # color words
+    map_chr(~ paste0(., collapse = " ")) %>%              # concatenate
+    map_chr(~ paste0("<span style='line-height: 1.7'>", ., "</span>"))
+  return(formatted_clusters)
+}
+
+kable_clusters <- function(clusters, title, ...) {
+  if (!is.null(clusters$membership)) { # igraph communities object
+    count <- length(clusters)
+    clusters <- unname(clusters[1:count])
+  }
+  colors <- viridis(4, alpha = 0.4, direction = -1)
+  max_count <- clusters %>%
+    unlist() %>%
+    table() %>% 
+    sort(decreasing = T) %>%
+    .[[1]]
+  color_display <- 1:max_count %>%
+    map_chr(~ apply_color_box(as.character(.), colors[[.]])) %>%
+    paste(collapse = " ")
+  tibble(clusters = clusters_to_html_vec(clusters, colors)) %>%
+    kable(format="html",
+          escape = FALSE,
+          col.names = c(str_glue("{title}  ({length(clusters)} Clusters)")),
+          align = c("l")) %>%
+    kable_styling(...) %>%
+    footnote(general = str_glue("Color indicates number of clusters in which a word occurs: {color_display}"), escape = F)
+}

### 2018-08-28 helpers/dynamics_helper.r

@@ -1,0 +1,113 @@
+# returns jacard distance between two igraphs / name vectors
+jacard_distance <- function(g1, g2) {
+  if (is_igraph(g1)) {
+    e1 <- V(g1)$name # elements of graph
+  } else {
+    e1 <- g1
+  }
+  if (is_igraph(g2)) {
+    e2 <- V(g2)$name # elements of graph
+  } else {
+    e2 <- g2
+  }
+  return(length(intersect(e1,e2)) / length(union(e1,e2)))
+}
+
+# returns list containing a list of subgraph clusters for each age
+get_subgraphs_by_age <- function(network, cluster_function) {
+  ages <- seq(min(V(network)$age), max(V(network)$age))
+  result <- list()
+  for (age_limit in ages) {
+    net <- network %N>% filter(age <= age_limit)
+    clusters <- cluster_function(net)
+    
+    subgraphs <- list()
+    for (i in 1:length(clusters)) {
+      subgraphs[[length(subgraphs) + 1]] <-
+        induced.subgraph(net,
+                         which(clusters$membership == i)) %>%
+        as_tbl_graph() %>%
+        set_graph_attr("age", age_limit)
+    }
+    ordered_subgraphs <- subgraphs[order(map_dbl(subgraphs, vcount), decreasing = T)]
+    
+    for (i in seq_along(ordered_subgraphs)) {
+      ordered_subgraphs[[i]] <- ordered_subgraphs[[i]] %>%
+        set_graph_attr("index", i)
+    }
+    
+    result[[length(result) + 1]] <- ordered_subgraphs
+  }
+  return(result)
+}
+
+# returns list of indices for predecessors at previous time step
+phi <- function(subgraphs_by_age, time_step, index, delta) {
+  previous_subgraphs <- subgraphs_by_age[[time_step - 1]]
+  
+  best_indices = integer(0)
+  best_jacard = 0
+  for (indices in powerset(seq_along(previous_subgraphs))) {
+    subgraphs <- previous_subgraphs[indices]
+    elements <- subgraphs %>% map(~ V(.)$name) %>% reduce(union)
+    jacard <- jacard_distance(elements, subgraphs_by_age[[time_step]][[index]])
+    if (jacard > best_jacard) {
+      best_indices <- indices
+      best_jacard <- jacard
+    }
+  }
+  
+  if (best_jacard < delta) {
+    best_indices <- integer(0)
+  }
+  
+  return(best_indices)
+}
+
[…]

### 2018-08-28 helpers/feature_helper.r

@@ -6,6 +6,13 @@ load_features <- function() {
   return(features)
 }
 
+filter_to_features <- function(vocab) {
+  features <- load_features()
+  
+  return (vocab %>%
+    filter(uni_lemma %in% features$Concept))
+}
+
 make_feature_links <- function(vocab, feature_types) {
   features <- load_features() %>%                  
     filter(Concept %in% vocab$uni_lemma) %>% # remove unneccessary features

### 2018-08-28 helpers/plot_helper.r

@@ -1,19 +1,19 @@
-layout_network <- function(g) {
-  l <- layout.forceatlas2(g %E>% select(weights),
-                          iterations=40000,
-                          plotstep=100000,
+layout_network <- function(g, iterations, delta = 5, gravity = 1, k = 1000) {
+  l <- layout.forceatlas2(g %E>% select(weight),
+                          iterations=iterations,
+                          plotstep=floor(iterations / 10),
                           directed = FALSE,
-                          delta = 3,
+                          delta = 6,
                           gravity = 1,
                           k = 10000)
   
   # move disconnected vertices to 0, 0
   l[degree(g) == 0,] <- 0
-
+  
   # move them to bottom
   y_size <- max(l[,2]) - min(l[,2])
   l[degree(g) == 0,2] <- min(l[,2]) - (y_size / 6)
-
+  
   # spread them out
   num_disconnected <- length(l[degree(g) == 0,1])
   x_size <- max(l[,1]) - min(l[,1])
@@ -22,11 +22,17 @@ layout_network <- function(g) {
   return(l)
 }
 
-plot_network <- function(g, layout = NULL, name=NA, frame=FALSE, labels=FALSE, clusters=NULL, title = NULL) {
+plot_vocab_network <- function(g, layout = NULL, name=NA, frame=FALSE, clusters=NULL, plot_title = NULL, edge_color = "grey", labels=V(g)$uni_lemma) {
   
-  # layout if no layout provided
-  if (is.null(layout)) {
-    layout <- layout_with_fr(g, niter = 500)
+  # layout 
+  if (!is.null(layout)) {
+    # do nothing
+  } else if (is.null(layout) && !is.null(V(g)$x)) {
+    x <- V(g)$x
+    y <- V(g)$y
+    layout <- cbind(x,y)
+  } else if (is.null(layout) && is.null(V(g)$x)) {
+    layout <- layout_with_fr(g)
   }
   
   # rescale layout
@@ -44,43 +50,107 @@ plot_network <- function(g, layout = NULL, name=NA, frame=FALSE, labels=FALSE, c
     #V(g)[ unlist(clusters)[ duplicated(unlist(clusters)) ] ]$color <- "red"
   }
   
-  if (labels) {
-    plot(g,
-         layout=layout,
-         frame=frame,
-         main=title,
-         rescale=FALSE,
-         asp=y_size / x_size,
-         xlim=c(min(layout[,1]), max(layout[,1])),
[…]

### 2018-08-28 helpers/word2vec_helper.r

@@ -19,6 +19,13 @@ trim_w2v <- function(w2v) {
   return(w2v)
 }
 
+filter_to_w2v <- function(vocab) {
+  w2v <- load_w2v()
+  
+  return (vocab %>%
+    filter(uni_lemma %in% w2v$from | uni_lemma %in% w2v$to)) # word must occur in word2vec data
+}
+
 make_w2v_links <- function(vocab) {
   w2v <- load_w2v() %>%
     filter(from %in% vocab$uni_lemma &

### 2018-11-17 languages.Rmd
cross-linguistic orders

--- 2018-08-28 Main.Rmd
@@
 ---
-title: "Comparison Word2Vec Analysis"
-author: "Isaac Scheinfeld"
+title: "Comparing order of acquisition cross-linguistically"
+author: "Abdellah Fourtassi"
 date: "`r Sys.Date()`"
@@
 library(networkD3)
-library(ForceAtlas2)
+#library(ForceAtlas2)
+library(boot)
+library(ggthemes)
 
 source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
+```
+
+Get cross-linguistic data from Wordbank
+```{r}
+
+languages = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish")
+
+admins <- get_administration_data() %>%
+  select(data_id, age, language, form) %>%
+  filter(language %in% languages)
+
+items <- get_item_data() %>%
+  filter(type == "word", lexical_class == "nouns") %>%
+  filter(language %in% languages)
+
+items_by_inst <- split(items, paste(items$language, items$form, sep = "_"))
+
+get_inst_data <- function(inst_items) {
+  inst_lang <- unique(inst_items$language)
+  inst_form <- unique(inst_items$form)
+  inst_admins <- filter(admins, language == inst_lang, form == inst_form)
+  get_instrument_data(language = inst_lang ,
+                      form = inst_form,
+                      administrations = inst_admins,
+                      items = inst_items$item_id,
+                      iteminfo = inst_items
+                      ) %>%
+    filter(!is.na(age)) %>%
+    mutate(produces = !is.na(value) & value == "produces",
+           understands = !is.na(value) & (value == "understands" | value == "produces")) %>%
+    select(-value) %>%
+    gather(measure, value, produces, understands) %>%
+    filter((measure == "understands" & form == "WG") | (measure == "produces" & form == "WS") ) %>%
+    mutate(language = inst_lang,
+           form = inst_form)
+
+}
+
+data_raw <- map(items_by_inst, get_inst_data)
+
+data_all <- bind_rows(data_raw) %>%
+  rename(item = num_item_id) %>%
+  group_by(language, form, measure,
+             lexical_category, lexical_class, uni_lemma,  item, definition, 
+             age) %>%
+  summarise(num_true = sum(value, na.rm = TRUE),
+              num_false = n() - num_true,
+              prop = mean(value, na.rm = TRUE))
+
+#feather::write_feather(data_all, "saved_data/data_all.feather")
+
+#I am taking out measure to keep only produce
+data_all <- feather::read_feather("saved_data/data_all.feather")
+
+data_all$language <- plyr::mapvalues(data_all$language, 
+                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
+                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))
+
+```
+
+Calculate the age of acquisition
+```{r}
+
+fit_inst_measure_uni <- function(inst_measure_uni_data) {
+  ages <- min(inst_measure_uni_data$age):max(inst_measure_uni_data$age)
+  model <- glm(cbind(num_true, num_false) ~ age, family = "binomial",
+               data = inst_measure_uni_data)
+  fit <- predict(model, newdata = data.frame(age = ages), se.fit = TRUE)
+  aoa <- -model$coefficients[["(Intercept)"]] / model$coefficients[["age"]]
+  constants <- inst_measure_uni_data %>%
+    ungroup()%>%
+    select(language, form, measure, lexical_category, lexical_class, uni_lemma, item, definition) %>%
+    distinct()
+
+  props <- inst_measure_uni_data %>%
+    ungroup() %>%
+    select(age, prop)
+
+  data.frame(age = ages,
+             fit_prop = inv.logit(fit$fit),
+             fit_se = fit$se.fit,
+             aoa = aoa, language = constants$language,
+             form = constants$form,
+             measure = constants$measure,
+             uni_lemma = constants$uni_lemma,
+             item = constants$item,
+             definition = constants$definition) %>%
+    left_join(props)
+}
+
+list_by_item <- data_all %>%
+  # make this filtering at the beginning, not here
+  split(paste(.$language, .$form, .$measure, .$item))
+
+data_aoa <- map(list_by_item, fit_inst_measure_uni) %>%
+  bind_rows()
+
+data_aoa <- data_aoa %>%
+  select(language, form, measure, uni_lemma, item, definition, aoa) %>%
+  distinct()
+
+#feather::write_feather(data_aoa, "saved_data/data_aoa.feather")
+
+data_aoa <- feather::read_feather("saved_data/data_aoa.feather")
+
+#I am taking out measure to keep only produce
+#data_aoa2 <- feather::read_feather("saved_data/aoa_data.feather") %>%
+#  rename(definition = defintion) %>%
+#  select(language, form, measure, uni_lemma, item, definition, aoa) %>%
+#  distinct()
+
+```
+
+Colculate the correlation
+```{r}
+
+#Correlation between comprehension and production in each language
+#For each pairwise comparision, compute correlation using values unilemmas which are avialable in both languages
+
+#I should have a double loop?
+#For each pair of languages, select the unilemmas and their aoa, rank the unilemmas based on aoa, and calcualte the correlation
+
+# rank unilemma asa function of AoA
+
+data_prod <- data_aoa %>%
+  filter(measure =='produces')
+
+data_by_lang <- split(data_prod, data_prod$language)
+
+pair_data <- function(lang1){
+
+  pair_cor_data <- function (lang2){
+
+  lang1_unilemmas <- unique(lang1$uni_lemma)
+  lang2_unilemmas <- unique(lang2$uni_lemma)
+  uni_intersect <-  intersect(lang1_unilemmas, lang2_unilemmas)
+
+  data_lang1 <- lang1 %>%
+    filter(!is.na(uni_lemma),
+           uni_lemma %in% uni_intersect) %>%
+    select(uni_lemma, aoa) %>%
+    group_by(uni_lemma) %>%
+    summarise(aoa1=mean(aoa))
+
+  data_lang2 <- lang2 %>%
+    filter(!is.na(uni_lemma),
+           uni_lemma %in% uni_intersect) %>%
+    select(uni_lemma, aoa) %>%
+    group_by(uni_lemma) %>%
+    summarise(aoa2=mean(aoa))
+
+  both <- data_lang1 %>%
+    left_join(data_lang2)
+
+  mycorr <- cor.test(rank(both$aoa1), rank(both$aoa2), method = 'kendall')
+  val=mycorr$estimate
+  p=mycorr$p.value
+  language1 = unique(lang1$language) 
+  language2 = unique(lang2$language)
+
+  data.frame(language1=language1, language2=language2, tau=val, sig = p)
+
+}
+  map(data_by_lang, pair_cor_data) %>%
+    bind_rows()
+
+}
+
+pair_random <- function(lang1){
+
+  pair_cor_rand <- function (lang2){
+
+  data_lang1 <- lang1 %>%
+    filter(!is.na(uni_lemma)) %>%
+    select(uni_lemma, aoa) %>%
+    group_by(uni_lemma) %>%
+    summarise(aoa1=mean(aoa))
+
+  order_lang1 <- rank(data_lang1$aoa1)
+  order_random <- sample(order_lang1, size = length(order_lang1), replace = FALSE)
+
+  mycorr <- cor.test(order_lang1, order_random, method = 'kendall')
+
+  val=mycorr$estimate
+  p=mycorr$p.value
+  language1 = unique(lang1$language) 
+  language2 = unique(lang2$language)
+
+  data.frame(language1=language1, language2=language2, tau=val, sig = p)
+
+}
+  map(data_by_lang, pair_cor_rand) %>%
+    bind_rows()
+
+}
+
+cor_data <- map(data_by_lang, pair_data) %>%
+  bind_rows() %>%
+  filter(language1!=language2) %>%
+  mutate(data="languages")
+
+cor_random <- map(data_by_lang, pair_random) %>%
+  bind_rows() %>%
+  mutate(data="random")
+
+cor_all <- cor_data %>%
+  bind_rows(cor_random)
+
+```
+
+plots
+```{r}
+
+ggplot(cor_all, 
+      aes(x = tau, fill=data)) +
+  geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+                 binwidth=0.05)+
+  #scale_x_log10() +
+  theme_few() + 
+  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +  #facet_grid(Segmentation ~ language)+
+  scale_y_continuous(labels = scales::percent)+
+  xlab("pairwise correlation") +ylab("Count")
+
 ```

### 2018-11-30 languages.Rmd
similarity based growth

@@
 
+```
+
+similarity-based learning mechanism
+```{r}
+
+unilemmas <- (data_by_lang[[3]] %>% #English (I should recode this to be more explcit)
+    filter(!is.na(uni_lemma)) %>%
+    trim_all_unilemma() %>%
+    select(uni_lemma) %>%
+    #(uni_lemma))$uni_lemma
+    unique())$uni_lemma
+
+#get the data frame for w2v
+w2v <- load_w2v() %>%
+  filter(from %in% unilemmas & to  %in% unilemmas)
+
+#Transfom the data fram into adjencency matrix
+g <- graph.data.frame(w2v, directed=FALSE)
+  #matrix_sim <- get.adjacency(g, attr="w2v_similarity", sparse=FALSE)
+  matrix_sim <- get.adjacency(g, attr="w2v_similarity")
+
+vocab <- names(matrix_sim[word_0, ])
+#Now generate a sequence based on the first word
+
+sim_learning <- function() {
+  seq_gen <- function(word_t0, sequence_t0) {
+
+    if (length(sequence_t0) == length(matrix_sim[word_t0, ])) {
+      return (sequence_t0)
+    } else {
+      #generate similarity values of all words to word_t
+      all_words <- matrix_sim[word_t0, ]
+      #Obtain indices of the words already known at time t (present in in sequence_t)
+      indices <- which(names(all_words) %in% sequence_t0)
+      #generate candidates for word_t+1 by subseting known words from all words
+      candidates <- all_words[-indices]
+      #the next word (i.e., word_t+1) is the most simialr to the last word acquired ()
+      index_t1 <- which.max(candidates)
+      word_t1 <- names(index_t1)
+      sequence_t1 <- c(sequence_t0, word_t1)
+
+      return(seq_gen(word_t1, sequence_t1))
+    }
+  }
+
+  word_0 <- sample(vocab, 1) # this is the only random compoenent
+  sequence_0 <- c(word_0)
+  #seq_gen(word_0, sequence_0)
+  return(seq_gen(word_0, sequence_0))
+}
+
+pair_sim <- function(lang1){
+  pair_cor_sim <- function (lang2){
+
+  #Orering based on word similarity
+
+  #Real ordering in the language 
+  data_lang1 <- lang1 %>%
+    filter(!is.na(uni_lemma)) %>%
+    trim_all_unilemma() %>%
+    filter(uni_lemma %in% vocab) %>% #Intersection with w2v data
+    select(uni_lemma, aoa) %>%
+    group_by(uni_lemma) %>%
+    summarise(aoa1=mean(aoa))
+
+  #Orering based on word similarity
+  sim_list <- sim_learning()
+  sim_data <- data.frame(uni_lemma=sim_list, orderSim = seq(1, length(sim_list)))
+
+  #Combine both
+  both_orders <- data_lang1 %>%
+    left_join(sim_data) %>%
+    filter(!is.na(orderSim),
+           !is.na(aoa1))
+
+  order_lang1 <- rank(both_orders$aoa1)
+  order_sim <- rank(both_orders$orderSim)
+
+  mycorr <- cor.test(order_lang1, order_sim, method = 'kendall')
+
+  val=mycorr$estimate
+  p=mycorr$p.value
+  language1 = unique(lang1$language) 
+  language2 = unique(lang2$language)
+
+  data.frame(language1=language1, language2=language2, tau=val, sig = p)
+
+}
+  map(data_by_lang, pair_cor_sim) %>%
+    bind_rows()
+
+}
+
+cor_sim <- map(data_by_lang, pair_sim) %>%
+  bind_rows() %>%
+  mutate(data="sim")
+
 cor_all <- cor_data %>%
-  bind_rows(cor_random)
+  bind_rows(cor_random) %>%
+  bind_rows(cor_sim)
 
@@
   geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+                 alpha=0.5,
                  binwidth=0.05)+
@@
 ```
-
-## Nouns
-
-We begin with roughly the same data used by Hills. *(TODO fix, get same data)*
-
-```{r warning=FALSE}
-# We begin by importing data from wordbank.
-Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word.
-We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,..
-but we will have to be careful in our choices if we are preparing later for publication.
-
-full_vocab <- make_vocab_dataframe(lang="English (American)",
-                                   lang_form = "WS",
-                                   lex_class = "nouns") %>%
-  trim_all_unilemma() %>%
-  trim_all_definition() %>%
-  arrange(age) %>%            # keep first age for duplicates
-  distinct(uni_lemma, .keep_all = TRUE) %>%
-  select(uni_lemma, definition, age, category)
-```
-
-The initial vocabulary contains `r nrow(full_vocab)` (compared to Hills' 312).
-
-## Perceptual & Conceptual Features
-
-Features taken from McRae et al. (2005), in which features were collected for 541 nouns from 725 adults, with 30 adults providing  14 features for each noun.
-
-```{r warning=FALSE, message=FALSE}
-features <- load_features()
-w2v <- load_w2v()
-
-hills_vocab <- full_vocab %>%
-  filter(age <= 30) %>%
-  filter(uni_lemma %in% features$Concept) # filter to words with features
-
-vocab <- hills_vocab %>%
-  filter(uni_lemma %in% w2v$from | uni_lemma %in% w2v$to)
-```
-
-To begin our analysis, we only consider the words for which feature data are available, an overlap of `r nrow(hills_vocab)` in our data compared to Hills' 130.
-Then we filter the `r nrow(hills_vocab) - nrow(vocab)` words for which word2vec data is not available, for a final vocabulary of `r nrow(vocab)`.
-
-## Build Network
-
-Using vocabulary obtained by 30 months and the same McRae features as Hills, we construct a network with edge attributes for perceptual and conceptual features, and for word2vec similarity.
-
-```{r message=FALSE}
-# perceptual and conceptual McRae feature types
-perceptual_features = c("sound", "taste", "smell", "tactile",
-                        "visual-form_and_surface", "visual-motion", "visual-color")
-conceptual_features = c("function")
-
-# count shared features between words in vocabulary
-perceptual_links <- make_feature_links(vocab = vocab,
-                                       feature_types = perceptual_features) %>%
-  rename(perceptual = shared)
-
-conceptual_links <- make_feature_links(vocab = vocab,
-                                       feature_types = conceptual_features) %>%
-  rename(conceptual = shared)
-
-# get word2vec distance between words in vocabulary
-w2v_links <- make_w2v_links(vocab = vocab) #TODO still problem w/ vocab matching w2v data
-
-links <- perceptual_links %>%
-  full_join(conceptual_links, by=c("from", "to")) %>%
-  full_join(w2v_links, by=c("from", "to"))
-
-network <- graph_from_data_frame(links, vertices = vocab, directed = FALSE) %>%
-  as_tbl_graph()
-```
-
-# Results
-
-## The Network
-
-First we generate a display layout for the network, based on the word2vec data.
-
-```{r}
-source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
-
-layout <- layout_network(network %E>% mutate(weights = w2v_similarity))
-
-network <- network %N>%
-  mutate(x = layout[,1]) %>%
-  mutate(y = layout[,2])
-```
-
-We can examine the networks generated by filtering edges with a word2vec similarity threshold.
-
-```{r out.width = '100%', dpi=300}
-source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
-
-par(mfrow=c(2, 2), mar=c(2,0.4,0.8,0.4)) # row x col, column first
-
-for (s in seq(0.35, 0.5, 0.05)) {
-  plot_network(network %E>% filter(w2v_similarity > s),
-               layout = layout,
-               labels=TRUE,
-               frame=FALSE,
-               title=str_glue("Threshold = {s}"))
-}
-
-```
-
-## Clustering algorithms
-
-```{r out.width='100%', fig.asp=1/2, dpi=300}
-# cluster_edge_betweenness - doesn't cluster reasonably, treats weights as distances?
-# 
-# cluster_infomap - returns one cluster
-# 
-# cluster_label_prop - returns one cluster
-# 
-# cluster_optimal - too computationally intensive for laptop, may not be possible (NP)
-
-source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
-
-par(mfrow=c(1, 2), mar=c(2,0.4,0.8,0.4)) # row x col, column first
-
-feature_network <- network %E>%
-  mutate_all(funs(replace(., is.na(.), 0))) %>%
-  mutate(features = perceptual + conceptual) %>%
-  filter(features > 0)
-
-# cluster_fast_greedy
-plot_network(network, layout = layout,
-             clusters = cluster_fast_greedy(network,
-                                            weights = E(network)$w2v_similarity)$membership,
-             labels=TRUE, frame=TRUE)
-
-plot_network(feature_network, layout = layout,
-             clusters = cluster_fast_greedy(feature_network,
-                                            weights = E(feature_network)$features)$membership,
-             labels=TRUE, frame=TRUE)
-
-# cluster_leading_eigen
-plot_network(network, layout = layout,
-             clusters = cluster_leading_eigen(network,
-                                              weights = E(network)$w2v_similarity)$membership,
-             labels=TRUE, frame=TRUE)
-
-plot_network(feature_network, layout = layout,
-             clusters = cluster_leading_eigen(feature_network,
-                                              weights = E(feature_network)$features)$membership,
-             labels=TRUE, frame=TRUE)
-
-# cluster_louvain
-plot_network(network, layout = layout,
-             clusters = cluster_louvain(network,
-                                        weights = E(network)$w2v_similarity)$membership,
-             labels=TRUE, frame=TRUE)
-
-plot_network(feature_network, layout = layout,
-             clusters = cluster_louvain(feature_network,
-                                        weights = E(feature_network)$features)$membership,
-             labels=TRUE, frame=TRUE)
-
-# cluster_spinglass
-plot_network(network, layout = layout,
-             clusters = cluster_spinglass(network,
-                                          weights = E(network)$w2v_similarity)$membership,
-             labels=TRUE, frame=TRUE)
-
-plot_network(feature_network, layout = layout,
-             clusters = cluster_spinglass(feature_network,
-                                          weights = E(feature_network)$features)$membership,
-             labels=TRUE, frame=TRUE)
-
-# cluster_walktrap
-plot_network(network, layout = layout,
-             clusters = cluster_walktrap(network,
-                                         weights = E(network)$w2v_similarity)$membership,
-             labels=TRUE, frame=TRUE)
-
-plot_network(feature_network, layout = layout,
-             clusters = cluster_walktrap(feature_network,
-                                         weights = E(feature_network)$features)$membership,
-             labels=TRUE, frame=TRUE)
-```
-
-```{r out.width='100%', fig.asp=1/2, dpi=300}
-# cluster_walktrap
-for (age_limit in seq(16, 30, by=2)) {
-  net_at_age <- network %N>% filter(age <= age_limit) %E>% mutate(weights = w2v_similarity)
-
-  plot_network(net_at_age,
-               clusters = cluster_walktrap(net_at_age,
-                                           weights = E(net_at_age)$w2v_similarity)$membership,
-               labels = TRUE,
-               frame = TRUE)
-}
-```
-
-```{r}
-feature_net <- network %E>% mutate(weights = perceptual) %E>% filter(weights > 0) %N>% filter(!node_is_isolated())
-feature_layout <- layout_network(feature_net)
-
-feature_net <- feature_net %N>%
-  mutate(x = feature_layout[,1]) %>%
-  mutate(y = feature_layout[,2])
-
-```
-
-```{r out.width='100%', fig.asp=1/2, dpi=300}
-# cluster_walktrap
-for (age_limit in seq(16, 30, by=2)) {
-  net_at_age <- feature_net %N>% filter(age <= age_limit) %E>% mutate(weights = perceptual)
-
-  plot_network(net_at_age,
-               clusters = cluster_walktrap(net_at_age,
-                                           weights = E(net_at_age)$perceptual)$membership,
-               labels = TRUE,
-               frame = TRUE)
-}
-```

### 2018-12-17 languages.Rmd
new sampling mechanisms

@@
 
-unilemmas <- (data_by_lang[[3]] %>% #English (I should recode this to be more explcit)
+unilemmas <- (data_by_lang[[3]] %>% #I use English data to derive unilemmas, see above (but I should recode this to be cleaner)
     filter(!is.na(uni_lemma)) %>%
@@
 vocab <- names(matrix_sim[word_0, ])
-#Now generate a sequence based on the first word
 
-sim_learning <- function() {
+#Sampling via
+
+## Sampling via comparing similarity to last known words
+
+lastWord <- function() {
   seq_gen <- function(word_t0, sequence_t0) {
@@
 }
+
+## Sampling via averaging to similarity to all known
+
+allWords <- function() {
+  seq_gen <- function(sequence_t0) {
+
+    if (length(sequence_t0) == length(matrix_sim[sequence_t0[1], ])) {
+      return (sequence_t0)
+    } else {
+
+      ave_sim <- function(candidate) {
+        all <- matrix_sim[candidate, ] #Similarity values to all words 
+        values <- all[names(all) %in% sequence_t0] # Similarity values to known words only
+        return(data.frame(word = candidate, value = mean(values)))
+      }
+
+      #all words
+      all <- names(matrix_sim[sequence_t0[1], ])
+      candidates <- setdiff(all, sequence_t0)
+      list_sim  <- map(candidates, ave_sim) %>%
+        bind_rows()
+      max_value <- list_sim[which.max(list_sim$value),]
+      word_t1 <- max_value$word[1]
+      sequence_t1 <- c(sequence_t0, word_t1)
+
+      return(seq_gen(sequence_t1))
+    }
+  }
+  word_0 <- sample(vocab, 1) # this is the only random compoenent
+  sequence_0 <- c(word_0)
+  return(seq_gen(sequence_0))
+}
+
+```
+
+```{r}
 

### 2019-01-28 conceptNet-cogsci/Cogsci.Rmd
copied cogsci to folder

---
title: "CogSci Analysis"
author: "Isaac Scheinfeld"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: default
---

# Setup

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(igraph) # network analysis and visualization
library(tibble) # modern dataframes
library(tidygraph)
library(matrixStats)
library(memoise)

source("helpers/wb_helper.r")
source("helpers/word2vec_helper.r")
source("helpers/network_helper.r")
source("helpers/random_helper.r")
source("helpers/dynamics_helper.r")
source("helpers/statistics_helper.r")
```

## Nouns

We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.

```{r warning=FALSE}
get_language_vocab_ <- function(lang) {
  return(make_vocab_dataframe(lang=lang,
                              lang_form = "WS",
                              lex_class = "nouns") %>%
           trim_all_unilemma() %>% # TODO check trimming
           trim_all_definition() %>%
           arrange(age) %>%            # keep first age for duplicates
           distinct(uni_lemma, .keep_all = TRUE) %>%
           select(uni_lemma, definition, age, category))
}

get_language_vocab <- memoize(get_language_vocab_) # memoize to prevent re-downloading dataset TODO check if this works
```

##

## Build Word2Vec Network Evolution

```{r message=FALSE}
clusters_evolution <- function(vocab, n_clusters, min_age, max_age, randomization) {

  if(randomization == "none") {
    # do nothing
  } else if(randomization == "random_aoa") {
    vocab <- randomize_aoa(vocab) # TODO handle randomization, write "randomize_aoa"" in random_helper.r
  } else if(randomization == "to_nearest_aoa") {
    vocab <- randomize_aoa_to_nearest(vocab)
  } else if(randomization == "within_last_clustering") {
    vocab <- randomize_within_last_clustering(vocab, n_clusters)
  } else {
    stop("Randomization argument incorrect.")
  }

  vocab_network <- vocab_to_w2v_network(vocab) # drops words w/o w2v data, NOTE memoizes w2v data

  # list of networks at each age
  net_evo <- min_age:max_age %>%
    map(~ filter(activate(vocab_network, nodes), age <= .))

  # list of vocabulaires at each age
  vocab_evo <- net_evo %>%
    map(V)

  # list of cluster membership index vectors at each age
  membership_evo <- net_evo %>%
    map(w2v_waltrap) %>%
    map(~ cut_at(., no = n_clusters))

  # list of word clusters at each age
  clusters_evo <- map2(vocab_evo, membership_evo, build_clusters)

  return(clusters_evo)
}
```

# Analysis

## Measure Clustering Dynamics

```{r}
# language, n_clusters, age range, random samples, dynamics measure -> analysis
# example measure is function(clusters_evo) {pair_measures_to_last(clusters_evo, measure)}
run_measure <- function(clusters_evo, measure) {
  if (measure == "pair_precision_to_last") {
    return(pair_measures_to_last(clusters_evo, pair_precision))
  } else if (measure == "pair_recall_to_last") {
    return(pair_measures_to_last(clusters_evo, pair_recall))
  } else if (measure == "pair_f1_to_last") {
    return(pair_measures_to_last(clusters_evo, pair_f1))
  } else if (measure == "min_max_size_ratio") {
    return(map_dbl(clusters_evo, min_max_size_ratio))
  } else if (measure == "modularity") {
    return(map_dbl(clusters_evo, min_max_size_ratio))
  } else {
    stop("Incorrect Dynamics Measure Name")
  }
}

# -----------------------------------------------------------------------------------------------
# given a language and # of clusters, the dynamics measures and randomizations are calculated
# together to avoid repeatedly sampling clusterings
# -----------------------------------------------------------------------------------------------

measure_cluster_dynamics <- function(language, n_clusters, measures, randomizations, samples) {
    vocab <- get_language_vocab(language)

    # measurement schema : age, measure, randomization, sample, value
    measurements <- list() # list of measurement tibbles

    # true vocabulary sizes (full vocabulary size at each month)
    measurements[["true_vocab_sizes"]] <-
      tibble(age = min(vocab$age):max(vocab$age),
             measure = "true_vocab_size",
             randomization = NA, # same for all randomizations
             sample = NA,
             value = min(vocab$age):max(vocab$age) %>%
               map(~ filter(vocab, age <= .)) %>%
               map(nrow) %>%
               unlist())

    # --------------------- true aoa measures --------------------- #
    true_clusters_evo <- clusters_evolution(vocab,
                                            n_clusters,
                                            min(vocab$age),
                                            max(vocab$age),
                                            randomization = "none")

    # w2v vocabulary sizes (number of words know at each month in clustering)
    measurements[["w2v_vocab_sizes"]] <- 
      tibble(age = min(vocab$age):max(vocab$age),
             measure = "w2v_vocab_size",
             randomization = NA, # same for all randomizations
             sample = NA,
             value = unlist(map(true_clusters_evo, ~ length(unlist(.)))))

    # dynamics measures
    for (measure in measures) {
      value <- run_measure(true_clusters_evo, measure)
      measurements[[measure]] <-
        tibble(age = min(vocab$age):max(vocab$age),
               measure = measure,
               randomization = "none",
               sample = NA,
               value = value)
    }

    # --------------------- randomized aoa measures --------------------- #
    for (randomization in randomizations) {

      for (sample in 1:samples) {
        random_clusters_evo <- clusters_evolution(vocab,
                                                  n_clusters,
                                                  min(vocab$age),
                                                  max(vocab$age),
                                                  randomization = randomization)

        for (measure in measures) {
          value <- run_measure(random_clusters_evo, measure)
          measurements[[paste(randomization, measure, sample, sep = "__")]] <-
            tibble(age = min(vocab$age):max(vocab$age),
                   measure = measure,
                   randomization = randomization,
                   sample = sample,
                   value = value)
        }
      }
    }

    return(bind_rows(measurements))
}

run_experiment <- function(languages, measures, randomizations, cluster_counts, samples) {
  measurements = list()
  cat("measuring dynamics\n")
  for(language in languages) {
    cat("  language:", language, "\n")
    for(n_clusters in cluster_counts) {
      cat("    n_clusters: ", n_clusters, "\n")
      measurements[[length(measurements) + 1]] <- 
        measure_cluster_dynamics(language, n_clusters, measures, randomizations, samples) %>%
        mutate(language = language) %>%
        mutate(n_clusters = n_clusters) %>%
        select(language, n_clusters, everything())
    }
  }
  return(bind_rows(measurements))
}
```

## Run Experiment

```{r warning=FALSE, message=FALSE}
languages <-  c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish")

measures <- c("pair_precision_to_last", "pair_recall_to_last", "pair_f1_to_last", "min_max_size_ratio")

randomizations <- c("random_aoa", "to_nearest_aoa", "within_last_clustering")

### compute measurements, TAKES A LONG TIME

# measurements <- run_experiment(languages = languages,
#                           measures = measures,
#                           randomizations = randomizations,
#                           cluster_counts = 2:5,
#                           samples = 50)
# 
#saveRDS(measurements, "measurements.rds")

measurements <- readRDS("measurements.rds")

```

## Summarize and Visualize Results
```{r}
to_pdf = FALSE

### Plot vocab sizes
vocab_sizes <- measurements %>%
  select(language, n_clusters, age, measure, value) %>%
  filter(measure %in% c("true_vocab_size", "w2v_vocab_size"))

if (to_pdf) {
  pdf("output/vocab_size.pdf", width=20, height=3)
}
ggplot(vocab_sizes) +
  geom_line(aes(x = age, y = value, colour = measure)) + 
  facet_grid(~ language)
if (to_pdf) {
  dev.off()
}
```
```{r}
### Plot measure summary
to_pdf = FALSE

for (measure_to_plot in measures) {
  for (randomization_to_plot in randomizations) {

    summary_fname <- paste(measure_to_plot, randomization_to_plot, sep="__") %>%
      paste("pdf", sep = ".")

    # APPROACH # 1
    true_evolution <- measurements %>%
      filter(measure == measure_to_plot) %>%
      filter(randomization == "none") %>%
      select(language, n_clusters, age, value)

    random_evolution <- measurements %>%
      filter(measure == measure_to_plot) %>%
      filter(randomization == randomization_to_plot) %>%
      group_by(language, n_clusters, age) %>%
      summarise(mean = mean(value),
                sd = sd(value),
                `25%`=quantile_func(value, probs=0.25),
                `50%`=quantile_func(value, probs=0.5),
                `75%`=quantile_func(value, probs=0.75),
                `10%`=quantile_func(value, probs=0.1),
                `90%`=quantile_func(value, probs=0.9)) %>%
      ungroup()

    evolution <- full_join(true_evolution, random_evolution, by = c("language", "n_clusters", "age"))

    if (to_pdf) {
      pdf(paste("output",summary_fname,sep="/"), width=20, height=10)
    }
    print(
      ggplot(evolution, aes(x = age)) +
        geom_ribbon(aes(ymin = `10%`,
                        ymax = `90%`),
                    colour="yellow",
                    fill="yellow",
                    linetype=2,
                    alpha= 0.2) +
        geom_ribbon(aes(ymin = `25%`,
                        ymax = `75%`),
                    colour="orange",
                    fill="orange",
                    linetype=2,
                    alpha= 0.3) +
        geom_line(aes(y = `50%`), color = "red", alpha = 0.4) + 
        geom_line(aes(y = value), color = "blue") +
        labs(title = paste("True value against",
                           randomization_to_plot,
                           "statistics on",
                           max(measurements$sample, na.rm = TRUE), 
                           "samples"),
             subtitle = "25%-75% and 10%-90% quantiles shown",
             x ="Age (m)", y = measure_to_plot) +
        facet_grid(n_clusters ~ language)
    )
    if (to_pdf) {
      dev.off()
    }
  }
}
```

# Deprecated

```{r}
# for pdf, put "pdf("precision_20_samples.pdf", width=10, height=5)" before and "dev.off()" after plotting
# ggplot(results_precision, aes(x=age)) +
#   geom_line(aes(y = full_vocab_size, colour = "Full Vocab")) +
#   geom_line(aes(y = w2v_vocab_size, colour = "W2V Vocab")) +
#   theme(legend.title=element_blank()) +
#   facet_grid(. ~ language) +
#   labs(title="Vocab size by month", x="Age", y="Vocab Size")

## plus-minus standard

for (measure in measures) {
  print(measure)
  # for (randomization in randomizations) {
  #   print("plotting")
  #   c("plotting\n")
  #   # mean_name <- random_measurement_name(measure, randomization, "mean")
  #   # sd_name <- random_measurement_name(measure, randomization, "sd")
  #   # 
  #   # print("plotting")
  #   # ggplot(results, aes(x=age)) +
  #   #   geom_line(aes(y = !! measure)) +
  #   #   facet_grid(n_clusters ~ language)
  # }
}

# ggplot(results_precision, aes(x=age)) +
#   geom_ribbon(aes(ymin=rand_measure_evo_mean - rand_measure_evo_sd,
#                   ymax=rand_measure_evo_mean + rand_measure_evo_sd),
#               colour="grey",
#               fill="grey",
#               linetype=2,
#               alpha= 0.2) +
#   geom_ribbon(aes(ymin=rand_measure_evo_mean - 2 * rand_measure_evo_sd,
#                   ymax=rand_measure_evo_mean + 2 * rand_measure_evo_sd),
#               colour="grey",
#               fill="grey",
#               linetype=2,
#               alpha= 0.2) +
# #  geom_line(aes(y = rand_measure_evo_mean),
# #            color="grey") +
#   geom_line(aes(y = measure_evo),
#             color="black") +
#   theme(legend.title=element_blank()) +
#   facet_grid(n_clusters ~ language) +
#   labs(title="Precision against clustering at 30 months", x="Age", y="Measure")

```

### 2019-01-28 conceptNet-cogsci/helpers/all_helper.r

@@ -1,0 +1,10 @@
+source("wb_helper.r")
+source("assoc_helper.r")
+source("feature_helper.r")
+source("word2vec_helper.r")
+source("plot_helper.r")
+source("clique_percolation.r")
+source("cluster_helper.r")
+source("cfinder_helper.r")
+source("river_helper.r")
+source("dynamics_helper.r")

### 2019-01-28 conceptNet-cogsci/helpers/assoc_helper.r

@@ -1,0 +1,42 @@
+make_assoc_pairs <- function(lemma_list) {
+  
+  cue_target<- read.csv("data/association_cue_target.csv", as.is = T)
+  # filter until words in lemma_list remain
+  lemma_list<- lemma_list %>% filter((uni_lemma %in% cue_target$cue) | (uni_lemma %in% cue_target$target))
+  lemma<- lemma_list$uni_lemma
+  cue_target<- cue_target %>% 
+    filter(cue %in% lemma, 
+           target %in% lemma, 
+           normed=="YES") %>% 
+    select(cue, target) %>% 
+    mutate(link=1)
+  
+  assoc_table<- expand.grid(cue= lemma, target= lemma) %>% 
+    left_join(cue_target) %>% 
+    mutate(link=if_else(is.na(link),0,link))
+  
+  #make a association network dataframe with item number
+  #rename stuffs so it could conform to the format  needs
+  #item corresponds to target ;  pair corresponds to cue
+  assoc_link <- assoc_table %>%
+    rename(pair.definition = cue) %>%
+    left_join(lemma_list, c("pair.definition" = "uni_lemma")) %>%
+    rename(pair = item, item.definition = target) %>%
+    left_join(lemma_list, c("item.definition" = "uni_lemma")) %>%
+    select(item, item.definition, pair, pair.definition, link) %>%
+    arrange(item, pair) %>%
+    filter(item > pair) # filters item = pair and duplicates
+  
+  return(assoc_link)
+}
+
+assoc_network <- function(vocab, max_age) {
+  vocab_up_to_age = filter(vocab, age <= max_age)
+  assoc_links <- make_assoc_pairs(lemma_list = vocab_up_to_age) %>%
+    filter(link==1) %>%
+    select(item, pair)
+  graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=vocab_up_to_age) %>%
+    set.graph.attribute("name", "Assoc") %>%
+    set.graph.attribute("age", max_age)
+  return(graph)
+}

### 2019-01-28 conceptNet-cogsci/helpers/cfinder_helper.R

@@ -1,0 +1,53 @@
+cluster_cfinder <- function(g, debug = FALSE, cfinder_program) {
+  temp_dir <- paste(tempdir(), as.integer(Sys.time()), sep = "/")
+  while (dir.exists(temp_dir)) {temp_dir <- paste(temp_dir,"_",sep = "")}
+  dir.create(temp_dir)
+  if (debug) {print(str_glue("Working in directory: {temp_dir}"))}
+  write_graph(g, str_glue("{temp_dir}/graph"), format = "ncol")
+  system(str_glue("{cfinder_program} -i {temp_dir}/graph"),
+         ignore.stdout = !debug,
+         ignore.stderr = !debug)
+  
+  ## load calculated clusterings
+  k <- 3
+  clusterings <- list()
+  file <- str_glue("{temp_dir}/graph_files/k={k}/communities")
+  while (file.exists(file)) {
+    clusterings[[k]] <- load_cfinder_communities(file)
+    k <- k + 1
+    file <- str_glue("{temp_dir}/graph_files/k={k}/communities")
+  }
+ 
+  # optimal <- FALSE
+  # k <- 3
+  # while (!optimal) {
+  #   file <- str_glue("{temp_dir}/graph_files/k={k}/communities")
+  #   if (file.exists(file)) {
+  #     clusters <- load_cfinder_communities(file)
+  #   } else {
+  #     k <- NULL
+  #     break
+  #   }
+  #   sizes <- sort(map_int(clusters, length), decreasing = T)
+  #   if (length(clusters) >= 2 && sizes[[2]] * 2 > sizes[[1]]) {
+  #     optimal <- TRUE
+  #   } else {
+  #     k <- k + 1
+  #   }
+  # }
+  # 
+  # if (is.null(k)) {
+  #   clusters <- list()
+  # } else {
+  #   clusters <- load_cfinder_communities(str_glue("{temp_dir}/graph_files/k={k}/communities"))
+  # }
+  # return(list(clusters = clusters, k = k))
+  
+  return(clusterings)
+}
+
+load_cfinder_communities <- function(file) {
+  x <- system(str_glue("grep -v -E '(^#|^[[:space:]]*$)' {file} | sed 's/^[^:]*://g'"), intern = TRUE)
+  string_to_vec <- function(s) {unlist(str_split(str_trim(s), " "))}
+  return(map(x, string_to_vec))
+}

### 2019-01-28 conceptNet-cogsci/helpers/clique_percolation.r

@@ -1,0 +1,116 @@
+# https://github.com/angelosalatino/CliquePercolationMethod-R
+
+clique.community <- function(graph, k) {
+  require(igraph)
+  clq <- cliques(graph, min=k, max=k) %>% lapply(as.vector)
+  
+  
+  #find edges
+  edges <- c()
+  for (i in seq_along(clq)) {
+    for (j in seq_along(clq)) {
+      if ( length(unique(c(clq[[i]], clq[[j]]))) == k+1 ) {
+        edges[[length(edges)+1]] <- c(i,j)
+      }
+    }
+  }
+  
+  #Create an empty graph and then adding edges
+  clq.graph <- make_empty_graph(n = length(clq)) %>% add_edges(unlist(edges))
+  clq.graph <- simplify(clq.graph)
+  V(clq.graph)$name <- seq_len(vcount(clq.graph))
+  
+  
+  comps <- decompose.graph(clq.graph)
+  
+  lapply(comps, function(x) {
+    unique(unlist(clq[ V(x)$name ]))
+  })
+}
+
+######################################################################################################################
+
+clique.community.opt <- function(graph, k){
+  require(igraph)
+  
+  ###################################
+  ### STEP #1: Clique discovery
+  ###################################
+  
+  clq <- cliques(graph, min=k, max=k) %>% lapply(as.vector)
+  
+  
+  ###################################
+  ### STEP #2: Clique-graph creation
+  ###################################
+  
+  #find edges between cliques
+  edges <- c()
+  for (i in 1:(length(clq)-1)) {
+    for (j in (i+1):length(clq)) {
+      if ( length(unique(c(clq[[i]], clq[[j]]))) == k+1 ) {
+        edges[[length(edges)+1]] <- c(i,j)
+      }
+    }
+  }
+  
+  #Create an empty graph and then adding edges
+  clq.graph <- make_empty_graph(n = length(clq)) %>% add_edges(unlist(edges))
+  clq.graph <- simplify(clq.graph)
+  V(clq.graph)$name <- seq_len(vcount(clq.graph))
+  
+  
+  comps <- decompose.graph(clq.graph)
+  
+  lapply(comps, function(x) {
+    unique(unlist(clq[ V(x)$name ]))
+  })
+}
+
+######################################################################################################################
+
+clique.community.opt.par <- function(graph, k){
+  require(igraph)
[…]

### 2019-01-28 conceptNet-cogsci/helpers/cluster_helper.r

@@ -1,0 +1,11 @@
+build_clusters <- function(vocab, membership_vec) {
+  vocab <- as_ids(vocab)
+  clusters <- list()
+  if (length(membership_vec) == 0) {
+    membership_vec = 1
+  }
+  for (i in 1:max(membership_vec)) {
+    clusters[[i]] <- vocab[membership_vec == i]
+  }
+  return(clusters)
+}

### 2019-01-28 conceptNet-cogsci/helpers/dynamics_helper.r

@@ -1,0 +1,94 @@
+### Basic cluster measures
+min_max_size_ratio <- function(clusters) {
+  sizes <- clusters %>%
+    map_int(length)
+  
+  return(min(sizes) / max(sizes))
+}
+
+
+
+### Pairwise statistics
+
+check_same_cluster <- function(elem1, elem2, clusters) {
+  for (cluster in clusters) {
+    if (elem1 %in% cluster & elem2 %in% cluster) {
+      return(TRUE)
+    }
+  }
+  return(FALSE)
+}
+
+# pairwise measurements between clusters
+# NOTE these functions only correspond to the definition for partitions
+pair_true_positives <- function(clusters, true_clusters) {
+  total <- 0
+  for (cluster in clusters) {
+    if (length(cluster) > 1) {
+      for (pair in combn(cluster, 2, simplify = FALSE)) {
+        if (check_same_cluster(pair[[1]], pair[[2]], true_clusters)) {
+          total = total + 1
+        }
+      }
+    }
+  }
+  return(total)
+}
+
+pair_false_positives <- function(clusters, true_clusters) {
+  total <- 0
+  for (cluster in clusters) {
+    if (length(cluster) > 1) {
+      for (pair in combn(cluster, 2, simplify = FALSE)) {
+        if (!check_same_cluster(pair[[1]], pair[[2]], true_clusters)) {
+          total = total + 1
+        }
+      }
+    }
+  }
+  return(total)
+}
+
+pair_false_negatives <- function(clusters, true_clusters) {
+  available_words <- unlist(clusters)
+  true_clusters <- true_clusters %>%
+    map(~ .[. %in% available_words])
+  return(pair_false_positives(true_clusters, clusters))
+}
+
+pair_precision <- function(clusters, true_clusters) {
+  tp <- pair_true_positives(clusters, true_clusters)
+  fp <- pair_false_positives(clusters, true_clusters)
+  return(tp / (tp + fp))
+}
+
+pair_recall <- function(clusters, true_clusters) {
+  tp <- pair_true_positives(clusters, true_clusters)
+  fn <- pair_false_negatives(clusters, true_clusters)
+  return(tp / (tp + fn))
+}
+
+pair_f1 <- function(clusters, true_clusters) {
+  precision <- pair_precision(clusters, true_clusters)
+  recall <- pair_recall(clusters, true_clusters)
+  return(2 * (precision * recall) / (precision + recall))
+}
+
[…]

### 2019-01-28 conceptNet-cogsci/helpers/feature_helper.r

@@ -1,0 +1,28 @@
+load_features <- function() {
+  features <- read_delim("data/MacRae.csv", delim = ",") %>%
+    select(Concept, Feature, WB_Label, BR_Label)# %>%
+  #rename(uni_lemma=Concept)
+  
+  return(features)
+}
+
+filter_to_features <- function(vocab) {
+  features <- load_features()
+  
+  return (vocab %>%
+    filter(uni_lemma %in% features$Concept))
+}
+
+make_feature_links <- function(vocab, feature_types) {
+  features <- load_features() %>%                  
+    filter(Concept %in% vocab$uni_lemma) %>% # remove unneccessary features
+    filter(BR_Label %in% feature_types) %>%  # filter to feature type
+    select(Concept, Feature)
+  
+  pairs <- inner_join(features, features, by="Feature") %>%
+    filter(Concept.x < Concept.y) %>% # remove duplicates
+    count(Concept.x, Concept.y) %>%
+    rename(from = Concept.x, to = Concept.y, shared = n)
+  
+  return(pairs)
+}

### 2019-01-28 conceptNet-cogsci/helpers/network_helper.R

@@ -1,0 +1,29 @@
+# a vocabulary with aoa data -> a word2vec network
+vocab_to_w2v_network <- function(vocab) {
+  vocab <- filter_to_w2v(vocab)
+  w2v_links <- make_w2v_links(vocab = vocab)
+  network <- graph_from_data_frame(w2v_links, vertices = vocab, directed = FALSE) %>%
+    as_tbl_graph() %E>%
+    mutate(weight = w2v_similarity) # layout and clustering algorithms automatically use the weight attribute
+}
+
+# igraph network -> communities object
+w2v_waltrap <- function(w2v_network) {
+  communities_obj <- w2v_network %E>%
+    filter(w2v_similarity > 0) %>%
+    cluster_walktrap(weights = E(.)$w2v_similarity)
+  return(communities_obj)
+}
+
+
+build_clusters <- function(vocab, membership_vec) {
+  vocab <- as_ids(vocab)
+  clusters <- list()
+  if (length(membership_vec) == 0) {
+    membership_vec = 1
+  }
+  for (i in 1:max(membership_vec)) {
+    clusters[[i]] <- vocab[membership_vec == i]
+  }
+  return(clusters)
+}

### 2019-01-28 conceptNet-cogsci/helpers/plot_helper.r

@@ -1,0 +1,156 @@
+layout_network <- function(g, iterations = 10000, delta = 1, gravity = 5, k = 5000) {
+  l <- layout.forceatlas2(g %E>% select(weight),
+                          iterations=iterations,
+                          plotstep=floor(iterations / 10),
+                          directed = FALSE,
+                          delta = delta,
+                          gravity = gravity,
+                          k = k)
+  
+  # move disconnected vertices to 0, 0
+  l[degree(g) == 0,] <- 0
+  
+  # move them to bottom
+  y_size <- max(l[,2]) - min(l[,2])
+  l[degree(g) == 0,2] <- min(l[,2]) - (y_size / 6)
+  
+  # spread them out
+  num_disconnected <- length(l[degree(g) == 0,1])
+  x_size <- max(l[,1]) - min(l[,1])
+  l[degree(g) == 0,1] <- (0:(num_disconnected - 1) / (num_disconnected - 1)) * x_size + min(l[,1])
+  
+  return(l)
+}
+
+plot_vocab_network <- function(g, layout = NULL, name=NA, frame=FALSE, clusters=NULL, plot_title = NULL, edge_color = "grey", labels=V(g)$uni_lemma) {
+  
+  # layout 
+  if (!is.null(layout)) {
+    # do nothing
+  } else if (is.null(layout) && !is.null(V(g)$x)) {
+    x <- V(g)$x
+    y <- V(g)$y
+    layout <- cbind(x,y)
+  } else if (is.null(layout) && is.null(V(g)$x)) {
+    layout <- layout_with_fr(g)
+  }
+  
+  # rescale layout
+  x_size <- max(layout[,1]) - min(layout[,1])
+  y_size <- max(layout[,2]) - min(layout[,2])
+  max_size <- max(x_size, y_size)
+  
+  layout <- layout / max_size
+  
+  # color clusters
+  if (!is.null(clusters)) {
+    V(g)$color <- clusters+1
+    
+    ## Paint the vertices in multiple communities to red
+    #V(g)[ unlist(clusters)[ duplicated(unlist(clusters)) ] ]$color <- "red"
+  }
+  
+  
+  plot(g,
+       layout=layout,
+       frame=frame,
+       rescale=FALSE,
+       asp=0, #y_size / x_size,
+       xlim=c(min(layout[,1]), max(layout[,1])),
+       ylim=c(min(layout[,2]), max(layout[,2])),
+       
+       # === vertex
[…]

### 2019-01-28 conceptNet-cogsci/helpers/random_helper.r

@@ -1,0 +1,92 @@
+# random_clusters_of_shape <- function(shape_clusters, source_clusters) {
+#   source_vocab <- unlist(source_clusters)
+#   random_vocab <- sample(source_vocab, length(unlist(shape_clusters)))
+#   
+#   random_clusters <- list()
+#   for (cl in 1:length(shape_clusters)) {
+#     start_idx <- length(unlist(shape_clusters[1:cl - 1])) + 1
+#     end_idx <- length(unlist(shape_clusters[1:cl]))
+#     random_clusters[[cl]] <- random_vocab[start_idx: end_idx]
+#   }
+#   return(random_clusters)
+# }
+
+# randomize_clusters_evo <- function(clusters_evo) {
+#   random_clusters_evo <- list()
+#   random_clusters_evo[[length(clusters_evo)]] <- clusters_evo[[length(clusters_evo)]]
+#   for (age in (length(clusters_evo) - 1):1) {
+#     random_clusters_evo[[age]] <- random_clusters_of_shape(clusters_evo[[age]], random_clusters_evo[[age + 1]])
+#   }
+#   return(random_clusters_evo)
+# }
+
+# randomize_network_evo <- function(net_evo) {
+#   net_sizes <- map(net_evo, ~ length(V(.)) )
+#   random_net_evo <- list()
+#   random_net_evo[[length(net_evo)]] <- net_evo[[length(net_evo)]]
+#   for (age in (length(net_evo) - 1):1) {
+#     random_net_evo[[age]] <-random_net_evo[[age + 1]] %N>% sample_n(net_sizes[[age]])
+#   }
+#   return(random_net_evo)
+# }
+
+randomize_aoa <- function(vocab) {
+  shuffled <- vocab[sample(nrow(vocab)),]
+  return(tibble(
+    uni_lemma = shuffled$uni_lemma,
+    definition = shuffled$definition,
+    age = vocab$age,
+    category = shuffled$category
+  ))
+}
+
+randomize_aoa_to_nearest <- function(vocab) {
+  vocab <- randomize_aoa(vocab) # picks random first word and randomizes ties in similarity comparisons
+  w2v <- load_w2v() %>%
+    filter(from %in% vocab$uni_lemma) %>%
+    filter(to %in% vocab$uni_lemma)
+  for(i in 2:(nrow(vocab) - 1)) {
+    learned <- vocab$uni_lemma[1:(i-1)]
+    unlearned <- vocab$uni_lemma[i:nrow(vocab)]
[…]

### 2019-01-28 conceptNet-cogsci/helpers/river_helper.r

@@ -1,0 +1,45 @@
+cluster_river <- function(subgraphs_by_age) {
+  
+  # river node data
+  nodes = data.frame(ID = character(0),
+                     x = integer(0),
+                     labels = character(0),
+                     stringsAsFactors = FALSE)
+  
+  for (i in 1:length(subgraphs_by_age)) {
+    subgraphs <- subgraphs_by_age[[i]]
+    for (j in 1:length(subgraphs)) {
+      id <- str_glue("{i}_{j}")
+      x <- i
+      g <- subgraphs[[j]]
+      label <- "" # V(g)[which.max(eigen_centrality(g)$vector)]$name 
+      nodes[nrow(nodes) + 1,] <- list(id, x, label)
+    }
+  }
+  
+  # edge data
+  edges = data.frame(N1 = character(0),
+                     N2 = character(0),
+                     Value = integer(0),
+                     stringsAsFactors = FALSE)
+  
+  for (i in 1:(length(subgraphs_by_age) - 1)) {
+    curr_subgraphs <- subgraphs_by_age[[i]]
+    next_subgraphs <- subgraphs_by_age[[i + 1]]
+    
+    for(from in 1:length(curr_subgraphs)) {
+      for(to in 1:length(next_subgraphs)) {
+        from_id <- str_glue("{i}_{from}")
+        to_id <- str_glue("{i + 1}_{to}")
+        flow <- length(intersect(V(curr_subgraphs[[from]])$name,
+                                 V(next_subgraphs[[to]])$name))
+        if (flow > 0) {
+          edges[nrow(edges) + 1,] <- list(from_id, to_id, flow)
+        }
+      }
+    }
+  }
+  
+  return(makeRiver(nodes = nodes, edges = edges))
+}
+

### 2019-01-28 conceptNet-cogsci/helpers/river_helper_network3d.R

@@ -1,0 +1,53 @@
+cluster_river <- function(subgraphs_by_age) {
+  
+  # river node data
+  nodes = tibble(name = character(0))
+  
+  for (i in 1:length(subgraphs_by_age)) {
+    subgraphs <- subgraphs_by_age[[i]]
+    for (j in 1:length(subgraphs)) {
+      name <- V(g)[which.max(eigen_centrality(g)$vector)]$name 
+      nodes[nrow(nodes) + 1,] <- list(name)
+    }
+  }
+  
+  # edge data
+  edges = tibble(source = integer(0),
+                 target = integer(0),
+                 value = double(0))
+  
+  for (i in 1:(length(subgraphs_by_age) - 1)) {
+    curr_subgraphs <- subgraphs_by_age[[i]]
+    next_subgraphs <- subgraphs_by_age[[i + 1]]
+    
+    for(from in 1:length(curr_subgraphs)) {
+      for(to in 1:length(next_subgraphs)) {
+        from_id <- str_glue("{i}_{from}")
+        to_id <- str_glue("{i + 1}_{to}")
+        flow <- length(intersect(V(curr_subgraphs[[from]])$name,
+                                 V(next_subgraphs[[to]])$name))
+        if (flow > 0) {
+          edges[nrow(edges) + 1,] <- list(from_id, to_id, flow)
+        }
+      }
+    }
+  }
+  
+  # enumerate
+  edges <- edges %>%
+    mutate(source = map(edges$source, ~ which(nodes$id == .)[1] - 1),
+           target = map(edges$target, ~ which(nodes$id == .)[1] - 1))
+  nodes <- nodes %>%
+    mutate(id = seq(0,length(nodes$id) - 1))
+  
+  #return(list(nodes = nodes, edges = edges))
+  
+  
+  
+  nodes <- tibble(name = c("One", "Two", "Three", "Four", "Five", "Six"))
+  links <- tibble(source = c(0,0,1,1,2,2,3,3),
+                  target = c(2,3,2,3,4,5,4,5),
+                  value = c(1.0,2,3,4,1,2,3,4))
+  return(list(nodes = nodes, links = links))
+}
+

### 2019-01-28 conceptNet-cogsci/helpers/statistics_helper.r

@@ -1,0 +1,7 @@
+quantile_func <- function(x, probs){
+  if (anyNA(x)){
+    return(NA)
+  } else {
+    return(quantile(x, probs = probs))
+  }
+}

### 2019-01-28 conceptNet-cogsci/helpers/wb_helper.r

@@ -1,0 +1,208 @@
+# This file contains functions used to get item data, admin data, etc. , and generate dataframes for analysis
+import_all_library<- function(){
+  library(tidyr)
+  library(purrr)
+  library(readr)
+  library(ggplot2)
+  library(langcog)
+  library(boot)
+  library(lazyeval)
+  library(dplyr)
+  library(wordbankr)
+  library(directlabels)
+  library(scales)
+  library(stringr)
+  library(lmtest)
+}
+######################################################################################################################
+get_lang_item_data <- function(lang, lang_form = "WS", lex_class = "nouns") {
+
+  item_data <- get_item_data(language = lang, form = lang_form) %>%
+    select(num_item_id, definition, type, lexical_class, uni_lemma, category) %>%
+    filter(type == "word", lexical_class == lex_class) %>%
+    rename(item = num_item_id)
+  
+  #Initialize every item as NA (NOT yet learnt)
+  lang_item <- item_data %>%
+    select(item, definition, uni_lemma, category) %>%
+    mutate(age = NA)
+  
+  return(lang_item)
+}
+
+######################################################################################################################
+# get only "useful" admin data (where production is not NA)
+get_lang_admin_data <- function(lang, lang_form = "WS") {
+  #get the kids' data_id from every age
+  admin_data <- get_administration_data() %>%
+    ## get_administration_data() %>% filter(form == "WS", !is.na(production), language == "German") %>% .$source_name %>% unique()
+    filter(form == lang_form, !is.na(production), language == lang) %>%
+    select(data_id, age) %>%
+    arrange(age)
+  
+  return(admin_data)
+}
+
+######################################################################################################################
+# See how many kids we have in every age
+get_kids_by_age <- function(admin_data) {
+  #get number of kids by age
+  nkids_by_age <- admin_data %>%
+    group_by(age) %>%
+    summarise(n = n())
+  return(nkids_by_age)
+}
+
+######################################################################################################################
+#get "produces" instrument data 
+get_lang_instr_data <- function(lang, lang_form = "WS") {
+  instr_data <- get_instrument_data(language = lang,
+                                    form = lang_form) %>%
+    filter(value == "produces") %>%
+    arrange(num_item_id) %>%
+    rename(item = num_item_id)
+  
+  return(instr_data)
+}
[…]

### 2019-01-28 conceptNet-cogsci/helpers/word2vec_helper.r

@@ -1,0 +1,37 @@
+load_w2v_ <- function() {
+  w2v <- read_delim("data/w2v_pair.csv", delim = ",") %>%
+    rename(from = item.definition, to = pair.definition, w2v_similarity = sim) %>%
+    # filter(w2v_similarity > 0.000001) %>%
+    filter(from < to) %>% # remove duplicates
+    trim_w2v()
+
+  return(w2v)
+}
+
+load_w2v <- memoise(load_w2v_)
+
+trim_w2v <- function(w2v) {
+  w2v <- w2v %>%
+    mutate(from = gsub(" \\s*\\([^\\)]+\\)","", from)) %>% # remove parenthesized
+    mutate(to = gsub(" \\s*\\([^\\)]+\\)","", to)) %>%
+    group_by(from, to) %>%
+    summarise(w2v_similarity = max(w2v_similarity)) %>%
+    filter(from < to) # remove duplicates created during trimming
+  
+  return(w2v)
+}
+
+filter_to_w2v <- function(vocab) {
+  w2v <- load_w2v()
+  
+  return (vocab %>%
+    filter(uni_lemma %in% w2v$from | uni_lemma %in% w2v$to)) # word must occur in word2vec data
+}
+
+make_w2v_links <- function(vocab) {
+  w2v <- load_w2v() %>%
+    filter(from %in% vocab$uni_lemma &
+             to %in% vocab$uni_lemma)
+  
+  return(w2v)
+}

### 2019-02-12 conceptNet-cogsci/CogsciBackground.Rmd
Added CogsciBackground

--- 2019-01-28 conceptNet-cogsci/Cogsci.Rmd
@@
 ---
-title: "CogSci Analysis"
+title: "CogSci Background Analysis"
 author: "Isaac Scheinfeld"
@@
 ## Build Word2Vec Network Evolution
+```{r message=FALSE}
+test_vocab <- get_language_vocab("German")
+test_w2v_network <- vocab_to_w2v_network(test_vocab)
+test_feature_network <- vocab_to_feature_network(test_vocab, c('function'))
 
-```{r message=FALSE}
-clusters_evolution <- function(vocab, n_clusters, min_age, max_age, randomization) {
+transitivity(test_w2v_network)
+transitivity(test_feature_network)
 
-  if(randomization == "none") {
-    # do nothing
-  } else if(randomization == "random_aoa") {
-    vocab <- randomize_aoa(vocab) # TODO handle randomization, write "randomize_aoa"" in random_helper.r
-  } else if(randomization == "to_nearest_aoa") {
-    vocab <- randomize_aoa_to_nearest(vocab)
-  } else if(randomization == "within_last_clustering") {
-    vocab <- randomize_within_last_clustering(vocab, n_clusters)
-  } else {
-    stop("Randomization argument incorrect.")
-  }
-
-  vocab_network <- vocab_to_w2v_network(vocab) # drops words w/o w2v data, NOTE memoizes w2v data
-
-  # list of networks at each age
-  net_evo <- min_age:max_age %>%
-    map(~ filter(activate(vocab_network, nodes), age <= .))
-
-  # list of vocabulaires at each age
-  vocab_evo <- net_evo %>%
-    map(V)
-
-  # list of cluster membership index vectors at each age
-  membership_evo <- net_evo %>%
-    map(w2v_waltrap) %>%
-    map(~ cut_at(., no = n_clusters))
-
-  # list of word clusters at each age
-  clusters_evo <- map2(vocab_evo, membership_evo, build_clusters)
-
-  return(clusters_evo)
-}
-```
-
-# Analysis
-
-## Measure Clustering Dynamics
-
-```{r}
-# language, n_clusters, age range, random samples, dynamics measure -> analysis
-# example measure is function(clusters_evo) {pair_measures_to_last(clusters_evo, measure)}
-run_measure <- function(clusters_evo, measure) {
-  if (measure == "pair_precision_to_last") {
-    return(pair_measures_to_last(clusters_evo, pair_precision))
-  } else if (measure == "pair_recall_to_last") {
-    return(pair_measures_to_last(clusters_evo, pair_recall))
-  } else if (measure == "pair_f1_to_last") {
-    return(pair_measures_to_last(clusters_evo, pair_f1))
-  } else if (measure == "min_max_size_ratio") {
-    return(map_dbl(clusters_evo, min_max_size_ratio))
-  } else if (measure == "modularity") {
-    return(map_dbl(clusters_evo, min_max_size_ratio))
-  } else {
-    stop("Incorrect Dynamics Measure Name")
-  }
-}
-
-# -----------------------------------------------------------------------------------------------
-# given a language and # of clusters, the dynamics measures and randomizations are calculated
-# together to avoid repeatedly sampling clusterings
-# -----------------------------------------------------------------------------------------------
-
-measure_cluster_dynamics <- function(language, n_clusters, measures, randomizations, samples) {
-    vocab <- get_language_vocab(language)
-
-    # measurement schema : age, measure, randomization, sample, value
-    measurements <- list() # list of measurement tibbles
-
-    # true vocabulary sizes (full vocabulary size at each month)
-    measurements[["true_vocab_sizes"]] <-
-      tibble(age = min(vocab$age):max(vocab$age),
-             measure = "true_vocab_size",
-             randomization = NA, # same for all randomizations
-             sample = NA,
-             value = min(vocab$age):max(vocab$age) %>%
-               map(~ filter(vocab, age <= .)) %>%
-               map(nrow) %>%
-               unlist())
-
-    # --------------------- true aoa measures --------------------- #
-    true_clusters_evo <- clusters_evolution(vocab,
-                                            n_clusters,
-                                            min(vocab$age),
-                                            max(vocab$age),
-                                            randomization = "none")
-
-    # w2v vocabulary sizes (number of words know at each month in clustering)
-    measurements[["w2v_vocab_sizes"]] <- 
-      tibble(age = min(vocab$age):max(vocab$age),
-             measure = "w2v_vocab_size",
-             randomization = NA, # same for all randomizations
-             sample = NA,
-             value = unlist(map(true_clusters_evo, ~ length(unlist(.)))))
-
-    # dynamics measures
-    for (measure in measures) {
-      value <- run_measure(true_clusters_evo, measure)
-      measurements[[measure]] <-
-        tibble(age = min(vocab$age):max(vocab$age),
-               measure = measure,
-               randomization = "none",
-               sample = NA,
-               value = value)
-    }
-
-    # --------------------- randomized aoa measures --------------------- #
-    for (randomization in randomizations) {
-
-      for (sample in 1:samples) {
-        random_clusters_evo <- clusters_evolution(vocab,
-                                                  n_clusters,
-                                                  min(vocab$age),
-                                                  max(vocab$age),
-                                                  randomization = randomization)
-
-        for (measure in measures) {
-          value <- run_measure(random_clusters_evo, measure)
-          measurements[[paste(randomization, measure, sample, sep = "__")]] <-
-            tibble(age = min(vocab$age):max(vocab$age),
-                   measure = measure,
-                   randomization = randomization,
-                   sample = sample,
-                   value = value)
-        }
-      }
-    }
-
-    return(bind_rows(measurements))
-}
-
-run_experiment <- function(languages, measures, randomizations, cluster_counts, samples) {
-  measurements = list()
-  cat("measuring dynamics\n")
-  for(language in languages) {
-    cat("  language:", language, "\n")
-    for(n_clusters in cluster_counts) {
-      cat("    n_clusters: ", n_clusters, "\n")
-      measurements[[length(measurements) + 1]] <- 
-        measure_cluster_dynamics(language, n_clusters, measures, randomizations, samples) %>%
-        mutate(language = language) %>%
-        mutate(n_clusters = n_clusters) %>%
-        select(language, n_clusters, everything())
-    }
-  }
-  return(bind_rows(measurements))
-}
-```
-
-## Run Experiment
-
-```{r warning=FALSE, message=FALSE}
-languages <-  c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish")
-
-measures <- c("pair_precision_to_last", "pair_recall_to_last", "pair_f1_to_last", "min_max_size_ratio")
-
-randomizations <- c("random_aoa", "to_nearest_aoa", "within_last_clustering")
-
-### compute measurements, TAKES A LONG TIME
-
-# measurements <- run_experiment(languages = languages,
-#                           measures = measures,
-#                           randomizations = randomizations,
-#                           cluster_counts = 2:5,
-#                           samples = 50)
-# 
-#saveRDS(measurements, "measurements.rds")
-
-measurements <- readRDS("measurements.rds")
+# weights = E(test_w2v_network)$w2v_similarity
+# weights = E(test_feature_network)$shared
 
@@
 
-## Summarize and Visualize Results
 ```{r}
-to_pdf = FALSE
+w2v_clusters <- cut_at(w2v_walktrap(test_w2v_network), no = 3)
+feature_clusters <- cut_at(feature_walktrap(test_feature_network), no = 3)
 
-### Plot vocab sizes
-vocab_sizes <- measurements %>%
-  select(language, n_clusters, age, measure, value) %>%
-  filter(measure %in% c("true_vocab_size", "w2v_vocab_size"))
-
-if (to_pdf) {
-  pdf("output/vocab_size.pdf", width=20, height=3)
-}
-ggplot(vocab_sizes) +
-  geom_line(aes(x = age, y = value, colour = measure)) + 
-  facet_grid(~ language)
-if (to_pdf) {
-  dev.off()
-}
+plot_vocab_network(test_w2v_network, 
+                   layout = NULL, 
+                   name=NA, 
+                   frame=FALSE, 
+                   clusters=w2v_clusters, 
+                   plot_title = NULL, 
+                   edge_color = "grey", 
+                   labels=V(test_w2v_network)$uni_lemma)
 ```
-```{r}
-### Plot measure summary
-to_pdf = FALSE
-
-for (measure_to_plot in measures) {
-  for (randomization_to_plot in randomizations) {
-
-    summary_fname <- paste(measure_to_plot, randomization_to_plot, sep="__") %>%
-      paste("pdf", sep = ".")
-
-    # APPROACH # 1
-    true_evolution <- measurements %>%
-      filter(measure == measure_to_plot) %>%
-      filter(randomization == "none") %>%
-      select(language, n_clusters, age, value)
-
-    random_evolution <- measurements %>%
-      filter(measure == measure_to_plot) %>%
-      filter(randomization == randomization_to_plot) %>%
-      group_by(language, n_clusters, age) %>%
-      summarise(mean = mean(value),
-                sd = sd(value),
-                `25%`=quantile_func(value, probs=0.25),
-                `50%`=quantile_func(value, probs=0.5),
-                `75%`=quantile_func(value, probs=0.75),
-                `10%`=quantile_func(value, probs=0.1),
-                `90%`=quantile_func(value, probs=0.9)) %>%
-      ungroup()
-
-    evolution <- full_join(true_evolution, random_evolution, by = c("language", "n_clusters", "age"))
-
-    if (to_pdf) {
-      pdf(paste("output",summary_fname,sep="/"), width=20, height=10)
-    }
-    print(
-      ggplot(evolution, aes(x = age)) +
-        geom_ribbon(aes(ymin = `10%`,
-                        ymax = `90%`),
-                    colour="yellow",
-                    fill="yellow",
-                    linetype=2,
-                    alpha= 0.2) +
-        geom_ribbon(aes(ymin = `25%`,
-                        ymax = `75%`),
-                    colour="orange",
-                    fill="orange",
-                    linetype=2,
-                    alpha= 0.3) +
-        geom_line(aes(y = `50%`), color = "red", alpha = 0.4) + 
-        geom_line(aes(y = value), color = "blue") +
-        labs(title = paste("True value against",
-                           randomization_to_plot,
-                           "statistics on",
-                           max(measurements$sample, na.rm = TRUE), 
-                           "samples"),
-             subtitle = "25%-75% and 10%-90% quantiles shown",
-             x ="Age (m)", y = measure_to_plot) +
-        facet_grid(n_clusters ~ language)
-    )
-    if (to_pdf) {
-      dev.off()
-    }
-  }
-}
-```
-
-# Deprecated
-
-```{r}
-# for pdf, put "pdf("precision_20_samples.pdf", width=10, height=5)" before and "dev.off()" after plotting
-# ggplot(results_precision, aes(x=age)) +
-#   geom_line(aes(y = full_vocab_size, colour = "Full Vocab")) +
-#   geom_line(aes(y = w2v_vocab_size, colour = "W2V Vocab")) +
-#   theme(legend.title=element_blank()) +
-#   facet_grid(. ~ language) +
-#   labs(title="Vocab size by month", x="Age", y="Vocab Size")
-
-## plus-minus standard
-
-for (measure in measures) {
-  print(measure)
-  # for (randomization in randomizations) {
-  #   print("plotting")
-  #   c("plotting\n")
-  #   # mean_name <- random_measurement_name(measure, randomization, "mean")
-  #   # sd_name <- random_measurement_name(measure, randomization, "sd")
-  #   # 
-  #   # print("plotting")
-  #   # ggplot(results, aes(x=age)) +
-  #   #   geom_line(aes(y = !! measure)) +
-  #   #   facet_grid(n_clusters ~ language)
-  # }
-}
-
-# ggplot(results_precision, aes(x=age)) +
-#   geom_ribbon(aes(ymin=rand_measure_evo_mean - rand_measure_evo_sd,
-#                   ymax=rand_measure_evo_mean + rand_measure_evo_sd),
-#               colour="grey",
-#               fill="grey",
-#               linetype=2,
-#               alpha= 0.2) +
-#   geom_ribbon(aes(ymin=rand_measure_evo_mean - 2 * rand_measure_evo_sd,
-#                   ymax=rand_measure_evo_mean + 2 * rand_measure_evo_sd),
-#               colour="grey",
-#               fill="grey",
-#               linetype=2,
-#               alpha= 0.2) +
-# #  geom_line(aes(y = rand_measure_evo_mean),
-# #            color="grey") +
-#   geom_line(aes(y = measure_evo),
-#             color="black") +
-#   theme(legend.title=element_blank()) +
-#   facet_grid(n_clusters ~ language) +
-#   labs(title="Precision against clustering at 30 months", x="Age", y="Measure")
-
-```

### 2019-02-12 conceptNet-cogsci/helpers/feature_helper.r

@@ -21,7 +21,9 @@ make_feature_links <- function(vocab, feature_types) {
   
   pairs <- inner_join(features, features, by="Feature") %>%
     filter(Concept.x < Concept.y) %>% # remove duplicates
-    count(Concept.x, Concept.y) %>%
+    group_by(Concept.x, Concept.y) %>%
+    summarise(n=n()) %>%
+    ungroup() %>%
     rename(from = Concept.x, to = Concept.y, shared = n)
   
   return(pairs)

### 2019-02-12 conceptNet-cogsci/helpers/network_helper.R

@@ -1,17 +1,73 @@
 # a vocabulary with aoa data -> a word2vec network
-vocab_to_w2v_network <- function(vocab) {
-  vocab <- filter_to_w2v(vocab)
+# vocab_to_w2v_network <- function(vocab) {
+#   vocab <- filter_to_w2v(vocab)
+#   w2v_links <- make_w2v_links(vocab = vocab)
+#   network <- graph_from_data_frame(w2v_links, vertices = vocab, directed = FALSE) %>%
+#     as_tbl_graph() %E>%
+#     mutate(weight = w2v_similarity) # layout and clustering algorithms automatically use the weight attribute
+# }
+
+# a vocabulary with aoa data -> a word2vec network
+vocab_to_w2v_network <- function(vocab, filter_to = "both") {
+  if (filter_to == "both") {  # filter vocab to just words for which we have both w2v and features
+    vocab <- vocab %>%
+      filter_to_w2v() %>%
+      filter_to_features()
+  } else if (filter_to == "w2v") {
+    vocab <- filter_to_w2v(vocab)
+  } else if (filter_to == "features") {
+    vocab <- filter_to_features(vocab)
+  } else {
+    # don't filter vocab
+  }
+ 
   w2v_links <- make_w2v_links(vocab = vocab)
-  network <- graph_from_data_frame(w2v_links, vertices = vocab, directed = FALSE) %>%
-    as_tbl_graph() %E>%
-    mutate(weight = w2v_similarity) # layout and clustering algorithms automatically use the weight attribute
+  
+  return(
+    graph_from_data_frame(w2v_links, vertices = vocab, directed = FALSE) %>%
+      as_tbl_graph() %E>%
+      mutate(weight = w2v_similarity)
+  ) # layout and clustering algorithms automatically use the weight attribute
+  
 }
 
+vocab_to_feature_network <- function(vocab, feature_types, filter_to = "both") {
+  if (filter_to == "both") {  # filter vocab to just words for which we have both w2v and features
+    vocab <- vocab %>%
+      filter_to_w2v() %>%
+      filter_to_features()
+  } else if (filter_to == "w2v") {
+    vocab <- filter_to_w2v(vocab)
+  } else if (filter_to == "features") {
+    vocab <- filter_to_features(vocab)
+  } else {
+    # don't filter vocab
+  }
+  
+  feature_links <- make_feature_links(vocab = vocab, feature_types)
+  
+  return(
[…]

### 2019-02-12 CMCL/ms.Rmd
paper

---
title: "How to Make a Camera-Ready Proceedings Contribution"

author-information: > 
    \author{{\large \bf Author 1} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University
    \And {\large \bf Author 2} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University}

abstract: 
    "This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of EACL-2017. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document."

final_submission: no
# If yes, uncomment line below and add your own ID
# eaclpaperid: "1234"

# Uncomment and change if you want a smaller titlebox; minimum length is 5cm
# titlebox_length: "5cm"

output: acl2017::acl_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(dplyr)
library(ggplot2)
library(grid)
library(lme4)
library(lmerTest)
library(ggthemes)
library(ggplot2)
library(xtable)
```

# Methods

##Nouns 
We used data from Wordbank (Frank et al., 2017), an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version. Parent report is a reliable and valid measure of children's vocabulary (Fenson et al., 1994). We used a set of nouns representing hand-checked translation equivalents  across 10 languages (available in Wordbank database). We "assume" (i should ask what were the criteria for the unilemma selection) that this set of translation equivalents is representative of a core shared vocabulary across all children (in different cultures) by around 30 months, 
<!--and we study possible cross-lingusitic variation in the way this shared knowledge is arrived at in development. -->

The conceptual organization derived from this shared vocabulary is obviousely identical across languages, but we investigate whether there are systematic cross-lingusitc variations in the order of aquisition of words that make up this vocabulary, and crucially, whether such variation influences the induced conceptual organization at different points in time. In fact, differences in the order of acqusition of words do not necessarily give rise to different conceptual organization. Imagine that two languages vary in whether "cow" or "dog" is acquired first. This difference will not change the induced conceptual organization across time since both "dog" and "cow" are instances of the same high-level concept "animal".

```{r fig.env = "figure", fig.pos = "h", fig.align = "center", set.cap.width=T, fig.width=4, fig.height=3, num.cols.cap=2, fig.cap = "bla bla"}

cor_all <- feather::read_feather("../saved_data/data_corr_all.feather")

ggplot(cor_all, 
      aes(x = tau, fill=data)) +
  geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
                 alpha=0.5,
                 binwidth=0.05)+
  #scale_x_log10() +
  theme_few() + 
  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +  #facet_grid(Segmentation ~ language)+
  scale_y_continuous(labels = scales::percent)+
  xlab("pairwise correlation") +ylab("Count")

```

## Features
We used two sources of information which represent two ways words may be related to one another in the semantic network. The first source was the MacRae features (McRae et al., 2005). These features were collected by giving adult participants a set of nouns and prompting them to provide various kinds of properties (perceptual, functional, encyclopedic, and taxonomic). We followed Hills et al. 2010 in excluding the encyclopedic and taxonomic properties as their role may not be important at this stage of development. The other source was the semantic similarity derived based on co-occurrence in the corpus of CHILDES, using word2vec.

##Network 
We constructed networks using CDI words as nodes. Pairs of words were linked by an edge weighted by the number of shared MacRae feature or with the continuous distance obtained via Word2vec.  To model change in the conceptual organization from month to month, we constructed a different network at each month, based on the words that have been acquired by that month. We defined the age of acquisiton of a given word by the month at which this noun was produced by at least 50% of children, in each language (Goodman et al., 2008).

## Small World properties
We test whether the networks display the so-called "small-world" properties similar to other semantic and real-world networks (Steyvers & Tenenbaum, 2005; Watts & Strogatz, 1998). Small world properties are characterized with the average clustering coefficient $C$ and the average shortest path $L$. The former measures the extent to which the network is clustered, i.e., made of highly connectned sub-networks, whereas the latter measures the typical separation between tow nodes in the network. A network is small-word if it has a higher clustering coeffient comapred to a randomly connected network of the same size $C \gg C_{random}$, while still having a shorest path length as small as the one typically observed in random networks, that is $L \approx L_{random}$.

```{r fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=14, fig.cap = "bla bla"}
measurements <- readRDS("data/measurements.rds")

all <- measurements %>%
  filter(measure %in% c("pair_precision_to_last", "pair_recall_to_last"),
         randomization != "to_nearest_aoa") #%>%
  #group_by(n_clusters, age, measure, randomization) %>%
  #summarise(mean = mean(value))

all_sum <- all %>%
  group_by(measure, randomization, age) %>%
  summarise(myMean = mean(value, na.rm = TRUE))

ggplot(data=all, aes(x=age, y=value, col=randomization)) +
  #geom_point() +
  geom_smooth(method="lm", formula = y ~ poly(x, 3)) +
  #geom_smooth(method="lm", formula = y ~ log(x)) +
  theme_few() + 
  theme(aspect.ratio = 0.7)+
  facet_grid(.~measure)
```
## Clustering analysis
We identified network clusters using WalkTrap (Pons & Latapy, 2006), a community detection algorithm based on the fact that a random walker tends to be trapped in dense parts of a network corresponding to highly interconnected sub-groups of nodes.

## Evaluation of clusterings aross development
We note $\mathcal{C}_t$ the clustering at month $t$, based on the subset of the vocabulary acquired by that month in each language. The evaluation consists in comparing $\mathcal{C}_t$ to the final clustering $\mathcal{C}^*$ obtained using the full vocabulary by the last month of acquisition (i.e., $\mathcal{C}^*$=$\mathcal{C}_t$ for $t$=30 months). Such comparison allows us to study how words acquired at different points in time may induce changes in the conceptual organization. In addition, we investigate consistency and variability in this change across languages.

We compare $\mathcal{C}_t$ to $\mathcal{C}^*$ using a standard method in clustering comparison, which is based on counting word pairs on which the two clusterings agree or disagree (Rand, 1971; Hubert and Arabie, 1985). A pair of words learned by month $t$ can fall under one of the four follwoing cases: 1) pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$ (True positives, noted as $tp(\mathcal{C}_t)$), 2) pairs placed in different clsuters under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$ (True negatives, $tn(\mathcal{C}_t)$), 3) pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$ (False positive, $fp(\mathcal{C}_t)$), and 4) pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$ (False negatives, $fn(\mathcal{C}_t)$).

The clustering precison $P(\mathcal{C}_t)$ and recall $R(\mathcal{C}_t)$ are defiend as follows:

$$
P(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fp(\mathcal{C}_t)|}
$$
$$
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
$$
Both Precison and Recall converge to 1 (perfect score) as $\mathcal{C}_t$ becomes more and more similar to $\mathcal{C}^*$. If precision starts low before converging to 1 (as opposed to being a constant at 1), this pattern would indicate that some pairs that should be differentiated are initially lumped together, suggesting a process of "differentiation" over development. Similarly, if we observe an increase in Recall, this pattern would indicate that some pairs that should be associated are initially differentiate, suggesting a process of "coelescence" over development.

## Word ordering 
The question we are addressing is whether the order of acqusition of words affect the

#Results

For real and random: results show that both precision and recall increase across development, suggesting that the conceptual organization undergoes both differentiation for some word pairs (example), and coelescecne for other pairs (examples).

For within-cluster: precision is high, but recall is low: explain why

How to explain this change?

>Assuming a random/real ranking of words:
-Some words may be lamped together initially (even if we force a relatively high number of clusters) because of the smaller vocabulary size? Can we have an example of this? Are the other clsuters empty?
-Some words may be differentiated initially because of the forcing?
-Is there a roleof noise? maybe clustering is just more random for smaller size vocabulary?

>Assuming a with-cluster ranking of words:
-Some words may be lamped together initially (even if we force a relatively high number of clusters): this does not happen, at least while we are still working with the first cluster...that's why precision is generally high
-Some words may be differentiated initially because they

<!--
If precision is lower early on, it means that initial concepts are not differentiated enough, that is, pairs that should belong to different concpets are intially lamped together (false positives), despite the fact that we forced the same number of clsuters in both $\mathcal{C}_t$ and $\mathcal{C}^*$ (Why is this the case? This looks like an artefact of the clustering algorithm with smaller size data? Should discuss this with Isaac. Also, what is an exmaple of a clustering $\mathcal{C}_t$ for a smaller size: are some clusters totally empty?)

Quetions:
Why does the control precision decreese a bit during developmnt, isn't supposed to be 1 all along? since we are splitting words within the same cluster (unless maybe some clusters are empty) : Oh I guess because we start introducing additional categories
-->

## Order of word learning

# Sudy of the conceptual development

Models

```{r}
# What is the model that can predict values as a function of cluser number and the methio 
#m1_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_precision_to_last' & randomization != "random_aoa"),
#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

##Test of convergence
#(From: https://github.com/lme4/lme4/issues/120)
#relgrad <- with(m1_precision@optinfo$derivs,solve(Hessian,gradient))
#max(abs(relgrad))

#saveRDS(m1_precision, "model_1.rds")
m1_precision <- readRDS("model_1.rds")

#m2_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_precision_to_last' & randomization != "within_last_clustering"),
#           control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

#saveRDS(m2_precision, "model_2.rds")
m2_precision <- readRDS("model_2.rds")

##Test of convergence
#relgrad <- with(m2_precision@optinfo$derivs,solve(Hessian,gradient))
#max(abs(relgrad))

#m1_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_recall_to_last' & randomization != "random_aoa"),
#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

#saveRDS(m1_recall, "model_recall_1.rds")
m1_recall <- readRDS("model_recall_1.rds")

#m2_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_recall_to_last' & randomization != "within_last_clustering"),
#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

#saveRDS(m2_recall, "model_recall_2.rds")
m2_recall <- readRDS("model_recall_2.rds")

```

# Important citation stuff! READ!

## Why we can't have nice things

So because the ACL committee wants their `.tex` files all nice and consistent, the old version of this package isn't good for what they want.  The Markdown-to-Latex conversion would automatically add in the references and citations, but would literally hardcode them into the `.tex` file.  We can't have that, now can we?  The only ways you were allowed to cite in your `.tex` file was with `\cite{Gusfield97}`, `\shortcite{Gusfield97}`, or `\newcite{Gusfield97}`, which corresponded to "(Gusfield, 1997)", "(1997)", or "Gusfield (1997)", respectively.

This means you couldn't do anything like "(e.g., Gusfield, 2017)", and their `.bst` file was incompatible with `natbib`. Obviously.  However, I have come to the rescue.  In the `eacl2017.sty` file in this package, I have added my own bit of magic: the `\barecite{}` command, which corresponds to "Burchill, 2017".  Notice this version doesn't have parentheses, so you can get stuff like "(e.g., Burchill, 2017)" with `(e.g., \barecite{Gusfield97})`.  Just be careful about making sure you don't forget parentheses.  Also not that when you submit the `.zip` folder, you should make sure to include the edited `eacl2017.sty` file.

## Examples

 * `\cite{Gusfield97}` becomes \cite{Gusfield97}
 * `\shortcite{Gusfield97}` becomes \shortcite{Gusfield97}
 * `\newcite{Gusfield97}` becomes \newcite{Gusfield97}
 * `\barecite{Gusfield97}` becomes \barecite{Gusfield97}
 * `\cite{Gusfield97,Aho72}` becomes \cite{Gusfield97,Aho72}
 * `\barecite{Gusfield97,Aho72}` becomes \barecite{Gusfield97,Aho72}

**Wait, _are those citations appearing as question marks?_  Don't worry, read on!**

## The two-step process of knitting this file

Because the ACL's you-need-to-use-our-citing-function formatting doesn't work well with R Markdown--which really likes to compile its own citations--knitting this is now a two-step process.  After you get it how you want it in RMarkdown, knit as usual.  You'll see that all citations are question marks, and that the bibliography is missing.  This is natural, don't panic.

For the current purposes, let's assume this file we're in right now is called `acl_draft.Rmd`.  Navigate into the directory containing `acl_draft.Rmd` via a terminal.  Then run the following command (swapping out your actual file name for "acl_draft")

`pdflatex acl_draft.tex; pdflatex acl_draft.tex; bibtex acl_draft.aux; pdflatex acl_draft.tex; pdflatex acl_draft.tex`

Now, check the `.pdf` file.  If all went well, it should now have all the citations in it as well as the reference section.  Good luck!

# General Formatting Instructions

All the default content below is lifted directly from Kyle MacDonald's Cogsci 2016 project (https://github.com/kemacdonald/cogsci2016), which this entire package is based on.  I haven't changed it, so it's up to you to ignore as you please.

For general information about authoring in markdown, see **http://rmarkdown.rstudio.com/authoring_basics.html.**

For standard spoken papers and standard posters, the entire 
contribution (including figures, references, everything) can be 
no longer than six pages. For abstract posters, the entire contribution 
can be no longer than one page. For symposia, the entire contribution 
can be no longer than two pages.

The text of the paper should be formatted in two columns with an
overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
cm), with 0.25 inches between the columns. Leave two line spaces
between the last author listed and the text of the paper. The left
margin should be 0.75 inches and the top margin should be 1 inch.
\textbf{The right and bottom margins will depend on whether you use
U.S. letter or A4 paper, so you must be sure to measure the width of
the printed text.} Use 10 point Times Roman with 12 point vertical
spacing, unless otherwise specified.

The title should be in 14 point, bold, and centered. The title should
be formatted with initial caps (the first letter of content words
capitalized and the rest lower case). Each author's name should appear
on a separate line, 11 point bold, and centered, with the author's
email address in parentheses. Under each author's name list the
author's affiliation and postal address in ordinary 10 point  type.

Indent the first line of each paragraph by 1/8~inch (except for the
first paragraph of a new section). Do not add extra vertical space
between paragraphs.

# First-Level Headings

First level headings should be in 12 point , initial caps, bold and
centered. Leave one line space above the heading and 1/4~line space
below the heading.

## Second-Level Headings

Second level headings should be 11 point , initial caps, bold, and
flush left. Leave one line space above the heading and 1/4~ line
space below the heading.

### Third-Level Headings

Third-level headings should be 10 point , initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.

# Formalities, Footnotes, and Floats

## Footnotes

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.}

## Figures

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10 point, after the figure with one line space
above the caption and one line space below it. If necessary, leave extra white space at
the bottom of the page to avoid splitting the figure and figure
caption. You may float figures to the top or bottom of a column, or
set wide figures across both columns.

## Two-column images

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

You might want to display a wide figure across both columns. To do this, you can change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`.

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", fig.cap = "This image spans both columns."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```

## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
       aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                      caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

```{r}
# References will be generated after this point after you run the following command. <file> is this file, but without the extension.  You should include the full path if you aren't running the command in the same directory.  This command should be run in a terminal, btw.

# The command:
# pdflatex <file>.tex; pdflatex <file>.tex; bibtex <file>.aux; pdflatex <file>.tex; pdflatex <file>.tex

# After running this command, check the new pdf file. It should hopefully have all the citations added in.
```

### 2019-02-25 conceptNet-cogsci/Cogsci.Rmd
Added CogsciBackground
Added cluster randomization

@@
 ```{r message=FALSE}
-clusters_evolution <- function(vocab, n_clusters, min_age, max_age, randomization) {
+clusters_evolution <- function(vocab, n_clusters, min_age, max_age,
+                               aoa_randomization, cluster_randomization = FALSE) {
 
-  if(randomization == "none") {
+  if(aoa_randomization == "none") {
     # do nothing
-  } else if(randomization == "random_aoa") {
+  } else if(aoa_randomization == "random_aoa") {
     vocab <- randomize_aoa(vocab) # TODO handle randomization, write "randomize_aoa"" in random_helper.r
-  } else if(randomization == "to_nearest_aoa") {
+  } else if(aoa_randomization == "to_nearest_aoa") {
     vocab <- randomize_aoa_to_nearest(vocab)
-  } else if(randomization == "within_last_clustering") {
+  } else if(aoa_randomization == "within_last_clustering") {
     vocab <- randomize_within_last_clustering(vocab, n_clusters)
@@
   membership_evo <- net_evo %>%
-    map(w2v_waltrap) %>%
+    map(w2v_walktrap) %>%
     map(~ cut_at(., no = n_clusters))
@@
   clusters_evo <- map2(vocab_evo, membership_evo, build_clusters)
+
+  if(cluster_randomization) {
+    clusters_evo <- map(clusters_evo, randomize_clustering)
+  }
 
@@
 
-measure_cluster_dynamics <- function(language, n_clusters, measures, randomizations, samples) {
+measure_cluster_dynamics <- function(language, n_clusters, measures,
+                                     aoa_randomizations, 
+                                     cluster_randomizations, # c(TRUE, FALSE)
+                                     samples) {
   vocab <- get_language_vocab(language)
@@
   # true vocabulary sizes (full vocabulary size at each month)
-    measurements[["true_vocab_sizes"]] <-
+  measurements[[length(measurements) + 1]] <-
     tibble(age = min(vocab$age):max(vocab$age),
            measure = "true_vocab_size",
-             randomization = NA, # same for all randomizations
+           aoa_randomization = NA, # same for all randomizations
+           cluster_randomization = NA,
            sample = NA,
@@
 
-    # --------------------- true aoa measures --------------------- #
+  # --------------------- measures that don't depend on randomizations --------------------- #
   true_clusters_evo <- clusters_evolution(vocab,
@@
                                           max(vocab$age),
-                                            randomization = "none")
+                                          aoa_randomization = "none",
+                                          cluster_randomization = FALSE)
 
   # w2v vocabulary sizes (number of words know at each month in clustering)
-    measurements[["w2v_vocab_sizes"]] <- 
+  measurements[[length(measurements) + 1]] <-
     tibble(age = min(vocab$age):max(vocab$age),
            measure = "w2v_vocab_size",
-             randomization = NA, # same for all randomizations
+           aoa_randomization = NA, # same for all randomizations
+           cluster_randomization = NA,
            sample = NA,
@@
 
-    # dynamics measures
-    for (measure in measures) {
-      value <- run_measure(true_clusters_evo, measure)
-      measurements[[measure]] <-
-        tibble(age = min(vocab$age):max(vocab$age),
-               measure = measure,
-               randomization = "none",
-               sample = NA,
-               value = value)
-    }
+  # --------------------- (optionally) randomized measures --------------------- #
 
-    # --------------------- randomized aoa measures --------------------- #
-    for (randomization in randomizations) {
+  for (cluster_randomization in cluster_randomizations) {
+
+    for (aoa_randomization in aoa_randomizations) {
 
@@
                                                   max(vocab$age),
-                                                  randomization = randomization)
+                                                  aoa_randomization = aoa_randomization,
+                                                  cluster_randomization = cluster_randomization)
 
@@
           value <- run_measure(random_clusters_evo, measure)
-          measurements[[paste(randomization, measure, sample, sep = "__")]] <-
+          measurements[[length(measurements) + 1]] <-
             tibble(age = min(vocab$age):max(vocab$age),
                    measure = measure,
-                   randomization = randomization,
+                   aoa_randomization = aoa_randomization,
+                   cluster_randomization = cluster_randomization,
                    sample = sample,
                    value = value)
+        }
       }
@@
 
-run_experiment <- function(languages, measures, randomizations, cluster_counts, samples) {
+run_experiment <- function(languages, measures, aoa_randomizations,
+                           cluster_randomizations, cluster_counts, samples) {
   measurements = list()
@@
       measurements[[length(measurements) + 1]] <- 
-        measure_cluster_dynamics(language, n_clusters, measures, randomizations, samples) %>%
+        measure_cluster_dynamics(language, n_clusters, measures,
+                                 aoa_randomizations, cluster_randomizations, samples) %>%
         mutate(language = language) %>%
@@
 
-randomizations <- c("random_aoa", "to_nearest_aoa", "within_last_clustering")
+aoa_randomizations <- c("none", "random_aoa", "to_nearest_aoa", "within_last_clustering")
+
+cluster_randomizations <-  c(TRUE, FALSE)
 
@@
 #                           measures = measures,
-#                           randomizations = randomizations,
+#                           aoa_randomizations = randomizations,
+#                           cluster_randomizations = c(FALSE)
 #                           cluster_counts = 2:5,
@@
 
+### compute cluster randomization measurements, TAKES A WHILE
+
+cluster_randomization_measurements <- run_experiment(
+                          languages = languages,
+                          measures = measures,
+                          aoa_randomizations = c("none"),
+                          cluster_randomizations = c(TRUE, FALSE),
+                          cluster_counts = 2:5,
+                          samples = 50)
+
+saveRDS(cluster_randomization_measurements, "cluster_randomization_measurements.rds")
+
 measurements <- readRDS("measurements.rds")
-
+cluster_randomization_measurements <- readRDS("cluster_randomization_measurements.rds")
 ```

### 2019-02-25 conceptNet-cogsci/helpers/random_helper.r

@@ -90,3 +90,15 @@ randomize_within_last_clustering <- function(vocab, n_clusters) {
     category = shuffled$category
   ))
 }
+
+randomize_clustering <- function(clustering) {
+  lengths <- map(clustering, length)
+  words <- sample(unlist(clustering))
+  
+  new_clustering <- list()
+  for (l in lengths) {
+    new_clustering[[length(new_clustering) + 1]] <- words[1:l]
+    words <- words[l+1:length(words)]
+  }
+  return(new_clustering)
+}

### 2019-02-25 conceptNet-cogsci/Cogsci.Rmd
Commented out cluster randomization experiment.

@@
 
-cluster_randomization_measurements <- run_experiment(
-                          languages = languages,
-                          measures = measures,
-                          aoa_randomizations = c("none"),
-                          cluster_randomizations = c(TRUE, FALSE),
-                          cluster_counts = 2:5,
-                          samples = 50)
-
-saveRDS(cluster_randomization_measurements, "cluster_randomization_measurements.rds")
+# cluster_randomization_measurements <- run_experiment(
+#                           languages = languages,
+#                           measures = measures,
+#                           aoa_randomizations = c("none"),
+#                           cluster_randomizations = c(TRUE, FALSE),
+#                           cluster_counts = 2:5,
+#                           samples = 50)
+# 
+# saveRDS(cluster_randomization_measurements, "cluster_randomization_measurements.rds")
 

### 2019-02-25 CMCL/ms.Rmd

@@
 ---
-title: "How to Make a Camera-Ready Proceedings Contribution"
+title: "The development of abstract concepts in the early lexical network"
 
@@
 abstract: 
-    "This document contains the instructions for preparing a camera-ready
-  manuscript for the proceedings of EACL-2017. The document itself
-  conforms to its own specifications, and is therefore an example of
-  what your manuscript should look like. These instructions should be
-  used for both papers submitted for review and for final versions of
-  accepted papers.  Authors are asked to conform to all the directions
-  reported in this document."
+    "How do children learn abstract concepts such as animal vs.
+artefact?
+Previous research suggests that such concepts can be derived using cues from the language they hear around them, e.g., word co-occurrence.
+We propose that such information can be integrated in the evolving lexical network, and higher-level organization can be identified bottom-up as the dense components in this network.
+We found that early abstract categories develop simultaneously thanks to the children's word trajectory which favors the exploration of the global conceptual space."
 
@@
 library(dplyr)
+library(plyr)
+library(broom)
+#library(tidyr)
+library(purrr)
+library(langcog)
 library(ggplot2)
@@
 
-# Methods
+#Introduction:
+<!--Different factors influence word learning. But here we are interested in how this order may influnce conceptual development
+-The role of language is particularly important in the acquisition of higher levels concepts (because shared features are not necessarily perceived).
+One idea is to used the way words are distributed in child directed speech to infer the underlying categories
 
-##Nouns 
-We used data from Wordbank (Frank et al., 2017), an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version.
-Parent report is a reliable and valid measure of children's vocabulary (Fenson et al., 1994).
-We used a set of nouns representing hand-checked translation equivalents  across 10 languages (available in Wordbank database).
-We "assume" (i should ask what were the criteria for the unilemma selection) that this set of translation equivalents is representative of a core shared vocabulary across all children (in different cultures) by around 30 months,
-<!--and we study possible cross-lingusitic variation in the way this shared knowledge is arrived at in development. -->
+Concepts are the building blocks of ideas.
+For example, the thought "birds are animals" requires the knowledge of both the concept "birds" and the concept "animal".
+They enable inductive reasoning and predictive inferences which guide behavior and explanation (Murphy, 2002).
+-->
+One of the central challenges in cognitive development is to understand how concepts develop \cite{carey2009,keil1992,gopnik1997}.
+Of particular interest is the case of abstract concepts which have non-obvious shared properties such as "animal" and "artefacts".
+For example, a cat and a bird are perceptually quite different but they share some fundamental properties (e.g., breathing, feeding, and reproducing) which make them animals, and which set them apart from  the category of artefacts.
+In such cases learning requires, at least in part, cultural/linguistic cues which provide information beyond what can be obtained through the senses \cite{gelman2009,harris2012,csibra2009}
 
-The conceptual organization derived from this shared vocabulary is obviousely identical across languages, but we investigate whether there are systematic cross-lingusitc variations in the order of aquisition of words that make up this vocabulary, and crucially, whether such variation influences the induced conceptual organization at different points in time.
+One way children's conceptual learning can benefit from the language they hear around them is through word co-occurrence.
+For example, one can learn an abstract concept (e.g., animal) simply by observing how its instances (e.g., "cat" and "bird") go together in speech.
+This is a plausible learning strategy.
+On the one hand, experimental research has shown that children track co-occurrence statistics \cite{saffran1996}.
+On the other hand, inspection of the caregiver’s input shows that it contains rich co-occurrence information about various abstract concepts \cite{huebner2018}.
+
+What remains to be investigated is the way abstract concepts develop from the interaction of the children's learning mechanisms and the structure of their linguistic input.
+We study this development and compare it to two hypothetical developmental scenarios.
+On the first, learning starts by exploring the global conceptual structure; categories are refined simultaneously over development (we call this mechanism exploration-based learning).
+On the second scenario, learning starts by exploring a small region of the conceptual space (e.g., the category "animals") and only after the refinement of this category, does the learner move to another (we call this mechanism exploitation-based learning).
+
+The paper is organized as follows.
+First we describe the research strategy.
+In brief, we represented the developing lexicon as an evolving network and we used word co-occurrence in parent speech as a measure of words' relatedness.
+We operationalized high-level concepts as the highly interconnected components of the network.
+Second, we explore how the pattern of children's word learning influences higher-level conceptual development, and we compare this pattern to the development induced by the exploration-based and exploitation-based mechanisms.
+Finally, we discuss the findings in light of previous research.
+
+```{r network, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=5, fig.height=8, fig.cap = "Network obtained using a sample of nouns in CDI data (nodes), and co-occurrence-based similarity from a corpus of child-directed speech (edges).
+Colors indicate highly interconnected clusters identified using unsupervised network community detection.
+The clusters correspond, overall, to four higher-level concepts: animal, food, clothes, and artefacts."}
+
+img <- png::readPNG("figs/graph.png")
+grid::grid.raster(img)
+
+```
+
+# Data and Methods
+
+## Constructing lexical networks
+
+The networks' nodes were nouns form  Wordbank \cite{frank2017}, an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version \cite{fenson94}.
+Pairs of nouns were linked by weighted edges representing their semantic similarity derived based on co-occurrence in the corpus of child directed speech CHILDES \cite{macwhinney2014}, using Word2Vec algorithm \cite{mikolov2013}.
+
+First, we constructed the end-state network based on a subset of CDI data.
+This subset was made of nouns belonging to a diversity of semantic categories.
+Items of this subset (named "uni_lemmas" in the WordBank database) were translated across the languages used in this study, allowing us to account for cross-linguistic variability.
+Second, to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.
+
+## Identifying high-level concepts in a network
+
+We assume that high-level concepts correspond to clusters of highly interconnected nodes in the networks.
+We identified such clusters using  WalkTrap \cite{pons2006}, an unsupervised community detection algorithm based on the fact that a random walker tends to be trapped in dense parts of a network.
+Figure \ref{fig:network} shows the outcome of cluster identification in the end-state network.
+The algorithm obtained four major clusters corresponding to the categories of clothes, food, animal and artefacts.
+We refer to this end-state clustering as $\mathcal{C}^*$.
+To examine developmental change in the conceptual organization, we run the cluster identification algorithm at each month of acquisition $t$, and we compare the resulting clustering, noted $\mathcal{C}_t$, to that of the end-state $\mathcal{C}^*$.
+The method of this comparison is detailed below.
+
+```{r results, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, across different languages.
+Colors indicates real and hypothetical word sampling mechanisms.
+Errors bars represent 95\\% confidence intervals."}
+
+measurements <- readRDS("data/measurements.rds")
+
+all <- measurements %>%
+  filter(measure %in% c("pair_precision_to_last", "pair_recall_to_last"),
+         randomization != "to_nearest_aoa",
+         n_clusters != '5') #%>%
+  #group_by(n_clusters, age, measure, randomization) %>%
+  #summarise(mean = mean(value))
+
+all_sum <- all %>%
+  group_by(measure, randomization, age) %>%
+  multi_boot_standard(col = "value", na.rm = TRUE)
+  #summarise(myMean = mean(value, na.rm = TRUE))
+
+all_sum$measure <- mapvalues(all_sum$measure, from = c("pair_precision_to_last", "pair_recall_to_last"), to = c("Precision", "Recall"))
+all_sum$randomization <- mapvalues(all_sum$randomization, from = c("none", "random_aoa", "within_last_clustering"), to = c("Real", "Exploration","Exploitation"))
+
+all_sum$randomization <- factor(all_sum$randomization, levels = c("Real", "Exploration","Exploitation"))
+
+ggplot(data=all_sum, aes(x=age, y=mean, col=randomization)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
+                  position = position_dodge(width = .1),
+                  size=0.1)+
+  geom_line()+
+  xlab("Age") + ylab("Mean score") +
+  #geom_smooth(method="lm", formula = y ~ poly(x, 3)) +
+  #geom_smooth(method="lm", formula = y ~ log(x)) +
+  theme_few() + 
+  theme(aspect.ratio = 0.7,
+        legend.title = element_blank())+
+  facet_grid(.~measure) +
+  theme(legend.position="bottom")
+```
+
+## Measuring conceptual development
+
+We measure conceptual development by comparing $\mathcal{C}_t$ to $\mathcal{C}^*$ across time.
+We used a standard method in clustering comparison, which is based on counting word pairs on which the two clusterings agree or disagree \cite{rand1971,hubert1985}.
+A pair of words learned by month $t$ can fall under one of the four following cases:
+
+\begin{enumerate}
+
+  \item True positives $tp(\mathcal{C}_t)$: pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
+  \item True negatives $tn(\mathcal{C}_t)$: pairs placed in different clusters under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
+  \item False positive $fp(\mathcal{C}_t)$: pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
+  \item False negatives $fn(\mathcal{C}_t)$: pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
+
+\end{enumerate}
+
+We quantify clustering comparison using precision $P(\mathcal{C}_t)$ and recall $R(\mathcal{C}_t)$, defined as follows:
+
+$$
+P(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fp(\mathcal{C}_t)|}
+$$
+
+$$
+R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
+$$
+We made this comparison using different degrees of clustering granularity.
+More precisely, we fixed the same number of clusters for both $\mathcal{C}_t$ and $\mathcal{C}^*$, and we varied this number from two to four clusters.
+We did not use the trivial case of one cluster, nor did we did use more than four clusters, since this number was optimal for the largest network (i.e., the end-state network) based on the modularity maximization criterion \cite{newman2006}.
+
+<!--We investigate whether there are systematic cross-lingusitc variations in the order of aquisition of words that make up this vocabulary, and crucially, whether such variation influences the induced conceptual organization at different points in time.
 In fact, differences in the order of acqusition of words do not necessarily give rise to different conceptual organization.
@@
 This difference will not change the induced conceptual organization across time since both "dog" and "cow" are instances of the same high-level concept "animal".
+-->
 
-```{r fig.env = "figure", fig.pos = "h", fig.align = "center", set.cap.width=T, fig.width=4, fig.height=3, num.cols.cap=2, fig.cap = "bla bla"}
+<!--## Features
+We used two sources of information which represent two ways words may be related to one another in the semantic network.
+The first source was the MacRae features (McRae et al., 2005).
+These features were collected by giving adult participants a set of nouns and prompting them to provide various kinds of properties (perceptual, functional, encyclopedic, and taxonomic).
+We followed Hills et al.
+2010 in excluding the encyclopedic and taxonomic properties as their role may not be important at this stage of development.
+The other source was the semantic similarity derived based on co-occurrence in the corpus of CHILDES, using word2vec.
+-->
+
+<!--
+## Small World properties
+We test whether the networks display the so-called "small-world" properties similar to other semantic and real-world networks (Steyvers & Tenenbaum, 2005; Watts & Strogatz, 1998).
+Small world properties are characterized with the average clustering coefficient $C$ and the average shortest path $L$.
+The former measures the extent to which the network is clustered, i.e., made of highly connectned sub-networks, whereas the latter measures the typical separation between tow nodes in the network.
+A network is small-word if it has a higher clustering coeffient comapred to a randomly connected network of the same size $C \gg C_{random}$, while still having a shorest path length as small as the one typically observed in random networks, that is $L \approx L_{random}$.
+-->
+
+<!--Both Precison and Recall converge to 1 (perfect score) as $\mathcal{C}_t$ becomes more and more similar to $\mathcal{C}^*$.
+If precision starts low before converging to 1 (as opposed to being a constant at 1), this pattern would indicate that some pairs that should be differentiated are initially lumped together, suggesting a process of "differentiation" over development.
+Similarly, if we observe an increase in Recall, this pattern would indicate that some pairs that should be associated are initially differentiate, suggesting a process of "coelescence" over development.
+-->
+
+## Learning mechanisms
+
+We examined how higher-order concepts develop under the children's real word learning trajectory.
+We compared this development to the development induced by an exploration- and an exploitation-like learning.
+To construct the real word learning trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}.
+
+The exploration-based learning was instantiated as a uniform sampling from the end-state vocabulary.
+The exploitation-based learning had the additional constraint of sampling from one category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster.
+After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.\footnote{Note that the way we instantiated the exploitation-based learning is not fully unsupervised, but we were more interested in modeling extreme cases to which real learning can be compared.}
+<!--
+Since we are interested in the cross-linguistic study of development, we started by investigating the degree to which languages vary in their normative order of word learning.
+To this end, we calulated the pairwise Kendall rank correlation coefficient between languages, and we comapre it to the same measure obtained by comparing trajectories in different languages to random orderings.
+The corresponding distributions, shown in Figure XX, do not overlap indicating that languages are more similar to each other than to random word orderings.
+The between-language distribution also shows there to be susbtantial cross-linguitc variability since the values are smaller than 1 (i.e., perfect correlation).
+-->
+
+<!--
+```{r fig.env = "figure", fig.pos = "H", fig.align = "center", set.cap.width=T, fig.width=3, fig.height=4, num.cols.cap=2, fig.cap = "bla bla"}
 
@@
   theme_few() + 
-  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +  #facet_grid(Segmentation ~ language)+
+  theme(legend.title = element_blank(),
+      legend.text=element_text(size=7.5),
+      axis.text = element_text(size = 7.5),
+      strip.text = element_text(size = 7.5),
+      axis.title = element_text(size = 7.5),
+      aspect.ratio = 0.7
+      )  +  #facet_grid(Segmentation ~ language)+
   scale_y_continuous(labels = scales::percent)+
-  xlab("pairwise correlation") +ylab("Count")
+  xlab("pairwise correlation") +ylab("Count") +
+  theme(legend.position="bottom")
+
+```
+-->
+# Results
+
+```{r hi}
+#Models
+
+#m1_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
+#           data = subset(all, measure =='pair_precision_to_last' & randomization != "random_aoa"),
+#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+##Test of convergence
+#(From: https://github.com/lme4/lme4/issues/120)
+#relgrad <- with(m1_precision@optinfo$derivs,solve(Hessian,gradient))
+#max(abs(relgrad))
+
+#saveRDS(m1_precision, "model_1.rds")
+#xl_precision <- readRDS("model_1.rds")
+
+#m2_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
+#           data = subset(all, measure =='pair_precision_to_last' & randomization != "within_last_clustering"),
+#           control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 1000000)))
+
+#saveRDS(m2_precision, "model_2.rds")
+#xp_precision <- readRDS("model_2.rds")
+
+##Test of convergence
+#relgrad <- with(xp_precision@optinfo$derivs,solve(Hessian,gradient))
+#max(abs(relgrad))
+
+#xl_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
+#           data = subset(all, measure =='pair_recall_to_last' & randomization != "random_aoa"),
+#                     control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+#saveRDS(xl_recall, "xl_recall.rds")
+#xl_recall <- readRDS("xl_recall.rds")
+
+#m2_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
+#           data = subset(all, measure =='pair_recall_to_last' & randomization != "within_last_clustering"),
+#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 1000000)))
+
+#saveRDS(m2_recall, "model_recall_2.rds")
+#xp_recall <- readRDS("model_recall_2.rds")
+
+#relgrad <- with(xp_recall@optinfo$derivs,solve(Hessian,gradient))
+#max(abs(relgrad))
+
+#xl_prec_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xl_precision))), "effect") %>%
+#  mutate(sampling = "exploitation", score = "precision")
+#xp_prec_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xp_precision))), "effect") %>%
+#  mutate(sampling = "exploration", score = "precision")
+#xl_recall_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xl_recall))), "effect") %>%
+#  mutate(sampling = "exploitation", score = "recall")
+#xp_recall_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xp_recall))), "effect") %>%
+#  mutate(sampling = "exploration", score ="recall")
+
+#coef_all <- xl_prec_coef %>%
+#  bind_rows(xp_prec_coef) %>%
+#  bind_rows(xl_recall_coef) %>%
+#  bind_rows(xp_recall_coef)
+
+#feather::write_feather(coef_all, "../saved_data/coef_all.feather")
+coef_all <- feather::read_feather("../saved_data/coef_all.feather")
+
+p_val <- function(val) {
+  if(val < 0.001) 
+    {'< 0.001'} 
+  else if(val < 0.01)
+    {'<0.01'} 
+  else if(val < 0.05)
+    {'<0.05'} 
+  else {paste('=', round(val,2))}
+}
+
+#Age 
+age_xl_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
+                                                  coef_all$sampling=="exploitation" &
+                                                  coef_all$score =="precision")],2)
+
+age_xp_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
+                                                  coef_all$sampling=="exploration" &
+                                                  coef_all$score =="precision")],2)
+
+age_xl_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
+                                                  coef_all$sampling=="exploitation" &
+                                                  coef_all$score =="recall")],2)
+
+age_xp_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
+                                                  coef_all$sampling=="exploration" &
+                                                  coef_all$score =="recall")],2)
+
+age_xl_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
+                                                  coef_all$sampling=="exploitation" &
+                                                  coef_all$score =="precision")]
+
+age_xp_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
+                                                  coef_all$sampling=="exploration" &
+                                                  coef_all$score =="precision")]
+
+age_xl_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age"  &
+                                                  coef_all$sampling=="exploitation" &
+                                                  coef_all$score =="recall")]
+
+age_xp_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
+                                                  coef_all$sampling=="exploration" &
+                                                  coef_all$score =="recall")]
+
+#Real vs. exploration
+
+diff_xl_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationwithin_last_clustering" &
+                                                  coef_all$sampling=="exploitation" &
+                                                  coef_all$score =="precision")],2)
+
+diff_xp_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationrandom_aoa" &
+                                                  coef_all$sampling=="exploration" &
+                                                  coef_all$score =="precision")],2)
+
+diff_xl_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationwithin_last_clustering" &
+                                                  coef_all$sampling=="exploitation" &
+                                                  coef_all$score =="recall")],2)
+
+diff_xp_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationrandom_aoa" &
+                                                  coef_all$sampling=="exploration" &
+                                                  coef_all$score =="recall")],2)
+
+diff_xl_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationwithin_last_clustering" &
+                                                  coef_all$sampling=="exploitation" &
+                                                  coef_all$score =="precision")]
+
+diff_xp_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationrandom_aoa" &
+                                                  coef_all$sampling=="exploration" &
+                                                  coef_all$score =="precision")]
+
+diff_xl_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationwithin_last_clustering" &
+                                                  coef_all$sampling=="exploitation" &
+                                                  coef_all$score =="recall")]
+
+diff_xp_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationrandom_aoa" &
+                                                  coef_all$sampling=="exploration" &
+                                                  coef_all$score =="recall")]
 
@@
 
-## Features
-We used two sources of information which represent two ways words may be related to one another in the semantic network.
-The first source was the MacRae features (McRae et al., 2005).
-These features were collected by giving adult participants a set of nouns and prompting them to provide various kinds of properties (perceptual, functional, encyclopedic, and taxonomic).
-We followed Hills et al.
-2010 in excluding the encyclopedic and taxonomic properties as their role may not be important at this stage of development.
-The other source was the semantic similarity derived based on co-occurrence in the corpus of CHILDES, using word2vec.
+Figure \ref{fig:results} shows the scores obtained through comparing $\mathcal{C}^*$ to $\mathcal{C}_t$ at different points in time $t$.
+For the real word learning trajectory, both precision and recall start relatively low, indicating that the induced conceptual organization is initially quite different from that of the end-state.
+Both measures converge towards 1 (i.e., perfect score) as $\mathcal{C}_t$ becomes more and more similar to $\mathcal{C}^*$.
 
-##Network 
-We constructed networks using CDI words as nodes.
-Pairs of words were linked by an edge weighted by the number of shared MacRae feature or with the continuous distance obtained via Word2vec.
-To model change in the conceptual organization from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.
-We defined the age of acquisiton of a given word by the month at which this noun was produced by at least 50% of children, in each language (Goodman et al., 2008).
+We first compared the real conceptual development to the one induced by exploration-based learning.
+To this end, we fit a mixed-effect regression using age and learning (real vs.
+exploration-based) as fixed effects, and using language and number of fixed clusters as random effects accounting for the nested structure of the data.
+Real and exploration-based patterns of conceptual developmental were indistinguishable for both precision ($\beta =$ `r diff_xp_prec_co`, $p$ `r p_val(diff_xp_prec_p)`) and recall ($\beta =$ `r diff_xp_rec_co`, $p$ `r p_val(diff_xp_rec_p)`).
 
-## Small World properties
-We test whether the networks display the so-called "small-world" properties similar to other semantic and real-world networks (Steyvers & Tenenbaum, 2005; Watts & Strogatz, 1998).
-Small world properties are characterized with the average clustering coefficient $C$ and the average shortest path $L$.
-The former measures the extent to which the network is clustered, i.e., made of highly connectned sub-networks, whereas the latter measures the typical separation between tow nodes in the network.
-A network is small-word if it has a higher clustering coeffient comapred to a randomly connected network of the same size $C \gg C_{random}$, while still having a shorest path length as small as the one typically observed in random networks, that is $L \approx L_{random}$.
+Similarly, we compared real conceptual development to exploitation-based learning.
+Using a similar regression, we found a difference in both precision ($\beta =$ `r diff_xl_prec_co`, $p$ `r p_val(diff_xl_prec_p)`) and recall ($\beta =$ `r diff_xl_rec_co`, $p$ `r p_val(diff_xl_rec_p)`).
+Exploitation-base learning had generally higher precision, indicating there to be less false positive pairs.
+This result is due to the fact that we sampled instances from a same category.
+However, the same type of learning had lower recall, indicating there to be less false negative pairs.
+This second result was due to the fact that sampling from a same category leads to clusterings that are finer in their conceptual granularity than the end-state.
 
-```{r fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=14, fig.cap = "bla bla"}
-measurements <- readRDS("data/measurements.rds")
+# Discussion
 
-all <- measurements %>%
-  filter(measure %in% c("pair_precision_to_last", "pair_recall_to_last"),
-         randomization != "to_nearest_aoa") #%>%
-  #group_by(n_clusters, age, measure, randomization) %>%
-  #summarise(mean = mean(value))
+This paper asks whether children can learn abstract concepts based on word co-occurrence in the language they hear around them.
+We found that, when using co-occurrence information in the developing lexical network, several high-level concepts such as "animal", "artefact", "food" and "clothes" emerge bottom-up as clusters of highly inter-connected nodes.
+In addition, these categories develop simultaneously thanks to the children's word learning trajectory which tends to favor the exploration of the global conceptual landscape rather than the exploitation and refinement of one specific category at time.
 
-all_sum <- all %>%
-  group_by(measure, randomization, age) %>%
-  summarise(myMean = mean(value, na.rm = TRUE))
+The development of the higher-level conceptual structure seems to be unaffected by the order with which words are acquired (as long as this order approximates a uniform/exploration-like sampling), suggesting that the process of conceptual development can accommodate a wide range of word learning trajectories without qualitative change in the higher order organization.
+For example, whether acquisition start first with the words "cat" and "banana" or with the words "cow" and "potato" does not qualitatively affect the higher-level organization involving "animal" and "food".
+This property is important as it suggests, for instance, that development may be resilient to variability in the children's linguistic input \cite{slobin2014,hart1995}.
 
-ggplot(data=all, aes(x=age, y=value, col=randomization)) +
-  #geom_point() +
-  geom_smooth(method="lm", formula = y ~ poly(x, 3)) +
-  #geom_smooth(method="lm", formula = y ~ log(x)) +
-  theme_few() + 
-  theme(aspect.ratio = 0.7)+
-  facet_grid(.~measure)
-```
-## Clustering analysis
-We identified network clusters using WalkTrap (Pons & Latapy, 2006), a community detection algorithm based on the fact that a random walker tends to be trapped in dense parts of a network corresponding to highly interconnected sub-groups of nodes.
+Developmental changes were captured by precision and recall.
+The increase in precision means that false positives decrease over time: some word pairs that are initially lumped together in a same category, are eventually differentiated.
+Similarly, the increase in recall means that false negatives decrease, that is, some word pairs that are initially distinct, become eventually subsumed by a same category.
+These patterns suggest a process of conceptual reorganization involving both "differentiation" and "coalescence" as was suggested in the developmental literature \cite{carey2009}.
 
-## Evaluation of clusterings aross development
-We note $\mathcal{C}_t$ the clustering at month $t$, based on the subset of the vocabulary acquired by that month in each language.
-The evaluation consists in comparing $\mathcal{C}_t$ to the final clustering $\mathcal{C}^*$ obtained using the full vocabulary by the last month of acquisition (i.e., $\mathcal{C}^*$=$\mathcal{C}_t$ for $t$=30 months).
-Such comparison allows us to study how words acquired at different points in time may induce changes in the conceptual organization.
-In addition, we investigate consistency and variability in this change across languages.
+That said, these developmental changes were not necessarily related to specific concepts (since the patterns were similar when we randomized the order of word learning).
+Instead, this finding suggests that differentiation and coalescence of word pairs in our data are related to the change in the vocabulary size across development: As more words are added to their lexical network, learners may approximate better the underlying conceptual organization of the mature lexicon, and would make less categorization errors.
+Indeed, research in network science indicates that properties of a real networks become more distorted as the size of a sampled sub-network decreases \cite{leskovec2006}.
 
-We compare $\mathcal{C}_t$ to $\mathcal{C}^*$ using a standard method in clustering comparison, which is based on counting word pairs on which the two clusterings agree or disagree (Rand, 1971; Hubert and Arabie, 1985).
-A pair of words learned by month $t$ can fall under one of the four follwoing cases: 1) pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$ (True positives, noted as $tp(\mathcal{C}_t)$), 2) pairs placed in different clsuters under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$ (True negatives, $tn(\mathcal{C}_t)$), 3) pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$ (False positive, $fp(\mathcal{C}_t)$), and 4) pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$ (False negatives, $fn(\mathcal{C}_t)$).
+One limitation of this study is that we used the normative age of acquisition, computed using different children at different age groups.
+This choice was due to the cross-sectional nature of available CDI data.
+Though such a measure has been widely used to study important aspects of the early lexical network \cite{hills2009,stella2017,storkel2009}, it only applies at the population level.
+In our case, though we found that average concept development is driven more by an exploration-based mechanism, some individual children may display an exploitation-like behavior.
+For example, prior knowledge about dinosaurs may enable the learning of new dinosaur-related words more easily \cite{chi1983}.
 
-The clustering precison $P(\mathcal{C}_t)$ and recall $R(\mathcal{C}_t)$ are defiend as follows:
+In sum, this work provided a quantitative account of how abstract concepts can emerge from the interaction of the children's learning mechanism and the properties of their linguistic input.
+One important direction for future work is to investigate the extent to which the correlational findings obtained in this study (e.g., the identity of categories formed across development or the fact that categorization errors decrease with the size of the lexicon) can be corroborated by controlled behavioral experiments.
 
-$$
-P(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fp(\mathcal{C}_t)|}
-$$
-$$
-R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
-$$
-Both Precison and Recall converge to 1 (perfect score) as $\mathcal{C}_t$ becomes more and more similar to $\mathcal{C}^*$.
-If precision starts low before converging to 1 (as opposed to being a constant at 1), this pattern would indicate that some pairs that should be differentiated are initially lumped together, suggesting a process of "differentiation" over development.
-Similarly, if we observe an increase in Recall, this pattern would indicate that some pairs that should be associated are initially differentiate, suggesting a process of "coelescence" over development.
+<!--
 
-## Word ordering 
-The question we are addressing is whether the order of acqusition of words affect the
+leading to gradual improvements in the approximation of the underlying conceptual organization.
+More precisely, words are placed in a same cluster if they are more similar to one another than to words in a different clusters.
+However, this *relative* similarity depends on the existing items and their number.
+In particular, the larger the vocabulary, the better learners can approximate the underlying relative simialrity distribution of the mature lexicon, and the less categorization errors they make.
 
-#Results
+We compare the developmental patterns obtained with the normative trajectory to those obtained with the random trajectory.
+We demonstrated above that these trajectories are not correlated (Figure XX).
+Therefore, a priori it could have been the case that the normative trajectory has effects on higher-level conceptual organization above and beyond the effects induced by the random trajectory.
+Instead, Figure XX shows that the precsion and recall scores are strikingly similar in both trajectories across development.
+Thus, high level conceptual organizaton is quite robust to the order of word acquisition.
+To illustrate, acquisition may start with the word "dog" or with the word "cat", but this difference in the order of acquisition will not affect the induced super-ordinate category "animal".
+
+<!--
+
+We investigte whether the real conceptual development resembles more a pattern of exploitation- and exploration-based sampling.
+
+The real word leanrining trajectory induces a conceptual organization which starts different from the end-state (lower precion and recall scores), and which becomes increasingly similar to the end-state
+
+The results are shown for the real trajectory, as well
+
+First we compare the trajectory of word learning to the trajectories that result from the two sampling mechanisms.
+Second, we examine the extent to which these trajectories induce different patterns of conceptual development.
+
+Results are shown in Figure XX.
+We used mixed-effect linear regressions to examine how the trajectory of word learning compares to the two sampling mechanisms in the way they influence conceptual development.
+
+Furthermore, the fact that normative and random trajectories have almost identical effects on the higher-level organization suggests that the observed developmental patterns (i.e., differentiation and coalescence of pairs of words) are not due to some specific order in word acquisition.
+Rather, they are due to the increase in the vocabulary size across development, leading to gradual improvements in the approximation of the underlying conceptual organization.
+More precisely, words are placed in a same cluster if they are more similar to one another than to words in a different clusters.
+However, this *relative* similarity depends on the existing items and their number.
+In particular, the larger the vocabulary, the better learners can approximate the underlying relative simialrity distribution of the mature lexicon, and the less categorization errors they make.
+
+Next, we compare the normative and category-based learning (why?).
+Precsion is higher in the category-based trajectory, especially for earlier months.
+In contrast, the recall is lower.
+This pattern is due to the fact that learning is assumed to proceed based on conceptual similarity, e.g., if learning starts with an animal, then the next word will also be an animal.
+This learning produces less false postives because it samples instances from the same category (hence the high precison).
+Nevertheless, it also produces more false negative because it creates categories that are finer in their conceptual granualrity than the end-state (hence the low recall).
+
+# Conclusion
+This results suggests that real (normative) learning influences early conceptual development in a way that mimics random sampling and contrasts with category-based sampling.
+This suggests that early word learning favors exploration of the entire conceptual domain, rath
+
+<!--
+thus favoring exploration and which differ from category-based sampling.
+
+conceptual development show different properties when word learning deviate
+
+learning proceeds according to a similarity principle which sample words from the same category.
+
+In contrast, the recall is lower. Category-based trajectory does not show a clear differentia
+
+Finally, mixed effects model and cross-linguistic discussion,....
+
+more frequent it is to approximate the end-state organization and to misplace words in . This phenomenon is similar to
+
+The similarity of the scores in both trajectories also indicate that the increase in precision are recall are more likely due to small sample size, similar to the fact that a small size will not lead to prcise distribution,....
+
+If we picture a word learning trajectory as way one could samples words from the end-state vocabulary, then random ordering corresponds to sparse sampling,
+
+to the ones obtained with the randomly ranked trajectory.
+As shown in Figure XX, precision and recall scores in both trajectories are strinkingly similar across development.
+Thus, despite the fact that languages share some pattern of acquisition above and beyond chance (see Figure, XX), these shared patterns do not influence the higher level organizaton of these words.
+For example,
+
+Investigation of the random trajectory allows us to understand whether the developmental patterns are specific to
 
@@
 
-<!--
 If precision is lower early on, it means that initial concepts are not differentiated enough, that is, pairs that should belong to different concpets are intially lamped together (false positives), despite the fact that we forced the same number of clsuters in both $\mathcal{C}_t$ and $\mathcal{C}^*$ (Why is this the case?
@@
 
-Quetions:
-Why does the control precision decreese a bit during developmnt, isn't supposed to be 1 all along?
-since we are splitting words within the same cluster (unless maybe some clusters are empty) : Oh I guess because we start introducing additional categories
 -->
-
-## Order of word learning
-
-# Sudy of the conceptual development
-
-Models
-
-```{r}
-# What is the model that can predict values as a function of cluser number and the methio 
-#m1_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
-#           data = subset(all, measure =='pair_precision_to_last' & randomization != "random_aoa"),
-#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-##Test of convergence
-#(From: https://github.com/lme4/lme4/issues/120)
-#relgrad <- with(m1_precision@optinfo$derivs,solve(Hessian,gradient))
-#max(abs(relgrad))
-
-#saveRDS(m1_precision, "model_1.rds")
-m1_precision <- readRDS("model_1.rds")
-
-#m2_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
-#           data = subset(all, measure =='pair_precision_to_last' & randomization != "within_last_clustering"),
-#           control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-#saveRDS(m2_precision, "model_2.rds")
-m2_precision <- readRDS("model_2.rds")
-
-##Test of convergence
-#relgrad <- with(m2_precision@optinfo$derivs,solve(Hessian,gradient))
-#max(abs(relgrad))
-
-#m1_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
-#           data = subset(all, measure =='pair_recall_to_last' & randomization != "random_aoa"),
-#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-#saveRDS(m1_recall, "model_recall_1.rds")
-m1_recall <- readRDS("model_recall_1.rds")
-
-#m2_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
-#           data = subset(all, measure =='pair_recall_to_last' & randomization != "within_last_clustering"),
-#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-#saveRDS(m2_recall, "model_recall_2.rds")
-m2_recall <- readRDS("model_recall_2.rds")
-
-```
-
-# Important citation stuff! READ!
-
-## Why we can't have nice things
-
-So because the ACL committee wants their `.tex` files all nice and consistent, the old version of this package isn't good for what they want.
-The Markdown-to-Latex conversion would automatically add in the references and citations, but would literally hardcode them into the `.tex` file.
-We can't have that, now can we?
-The only ways you were allowed to cite in your `.tex` file was with `\cite{Gusfield97}`, `\shortcite{Gusfield97}`, or `\newcite{Gusfield97}`, which corresponded to "(Gusfield, 1997)", "(1997)", or "Gusfield (1997)", respectively.
-
-This means you couldn't do anything like "(e.g., Gusfield, 2017)", and their `.bst` file was incompatible with `natbib`.
-Obviously.
-However, I have come to the rescue.
-In the `eacl2017.sty` file in this package, I have added my own bit of magic: the `\barecite{}` command, which corresponds to "Burchill, 2017".
-Notice this version doesn't have parentheses, so you can get stuff like "(e.g., Burchill, 2017)" with `(e.g., \barecite{Gusfield97})`.
-Just be careful about making sure you don't forget parentheses.
-Also not that when you submit the `.zip` folder, you should make sure to include the edited `eacl2017.sty` file.
-
-## Examples
-
- * `\cite{Gusfield97}` becomes \cite{Gusfield97}
- * `\shortcite{Gusfield97}` becomes \shortcite{Gusfield97}
- * `\newcite{Gusfield97}` becomes \newcite{Gusfield97}
- * `\barecite{Gusfield97}` becomes \barecite{Gusfield97}
- * `\cite{Gusfield97,Aho72}` becomes \cite{Gusfield97,Aho72}
- * `\barecite{Gusfield97,Aho72}` becomes \barecite{Gusfield97,Aho72}
-
-**Wait, _are those citations appearing as question marks?_  Don't worry, read on!**
-
-## The two-step process of knitting this file
-
-Because the ACL's you-need-to-use-our-citing-function formatting doesn't work well with R Markdown--which really likes to compile its own citations--knitting this is now a two-step process.
-After you get it how you want it in RMarkdown, knit as usual.
-You'll see that all citations are question marks, and that the bibliography is missing.
-This is natural, don't panic.
-
-For the current purposes, let's assume this file we're in right now is called `acl_draft.Rmd`.
-Navigate into the directory containing `acl_draft.Rmd` via a terminal.
-Then run the following command (swapping out your actual file name for "acl_draft")
-
-`pdflatex acl_draft.tex; pdflatex acl_draft.tex; bibtex acl_draft.aux; pdflatex acl_draft.tex; pdflatex acl_draft.tex`
-
-Now, check the `.pdf` file.  If all went well, it should now have all the citations in it as well as the reference section.  Good luck!
-
-# General Formatting Instructions
-
-All the default content below is lifted directly from Kyle MacDonald's Cogsci 2016 project (https://github.com/kemacdonald/cogsci2016), which this entire package is based on.
-I haven't changed it, so it's up to you to ignore as you please.
-
-For general information about authoring in markdown, see **http://rmarkdown.rstudio.com/authoring_basics.html.**
-
-For standard spoken papers and standard posters, the entire 
-contribution (including figures, references, everything) can be 
-no longer than six pages. For abstract posters, the entire contribution 
-can be no longer than one page. For symposia, the entire contribution 
-can be no longer than two pages.
-
-The text of the paper should be formatted in two columns with an
-overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
-cm), with 0.25 inches between the columns. Leave two line spaces
-between the last author listed and the text of the paper. The left
-margin should be 0.75 inches and the top margin should be 1 inch.
-\textbf{The right and bottom margins will depend on whether you use
-U.S. letter or A4 paper, so you must be sure to measure the width of
-the printed text.} Use 10 point Times Roman with 12 point vertical
-spacing, unless otherwise specified.
-
-The title should be in 14 point, bold, and centered. The title should
-be formatted with initial caps (the first letter of content words
-capitalized and the rest lower case). Each author's name should appear
-on a separate line, 11 point bold, and centered, with the author's
-email address in parentheses. Under each author's name list the
-author's affiliation and postal address in ordinary 10 point  type.
-
-Indent the first line of each paragraph by 1/8~inch (except for the
-first paragraph of a new section). Do not add extra vertical space
-between paragraphs.
-
-# First-Level Headings
-
-First level headings should be in 12 point , initial caps, bold and
-centered. Leave one line space above the heading and 1/4~line space
-below the heading.
-
-## Second-Level Headings
-
-Second level headings should be 11 point , initial caps, bold, and
-flush left. Leave one line space above the heading and 1/4~ line
-space below the heading.
-
-### Third-Level Headings
-
-Third-level headings should be 10 point , initial caps, bold, and flush
-left. Leave one line space above the heading, but no space after the
-heading.
-
-# Formalities, Footnotes, and Floats
-
-## Footnotes
-
-Indicate footnotes with a number\footnote{Sample of the first
-footnote.} in the text. Place the footnotes in 9 point type at the
-bottom of the page on which they appear. Precede the footnote with a
-horizontal rule.\footnote{Sample of the second footnote.}
-
-## Figures
-
-All artwork must be very dark for purposes of reproduction and should
-not be hand drawn. Number figures sequentially, placing the figure
-number and caption, in 10 point, after the figure with one line space
-above the caption and one line space below it. If necessary, leave extra white space at
-the bottom of the page to avoid splitting the figure and figure
-caption. You may float figures to the top or bottom of a column, or
-set wide figures across both columns.
-
-## Two-column images
-
-You can read local images using png package for example and plot 
-it like a regular plot using grid.raster from the grid package. 
-With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**
-
-You might want to display a wide figure across both columns.
-To do this, you can change the `fig.env` chunk option to `figure*`.
-To align the image in the center of the page, set `fig.align` option to `center`.
-
-```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", fig.cap = "This image spans both columns."}
-img <- png::readPNG("figs/walrus.png")
-grid::grid.raster(img)
-```
-
-## One-column images
-
-Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`.
-
-```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, fig.cap = "One column image."}
-img <- png::readPNG("figs/lab_logo_stanford.png")
-grid::grid.raster(img)
-```
-
-## R Plots
-
-You can use R chunks directly to plot graphs. And you can use latex floats in the
-fig.pos chunk option to have more control over the location of your plot on the page.
-For more information on latex placement specifiers see **https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions**
-
-```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
-x <- 0:100
-y <- 2 * (x + rnorm(length(x), sd = 3) + 3)
-
-ggplot2::ggplot(data = data.frame(x, y), 
-       aes(x = x, y = y)) + 
-  geom_point() + 
-  geom_smooth(method = "lm")
-```
-
-## Tables
-
-Number tables consecutively; place the table number and title (in
-10 point) above the table with one line space above the caption and
-one line space below it, as in Table 1. You may float
-tables to the top or bottom of a column, set wide tables across both
-columns.
-
-You can use the xtable function in the xtable package.
-
-```{r xtable, results="asis"}
-n <- 100
-x <- rnorm(n)
-y <- 2*x + rnorm(n)
-out <- lm(y ~ x)
-
-tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
-                      caption = "This table prints across one column.")
-
-print(tab1, type="latex", comment = F, table.placement = "H")
-```
-
-# Acknowledgements
-
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
-
-```{r}
-# References will be generated after this point after you run the following command.
-<file> is this file, but without the extension.
-You should include the full path if you aren't running the command in the same directory.
-This command should be run in a terminal, btw.
-
-# The command:
-# pdflatex <file>.tex; pdflatex <file>.tex; bibtex <file>.aux; pdflatex <file>.tex; pdflatex <file>.tex
-
-# After running this command, check the new pdf file. It should hopefully have all the citations added in.
-```

### 2019-02-25 CMCL/ms.tex

%
% File eacl2017.tex
%
%% Based on the style files for ACL-2016
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn,
%% based on the style files for ACL-2010, which were, in turn,
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}

\usepackage[a4paper]{geometry}
\usepackage{eacl2017}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

% Added from MacDonald's .tex file ----------------------------
\usepackage{float}
\usepackage{caption}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}

% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% hyperref package, useful for hyperlinks
% \usepackage{hyperref}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% Sweave(-like)
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}

% -------------------------------------------------------------------------

% Added so that I could use the `fancy_lists` pandoc extension. If you don't want this or it's giving you errors, remove the line below and the line in `acl_article.R` that adds `+fancy_lists`
\def\tightlist{}

% If you have:
%   final_submission: yes
%   eaclpaperid: <your ID number>
% in the .Rmd metadata, it should have automatically
% added "\eaclfinalcopy" and "\def\eaclpaperid{<your ID number>}" above

% You can expand the titlebox if you need extra space
% to show all the authors. You can do this by uncommenting
% the line in the Rmd header:
%   # titlebox_length: "5cm"
% and substituting it with your own length.
% Please note that the minimum length is 5cm--they will
% check it and make you change it if it's smaller than that.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{How to Make a Camera-Ready Proceedings Contribution}

\author{{\large \bf Author 1} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University \And {\large \bf Author 2} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University}

\date{}

\begin{document}

\maketitle

\begin{abstract}
This document contains the instructions for preparing a camera-ready
manuscript for the proceedings of EACL-2017. The document itself
conforms to its own specifications, and is therefore an example of what
your manuscript should look like. These instructions should be used for
both papers submitted for review and for final versions of accepted
papers. Authors are asked to conform to all the directions reported in
this document.
\end{abstract}

\section{Methods}\label{methods}

\subsection{Nouns}\label{nouns}

We used data from Wordbank (Frank et al., 2017), an open repository
aggregating cross-linguistic language developmental data of the
MacArthur-Bates Communicative Development Inventory (CDI), a parent
report vocabulary checklist, Toddler version. Parent report is a
reliable and valid measure of children's vocabulary (Fenson et al.,
1994). We used a set of nouns representing hand-checked translation
equivalents across 10 languages (available in Wordbank database). We
``assume'' (i should ask what were the criteria for the unilemma
selection) that this set of translation equivalents is representative of
a core shared vocabulary across all children (in different cultures) by
around 30 months,

The conceptual organization derived from this shared vocabulary is
obviousely identical across languages, but we investigate whether there
are systematic cross-lingusitc variations in the order of aquisition of
words that make up this vocabulary, and crucially, whether such
variation influences the induced conceptual organization at different
points in time. In fact, differences in the order of acqusition of words
do not necessarily give rise to different conceptual organization.
Imagine that two languages vary in whether ``cow'' or ``dog'' is
acquired first. This difference will not change the induced conceptual
organization across time since both ``dog'' and ``cow'' are instances of
the same high-level concept ``animal''.

\begin{CodeChunk}
\captionsetup{width=0.8\textwidth}\begin{figure}[h]

{\centering \includegraphics{figs/unnamed-chunk-1-1}

}

\caption[bla bla]{bla bla}\label{fig:unnamed-chunk-1}
\end{figure}
\end{CodeChunk}

\subsection{Features}\label{features}

We used two sources of information which represent two ways words may be
related to one another in the semantic network. The first source was the
MacRae features (McRae et al., 2005). These features were collected by
giving adult participants a set of nouns and prompting them to provide
various kinds of properties (perceptual, functional, encyclopedic, and
taxonomic). We followed Hills et al. 2010 in excluding the encyclopedic
and taxonomic properties as their role may not be important at this
stage of development. The other source was the semantic similarity
derived based on co-occurrence in the corpus of CHILDES, using word2vec.

\subsection{Network}\label{network}

We constructed networks using CDI words as nodes. Pairs of words were
linked by an edge weighted by the number of shared MacRae feature or
with the continuous distance obtained via Word2vec. To model change in
the conceptual organization from month to month, we constructed a
different network at each month, based on the words that have been
acquired by that month. We defined the age of acquisiton of a given word
by the month at which this noun was produced by at least 50\% of
children, in each language (Goodman et al., 2008).

\subsection{Small World properties}\label{small-world-properties}

We test whether the networks display the so-called ``small-world''
properties similar to other semantic and real-world networks (Steyvers
\& Tenenbaum, 2005; Watts \& Strogatz, 1998). Small world properties are
characterized with the average clustering coefficient \(C\) and the
average shortest path \(L\). The former measures the extent to which the
network is clustered, i.e., made of highly connectned sub-networks,
whereas the latter measures the typical separation between tow nodes in
the network. A network is small-word if it has a higher clustering
coeffient comapred to a randomly connected network of the same size
\(C \gg C_{random}\), while still having a shorest path length as small
as the one typically observed in random networks, that is
\(L \approx L_{random}\).

\begin{CodeChunk}
\captionsetup{width=0.8\textwidth}\begin{figure*}[h]

{\centering \includegraphics{figs/unnamed-chunk-2-1}

}

\caption[bla bla]{bla bla}\label{fig:unnamed-chunk-2}
\end{figure*}
\end{CodeChunk}

\subsection{Clustering analysis}\label{clustering-analysis}

We identified network clusters using WalkTrap (Pons \& Latapy, 2006), a
community detection algorithm based on the fact that a random walker
tends to be trapped in dense parts of a network corresponding to highly
interconnected sub-groups of nodes.

\subsection{Evaluation of clusterings aross
development}\label{evaluation-of-clusterings-aross-development}

We note \(\mathcal{C}_t\) the clustering at month \(t\), based on the
subset of the vocabulary acquired by that month in each language. The
evaluation consists in comparing \(\mathcal{C}_t\) to the final
clustering \(\mathcal{C}^*\) obtained using the full vocabulary by the
last month of acquisition (i.e., \(\mathcal{C}^*\)=\(\mathcal{C}_t\) for
\(t\)=30 months). Such comparison allows us to study how words acquired
at different points in time may induce changes in the conceptual
organization. In addition, we investigate consistency and variability in
this change across languages.

We compare \(\mathcal{C}_t\) to \(\mathcal{C}^*\) using a standard
method in clustering comparison, which is based on counting word pairs
on which the two clusterings agree or disagree (Rand, 1971; Hubert and
Arabie, 1985). A pair of words learned by month \(t\) can fall under one
of the four follwoing cases: 1) pairs that are placed in the same
cluster under \(\mathcal{C}_t\) and in the same cluster under
\(\mathcal{C}^*\) (True positives, noted as \(tp(\mathcal{C}_t)\)), 2)
pairs placed in different clsuters under \(\mathcal{C}_t\) and in
different clusters under \(\mathcal{C}^*\) (True negatives,
\(tn(\mathcal{C}_t)\)), 3) pairs placed in the same cluster under
\(\mathcal{C}_t\) and in different clusters under \(\mathcal{C}^*\)
(False positive, \(fp(\mathcal{C}_t)\)), and 4) pairs placed in
different clusters under \(\mathcal{C}_t\) and in the same cluster under
\(\mathcal{C}^*\) (False negatives, \(fn(\mathcal{C}_t)\)).

The clustering precison \(P(\mathcal{C}_t)\) and recall
\(R(\mathcal{C}_t)\) are defiend as follows:

\[
P(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fp(\mathcal{C}_t)|}
\] \[
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
\] Both Precison and Recall converge to 1 (perfect score) as
\(\mathcal{C}_t\) becomes more and more similar to \(\mathcal{C}^*\). If
precision starts low before converging to 1 (as opposed to being a
constant at 1), this pattern would indicate that some pairs that should
be differentiated are initially lumped together, suggesting a process of
``differentiation'' over development. Similarly, if we observe an
increase in Recall, this pattern would indicate that some pairs that
should be associated are initially differentiate, suggesting a process
of ``coelescence'' over development.

\subsection{Word ordering}\label{word-ordering}

The question we are addressing is whether the order of acqusition of
words affect the

\section{Results}\label{results}

For real and random: results show that both precision and recall
increase across development, suggesting that the conceptual organization
undergoes both differentiation for some word pairs (example), and
coelescecne for other pairs (examples).

For within-cluster: precision is high, but recall is low: explain why

How to explain this change?

\begin{quote}
Assuming a random/real ranking of words: -Some words may be lamped
together initially (even if we force a relatively high number of
clusters) because of the smaller vocabulary size? Can we have an example
of this? Are the other clsuters empty? -Some words may be differentiated
initially because of the forcing? -Is there a roleof noise? maybe
clustering is just more random for smaller size vocabulary?
\end{quote}

\begin{quote}
Assuming a with-cluster ranking of words: -Some words may be lamped
together initially (even if we force a relatively high number of
clusters): this does not happen, at least while we are still working
with the first cluster\ldots{}that's why precision is generally high
-Some words may be differentiated initially because they
\end{quote}

\subsection{Order of word learning}\label{order-of-word-learning}

\section{Sudy of the conceptual
development}\label{sudy-of-the-conceptual-development}

Models

\section{Important citation stuff!
READ!}\label{important-citation-stuff-read}

\subsection{Why we can't have nice
things}\label{why-we-cant-have-nice-things}

So because the ACL committee wants their \texttt{.tex} files all nice
and consistent, the old version of this package isn't good for what they
want. The Markdown-to-Latex conversion would automatically add in the
references and citations, but would literally hardcode them into the
\texttt{.tex} file. We can't have that, now can we? The only ways you
were allowed to cite in your \texttt{.tex} file was with
\texttt{\textbackslash{}cite\{Gusfield97\}},
\texttt{\textbackslash{}shortcite\{Gusfield97\}}, or
\texttt{\textbackslash{}newcite\{Gusfield97\}}, which corresponded to
``(Gusfield, 1997)'', ``(1997)'', or ``Gusfield (1997)'', respectively.

This means you couldn't do anything like ``(e.g., Gusfield, 2017)'', and
their \texttt{.bst} file was incompatible with \texttt{natbib}.
Obviously. However, I have come to the rescue. In the
\texttt{eacl2017.sty} file in this package, I have added my own bit of
magic: the \texttt{\textbackslash{}barecite\{\}} command, which
corresponds to ``Burchill, 2017''. Notice this version doesn't have
parentheses, so you can get stuff like ``(e.g., Burchill, 2017)'' with
\texttt{(e.g.,\ \textbackslash{}barecite\{Gusfield97\})}. Just be
careful about making sure you don't forget parentheses. Also not that
when you submit the \texttt{.zip} folder, you should make sure to
include the edited \texttt{eacl2017.sty} file.

\subsection{Examples}\label{examples}

\begin{itemize}
\tightlist
\item
  \texttt{\textbackslash{}cite\{Gusfield97\}} becomes \cite{Gusfield97}
\item
  \texttt{\textbackslash{}shortcite\{Gusfield97\}} becomes
  \shortcite{Gusfield97}
\item
  \texttt{\textbackslash{}newcite\{Gusfield97\}} becomes
  \newcite{Gusfield97}
\item
  \texttt{\textbackslash{}barecite\{Gusfield97\}} becomes
  \barecite{Gusfield97}
\item
  \texttt{\textbackslash{}cite\{Gusfield97,Aho72\}} becomes
  \cite{Gusfield97,Aho72}
\item
  \texttt{\textbackslash{}barecite\{Gusfield97,Aho72\}} becomes
  \barecite{Gusfield97,Aho72}
\end{itemize}

\textbf{Wait, \emph{are those citations appearing as question marks?}
Don't worry, read on!}

\subsection{The two-step process of knitting this
file}\label{the-two-step-process-of-knitting-this-file}

Because the ACL's you-need-to-use-our-citing-function formatting doesn't
work well with R Markdown--which really likes to compile its own
citations--knitting this is now a two-step process. After you get it how
you want it in RMarkdown, knit as usual. You'll see that all citations
are question marks, and that the bibliography is missing. This is
natural, don't panic.

For the current purposes, let's assume this file we're in right now is
called \texttt{acl\_draft.Rmd}. Navigate into the directory containing
\texttt{acl\_draft.Rmd} via a terminal. Then run the following command
(swapping out your actual file name for ``acl\_draft'')

\texttt{pdflatex\ acl\_draft.tex;\ pdflatex\ acl\_draft.tex;\ bibtex\ acl\_draft.aux;\ pdflatex\ acl\_draft.tex;\ pdflatex\ acl\_draft.tex}

Now, check the \texttt{.pdf} file. If all went well, it should now have
all the citations in it as well as the reference section. Good luck!

\section{General Formatting
Instructions}\label{general-formatting-instructions}

All the default content below is lifted directly from Kyle MacDonald's
Cogsci 2016 project (\url{https://github.com/kemacdonald/cogsci2016}),
which this entire package is based on. I haven't changed it, so it's up
to you to ignore as you please.

For general information about authoring in markdown, see
**\url{http://rmarkdown.rstudio.com/authoring_basics.html.**}

For standard spoken papers and standard posters, the entire contribution
(including figures, references, everything) can be no longer than six
pages. For abstract posters, the entire contribution can be no longer
than one page. For symposia, the entire contribution can be no longer
than two pages.

The text of the paper should be formatted in two columns with an overall
width of 7 inches (17.8 cm) and length of 9.25 inches (23.5 cm), with
0.25 inches between the columns. Leave two line spaces between the last
author listed and the text of the paper. The left margin should be 0.75
inches and the top margin should be 1 inch.
\textbf{The right and bottom margins will depend on whether you use
U.S. letter or A4 paper, so you must be sure to measure the width of
the printed text.} Use 10 point Times Roman with 12 point vertical
spacing, unless otherwise specified.

The title should be in 14 point, bold, and centered. The title should be
formatted with initial caps (the first letter of content words
capitalized and the rest lower case). Each author's name should appear
on a separate line, 11 point bold, and centered, with the author's email
address in parentheses. Under each author's name list the author's
affiliation and postal address in ordinary 10 point type.

Indent the first line of each paragraph by 1/8\textasciitilde{}inch
(except for the first paragraph of a new section). Do not add extra
vertical space between paragraphs.

\section{First-Level Headings}\label{first-level-headings}

First level headings should be in 12 point , initial caps, bold and
centered. Leave one line space above the heading and
1/4\textasciitilde{}line space below the heading.

\subsection{Second-Level Headings}\label{second-level-headings}

Second level headings should be 11 point , initial caps, bold, and flush
left. Leave one line space above the heading and 1/4\textasciitilde{}
line space below the heading.

\subsubsection{Third-Level Headings}\label{third-level-headings}

Third-level headings should be 10 point , initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.

\section{Formalities, Footnotes, and
Floats}\label{formalities-footnotes-and-floats}

\subsection{Footnotes}\label{footnotes}

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.}

\subsection{Figures}\label{figures}

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10 point, after the figure with one line space
above the caption and one line space below it. If necessary, leave extra
white space at the bottom of the page to avoid splitting the figure and
figure caption. You may float figures to the top or bottom of a column,
or set wide figures across both columns.

\subsection{Two-column images}\label{two-column-images}

You can read local images using png package for example and plot it like
a regular plot using grid.raster from the grid package. With this method
you have full control of the size of your image. \textbf{Note: Image
must be in .png file format for the readPNG function to work.}

You might want to display a wide figure across both columns. To do this,
you can change the \texttt{fig.env} chunk option to \texttt{figure*}. To
align the image in the center of the page, set \texttt{fig.align} option
to \texttt{center}.

\begin{CodeChunk}
\begin{figure*}[h]

{\centering \includegraphics{figs/2-col-image-1}

}

\caption[This image spans both columns]{This image spans both columns.}\label{fig:2-col-image}
\end{figure*}
\end{CodeChunk}

\subsection{One-column images}\label{one-column-images}

Single column is the default option, but if you want set it explicitly,
set \texttt{fig.env} to \texttt{figure}.

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/image-1}

}

\caption[One column image]{One column image.}\label{fig:image}
\end{figure}
\end{CodeChunk}

\subsection{R Plots}\label{r-plots}

You can use R chunks directly to plot graphs. And you can use latex
floats in the fig.pos chunk option to have more control over the
location of your plot on the page. For more information on latex
placement specifiers see
**\url{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions**}

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/plot-1}

}

\caption[R plot]{R plot}\label{fig:plot}
\end{figure}
\end{CodeChunk}

\subsection{Tables}\label{tables}

Number tables consecutively; place the table number and title (in 10
point) above the table with one line space above the caption and one
line space below it, as in Table 1. You may float tables to the top or
bottom of a column, set wide tables across both columns.

You can use the xtable function in the xtable package.

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.07 & 0.09 & 0.7 & 0.49 \\ 
  x & 1.92 & 0.09 & 20.4 & 0.00 \\ 
   \hline
\end{tabular}
\caption{This table prints across one column.} 
\end{table}

\section{Acknowledgements}\label{acknowledgements}

Place acknowledgments (including funding information) in a section at
the end of the paper.

\bibliography{eacl2017}
\bibliographystyle{eacl2017}

\end{document}

### 2019-02-27 CMCL/ms.Rmd
ms

@@
 ---
-title: "The development of abstract concepts in the early lexical network"
+title: "The development of abstract concepts in children's early lexical networks"
 
@@
     "How do children learn abstract concepts such as animal vs.
-artefact?
-Previous research suggests that such concepts can be derived using cues from the language they hear around them, e.g., word co-occurrence.
-We propose that such information can be integrated in the evolving lexical network, and higher-level organization can be identified bottom-up as the dense components in this network.
-We found that early abstract categories develop simultaneously thanks to the children's word trajectory which favors the exploration of the global conceptual space."
+artifact?
+Previous research has suggested that such concepts can partly be derived using cues from the language children hear around them.
+Following this suggestion, we propose a model where we represent the children's developing lexicon as an evolving network.
+The nodes of this network are based on vocabulary knowledge as reported by parents, and the edges between pairs of nodes are based on the probability of their co-occurrence in a corpus of child-directed speech.
+We found that several abstract categories can be identified as the dense components in such networks.
+In addition, these categories develop simultaneously, rather than sequentially, thanks to the children's word learning trajectory which favors the exploration of the global conceptual space."
 
@@
 library(dplyr)
+library(tidyr)
 library(plyr)
@@
 One of the central challenges in cognitive development is to understand how concepts develop \cite{carey2009,keil1992,gopnik1997}.
-Of particular interest is the case of abstract concepts which have non-obvious shared properties such as "animal" and "artefacts".
-For example, a cat and a bird are perceptually quite different but they share some fundamental properties (e.g., breathing, feeding, and reproducing) which make them animals, and which set them apart from  the category of artefacts.
-In such cases learning requires, at least in part, cultural/linguistic cues which provide information beyond what can be obtained through the senses \cite{gelman2009,harris2012,csibra2009}
+Of particular interest is the case of abstract concepts which have non-obvious shared properties such as "animal" and "artifact".
+For example, a cat and a bird are perceptually quite different but they share some fundamental properties (e.g., breathing, feeding, and reproducing) which make them animals (as opposed to artifacts).
+In such cases, learning requires in part cultural/linguistic cues which provide information beyond what can be obtained through the senses \cite{gelman2009,harris2012,csibra2009}.
 
@@
 For example, one can learn an abstract concept (e.g., animal) simply by observing how its instances (e.g., "cat" and "bird") go together in speech.
-This is a plausible learning strategy.
-On the one hand, experimental research has shown that children track co-occurrence statistics \cite{saffran1996}.
-On the other hand, inspection of the caregiver’s input shows that it contains rich co-occurrence information about various abstract concepts \cite{huebner2018}.
+Indeed, previous work has shown that the caregiver’s input contains rich co-occurrence information about various abstract concepts \cite{huebner2018}.
+This work, however, has explored the conceptual space from an adult perspective (using the words uttered by the caregivers).
+Here we explore how abstract concepts may develop from the children's perspective, investigating how their word learning trajectory influences the higher-level organization.
 
-What remains to be investigated is the way abstract concepts develop from the interaction of the children's learning mechanisms and the structure of their linguistic input.
-We study this development and compare it to two hypothetical developmental scenarios.
-On the first, learning starts by exploring the global conceptual structure; categories are refined simultaneously over development (we call this mechanism exploration-based learning).
-On the second scenario, learning starts by exploring a small region of the conceptual space (e.g., the category "animals") and only after the refinement of this category, does the learner move to another (we call this mechanism exploitation-based learning).
+<!--On the other hand, children can track co-occurrence statistics \cite{saffran1996} and there is evidence that they use co-occurrence to make category-based generalization \cite{fisher2011,matlen2015}.
+Here we investigate the way abstract concepts may develop from the interaction of the children developing lexicon and co-occurrence information in the caregiver's speech. 
+-->
+We study development in light of two hypothetical models.
+On the first, called the simultaneous model, learning starts by exploring the global conceptual structure; categories are refined simultaneously over development.
+On the second, called the sequential model, learning starts by exploring a small region of the conceptual space (e.g., the category "animals") and only after the refinement of this category, does the learner move to another.
 
 The paper is organized as follows.
-First we describe the research strategy.
+First, we describe the research strategy.
 In brief, we represented the developing lexicon as an evolving network and we used word co-occurrence in parent speech as a measure of words' relatedness.
-We operationalized high-level concepts as the highly interconnected components of the network.
-Second, we explore how the pattern of children's word learning influences higher-level conceptual development, and we compare this pattern to the development induced by the exploration-based and exploitation-based mechanisms.
-Finally, we discuss the findings in light of previous research.
+We operationalized abstract concepts as the highly interconnected components of the network.
+Second, we explore how the pattern of children's word learning influences higher-level conceptual development, and whether this development corresponds to a simultaneous or a sequential conceptual growth.
 
@@
 Colors indicate highly interconnected clusters identified using unsupervised network community detection.
-The clusters correspond, overall, to four higher-level concepts: animal, food, clothes, and artefacts."}
+The clusters correspond, overall, to four higher-level concepts: animal, food, clothes, and artifacts."}
 
@@
 
-The networks' nodes were nouns form  Wordbank \cite{frank2017}, an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version \cite{fenson94}.
-Pairs of nouns were linked by weighted edges representing their semantic similarity derived based on co-occurrence in the corpus of child directed speech CHILDES \cite{macwhinney2014}, using Word2Vec algorithm \cite{mikolov2013}.
+The networks' nodes were nouns from Wordbank \cite{frank2017}, an open repository aggregating cross-linguistic developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version \cite{fenson94}.
+Pairs of nouns were linked by weighted edges representing their semantic similarity derived based on co-occurrence in the corpus of child-directed speech CHILDES \cite{macwhinney2014}, using Word2Vec algorithm \cite{mikolov2013}.
 
-First, we constructed the end-state network based on a subset of CDI data.
-This subset was made of nouns belonging to a diversity of semantic categories.
-Items of this subset (named "uni_lemmas" in the WordBank database) were translated across the languages used in this study, allowing us to account for cross-linguistic variability.
-Second, to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.
+First, we constructed the end-state network based on a subset of CDI nouns named "uni_lemmas" in the WordBank database.
+We used this subset since its items are translated across several languages, allowing us to account for cross-linguistic variability.
+We used the ten languages studied in \newcite{braginsky}.
+The size of this subset varied from XX in English (representing X% of total nouns in this language) to XX in XX (representing X% of total nouns).
+Second, in order to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.
 
-## Identifying high-level concepts in a network
+## Identifying abstract concepts in a network
 
-We assume that high-level concepts correspond to clusters of highly interconnected nodes in the networks.
+We assume that abstract concepts correspond to clusters of highly interconnected nodes in the networks.
 We identified such clusters using  WalkTrap \cite{pons2006}, an unsupervised community detection algorithm based on the fact that a random walker tends to be trapped in dense parts of a network.
 Figure \ref{fig:network} shows the outcome of cluster identification in the end-state network.
-The algorithm obtained four major clusters corresponding to the categories of clothes, food, animal and artefacts.
+The algorithm obtained four major clusters corresponding to the categories of clothes, food, animal and artifacts.
 We refer to this end-state clustering as $\mathcal{C}^*$.
-To examine developmental change in the conceptual organization, we run the cluster identification algorithm at each month of acquisition $t$, and we compare the resulting clustering, noted $\mathcal{C}_t$, to that of the end-state $\mathcal{C}^*$.
+To examine developmental change in the conceptual organization, we ran the cluster identification algorithm at each month of acquisition $t$, and we compared the resulting clustering, noted $\mathcal{C}_t$, to that of the end-state $\mathcal{C}^*$.
 The method of this comparison is detailed below.
@@
 all_sum$randomization <- mapvalues(all_sum$randomization, from = c("none", "random_aoa", "within_last_clustering"), to = c("Real", "Exploration","Exploitation"))
+
+all_sum_corr <- all_sum %>%
+  as.data.frame() %>%
+  select(-ci_lower, -ci_upper) %>%
+  spread(randomization, mean) %>%
+  group_by(measure) %>%
+  dplyr::summarise(sim = round(cor(Real, Exploration)^2, 2),
+            seq = round(cor(Real, Exploitation)^2, 2))
+
+r_sim_prec <- all_sum_corr$sim[which(all_sum_corr$measure=="Precision")]
+r_sim_rec <- all_sum_corr$sim[which(all_sum_corr$measure=="Recall")]
+
+r_seq_prec <- all_sum_corr$seq[which(all_sum_corr$measure=="Precision")]
+r_seq_rec <- all_sum_corr$seq[which(all_sum_corr$measure=="Recall")]
 
@@
 
-We examined how higher-order concepts develop under the children's real word learning trajectory.
-We compared this development to the development induced by an exploration- and an exploitation-like learning.
-To construct the real word learning trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}.
+We examined how abstract concepts develop under the children's real word learning trajectory.
+To construct this trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}.
+We compared this development to the development induced by a simultaneous model and the development induced by a sequential model.
 
-The exploration-based learning was instantiated as a uniform sampling from the end-state vocabulary.
-The exploitation-based learning had the additional constraint of sampling from one category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster.
-After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.\footnote{Note that the way we instantiated the exploitation-based learning is not fully unsupervised, but we were more interested in modeling extreme cases to which real learning can be compared.}
+The simultaneous model was instantiated as a uniform sampling across time from the end-state vocabulary.
+The sequential model had the additional constraint of sampling from one category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster.
+After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.\footnote{Note that the way we instantiated the sequential model is not fully unsupervised, but we were more interested in modeling extreme cases to which real learning can be compared.}
 <!--
@@
 
-```{r hi}
-#Models
-
-#m1_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
-#           data = subset(all, measure =='pair_precision_to_last' & randomization != "random_aoa"),
-#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-##Test of convergence
-#(From: https://github.com/lme4/lme4/issues/120)
-#relgrad <- with(m1_precision@optinfo$derivs,solve(Hessian,gradient))
-#max(abs(relgrad))
-
-#saveRDS(m1_precision, "model_1.rds")
-#xl_precision <- readRDS("model_1.rds")
-
-#m2_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
-#           data = subset(all, measure =='pair_precision_to_last' & randomization != "within_last_clustering"),
-#           control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 1000000)))
-
-#saveRDS(m2_precision, "model_2.rds")
-#xp_precision <- readRDS("model_2.rds")
-
-##Test of convergence
-#relgrad <- with(xp_precision@optinfo$derivs,solve(Hessian,gradient))
-#max(abs(relgrad))
-
-#xl_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
-#           data = subset(all, measure =='pair_recall_to_last' & randomization != "random_aoa"),
-#                     control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-#saveRDS(xl_recall, "xl_recall.rds")
-#xl_recall <- readRDS("xl_recall.rds")
-
-#m2_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
-#           data = subset(all, measure =='pair_recall_to_last' & randomization != "within_last_clustering"),
-#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 1000000)))
-
-#saveRDS(m2_recall, "model_recall_2.rds")
-#xp_recall <- readRDS("model_recall_2.rds")
-
-#relgrad <- with(xp_recall@optinfo$derivs,solve(Hessian,gradient))
-#max(abs(relgrad))
-
-#xl_prec_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xl_precision))), "effect") %>%
-#  mutate(sampling = "exploitation", score = "precision")
-#xp_prec_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xp_precision))), "effect") %>%
-#  mutate(sampling = "exploration", score = "precision")
-#xl_recall_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xl_recall))), "effect") %>%
-#  mutate(sampling = "exploitation", score = "recall")
-#xp_recall_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xp_recall))), "effect") %>%
-#  mutate(sampling = "exploration", score ="recall")
-
-#coef_all <- xl_prec_coef %>%
-#  bind_rows(xp_prec_coef) %>%
-#  bind_rows(xl_recall_coef) %>%
-#  bind_rows(xp_recall_coef)
-
-#feather::write_feather(coef_all, "../saved_data/coef_all.feather")
-coef_all <- feather::read_feather("../saved_data/coef_all.feather")
-
-p_val <- function(val) {
-  if(val < 0.001) 
-    {'< 0.001'} 
-  else if(val < 0.01)
-    {'<0.01'} 
-  else if(val < 0.05)
-    {'<0.05'} 
-  else {paste('=', round(val,2))}
-}
-
-#Age 
-age_xl_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
-                                                  coef_all$sampling=="exploitation" &
-                                                  coef_all$score =="precision")],2)
-
-age_xp_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
-                                                  coef_all$sampling=="exploration" &
-                                                  coef_all$score =="precision")],2)
-
-age_xl_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
-                                                  coef_all$sampling=="exploitation" &
-                                                  coef_all$score =="recall")],2)
-
-age_xp_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
-                                                  coef_all$sampling=="exploration" &
-                                                  coef_all$score =="recall")],2)
-
-age_xl_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
-                                                  coef_all$sampling=="exploitation" &
-                                                  coef_all$score =="precision")]
-
-age_xp_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
-                                                  coef_all$sampling=="exploration" &
-                                                  coef_all$score =="precision")]
-
-age_xl_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age"  &
-                                                  coef_all$sampling=="exploitation" &
-                                                  coef_all$score =="recall")]
-
-age_xp_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
-                                                  coef_all$sampling=="exploration" &
-                                                  coef_all$score =="recall")]
-
-#Real vs. exploration
-
-diff_xl_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationwithin_last_clustering" &
-                                                  coef_all$sampling=="exploitation" &
-                                                  coef_all$score =="precision")],2)
-
-diff_xp_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationrandom_aoa" &
-                                                  coef_all$sampling=="exploration" &
-                                                  coef_all$score =="precision")],2)
-
-diff_xl_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationwithin_last_clustering" &
-                                                  coef_all$sampling=="exploitation" &
-                                                  coef_all$score =="recall")],2)
-
-diff_xp_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationrandom_aoa" &
-                                                  coef_all$sampling=="exploration" &
-                                                  coef_all$score =="recall")],2)
-
-diff_xl_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationwithin_last_clustering" &
-                                                  coef_all$sampling=="exploitation" &
-                                                  coef_all$score =="precision")]
-
-diff_xp_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationrandom_aoa" &
-                                                  coef_all$sampling=="exploration" &
-                                                  coef_all$score =="precision")]
-
-diff_xl_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationwithin_last_clustering" &
-                                                  coef_all$sampling=="exploitation" &
-                                                  coef_all$score =="recall")]
-
-diff_xp_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationrandom_aoa" &
-                                                  coef_all$sampling=="exploration" &
-                                                  coef_all$score =="recall")]
-
-```
-
 Figure \ref{fig:results} shows the scores obtained through comparing $\mathcal{C}^*$ to $\mathcal{C}_t$ at different points in time $t$.
@@
 
-We first compared the real conceptual development to the one induced by exploration-based learning.
-To this end, we fit a mixed-effect regression using age and learning (real vs.
-exploration-based) as fixed effects, and using language and number of fixed clusters as random effects accounting for the nested structure of the data.
-Real and exploration-based patterns of conceptual developmental were indistinguishable for both precision ($\beta =$ `r diff_xp_prec_co`, $p$ `r p_val(diff_xp_prec_p)`) and recall ($\beta =$ `r diff_xp_rec_co`, $p$ `r p_val(diff_xp_rec_p)`).
-
-Similarly, we compared real conceptual development to exploitation-based learning.
-Using a similar regression, we found a difference in both precision ($\beta =$ `r diff_xl_prec_co`, $p$ `r p_val(diff_xl_prec_p)`) and recall ($\beta =$ `r diff_xl_rec_co`, $p$ `r p_val(diff_xl_rec_p)`).
-Exploitation-base learning had generally higher precision, indicating there to be less false positive pairs.
+The simultaneous model mimics closely the patterns of real conceptual development, explaining almost all the variance in mean precision  ($R^2 =$ `r r_sim_prec`) and recall ($R^2 =$ `r r_sim_rec`).
+In contrast, the sequential model had generally a higher precision, i.e., it induced less false positive pairs.
 This result is due to the fact that we sampled instances from a same category.
-However, the same type of learning had lower recall, indicating there to be less false negative pairs.
+However, the same model had generally lower recall scores, i.e., it induced more false negative pairs.
 This second result was due to the fact that sampling from a same category leads to clusterings that are finer in their conceptual granularity than the end-state.
+As a consequence of this discrepancy with respect to real development, the sequential model explained less variance than the simultaneous model did in both the mean precision ($R^2 =$ `r r_seq_prec`) and recall ($R^2 =$ `r r_seq_rec`).
 
@@
 
-This paper asks whether children can learn abstract concepts based on word co-occurrence in the language they hear around them.
-We found that, when using co-occurrence information in the developing lexical network, several high-level concepts such as "animal", "artefact", "food" and "clothes" emerge bottom-up as clusters of highly inter-connected nodes.
-In addition, these categories develop simultaneously thanks to the children's word learning trajectory which tends to favor the exploration of the global conceptual landscape rather than the exploitation and refinement of one specific category at time.
+Can children learn abstract concepts based on word co-occurrence in the language they hear around them?
+Previous work has shown that child-directed speech contains information about several abstract concepts \cite{huebner2018}.
+Here we investigated when and how this information becomes available to children as their lexical network grows.
+We found that even with a small lexicon, several high-level concepts such as "animal", "artifact", "food" and "clothes" emerge bottom-up as clusters of highly interconnected nodes in the network.
+Furthermore,  compared with a model that posited sequential learning, we found that these categories tended to emerge in concert with one another.
 
-The development of the higher-level conceptual structure seems to be unaffected by the order with which words are acquired (as long as this order approximates a uniform/exploration-like sampling), suggesting that the process of conceptual development can accommodate a wide range of word learning trajectories without qualitative change in the higher order organization.
-For example, whether acquisition start first with the words "cat" and "banana" or with the words "cow" and "potato" does not qualitatively affect the higher-level organization involving "animal" and "food".
-This property is important as it suggests, for instance, that development may be resilient to variability in the children's linguistic input \cite{slobin2014,hart1995}.
+<!--thanks to the children's word learning trajectory which favor the exploration of the global conceptual landscape rather than the exploitation and refinement of one specific category at a time. -->
+
+The development of the higher-level conceptual structure seems to be unaffected by the order with which words are acquired (as long as this order approximates a uniform sampling from the end-state lexicon), suggesting that the process of conceptual development can accommodate a wide range of word learning trajectories without a qualitative change in the higher-level organization.
+For example, whether acquisition starts first with the words "cat" and "banana" or with the words "cow" and "potato" does not qualitatively affect the higher-level organization involving "animal" and "food".
+This property is important as it suggests, for instance, that development is resilient to variability in the children's linguistic input \cite{slobin2014,hart1995}.
 
@@
 That said, these developmental changes were not necessarily related to specific concepts (since the patterns were similar when we randomized the order of word learning).
-Instead, this finding suggests that differentiation and coalescence of word pairs in our data are related to the change in the vocabulary size across development: As more words are added to their lexical network, learners may approximate better the underlying conceptual organization of the mature lexicon, and would make less categorization errors.
-Indeed, research in network science indicates that properties of a real networks become more distorted as the size of a sampled sub-network decreases \cite{leskovec2006}.
+Instead, this finding suggests that differentiation and coalescence of word pairs in our data are related to the change in the vocabulary size across development: As more words are added to their lexical network, learners may approximate better the underlying conceptual organization of the mature lexicon and would make fewer categorization errors.
+Indeed, research in network science indicates that properties of a real network become more distorted as the size of a sampled sub-network decreases \cite{leskovec2006}.
 
@@
 This choice was due to the cross-sectional nature of available CDI data.
-Though such a measure has been widely used to study important aspects of the early lexical network \cite{hills2009,stella2017,storkel2009}, it only applies at the population level.
-In our case, though we found that average concept development is driven more by an exploration-based mechanism, some individual children may display an exploitation-like behavior.
+Though such a measure has been widely used to study important aspects of the early lexical networks \cite{hills2009,stella2017,storkel2009}, it only applies at the population level.
+In our case, though we found that concepts develop simultaneously, individual children may display, at least locally, a sequential-like behavior.
 For example, prior knowledge about dinosaurs may enable the learning of new dinosaur-related words more easily \cite{chi1983}.
 
-In sum, this work provided a quantitative account of how abstract concepts can emerge from the interaction of the children's learning mechanism and the properties of their linguistic input.
+In sum, this work provided a quantitative account of how abstract concepts can emerge from the interaction of the children's emerging vocabulary and the properties of their linguistic input.
 One important direction for future work is to investigate the extent to which the correlational findings obtained in this study (e.g., the identity of categories formed across development or the fact that categorization errors decrease with the size of the lexicon) can be corroborated by controlled behavioral experiments.
@@
 If precision is lower early on, it means that initial concepts are not differentiated enough, that is, pairs that should belong to different concpets are intially lamped together (false positives), despite the fact that we forced the same number of clsuters in both $\mathcal{C}_t$ and $\mathcal{C}^*$ (Why is this the case?
-This looks like an artefact of the clustering algorithm with smaller size data?
+This looks like an artifact of the clustering algorithm with smaller size data?
 Should discuss this with Isaac.

### 2019-02-28 CMCL/ms.Rmd
ms

@@
 The nodes of this network are based on vocabulary knowledge as reported by parents, and the edges between pairs of nodes are based on the probability of their co-occurrence in a corpus of child-directed speech.
-We found that several abstract categories can be identified as the dense components in such networks.
-In addition, these categories develop simultaneously, rather than sequentially, thanks to the children's word learning trajectory which favors the exploration of the global conceptual space."
+We found that several abstract categories can be identified as the dense regions in such networks.
+In addition, our simulations suggest that these categories develop simultaneously, rather than sequentially, thanks to the children's word learning trajectory which favors the exploration of the global conceptual space."
 
@@
 This work, however, has explored the conceptual space from an adult perspective (using the words uttered by the caregivers).
-Here we explore how abstract concepts may develop from the children's perspective, investigating how their word learning trajectory influences the higher-level organization.
+Here we explore how abstract concepts may develop from the children's perspective, investigating how their word learning trajectory influences the higher-level organization of their developing lexicon.
 
@@
 We study development in light of two hypothetical models.
-On the first, called the simultaneous model, learning starts by exploring the global conceptual structure; categories are refined simultaneously over development.
+On the first, called the simultaneous model, learning starts by exploring all parts of the conceptual space; categories are refined simultaneously over development.
 On the second, called the sequential model, learning starts by exploring a small region of the conceptual space (e.g., the category "animals") and only after the refinement of this category, does the learner move to another.
@@
 In brief, we represented the developing lexicon as an evolving network and we used word co-occurrence in parent speech as a measure of words' relatedness.
-We operationalized abstract concepts as the highly interconnected components of the network.
+We operationalized abstract concepts as the highly interconnected regions of the network.
 Second, we explore how the pattern of children's word learning influences higher-level conceptual development, and whether this development corresponds to a simultaneous or a sequential conceptual growth.
@@
 
+```{r}
+
+data_all <- feather::read_feather("../saved_data/data_all.feather")
+
+data_all$language <- plyr::mapvalues(data_all$language, 
+                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
+                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))
+
+mysum <- data_all %>%
+  filter(measure == 'produces') %>%
+  #trim_all_unilemma() %>% # TODO check trimming
+  #trim_all_definition() %>%
+  distinct(language, uni_lemma, item) %>%
+  group_by(language) %>%
+  dplyr::summarise(missing = sum(is.na(uni_lemma)),
+            all = n()
+            ) %>%
+  mutate(n_uni = all-missing,
+    percent = (n_uni/all)*100) %>%
+    ungroup() %>%
+    filter(n_uni == min(n_uni) | n_uni == max(n_uni))
+
+max_n <- mysum$n_uni[which(mysum$language=="Russian")]
+max_per <- round(mysum$percent[which(mysum$language=="Russian")],2)
+
+min_n <- mysum$n_uni[which(mysum$language=="Turkish")]
+min_per <- round(mysum$percent[which(mysum$language=="Turkish")],2)
+
+```
+
 # Data and Methods
@@
 
-First, we constructed the end-state network based on a subset of CDI nouns named "uni_lemmas" in the WordBank database.
-We used this subset since its items are translated across several languages, allowing us to account for cross-linguistic variability.
-We used the ten languages studied in \newcite{braginsky}.
-The size of this subset varied from XX in English (representing X% of total nouns in this language) to XX in XX (representing X% of total nouns).
+First, we constructed the end-state network based on all nouns learned by the last age of acqusition.
+We used a subset of CDI nouns for which cross-linguistic translations are present, allowing us to explore cross-linguistic variability.
+We used data from the ten following languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish.
+The size of this subset varied from `r max_n` in Russian (representing `r max_per`% of total nouns in this language) to `r min_n` in Turkish (representing `r min_per`% of total nouns).
 Second, in order to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.
@@
 We identified such clusters using  WalkTrap \cite{pons2006}, an unsupervised community detection algorithm based on the fact that a random walker tends to be trapped in dense parts of a network.
-Figure \ref{fig:network} shows the outcome of cluster identification in the end-state network.
+Figure \ref{fig:network} shows the outcome of cluster identification in the end-state network in English.
 The algorithm obtained four major clusters corresponding to the categories of clothes, food, animal and artifacts.
@@
 
-```{r results, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, across different languages.
+```{r results, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, averaged across languages.
 Colors indicates real and hypothetical word sampling mechanisms.
@@
 measurements <- readRDS("data/measurements.rds")
+meas_rand <- readRDS("data/cluster_randomization_measurements.rds")
 
@@
 
+#all_rand <- meas_rand %>%
+#  filter(measure %in% c("pair_precision_to_last", "pair_recall_to_last"),
+#         #randomization != "to_nearest_aoa",
+#         n_clusters != '5') %>%
+#  as.data.frame()
+
 all_sum <- all %>%
@@
   multi_boot_standard(col = "value", na.rm = TRUE)
+  #summarise(myMean = mean(value, na.rm = TRUE))
+
+#all_sum_rand <- all_rand %>%
+#  group_by(measure, cluster_randomization, age) %>%
+#  multi_boot_standard(col = "value", na.rm = TRUE)
   #summarise(myMean = mean(value, na.rm = TRUE))
@@
   theme(legend.position="bottom")
+
 ```
@@
 We measure conceptual development by comparing $\mathcal{C}_t$ to $\mathcal{C}^*$ across time.
-We used a standard method in clustering comparison, which is based on counting word pairs on which the two clusterings agree or disagree \cite{rand1971,hubert1985}.
-A pair of words learned by month $t$ can fall under one of the four following cases:
-
-\begin{enumerate}
-
-  \item True positives $tp(\mathcal{C}_t)$: pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
-  \item True negatives $tn(\mathcal{C}_t)$: pairs placed in different clusters under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
-  \item False positive $fp(\mathcal{C}_t)$: pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
-  \item False negatives $fn(\mathcal{C}_t)$: pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
-
-\end{enumerate}
-
+We used a standard method in clustering comparison, which is based on word pairs on which the two clusterings agree or disagree \cite{rand1971,hubert1985}.
 We quantify clustering comparison using precision $P(\mathcal{C}_t)$ and recall $R(\mathcal{C}_t)$, defined as follows:
@@
 $$
+Where $tp(\mathcal{C}_t)$ are the true positives, defined as the word pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
+$fp(\mathcal{C}_t)$ are the false positives defined as the pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
+Finally, $fn(\mathcal{C}_t)$ are the false positives defiened as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
+
 We made this comparison using different degrees of clustering granularity.
@@
 
-<!--We investigate whether there are systematic cross-lingusitc variations in the order of aquisition of words that make up this vocabulary, and crucially, whether such variation influences the induced conceptual organization at different points in time.
-In fact, differences in the order of acqusition of words do not necessarily give rise to different conceptual organization.
-Imagine that two languages vary in whether "cow" or "dog" is acquired first.
-This difference will not change the induced conceptual organization across time since both "dog" and "cow" are instances of the same high-level concept "animal".
--->
-
-<!--## Features
-We used two sources of information which represent two ways words may be related to one another in the semantic network.
-The first source was the MacRae features (McRae et al., 2005).
-These features were collected by giving adult participants a set of nouns and prompting them to provide various kinds of properties (perceptual, functional, encyclopedic, and taxonomic).
-We followed Hills et al.
-2010 in excluding the encyclopedic and taxonomic properties as their role may not be important at this stage of development.
-The other source was the semantic similarity derived based on co-occurrence in the corpus of CHILDES, using word2vec.
--->
-
-<!--
-## Small World properties
-We test whether the networks display the so-called "small-world" properties similar to other semantic and real-world networks (Steyvers & Tenenbaum, 2005; Watts & Strogatz, 1998).
-Small world properties are characterized with the average clustering coefficient $C$ and the average shortest path $L$.
-The former measures the extent to which the network is clustered, i.e., made of highly connectned sub-networks, whereas the latter measures the typical separation between tow nodes in the network.
-A network is small-word if it has a higher clustering coeffient comapred to a randomly connected network of the same size $C \gg C_{random}$, while still having a shorest path length as small as the one typically observed in random networks, that is $L \approx L_{random}$.
--->
-
-<!--Both Precison and Recall converge to 1 (perfect score) as $\mathcal{C}_t$ becomes more and more similar to $\mathcal{C}^*$.
-If precision starts low before converging to 1 (as opposed to being a constant at 1), this pattern would indicate that some pairs that should be differentiated are initially lumped together, suggesting a process of "differentiation" over development.
-Similarly, if we observe an increase in Recall, this pattern would indicate that some pairs that should be associated are initially differentiate, suggesting a process of "coelescence" over development.
--->
-
 ## Learning mechanisms
 
-We examined how abstract concepts develop under the children's real word learning trajectory.
+We examined how abstract concepts develop under an average word learning trajectory derived from real developmental data.
 To construct this trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}.
@@
 The sequential model had the additional constraint of sampling from one category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster.
-After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.\footnote{Note that the way we instantiated the sequential model is not fully unsupervised, but we were more interested in modeling extreme cases to which real learning can be compared.}
-<!--
-Since we are interested in the cross-linguistic study of development, we started by investigating the degree to which languages vary in their normative order of word learning.
-To this end, we calulated the pairwise Kendall rank correlation coefficient between languages, and we comapre it to the same measure obtained by comparing trajectories in different languages to random orderings.
-The corresponding distributions, shown in Figure XX, do not overlap indicating that languages are more similar to each other than to random word orderings.
-The between-language distribution also shows there to be susbtantial cross-linguitc variability since the values are smaller than 1 (i.e., perfect correlation).
--->
+After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.
 
@@
 The simultaneous model mimics closely the patterns of real conceptual development, explaining almost all the variance in mean precision  ($R^2 =$ `r r_sim_prec`) and recall ($R^2 =$ `r r_sim_rec`).
-In contrast, the sequential model had generally a higher precision, i.e., it induced less false positive pairs.
-This result is due to the fact that we sampled instances from a same category.
+In contrast, the sequential model had generally a higher precision, i.e., it induced fewer false positive pairs.
+This result is due to the fact that we sampled instances from the same category.
 However, the same model had generally lower recall scores, i.e., it induced more false negative pairs.
-This second result was due to the fact that sampling from a same category leads to clusterings that are finer in their conceptual granularity than the end-state.
-As a consequence of this discrepancy with respect to real development, the sequential model explained less variance than the simultaneous model did in both the mean precision ($R^2 =$ `r r_seq_prec`) and recall ($R^2 =$ `r r_seq_rec`).
+This second result was due to the fact that sampling from the same category leads to clusterings that are finer in their conceptual granularity than the end-state.
+As a consequence of this discrepancy with respect to real development, the sequential model explained less variance than the simultaneous model did in both its mean precision ($R^2 =$ `r r_seq_prec`) and recall ($R^2 =$ `r r_seq_rec`).
 
@@
 
-<!--thanks to the children's word learning trajectory which favor the exploration of the global conceptual landscape rather than the exploitation and refinement of one specific category at a time. -->
-
 The development of the higher-level conceptual structure seems to be unaffected by the order with which words are acquired (as long as this order approximates a uniform sampling from the end-state lexicon), suggesting that the process of conceptual development can accommodate a wide range of word learning trajectories without a qualitative change in the higher-level organization.
@@
 Similarly, the increase in recall means that false negatives decrease, that is, some word pairs that are initially distinct, become eventually subsumed by a same category.
-These patterns suggest a process of conceptual reorganization involving both "differentiation" and "coalescence" as was suggested in the developmental literature \cite{carey2009}.
+These patterns suggest a process of conceptual reorganization involving both "differentiation" and "coalescence" as has been suggested in the developmental literature \cite{carey2009}.
 
-That said, these developmental changes were not necessarily related to specific concepts (since the patterns were similar when we randomized the order of word learning).
+That said, these developmental changes were not necessarily related to specific concepts (since the patterns were similar in the simultaneous model where we randomized the order of word learning).
 Instead, this finding suggests that differentiation and coalescence of word pairs in our data are related to the change in the vocabulary size across development: As more words are added to their lexical network, learners may approximate better the underlying conceptual organization of the mature lexicon and would make fewer categorization errors.
@@
 One important direction for future work is to investigate the extent to which the correlational findings obtained in this study (e.g., the identity of categories formed across development or the fact that categorization errors decrease with the size of the lexicon) can be corroborated by controlled behavioral experiments.
-
-<!--
-
-leading to gradual improvements in the approximation of the underlying conceptual organization.
-More precisely, words are placed in a same cluster if they are more similar to one another than to words in a different clusters.
-However, this *relative* similarity depends on the existing items and their number.
-In particular, the larger the vocabulary, the better learners can approximate the underlying relative simialrity distribution of the mature lexicon, and the less categorization errors they make.
-
-We compare the developmental patterns obtained with the normative trajectory to those obtained with the random trajectory.
-We demonstrated above that these trajectories are not correlated (Figure XX).
-Therefore, a priori it could have been the case that the normative trajectory has effects on higher-level conceptual organization above and beyond the effects induced by the random trajectory.
-Instead, Figure XX shows that the precsion and recall scores are strikingly similar in both trajectories across development.
-Thus, high level conceptual organizaton is quite robust to the order of word acquisition.
-To illustrate, acquisition may start with the word "dog" or with the word "cat", but this difference in the order of acquisition will not affect the induced super-ordinate category "animal".
-
-<!--
-
-We investigte whether the real conceptual development resembles more a pattern of exploitation- and exploration-based sampling.
-
-The real word leanrining trajectory induces a conceptual organization which starts different from the end-state (lower precion and recall scores), and which becomes increasingly similar to the end-state
-
-The results are shown for the real trajectory, as well
-
-First we compare the trajectory of word learning to the trajectories that result from the two sampling mechanisms.
-Second, we examine the extent to which these trajectories induce different patterns of conceptual development.
-
-Results are shown in Figure XX.
-We used mixed-effect linear regressions to examine how the trajectory of word learning compares to the two sampling mechanisms in the way they influence conceptual development.
-
-Furthermore, the fact that normative and random trajectories have almost identical effects on the higher-level organization suggests that the observed developmental patterns (i.e., differentiation and coalescence of pairs of words) are not due to some specific order in word acquisition.
-Rather, they are due to the increase in the vocabulary size across development, leading to gradual improvements in the approximation of the underlying conceptual organization.
-More precisely, words are placed in a same cluster if they are more similar to one another than to words in a different clusters.
-However, this *relative* similarity depends on the existing items and their number.
-In particular, the larger the vocabulary, the better learners can approximate the underlying relative simialrity distribution of the mature lexicon, and the less categorization errors they make.
-
-Next, we compare the normative and category-based learning (why?).
-Precsion is higher in the category-based trajectory, especially for earlier months.
-In contrast, the recall is lower.
-This pattern is due to the fact that learning is assumed to proceed based on conceptual similarity, e.g., if learning starts with an animal, then the next word will also be an animal.
-This learning produces less false postives because it samples instances from the same category (hence the high precison).
-Nevertheless, it also produces more false negative because it creates categories that are finer in their conceptual granualrity than the end-state (hence the low recall).
-
-# Conclusion
-This results suggests that real (normative) learning influences early conceptual development in a way that mimics random sampling and contrasts with category-based sampling.
-This suggests that early word learning favors exploration of the entire conceptual domain, rath
-
-<!--
-thus favoring exploration and which differ from category-based sampling.
-
-conceptual development show different properties when word learning deviate
-
-learning proceeds according to a similarity principle which sample words from the same category.
-
-In contrast, the recall is lower. Category-based trajectory does not show a clear differentia
-
-Finally, mixed effects model and cross-linguistic discussion,....
-
-more frequent it is to approximate the end-state organization and to misplace words in . This phenomenon is similar to
-
-The similarity of the scores in both trajectories also indicate that the increase in precision are recall are more likely due to small sample size, similar to the fact that a small size will not lead to prcise distribution,....
-
-If we picture a word learning trajectory as way one could samples words from the end-state vocabulary, then random ordering corresponds to sparse sampling,
-
-to the ones obtained with the randomly ranked trajectory.
-As shown in Figure XX, precision and recall scores in both trajectories are strinkingly similar across development.
-Thus, despite the fact that languages share some pattern of acquisition above and beyond chance (see Figure, XX), these shared patterns do not influence the higher level organizaton of these words.
-For example,
-
-Investigation of the random trajectory allows us to understand whether the developmental patterns are specific to
-
-For real and random: results show that both precision and recall increase across development, suggesting that the conceptual organization undergoes both differentiation for some word pairs (example), and coelescecne for other pairs (examples).
-
-For within-cluster: precision is high, but recall is low: explain why
-
-How to explain this change?
-
->Assuming a random/real ranking of words:
--Some words may be lamped together initially (even if we force a relatively high number of clusters) because of the smaller vocabulary size?
-Can we have an example of this?
-Are the other clsuters empty?
--Some words may be differentiated initially because of the forcing?
--Is there a roleof noise? maybe clustering is just more random for smaller size vocabulary?
-
->Assuming a with-cluster ranking of words:
--Some words may be lamped together initially (even if we force a relatively high number of clusters): this does not happen, at least while we are still working with the first cluster...that's why precision is generally high
--Some words may be differentiated initially because they
-
-If precision is lower early on, it means that initial concepts are not differentiated enough, that is, pairs that should belong to different concpets are intially lamped together (false positives), despite the fact that we forced the same number of clsuters in both $\mathcal{C}_t$ and $\mathcal{C}^*$ (Why is this the case?
-This looks like an artifact of the clustering algorithm with smaller size data?
-Should discuss this with Isaac.
-Also, what is an exmaple of a clustering $\mathcal{C}_t$ for a smaller size: are some clusters totally empty?)
-
--->

### 2019-02-28 CMCL/ms.Rmd
ms

@@
 
-First, we constructed the end-state network based on all nouns learned by the last age of acqusition.
+First, we constructed the end-state network based on all nouns learned by the last age of acquisition.
 We used a subset of CDI nouns for which cross-linguistic translations are present, allowing us to explore cross-linguistic variability.
@@
 
-```{r results, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, averaged across languages.
+```{r results, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, averaged across languages and numbers of clusters.
 Colors indicates real and hypothetical word sampling mechanisms.
@@
 measurements <- readRDS("data/measurements.rds")
-meas_rand <- readRDS("data/cluster_randomization_measurements.rds")
+#meas_rand <- readRDS("data/cluster_randomization_measurements.rds")
 
@@
 
-#all_rand <- meas_rand %>%
+##all_rand <- meas_rand %>%
 #  filter(measure %in% c("pair_precision_to_last", "pair_recall_to_last"),
@@
  #                 n_clusters != '5') %>%
-#  as.data.frame()
+ #as.data.frame()
 
@@
 #all_sum_rand <- all_rand %>%
-#  group_by(measure, cluster_randomization, age) %>%
+#  group_by(measure, language, cluster_randomization, age) %>%
 # multi_boot_standard(col = "value", na.rm = TRUE)
@@
 all_sum$measure <- mapvalues(all_sum$measure, from = c("pair_precision_to_last", "pair_recall_to_last"), to = c("Precision", "Recall"))
-all_sum$randomization <- mapvalues(all_sum$randomization, from = c("none", "random_aoa", "within_last_clustering"), to = c("Real", "Exploration","Exploitation"))
+all_sum$randomization <- mapvalues(all_sum$randomization, from = c("none", "random_aoa", "within_last_clustering"), to = c("Real", "Simultaneous","Sequential"))
 
@@
   group_by(measure) %>%
-  dplyr::summarise(sim = round(cor(Real, Exploration)^2, 2),
-            seq = round(cor(Real, Exploitation)^2, 2))
+  dplyr::summarise(sim = round(cor(Real, Simultaneous)^2, 2),
+            seq = round(cor(Real, Sequential)^2, 2))
 
@@
 
-all_sum$randomization <- factor(all_sum$randomization, levels = c("Real", "Exploration","Exploitation"))
+all_sum$randomization <- factor(all_sum$randomization, levels = c("Real", "Simultaneous","Sequential"))
 
@@
 $fp(\mathcal{C}_t)$ are the false positives defined as the pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
-Finally, $fn(\mathcal{C}_t)$ are the false positives defiened as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
+Finally, $fn(\mathcal{C}_t)$ are the false positives defined as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
 
 We made this comparison using different degrees of clustering granularity.
-More precisely, we fixed the same number of clusters for both $\mathcal{C}_t$ and $\mathcal{C}^*$, and we varied this number from two to four clusters.
+More precisely, we fixed the same number of clusters for *both* $\mathcal{C}_t$ and $\mathcal{C}^*$, and we varied this number from two to four clusters.
 We did not use the trivial case of one cluster, nor did we did use more than four clusters, since this number was optimal for the largest network (i.e., the end-state network) based on the modularity maximization criterion \cite{newman2006}.
@@
 One important direction for future work is to investigate the extent to which the correlational findings obtained in this study (e.g., the identity of categories formed across development or the fact that categorization errors decrease with the size of the lexicon) can be corroborated by controlled behavioral experiments.
+
+\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}} \vspace{1em}

### 2019-02-28 CMCL/ms.tex
ms

@@
 
-\title{How to Make a Camera-Ready Proceedings Contribution}
+\title{The development of abstract concepts in children's early lexical
+networks}
 
@@
 \begin{abstract}
-This document contains the instructions for preparing a camera-ready
-manuscript for the proceedings of EACL-2017. The document itself
-conforms to its own specifications, and is therefore an example of what
-your manuscript should look like. These instructions should be used for
-both papers submitted for review and for final versions of accepted
-papers. Authors are asked to conform to all the directions reported in
-this document.
+How do children learn abstract concepts such as animal vs.~artifact?
+Previous research has suggested that such concepts can partly be derived
+using cues from the language children hear around them. Following this
+suggestion, we propose a model where we represent the children's
+developing lexicon as an evolving network. The nodes of this network are
+based on vocabulary knowledge as reported by parents, and the edges
+between pairs of nodes are based on the probability of their
+co-occurrence in a corpus of child-directed speech. We found that
+several abstract categories can be identified as the dense regions in
+such networks. In addition, our simulations suggest that these
+categories develop simultaneously, rather than sequentially, thanks to
+the children's word learning trajectory which favors the exploration of
+the global conceptual space.
 \end{abstract}
 
-\section{Methods}\label{methods}
+\section{Introduction:}\label{introduction}
 
-\subsection{Nouns}\label{nouns}
+One of the central challenges in cognitive development is to understand
+how concepts develop \cite{carey2009,keil1992,gopnik1997}. Of particular
+interest is the case of abstract concepts which have non-obvious shared
+properties such as ``animal'' and ``artifact''. For example, a cat and a
+bird are perceptually quite different but they share some fundamental
+properties (e.g., breathing, feeding, and reproducing) which make them
+animals (as opposed to artifacts). In such cases, learning requires in
+part cultural/linguistic cues which provide information beyond what can
+be obtained through the senses \cite{gelman2009,harris2012,csibra2009}.
 
-We used data from Wordbank (Frank et al., 2017), an open repository
-aggregating cross-linguistic language developmental data of the
-MacArthur-Bates Communicative Development Inventory (CDI), a parent
-report vocabulary checklist, Toddler version. Parent report is a
-reliable and valid measure of children's vocabulary (Fenson et al.,
-1994). We used a set of nouns representing hand-checked translation
-equivalents across 10 languages (available in Wordbank database). We
-``assume'' (i should ask what were the criteria for the unilemma
-selection) that this set of translation equivalents is representative of
-a core shared vocabulary across all children (in different cultures) by
-around 30 months,
+One way children's conceptual learning can benefit from the language
+they hear around them is through word co-occurrence. For example, one
+can learn an abstract concept (e.g., animal) simply by observing how its
+instances (e.g., ``cat'' and ``bird'') go together in speech. Indeed,
+previous work has shown that the caregiver's input contains rich
+co-occurrence information about various abstract concepts
+\cite{huebner2018}. This work, however, has explored the conceptual
+space from an adult perspective (using the words uttered by the
+caregivers). Here we explore how abstract concepts may develop from the
+children's perspective, investigating how their word learning trajectory
+influences the higher-level organization of their developing lexicon.
 
-The conceptual organization derived from this shared vocabulary is
-obviousely identical across languages, but we investigate whether there
-are systematic cross-lingusitc variations in the order of aquisition of
-words that make up this vocabulary, and crucially, whether such
-variation influences the induced conceptual organization at different
-points in time. In fact, differences in the order of acqusition of words
-do not necessarily give rise to different conceptual organization.
-Imagine that two languages vary in whether ``cow'' or ``dog'' is
-acquired first. This difference will not change the induced conceptual
-organization across time since both ``dog'' and ``cow'' are instances of
-the same high-level concept ``animal''.
+We study development in light of two hypothetical models. On the first,
+called the simultaneous model, learning starts by exploring all parts of
+the conceptual space; categories are refined simultaneously over
+development. On the second, called the sequential model, learning starts
+by exploring a small region of the conceptual space (e.g., the category
+``animals'') and only after the refinement of this category, does the
+learner move to another.
 
-\begin{CodeChunk}
-\captionsetup{width=0.8\textwidth}\begin{figure}[h]
-
-{\centering \includegraphics{figs/unnamed-chunk-1-1}
-
-}
-
-\caption[bla bla]{bla bla}\label{fig:unnamed-chunk-1}
-\end{figure}
-\end{CodeChunk}
-
-\subsection{Features}\label{features}
-
-We used two sources of information which represent two ways words may be
-related to one another in the semantic network. The first source was the
-MacRae features (McRae et al., 2005). These features were collected by
-giving adult participants a set of nouns and prompting them to provide
-various kinds of properties (perceptual, functional, encyclopedic, and
-taxonomic). We followed Hills et al. 2010 in excluding the encyclopedic
-and taxonomic properties as their role may not be important at this
-stage of development. The other source was the semantic similarity
-derived based on co-occurrence in the corpus of CHILDES, using word2vec.
-
-\subsection{Network}\label{network}
-
-We constructed networks using CDI words as nodes. Pairs of words were
-linked by an edge weighted by the number of shared MacRae feature or
-with the continuous distance obtained via Word2vec. To model change in
-the conceptual organization from month to month, we constructed a
-different network at each month, based on the words that have been
-acquired by that month. We defined the age of acquisiton of a given word
-by the month at which this noun was produced by at least 50\% of
-children, in each language (Goodman et al., 2008).
-
-\subsection{Small World properties}\label{small-world-properties}
-
-We test whether the networks display the so-called ``small-world''
-properties similar to other semantic and real-world networks (Steyvers
-\& Tenenbaum, 2005; Watts \& Strogatz, 1998). Small world properties are
-characterized with the average clustering coefficient \(C\) and the
-average shortest path \(L\). The former measures the extent to which the
-network is clustered, i.e., made of highly connectned sub-networks,
-whereas the latter measures the typical separation between tow nodes in
-the network. A network is small-word if it has a higher clustering
-coeffient comapred to a randomly connected network of the same size
-\(C \gg C_{random}\), while still having a shorest path length as small
-as the one typically observed in random networks, that is
-\(L \approx L_{random}\).
+The paper is organized as follows. First, we describe the research
+strategy. In brief, we represented the developing lexicon as an evolving
+network and we used word co-occurrence in parent speech as a measure of
+words' relatedness. We operationalized abstract concepts as the highly
+interconnected regions of the network. Second, we explore how the
+pattern of children's word learning influences higher-level conceptual
+development, and whether this development corresponds to a simultaneous
+or a sequential conceptual growth.
 
@@
 
-{\centering \includegraphics{figs/unnamed-chunk-2-1}
+{\centering \includegraphics{figs/network-1}
 
@@
 
-\caption[bla bla]{bla bla}\label{fig:unnamed-chunk-2}
+\caption[Network obtained using a sample of nouns in CDI data (nodes), and co-occurrence-based similarity from a corpus of child-directed speech (edges)]{Network obtained using a sample of nouns in CDI data (nodes), and co-occurrence-based similarity from a corpus of child-directed speech (edges).
+Colors indicate highly interconnected clusters identified using unsupervised network community detection.
+The clusters correspond, overall, to four higher-level concepts: animal, food, clothes, and artifacts.}\label{fig:network}
 \end{figure*}
@@
 
-\subsection{Clustering analysis}\label{clustering-analysis}
+\section{Data and Methods}\label{data-and-methods}
 
-We identified network clusters using WalkTrap (Pons \& Latapy, 2006), a
-community detection algorithm based on the fact that a random walker
-tends to be trapped in dense parts of a network corresponding to highly
-interconnected sub-groups of nodes.
+\subsection{Constructing lexical
+networks}\label{constructing-lexical-networks}
 
-\subsection{Evaluation of clusterings aross
-development}\label{evaluation-of-clusterings-aross-development}
+The networks' nodes were nouns from Wordbank \cite{frank2017}, an open
+repository aggregating cross-linguistic developmental data of the
+MacArthur-Bates Communicative Development Inventory (CDI), a parent
+report vocabulary checklist, Toddler version \cite{fenson94}. Pairs of
+nouns were linked by weighted edges representing their semantic
+similarity derived based on co-occurrence in the corpus of
+child-directed speech CHILDES \cite{macwhinney2014}, using Word2Vec
+algorithm \cite{mikolov2013}.
 
-We note \(\mathcal{C}_t\) the clustering at month \(t\), based on the
-subset of the vocabulary acquired by that month in each language. The
-evaluation consists in comparing \(\mathcal{C}_t\) to the final
-clustering \(\mathcal{C}^*\) obtained using the full vocabulary by the
-last month of acquisition (i.e., \(\mathcal{C}^*\)=\(\mathcal{C}_t\) for
-\(t\)=30 months). Such comparison allows us to study how words acquired
-at different points in time may induce changes in the conceptual
-organization. In addition, we investigate consistency and variability in
-this change across languages.
+First, we constructed the end-state network based on all nouns learned
+by the last age of acquisition. We used a subset of CDI nouns for which
+cross-linguistic translations are present, allowing us to explore
+cross-linguistic variability. We used data from the ten following
+languages: Croatian, Danish, English, French, Italian, Norwegian,
+Russian, Spanish, Swedish, and Turkish. The size of this subset varied
+from 314 in Russian (representing 100\% of total nouns in this language)
+to 176 in Turkish (representing 59.26\% of total nouns). Second, in
+order to study development towards the end-state, we constructed a
+different network at each month, based on the nouns that have been
+learned by that month.
 
-We compare \(\mathcal{C}_t\) to \(\mathcal{C}^*\) using a standard
-method in clustering comparison, which is based on counting word pairs
-on which the two clusterings agree or disagree (Rand, 1971; Hubert and
-Arabie, 1985). A pair of words learned by month \(t\) can fall under one
-of the four follwoing cases: 1) pairs that are placed in the same
-cluster under \(\mathcal{C}_t\) and in the same cluster under
-\(\mathcal{C}^*\) (True positives, noted as \(tp(\mathcal{C}_t)\)), 2)
-pairs placed in different clsuters under \(\mathcal{C}_t\) and in
-different clusters under \(\mathcal{C}^*\) (True negatives,
-\(tn(\mathcal{C}_t)\)), 3) pairs placed in the same cluster under
-\(\mathcal{C}_t\) and in different clusters under \(\mathcal{C}^*\)
-(False positive, \(fp(\mathcal{C}_t)\)), and 4) pairs placed in
-different clusters under \(\mathcal{C}_t\) and in the same cluster under
-\(\mathcal{C}^*\) (False negatives, \(fn(\mathcal{C}_t)\)).
+\subsection{Identifying abstract concepts in a
+network}\label{identifying-abstract-concepts-in-a-network}
 
-The clustering precison \(P(\mathcal{C}_t)\) and recall
-\(R(\mathcal{C}_t)\) are defiend as follows:
+We assume that abstract concepts correspond to clusters of highly
+interconnected nodes in the networks. We identified such clusters using
+WalkTrap \cite{pons2006}, an unsupervised community detection algorithm
+based on the fact that a random walker tends to be trapped in dense
+parts of a network. Figure \ref{fig:network} shows the outcome of
+cluster identification in the end-state network in English. The
+algorithm obtained four major clusters corresponding to the categories
+of clothes, food, animal and artifacts. We refer to this end-state
+clustering as \(\mathcal{C}^*\). To examine developmental change in the
+conceptual organization, we ran the cluster identification algorithm at
+each month of acquisition \(t\), and we compared the resulting
+clustering, noted \(\mathcal{C}_t\), to that of the end-state
+\(\mathcal{C}^*\). The method of this comparison is detailed below.
+
+\begin{CodeChunk}
+\captionsetup{width=0.8\textwidth}\begin{figure*}[h]
+
+{\centering \includegraphics{figs/results-1}
+
+}
+
+\caption[Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, averaged across languages and numbers of clusters]{Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, averaged across languages and numbers of clusters.
+Colors indicates real and hypothetical word sampling mechanisms.
+Errors bars represent 95\% confidence intervals.}\label{fig:results}
+\end{figure*}
+\end{CodeChunk}
+
+\subsection{Measuring conceptual
+development}\label{measuring-conceptual-development}
+
+We measure conceptual development by comparing \(\mathcal{C}_t\) to
+\(\mathcal{C}^*\) across time. We used a standard method in clustering
+comparison, which is based on word pairs on which the two clusterings
+agree or disagree \cite{rand1971,hubert1985}. We quantify clustering
+comparison using precision \(P(\mathcal{C}_t)\) and recall
+\(R(\mathcal{C}_t)\), defined as follows:
 
@@
 P(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fp(\mathcal{C}_t)|}
-\] \[
+\]
+
+\[
 R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
-\] Both Precison and Recall converge to 1 (perfect score) as
-\(\mathcal{C}_t\) becomes more and more similar to \(\mathcal{C}^*\). If
-precision starts low before converging to 1 (as opposed to being a
-constant at 1), this pattern would indicate that some pairs that should
-be differentiated are initially lumped together, suggesting a process of
-``differentiation'' over development. Similarly, if we observe an
-increase in Recall, this pattern would indicate that some pairs that
-should be associated are initially differentiate, suggesting a process
-of ``coelescence'' over development.
+\] Where \(tp(\mathcal{C}_t)\) are the true positives, defined as the
+word pairs that are placed in the same cluster under \(\mathcal{C}_t\)
+and in the same cluster under \(\mathcal{C}^*\). \(fp(\mathcal{C}_t)\)
+are the false positives defined as the pairs placed in the same cluster
+under \(\mathcal{C}_t\) and in different clusters under
+\(\mathcal{C}^*\). Finally, \(fn(\mathcal{C}_t)\) are the false
+positives defined as the pairs placed in different clusters under
+\(\mathcal{C}_t\) and in the same cluster under \(\mathcal{C}^*\).
 
-\subsection{Word ordering}\label{word-ordering}
+We made this comparison using different degrees of clustering
+granularity. More precisely, we fixed the same number of clusters for
+\emph{both} \(\mathcal{C}_t\) and \(\mathcal{C}^*\), and we varied this
+number from two to four clusters. We did not use the trivial case of one
+cluster, nor did we did use more than four clusters, since this number
+was optimal for the largest network (i.e., the end-state network) based
+on the modularity maximization criterion \cite{newman2006}.
 
-The question we are addressing is whether the order of acqusition of
-words affect the
+\subsection{Learning mechanisms}\label{learning-mechanisms}
+
+We examined how abstract concepts develop under an average word learning
+trajectory derived from real developmental data. To construct this
+trajectory, we used the normative age of acquisition, that is, the age
+at which a word is produced by at least 50\% of children in each
+language \cite{goodman2008}. We compared this development to the
+development induced by a simultaneous model and the development induced
+by a sequential model.
+
+The simultaneous model was instantiated as a uniform sampling across
+time from the end-state vocabulary. The sequential model had the
+additional constraint of sampling from one category at a time: the first
+word is selected randomly from one cluster, subsequent words are sampled
+from the same cluster. After all words from this cluster are used, a
+word from a different cluster is chosen, and the same process is
+repeated until all clusters are covered.
 
@@
 
-For real and random: results show that both precision and recall
-increase across development, suggesting that the conceptual organization
-undergoes both differentiation for some word pairs (example), and
-coelescecne for other pairs (examples).
+Figure \ref{fig:results} shows the scores obtained through comparing
+\(\mathcal{C}^*\) to \(\mathcal{C}_t\) at different points in time
+\(t\). For the real word learning trajectory, both precision and recall
+start relatively low, indicating that the induced conceptual
+organization is initially quite different from that of the end-state.
+Both measures converge towards 1 (i.e., perfect score) as
+\(\mathcal{C}_t\) becomes more and more similar to \(\mathcal{C}^*\).
 
-For within-cluster: precision is high, but recall is low: explain why
+The simultaneous model mimics closely the patterns of real conceptual
+development, explaining almost all the variance in mean precision
+(\(R^2 =\) 0.94) and recall (\(R^2 =\) 0.99). In contrast, the
+sequential model had generally a higher precision, i.e., it induced
+fewer false positive pairs. This result is due to the fact that we
+sampled instances from the same category. However, the same model had
+generally lower recall scores, i.e., it induced more false negative
+pairs. This second result was due to the fact that sampling from the
+same category leads to clusterings that are finer in their conceptual
+granularity than the end-state. As a consequence of this discrepancy
+with respect to real development, the sequential model explained less
+variance than the simultaneous model did in both its mean precision
+(\(R^2 =\) 0.44) and recall (\(R^2 =\) 0.96).
 
-How to explain this change?
+\section{Discussion}\label{discussion}
 
-\begin{quote}
-Assuming a random/real ranking of words: -Some words may be lamped
-together initially (even if we force a relatively high number of
-clusters) because of the smaller vocabulary size? Can we have an example
-of this? Are the other clsuters empty? -Some words may be differentiated
-initially because of the forcing? -Is there a roleof noise? maybe
-clustering is just more random for smaller size vocabulary?
-\end{quote}
+Can children learn abstract concepts based on word co-occurrence in the
+language they hear around them? Previous work has shown that
+child-directed speech contains information about several abstract
+concepts \cite{huebner2018}. Here we investigated when and how this
+information becomes available to children as their lexical network
+grows. We found that even with a small lexicon, several high-level
+concepts such as ``animal'', ``artifact'', ``food'' and ``clothes''
+emerge bottom-up as clusters of highly interconnected nodes in the
+network. Furthermore, compared with a model that posited sequential
+learning, we found that these categories tended to emerge in concert
+with one another.
 
-\begin{quote}
-Assuming a with-cluster ranking of words: -Some words may be lamped
-together initially (even if we force a relatively high number of
-clusters): this does not happen, at least while we are still working
-with the first cluster\ldots{}that's why precision is generally high
--Some words may be differentiated initially because they
-\end{quote}
+The development of the higher-level conceptual structure seems to be
+unaffected by the order with which words are acquired (as long as this
+order approximates a uniform sampling from the end-state lexicon),
+suggesting that the process of conceptual development can accommodate a
+wide range of word learning trajectories without a qualitative change in
+the higher-level organization. For example, whether acquisition starts
+first with the words ``cat'' and ``banana'' or with the words ``cow''
+and ``potato'' does not qualitatively affect the higher-level
+organization involving ``animal'' and ``food''. This property is
+important as it suggests, for instance, that development is resilient to
+variability in the children's linguistic input
+\cite{slobin2014,hart1995}.
 
-\subsection{Order of word learning}\label{order-of-word-learning}
+Developmental changes were captured by precision and recall. The
+increase in precision means that false positives decrease over time:
+some word pairs that are initially lumped together in a same category,
+are eventually differentiated. Similarly, the increase in recall means
+that false negatives decrease, that is, some word pairs that are
+initially distinct, become eventually subsumed by a same category. These
+patterns suggest a process of conceptual reorganization involving both
+``differentiation'' and ``coalescence'' as has been suggested in the
+developmental literature \cite{carey2009}.
 
-\section{Sudy of the conceptual
-development}\label{sudy-of-the-conceptual-development}
+That said, these developmental changes were not necessarily related to
+specific concepts (since the patterns were similar in the simultaneous
+model where we randomized the order of word learning). Instead, this
+finding suggests that differentiation and coalescence of word pairs in
+our data are related to the change in the vocabulary size across
+development: As more words are added to their lexical network, learners
+may approximate better the underlying conceptual organization of the
+mature lexicon and would make fewer categorization errors. Indeed,
+research in network science indicates that properties of a real network
+become more distorted as the size of a sampled sub-network decreases
+\cite{leskovec2006}.
 
-Models
+One limitation of this study is that we used the normative age of
+acquisition, computed using different children at different age groups.
+This choice was due to the cross-sectional nature of available CDI data.
+Though such a measure has been widely used to study important aspects of
+the early lexical networks \cite{hills2009,stella2017,storkel2009}, it
+only applies at the population level. In our case, though we found that
+concepts develop simultaneously, individual children may display, at
+least locally, a sequential-like behavior. For example, prior knowledge
+about dinosaurs may enable the learning of new dinosaur-related words
+more easily \cite{chi1983}.
 
-\section{Important citation stuff!
-READ!}\label{important-citation-stuff-read}
+In sum, this work provided a quantitative account of how abstract
+concepts can emerge from the interaction of the children's emerging
+vocabulary and the properties of their linguistic input. One important
+direction for future work is to investigate the extent to which the
+correlational findings obtained in this study (e.g., the identity of
+categories formed across development or the fact that categorization
+errors decrease with the size of the lexicon) can be corroborated by
+controlled behavioral experiments.
 
-\subsection{Why we can't have nice
-things}\label{why-we-cant-have-nice-things}
+\vspace{1em}
 
-So because the ACL committee wants their \texttt{.tex} files all nice
-and consistent, the old version of this package isn't good for what they
-want. The Markdown-to-Latex conversion would automatically add in the
-references and citations, but would literally hardcode them into the
-\texttt{.tex} file. We can't have that, now can we? The only ways you
-were allowed to cite in your \texttt{.tex} file was with
-\texttt{\textbackslash{}cite\{Gusfield97\}},
-\texttt{\textbackslash{}shortcite\{Gusfield97\}}, or
-\texttt{\textbackslash{}newcite\{Gusfield97\}}, which corresponded to
-``(Gusfield, 1997)'', ``(1997)'', or ``Gusfield (1997)'', respectively.
-
-This means you couldn't do anything like ``(e.g., Gusfield, 2017)'', and
-their \texttt{.bst} file was incompatible with \texttt{natbib}.
-Obviously. However, I have come to the rescue. In the
-\texttt{eacl2017.sty} file in this package, I have added my own bit of
-magic: the \texttt{\textbackslash{}barecite\{\}} command, which
-corresponds to ``Burchill, 2017''. Notice this version doesn't have
-parentheses, so you can get stuff like ``(e.g., Burchill, 2017)'' with
-\texttt{(e.g.,\ \textbackslash{}barecite\{Gusfield97\})}. Just be
-careful about making sure you don't forget parentheses. Also not that
-when you submit the \texttt{.zip} folder, you should make sure to
-include the edited \texttt{eacl2017.sty} file.
-
-\subsection{Examples}\label{examples}
-
-\begin{itemize}
-\tightlist
-\item
-  \texttt{\textbackslash{}cite\{Gusfield97\}} becomes \cite{Gusfield97}
-\item
-  \texttt{\textbackslash{}shortcite\{Gusfield97\}} becomes
-  \shortcite{Gusfield97}
-\item
-  \texttt{\textbackslash{}newcite\{Gusfield97\}} becomes
-  \newcite{Gusfield97}
-\item
-  \texttt{\textbackslash{}barecite\{Gusfield97\}} becomes
-  \barecite{Gusfield97}
-\item
-  \texttt{\textbackslash{}cite\{Gusfield97,Aho72\}} becomes
-  \cite{Gusfield97,Aho72}
-\item
-  \texttt{\textbackslash{}barecite\{Gusfield97,Aho72\}} becomes
-  \barecite{Gusfield97,Aho72}
-\end{itemize}
-
-\textbf{Wait, \emph{are those citations appearing as question marks?}
-Don't worry, read on!}
-
-\subsection{The two-step process of knitting this
-file}\label{the-two-step-process-of-knitting-this-file}
-
-Because the ACL's you-need-to-use-our-citing-function formatting doesn't
-work well with R Markdown--which really likes to compile its own
-citations--knitting this is now a two-step process. After you get it how
-you want it in RMarkdown, knit as usual. You'll see that all citations
-are question marks, and that the bibliography is missing. This is
-natural, don't panic.
-
-For the current purposes, let's assume this file we're in right now is
-called \texttt{acl\_draft.Rmd}. Navigate into the directory containing
-\texttt{acl\_draft.Rmd} via a terminal. Then run the following command
-(swapping out your actual file name for ``acl\_draft'')
-
-\texttt{pdflatex\ acl\_draft.tex;\ pdflatex\ acl\_draft.tex;\ bibtex\ acl\_draft.aux;\ pdflatex\ acl\_draft.tex;\ pdflatex\ acl\_draft.tex}
-
-Now, check the \texttt{.pdf} file. If all went well, it should now have
-all the citations in it as well as the reference section. Good luck!
-
-\section{General Formatting
-Instructions}\label{general-formatting-instructions}
-
-All the default content below is lifted directly from Kyle MacDonald's
-Cogsci 2016 project (\url{https://github.com/kemacdonald/cogsci2016}),
-which this entire package is based on. I haven't changed it, so it's up
-to you to ignore as you please.
-
-For general information about authoring in markdown, see
-**\url{http://rmarkdown.rstudio.com/authoring_basics.html.**}
-
-For standard spoken papers and standard posters, the entire contribution
-(including figures, references, everything) can be no longer than six
-pages. For abstract posters, the entire contribution can be no longer
-than one page. For symposia, the entire contribution can be no longer
-than two pages.
-
-The text of the paper should be formatted in two columns with an overall
-width of 7 inches (17.8 cm) and length of 9.25 inches (23.5 cm), with
-0.25 inches between the columns. Leave two line spaces between the last
-author listed and the text of the paper. The left margin should be 0.75
-inches and the top margin should be 1 inch.
-\textbf{The right and bottom margins will depend on whether you use
-U.S. letter or A4 paper, so you must be sure to measure the width of
-the printed text.} Use 10 point Times Roman with 12 point vertical
-spacing, unless otherwise specified.
-
-The title should be in 14 point, bold, and centered. The title should be
-formatted with initial caps (the first letter of content words
-capitalized and the rest lower case). Each author's name should appear
-on a separate line, 11 point bold, and centered, with the author's email
-address in parentheses. Under each author's name list the author's
-affiliation and postal address in ordinary 10 point type.
-
-Indent the first line of each paragraph by 1/8\textasciitilde{}inch
-(except for the first paragraph of a new section). Do not add extra
-vertical space between paragraphs.
-
-\section{First-Level Headings}\label{first-level-headings}
-
-First level headings should be in 12 point , initial caps, bold and
-centered. Leave one line space above the heading and
-1/4\textasciitilde{}line space below the heading.
-
-\subsection{Second-Level Headings}\label{second-level-headings}
-
-Second level headings should be 11 point , initial caps, bold, and flush
-left. Leave one line space above the heading and 1/4\textasciitilde{}
-line space below the heading.
-
-\subsubsection{Third-Level Headings}\label{third-level-headings}
-
-Third-level headings should be 10 point , initial caps, bold, and flush
-left. Leave one line space above the heading, but no space after the
-heading.
-
-\section{Formalities, Footnotes, and
-Floats}\label{formalities-footnotes-and-floats}
-
-\subsection{Footnotes}\label{footnotes}
-
-Indicate footnotes with a number\footnote{Sample of the first
-footnote.} in the text. Place the footnotes in 9 point type at the
-bottom of the page on which they appear. Precede the footnote with a
-horizontal rule.\footnote{Sample of the second footnote.}
-
-\subsection{Figures}\label{figures}
-
-All artwork must be very dark for purposes of reproduction and should
-not be hand drawn. Number figures sequentially, placing the figure
-number and caption, in 10 point, after the figure with one line space
-above the caption and one line space below it. If necessary, leave extra
-white space at the bottom of the page to avoid splitting the figure and
-figure caption. You may float figures to the top or bottom of a column,
-or set wide figures across both columns.
-
-\subsection{Two-column images}\label{two-column-images}
-
-You can read local images using png package for example and plot it like
-a regular plot using grid.raster from the grid package. With this method
-you have full control of the size of your image. \textbf{Note: Image
-must be in .png file format for the readPNG function to work.}
-
-You might want to display a wide figure across both columns. To do this,
-you can change the \texttt{fig.env} chunk option to \texttt{figure*}. To
-align the image in the center of the page, set \texttt{fig.align} option
-to \texttt{center}.
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/2-col-image-1}
-
-}
-
-\caption[This image spans both columns]{This image spans both columns.}\label{fig:2-col-image}
-\end{figure*}
-\end{CodeChunk}
-
-\subsection{One-column images}\label{one-column-images}
-
-Single column is the default option, but if you want set it explicitly,
-set \texttt{fig.env} to \texttt{figure}.
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/image-1}
-
-}
-
-\caption[One column image]{One column image.}\label{fig:image}
-\end{figure}
-\end{CodeChunk}
-
-\subsection{R Plots}\label{r-plots}
-
-You can use R chunks directly to plot graphs. And you can use latex
-floats in the fig.pos chunk option to have more control over the
-location of your plot on the page. For more information on latex
-placement specifiers see
-**\url{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions**}
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/plot-1}
-
-}
-
-\caption[R plot]{R plot}\label{fig:plot}
-\end{figure}
-\end{CodeChunk}
-
-\subsection{Tables}\label{tables}
-
-Number tables consecutively; place the table number and title (in 10
-point) above the table with one line space above the caption and one
-line space below it, as in Table 1. You may float tables to the top or
-bottom of a column, set wide tables across both columns.
-
-You can use the xtable function in the xtable package.
-
-\begin{table}[H]
-\centering
-\begin{tabular}{rrrrr}
-  \hline
- & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
-  \hline
-(Intercept) & 0.07 & 0.09 & 0.7 & 0.49 \\ 
-  x & 1.92 & 0.09 & 20.4 & 0.00 \\ 
-   \hline
-\end{tabular}
-\caption{This table prints across one column.} 
-\end{table}
-
-\section{Acknowledgements}\label{acknowledgements}
-
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
+\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}}
+\vspace{1em}
 

### 2019-04-04 CMCL/ms.Rmd
final

@@
 ---
-title: "The development of abstract concepts in children's early lexical networks"
+title: "The Development of Abstract Concepts in Children's Early Lexical Networks"
 
 author-information: > 
-    \author{{\large \bf Author 1} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University
-    \And {\large \bf Author 2} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University}
+    \author{{\large \bf Abdellah Fourtassi *} 
+    \qquad {\large \bf Isaac L. Scheinfeld *}
+    \qquad {\large \bf Michael C. Frank} \\ \texttt{\{afourtas, ischeinfeld, mcfrank\}@stanford.edu} \\ Department of Psychology \\ Stanford University}
 
@@
 
-final_submission: no
+final_submission: yes
 # If yes, uncomment line below and add your own ID
@@
 -->
-We study development in light of two hypothetical models.
-On the first, called the simultaneous model, learning starts by exploring all parts of the conceptual space; categories are refined simultaneously over development.
-On the second, called the sequential model, learning starts by exploring a small region of the conceptual space (e.g., the category "animals") and only after the refinement of this category, does the learner move to another.
+We study the real conceptual development (i.e.
+as induced by the real trajectory of word learning) in comparison to two hypothetical developmental scenarios induced by two divergent proposals about the trajectory of word learning.
+On the first proposal, past lexical knowledge facilitates the future learning of related words, e.g., the word "cat" is more likely to be followed by another animal name than it is to be followed by a food name \cite{steyvers2005,borovsky2016}.
+On the second proposal, past lexical knowledge does not influence future learning, e.g., learning the word "cat" does not necessarily increase the odds that the next word will be another animal name  \cite{hills2009,sizemore2018}.
 
@@
 
-## Constructing lexical networks
+## Constructing Lexical Networks
 
@@
 
-## Identifying abstract concepts in a network
+## Identifying Abstract Concepts in a Network
 
@@
 
-## Measuring conceptual development
+## Measuring Conceptual Development
 
@@
 $fp(\mathcal{C}_t)$ are the false positives defined as the pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
-Finally, $fn(\mathcal{C}_t)$ are the false positives defined as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
+Finally, $fn(\mathcal{C}_t)$ are the false negatives defined as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
 
@@
 More precisely, we fixed the same number of clusters for *both* $\mathcal{C}_t$ and $\mathcal{C}^*$, and we varied this number from two to four clusters.
-We did not use the trivial case of one cluster, nor did we did use more than four clusters, since this number was optimal for the largest network (i.e., the end-state network) based on the modularity maximization criterion \cite{newman2006}.
+We did not use the trivial case of one cluster, nor did we use more than four clusters, since this number was optimal for the largest network (i.e., the end-state network) based on the modularity maximization criterion \cite{newman2006}.
 
-## Learning mechanisms
+## Learning Mechanisms
 
@@
 To construct this trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}.
-We compared this development to the development induced by a simultaneous model and the development induced by a sequential model.
+As mentioned above, we compared this development to the development induced by a first hypothetical trajectory where known words influence future word learning and a second hypothetical trajectory where learning proceeds regardless of what words are already known.
 
-The simultaneous model was instantiated as a uniform sampling across time from the end-state vocabulary.
-The sequential model had the additional constraint of sampling from one category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster.
+We instantiated the first trajectory through sampling from one conceptual category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster.
 After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.
+We call this sampling procedure the *sequential model*.
+We instantiated the second trajectory through a uniform sampling across time from the end-state vocabulary.
+We call this sampling procedure the *simultaneous model*.
 
@@
 
-\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}} \vspace{1em}
+\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code are available at https://github.com/afourtassi/conceptNet}} \vspace{1em}

### 2019-04-04 CMCL/ms.tex
final

@@
 
+\eaclfinalcopy
+\def\eaclpaperid{}
 % If you have:
@@
 
-\title{The development of abstract concepts in children's early lexical
-networks}
+\title{The Development of Abstract Concepts in Children's Early Lexical
+Networks}
 
-\author{{\large \bf Author 1} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University \And {\large \bf Author 2} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University}
+\author{{\large \bf Abdellah Fourtassi *}  \qquad {\large \bf Isaac L.
+Scheinfeld *} \qquad {\large \bf Michael C.
+Frank} \\ \texttt{\{afourtas, ischeinfeld, mcfrank\}@stanford.edu} \\ Department of Psychology \\ Stanford University}
 
@@
 
-We study development in light of two hypothetical models. On the first,
-called the simultaneous model, learning starts by exploring all parts of
-the conceptual space; categories are refined simultaneously over
-development. On the second, called the sequential model, learning starts
-by exploring a small region of the conceptual space (e.g., the category
-``animals'') and only after the refinement of this category, does the
-learner move to another.
+We study the real conceptual development (i.e.~as induced by the real
+trajectory of word learning) in comparison to two hypothetical
+developmental scenarios induced by two divergent proposals about the
+trajectory of word learning. On the first proposal, past lexical
+knowledge facilitates the future learning of related words, e.g., the
+word ``cat'' is more likely to be followed by another animal name than
+it is to be followed by a food name \cite{steyvers2005,borovsky2016}. On
+the second proposal, past lexical knowledge does not influence future
+learning, e.g., learning the word ``cat'' does not necessarily increase
+the odds that the next word will be another animal name
+\cite{hills2009,sizemore2018}.
 
@@
 
-\subsection{Constructing lexical
-networks}\label{constructing-lexical-networks}
+\subsection{Constructing Lexical
+Networks}\label{constructing-lexical-networks}
 
@@
 
-\subsection{Identifying abstract concepts in a
-network}\label{identifying-abstract-concepts-in-a-network}
+\subsection{Identifying Abstract Concepts in a
+Network}\label{identifying-abstract-concepts-in-a-network}
 
@@
 
-\subsection{Measuring conceptual
-development}\label{measuring-conceptual-development}
+\subsection{Measuring Conceptual
+Development}\label{measuring-conceptual-development}
 
@@
 \(\mathcal{C}^*\). Finally, \(fn(\mathcal{C}_t)\) are the false
-positives defined as the pairs placed in different clusters under
+negatives defined as the pairs placed in different clusters under
 \(\mathcal{C}_t\) and in the same cluster under \(\mathcal{C}^*\).
@@
 number from two to four clusters. We did not use the trivial case of one
-cluster, nor did we did use more than four clusters, since this number
-was optimal for the largest network (i.e., the end-state network) based
-on the modularity maximization criterion \cite{newman2006}.
+cluster, nor did we use more than four clusters, since this number was
+optimal for the largest network (i.e., the end-state network) based on
+the modularity maximization criterion \cite{newman2006}.
 
-\subsection{Learning mechanisms}\label{learning-mechanisms}
+\subsection{Learning Mechanisms}\label{learning-mechanisms}
 
@@
 at which a word is produced by at least 50\% of children in each
-language \cite{goodman2008}. We compared this development to the
-development induced by a simultaneous model and the development induced
-by a sequential model.
+language \cite{goodman2008}. As mentioned above, we compared this
+development to the development induced by a first hypothetical
+trajectory where known words influence future word learning and a second
+hypothetical trajectory where learning proceeds regardless of what words
+are already known.
 
-The simultaneous model was instantiated as a uniform sampling across
-time from the end-state vocabulary. The sequential model had the
-additional constraint of sampling from one category at a time: the first
-word is selected randomly from one cluster, subsequent words are sampled
-from the same cluster. After all words from this cluster are used, a
-word from a different cluster is chosen, and the same process is
-repeated until all clusters are covered.
+We instantiated the first trajectory through sampling from one
+conceptual category at a time: the first word is selected randomly from
+one cluster, subsequent words are sampled from the same cluster. After
+all words from this cluster are used, a word from a different cluster is
+chosen, and the same process is repeated until all clusters are covered.
+We call this sampling procedure the \emph{sequential model}. We
+instantiated the second trajectory through a uniform sampling across
+time from the end-state vocabulary. We call this sampling procedure the
+\emph{simultaneous model}.
 
@@
 
-\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}}
+\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code are available at https://github.com/afourtassi/conceptNet}}
 \vspace{1em}

### 2019-07-16 CMCL/ms.Rmd

@@
 We study the real conceptual development (i.e.
-as induced by the real trajectory of word learning) in comparison to two hypothetical developmental scenarios induced by two divergent proposals about the trajectory of word learning.
-On the first proposal, past lexical knowledge facilitates the future learning of related words, e.g., the word "cat" is more likely to be followed by another animal name than it is to be followed by a food name \cite{steyvers2005,borovsky2016}.
-On the second proposal, past lexical knowledge does not influence future learning, e.g., learning the word "cat" does not necessarily increase the odds that the next word will be another animal name  \cite{hills2009,sizemore2018}.
+as induced by the real trajectory of word learning) in comparison to two hypothetical developmental scenarios induced by two possible mechanisms of word learning.
+On the first mechanism, past lexical knowledge facilitates the future learning of related words, e.g., the word "cat" is more likely to be followed by another animal name than it is to be followed by a food name \cite{steyvers2005,borovsky2016}.
+On the second mechanism, past lexical knowledge does not influence future learning, e.g., learning the word "cat" does not necessarily increase the odds that the next word will be another animal name  \cite{hills2009,sizemore2018}.
 
@@
 We operationalized abstract concepts as the highly interconnected regions of the network.
-Second, we explore how the pattern of children's word learning influences higher-level conceptual development, and whether this development corresponds to a simultaneous or a sequential conceptual growth.
+Second, we explore how the pattern of children's word learning influences higher-level conceptual development, and whether this development corresponds to simultaneous or sequential conceptual growth.
 
@@
 
-The networks' nodes were nouns from Wordbank \cite{frank2017}, an open repository aggregating cross-linguistic developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version \cite{fenson94}.
-Pairs of nouns were linked by weighted edges representing their semantic similarity derived based on co-occurrence in the corpus of child-directed speech CHILDES \cite{macwhinney2014}, using Word2Vec algorithm \cite{mikolov2013}.
+The networks' nodes were nouns from Wordbank \cite{frank2017}, an open repository aggregating cross-linguistic developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), Toddler version \cite{fenson94}.
+Pairs of nouns were linked by weighted edges representing their semantic similarity derived based on co-occurrence in the corpus of child-directed speech CHILDES \cite{macwhinney2014}, using the Word2Vec algorithm \cite{mikolov2013}.
 
@@
 We used a subset of CDI nouns for which cross-linguistic translations are present, allowing us to explore cross-linguistic variability.
-We used data from the ten following languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish.
-The size of this subset varied from `r max_n` in Russian (representing `r max_per`% of total nouns in this language) to `r min_n` in Turkish (representing `r min_per`% of total nouns).
+We used data from the following ten languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish.
+The size of this subset varied from `r max_n` in Russian (representing `r max_per`% of total nouns present in the CDI data of this language) to `r min_n` in Turkish (representing `r min_per`% of total nouns).
 Second, in order to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.
@@
 Where $tp(\mathcal{C}_t)$ are the true positives, defined as the word pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
-$fp(\mathcal{C}_t)$ are the false positives defined as the pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
-Finally, $fn(\mathcal{C}_t)$ are the false negatives defined as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
+$fp(\mathcal{C}_t)$ are the false positives,
+defined as the pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
+Finally, $fn(\mathcal{C}_t)$ are the false negatives, defined as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
 

### 2019-07-16 CMCL/ms.tex

@@
 trajectory of word learning) in comparison to two hypothetical
-developmental scenarios induced by two divergent proposals about the
-trajectory of word learning. On the first proposal, past lexical
-knowledge facilitates the future learning of related words, e.g., the
-word ``cat'' is more likely to be followed by another animal name than
-it is to be followed by a food name \cite{steyvers2005,borovsky2016}. On
-the second proposal, past lexical knowledge does not influence future
-learning, e.g., learning the word ``cat'' does not necessarily increase
-the odds that the next word will be another animal name
-\cite{hills2009,sizemore2018}.
+developmental scenarios induced by two possible mechanisms of word
+learning. On the first mechanism, past lexical knowledge facilitates the
+future learning of related words, e.g., the word ``cat'' is more likely
+to be followed by another animal name than it is to be followed by a
+food name \cite{steyvers2005,borovsky2016}. On the second mechanism,
+past lexical knowledge does not influence future learning, e.g.,
+learning the word ``cat'' does not necessarily increase the odds that
+the next word will be another animal name \cite{hills2009,sizemore2018}.
 
@@
 pattern of children's word learning influences higher-level conceptual
-development, and whether this development corresponds to a simultaneous
-or a sequential conceptual growth.
+development, and whether this development corresponds to simultaneous or
+sequential conceptual growth.
 
@@
 repository aggregating cross-linguistic developmental data of the
-MacArthur-Bates Communicative Development Inventory (CDI), a parent
-report vocabulary checklist, Toddler version \cite{fenson94}. Pairs of
-nouns were linked by weighted edges representing their semantic
-similarity derived based on co-occurrence in the corpus of
-child-directed speech CHILDES \cite{macwhinney2014}, using Word2Vec
-algorithm \cite{mikolov2013}.
+MacArthur-Bates Communicative Development Inventory (CDI), Toddler
+version \cite{fenson94}. Pairs of nouns were linked by weighted edges
+representing their semantic similarity derived based on co-occurrence in
+the corpus of child-directed speech CHILDES \cite{macwhinney2014}, using
+the Word2Vec algorithm \cite{mikolov2013}.
 
@@
 cross-linguistic translations are present, allowing us to explore
-cross-linguistic variability. We used data from the ten following
+cross-linguistic variability. We used data from the following ten
 languages: Croatian, Danish, English, French, Italian, Norwegian,
 Russian, Spanish, Swedish, and Turkish. The size of this subset varied
-from 314 in Russian (representing 100\% of total nouns in this language)
-to 176 in Turkish (representing 59.26\% of total nouns). Second, in
-order to study development towards the end-state, we constructed a
-different network at each month, based on the nouns that have been
-learned by that month.
+from 314 in Russian (representing 100\% of total nouns present in the
+CDI data of this language) to 176 in Turkish (representing 59.26\% of
+total nouns). Second, in order to study development towards the
+end-state, we constructed a different network at each month, based on
+the nouns that have been learned by that month.
 
@@
 and in the same cluster under \(\mathcal{C}^*\). \(fp(\mathcal{C}_t)\)
-are the false positives defined as the pairs placed in the same cluster
+are the false positives, defined as the pairs placed in the same cluster
 under \(\mathcal{C}_t\) and in different clusters under
 \(\mathcal{C}^*\). Finally, \(fn(\mathcal{C}_t)\) are the false
-negatives defined as the pairs placed in different clusters under
+negatives, defined as the pairs placed in different clusters under
 \(\mathcal{C}_t\) and in the same cluster under \(\mathcal{C}^*\).
